### 2018-05-10 cover-letter/cover-letter.tex
adds cover letter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
% It was modified by Katy Huff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\usepackage[left=1.25in,right=1.25in,top=1in,bottom=1in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\usepackage{eso-pic,graphicx}

%--------------------------------------------------------------------------------------
%--------INPUT DATA
%--------------------------------------------------------------------------------------
\usepackage{xspace}
\newcommand{\StudentFirstName}{Andrei\xspace}
\newcommand{\StudentLastName}{Rykhlevskii\xspace}
\newcommand{\RecipientName}{Profs. Ghiaasiaan, Pazsit, and Pozzi\xspace}
\newcommand{\RecipientAddress}{Executive Editors\\Annals of Nuclear Energy}
%\newcommand{\<++>}{<++>\xspace}

\begin{document}
\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

%----------------------------------------------------------------------------------------
%    ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{\RecipientName\\
        \RecipientAddress\xspace}

%-------------------------------------------------------------------------------
%    YOUR NAME & ADDRESS SECTION
%-------------------------------------------------------------------------------
\address{Kathryn D. Huff\\
kdhuff@illinois.edu\\
118 Talbot Laboratory\\
104 Wright Street\\
MC-234\\
Urbana, IL 61801}

%-------------------------------------------------------------------------------
%    LETTER CONTENT SECTION
%-------------------------------------------------------------------------------

\opening{To \RecipientName,}

Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor'' which Mr. 
Andrei Rykhlevskii and I are submitting for exclusive consideration of 
publication as a research article in Annals of Nuclear Energy.

This manuscript describes and demonstrates a computational modeling capability
for Molten Salt Reactor (MSR) online reprocessing analysis.  A Python package,
SaltProc, has been developed to simulate MSR online reprocessing by modeling
the changing isotopic composition of an irradiated fuel salt. The simulation
workflow additionally leverages the SERPENT 2 Monte Carlo software for neutron
transport and depletion calculations. An introduction to SaltProc capabilities
is followed by demonstration in the context of online reprocessing in the
Molten Salt Breeder Reactor (MSBR).

Thank you for your consideration of our work.  I expect it will be of interest
to a broad readership concerned with multi-physics simulation of next generation
reactors.  Please address all correspondence concerning this manuscript to me at the University of Illinois.

\closing{Sincere regards,
\includegraphics[height=2cm]{signature}\\
        \fromsig{Kathryn Huff\\
Assistant Professor\\
Nuclear, Plasma, \& Radiological Eng.\\
U. Illinois at Urbana-Champaign}
}

%-------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2018-05-10 abstract.tex
adds highlights and graphical abstract

\begin{abstract}
        % motivation
        % problem statement
        % approach
        % results
        % conclusions
\end{abstract}

### 2018-05-10 acks.tex
adds highlights and graphical abstract

\section{Acknowledgments}

This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 and 
ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the 
University of Illinois at Urbana-Champaign and its National Center for 
Supercomputing Applications

The authors would like to thank  members of Advanced Reactors and Fuel Cycles
research group (ARFC) at the University of Illinois - Urbana Champaign who 
provided valuable code reviews and proofreading.

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Mr. Rykhlevskii is supported by the 
Department of Nuclear, Plasma, and Radiological Engineering.

Kathryn D. Huff directed and 
supervised the work, conceived and designed the simulations, wrote the paper, 
contributed to the software product, and reviewed drafts of the paper.  Prof. 
Huff is supported by the Nuclear Regulatory Commission Faculty Development 
Program, the National Center for Supercomputing Applications, the NNSA Office 
of Defense Nuclear Nonproliferation R\&D through the Consortium for Verfication 
Technologies and the Consortium for Nonproliferation Enabling Capabilities, and 
the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and 
Technology.

### 2018-05-10 acros.tex
adds highlights and graphical abstract

%\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
\newacronym{ADS}{ADS}{Accelerator-Driven Systems}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{ANS}{ANS}{American Nuclear Society}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ASTRID}{ASTRID}{Advanced Sodium Technological Reactor for Industrial Demonstration}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{BWR}{BWR}{Boiling Water Reactor}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDF}{EDF}{Électricité de France}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EPR}{EPR}{European Pressurized Reactor}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{EU}{EU}{European Union}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{FP}{FP}{Fission Products}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
\newacronym{IRP}{IRP}{Integrated Research Project}
\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
\newacronym{ISRG}{ISRG}{Independent Student Research Group}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOX}{MOX}{Mixed Oxide Fuel}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{MWe}{MWe}{Mega Watt electric}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWF}{NWF}{Nuclear Waste Fund}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PHWR}{Pressurized Heavy Water Reactor}{Pressurized Heavy Water Reactor}
\newacronym{PRIS}{PRIS}{Power Reactor Information System}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PWR}{PWR}{Pressurized Water Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UNF}{UNF}{Used Nuclear Fuel}
\newacronym{UOX}{UOX}{Uranium Oxide Fuel}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}

### 2018-05-10 conclusion.tex
adds highlights and graphical abstract

\section{Conclusion}

% The main conclusions of the study may be presented in a short Conclusions
% section, which may stand alone or form a subsection of a Discussion or Results
% and Discussion section.

\FloatBarrier

### 2018-05-10 discussion.tex
adds highlights and graphical abstract

\section{Discussion}
% This should explore the significance of the results of the work, not repeat
% them. A combined Results and Discussion section is often appropriate. Avoid
% extensive citations and discussion of published literature.

### 2018-05-10 graph-abs/graph-abs.tex
adds highlights and graphical abstract

\documentclass[review]{elsarticle}

\usepackage{lineno}
\usepackage{xspace}
\modulolinenumbers[5]

\journal{Annals of Nuclear Energy}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%%%% packages and definitions (optional)
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{hhline}
\usepackage{amsmath}

%\usepackage[demo]{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{x}{>{\hsize=.25\hsize}X}

\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\graphicspath{ {images/} }

% tikz %
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

% hyperref %
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{frontmatter}
\title{Graphical Abstract\\
Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\date{}                     %% if you don't need date to appear

\end{frontmatter}

\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{./highlight.png}
    \end{center}
    \caption{A very fancy image important to the paper.}
    \label{fig:graph-abs}
\end{figure}

\end{document}

### 2018-05-10 highlights/highlights.tex
adds highlights and graphical abstract

--- 2018-05-10 graph-abs/graph-abs.tex
@@
 
-\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
-\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
-\graphicspath{ {images/} }
+\graphicspath{ {figures/} }
 
@@
 \begin{frontmatter}
-\title{Graphical Abstract\\
-Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
-\date{}                     %% if you don't need date to appear
-
+\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
 \end{frontmatter}
-
-\begin{figure}[htbp!]
-    \begin{center}
-        \includegraphics[width=\textwidth]{./highlight.png}
-    \end{center}
-    \caption{A very fancy image important to the paper.}
-    \label{fig:graph-abs}
-\end{figure}
-
+\section*{Highlights}
+\begin{itemize}
+       \item Highlight 1
+       \item Highlight 2
+       \item Highlight 3
+\end{itemize}
 \end{document}

### 2018-05-10 introduction.tex
adds highlights and graphical abstract

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.

### 2018-05-10 methods.tex
adds highlights and graphical abstract

\section{Methods}

% Material and methods

% Provide sufficient details to allow the work to be reproduced by an
% independent researcher. Methods that are already published should be
% summarized, and indicated by a reference. If quoting directly from a previously
% published method, use quotation marks and also cite the source. Any
% modifications to existing methods should also be described.

% Theory/calculation 
% A Theory section should extend, not repeat, the background to the article
% already dealt with in the Introduction and lay the foundation for further work.
% In contrast, a Calculation section represents a practical development from a
% theoretical basis.

### 2018-05-10 results.tex
adds highlights and graphical abstract

\section{Results}

% Results should be clear and concise.

### 2018-05-18 conclusion.tex
Paper outline finished

@@
 
-% The main conclusions of the study may be presented in a short Conclusions
-% section, which may stand alone or form a subsection of a Discussion or Results
-% and Discussion section.
+Condensed copy-paste of the thesis conclusion.
+\begin{itemize}
+    \item Full-core model which is better the most exists. Importance of full-core approach for multi-region designs.
+    \item K-eff dynamics and explanation of this dynamics.
+    \item Spectral shift explanation.
+    \item Why spectral shift causes safety parameters worsening and power profile changes.
+    \item $^{232}$Th rate is in a good agreement with references.
+\end{itemize}
 

### 2018-05-18 introduction.tex
Paper outline finished

@@
 % a detailed literature survey or a summary of the results.
+\begin{itemize}
+	\item Background and motivation from the thesis. 
+	\item Brief \gls{MSR} overview and 1 paragraph history. 
+	\item \gls{MSBR} advantages. Objectives from the thesis. 
+	\item Changed simulation time 40 years (or more). 
+	\item Figure 2.3: Isotopic build-up in $^{232}$Th and $^{238}$U breeding systems. 
+	\item Literature review from Section 2.3 without multiphysics + existing full-core simulations (Park et al., Skirpan et al.)
+\end{itemize}

### 2018-05-18 results.tex
Paper outline finished

@@
 
-% Results should be clear and concise.
+\begin{itemize}
+  \item K-eff over 40 years of simulation with $<$15pcm uncertainty.
+  \item Dynamics isotope composition from initial to equilibrium composition.
+  \item Dynamics of fissile vs non-fissile isotopes over 40 years.
+  \item Neutron spectrum for both states and separately for Zone I and Zone II (probably, even Zone II-A and II-B).
+  \item Power distribution plot (without breeding, too much pics).
+  \item Control rod worth \& Six factor analysis \& temperature coefficients.
+  \item $^{232}$Th refill rate.
+  \item Bried discussion (2-3 paragraph).
+\end{itemize}

### 2018-06-30 introduction.tex
Introduction finished. Table capture should be fixed

--- 2018-05-10 introduction.tex
@@
 % a detailed literature survey or a summary of the results.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
+More recently, \gls{MSR} was included in the six advanced reactor concepts that have been chosen by the Generation IV International Forum (GIF) for further research and development.
+\glspl{MSR} offer significant improvements ``in the four broad areas of sustainability, economics, safety and reliability, and proliferation resistance and physical protection" \cite{doe_technology_2002}.
+To achieve the goals formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and improve inherent safety by using liquid coolant which is also a fuel.
+
+ In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e.
+UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
+These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
+The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium.
+With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{$^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
+Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}.
+The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle.
+Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.
+
+Modeling liquid-fueled systems with existing neutron transport and depletion tools is challenging because most of these tools are designed for the solid-fueled reactors simulation.
+The fuel material flows and potential online separations or feeds of specific elements or nuclides are the main challenges
+of liquid-fueled systems.
+Furthermore, no established tool for liquid-fueled \gls{MSR} neutronics and fuel cycle evaluation exist, though internally developed tools from universities and research institutions can approximate online refueling \cite{serp_molten_2014}.
+The foundation for these tools was based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.
+More recent research efforts in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis and couple external tools to neutron transport and depletion codes take into account continuous feeds and removals in \glspl{MSR}.
+Four of these efforts are listed in table~\ref{tab:fs_codes}.
+
+\begin{table}[ht!]
+\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
+\begin{tabularx}{\textwidth}{ x | s | s | m | x } 
+\# & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
+\hline
+1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM \cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
+\hline
+2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
+\hline
+3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
+\hline
+4 & SERPENT 2 \cite{leppanen_serpent_2015}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
+\hline
+5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
+\hline
+6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
+\hline
+7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton \cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
+\hline
+8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
+\hline
+9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\
+\end{tabularx}
+  \label{tab:fs_codes}
+\end{table}
+\FloatBarrier
+
+Most of these methods are also applicable to thermal spectrum \glspl{MSR}. Additional tools developed specifically for thermal \gls{MSR} applications are also listed in table~\ref{tab:fs_codes}.
+
+Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 5, 6, 8, 9) use a set of all nuclides in depletion calculations.
+
+Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch).
+To account for batch discharge, a depletion tool must remove some or all material at specified intervals.
+This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
+Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations.
+In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation.
+Methods (1, 4, 8) model true continuous feeds and removals, while other methods employ a batch-wise approach.
+\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing.
+This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
+
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this thesis are described in (6, 7, 8, 9).
+Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
+
+Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: one for salt channels, one for two salt plena above and below the core and the last cell for the annulus, consequently, two-region reactor core was approximated by one region with averaged fuel/moderator ratio \cite{nuttin_potential_2005}.
+A similar approach was used by Powers \emph{et al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and clearly misrepresent the two-region breeder reactor concept.
+The unit-cell or one-region models may produce reliable results for homogeneous reactor cores (i.e.
+\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e.
+\gls{MSRE}).
+A two-region \gls{MSBR} must be simulated using a whole-core model to represent different neutron transport in the inner and outer regions of the core, because most fissions happens in the inner region while breeding occurs in the outer zone.
+
+Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and employed it to study the material isotopic evolution of the \gls{MSFR}.
+The developed extension directly takes into account the effects of online fuel reprocessing on depletion calculations and features a reactivity control algorithm.
+The extended version of SERPENT 2 was assessed against a dedicated version of the deterministic ERANOS-based EQL3D procedure \cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt isotopic evolution.
+We employed this extended SERPENT 2 for a simplified unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained results which contradict existing \gls{MSBR} depletion simulations \cite{jeong_equilibrium_2016}.
+
+The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
+It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}.
+The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion.
+The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states.
+Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.
+
+The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}.
+Note that this thesis leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
+This article only discusses liquid-fueled \glspl{MSR}.
+Discussions of \glspl{MSR} herein refer only to the liquid-fueled variants.
+Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.

### 2018-07-02 methods.tex
Paper outline finished
saltproc descritpion

@@
 
-% Material and methods
+\begin{itemize}
+        \item \gls{MSBR} design description.
+	\item SERPENT2 very short overview (couple paragraphs).
+	\item Full-core model description.
+	\item Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.
+\end{itemize}
 
-% Provide sufficient details to allow the work to be reproduced by an
-% independent researcher. Methods that are already published should be
-% summarized, and indicated by a reference. If quoting directly from a previously
-% published method, use quotation marks and also cite the source. Any
-% modifications to existing methods should also be described.
+\subsection{Saltproc}
 
-% Theory/calculation 
-% A Theory section should extend, not repeat, the background to the article
-% already dealt with in the Introduction and lay the foundation for further work.
-% In contrast, a Calculation section represents a practical development from a
-% theoretical basis.
+The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
+The python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
+simulate continuous feeds and removals in the \gls{MSR}.
+
+The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE developed in \gls{ORNL} \cite{powers_new_2013}.
+SaltProc is coupled with Monte Carlo SERPENT 2 software which allows to simulate online reprocessing for irregular full-core geometry with high level of fidelity.
+The primary function of SaltProc is to manage material streams while SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion calculations.
+Each material stream represents a fluid in the core design and has specific parameters (e.g.
+isotopic composition, reprocessing interval, mass rate, removal efficacy, etc).
+In addition, SaltProc provides a set of functions for each stream: read and write isotopic data in/from database, separate out specific isotopes from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant number density of specific nuclide in the core.
+These attributes and functions are crucial to simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for myriad reactor systems.
+
+Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
+SaltProc reads an external SERPENT 2 template file which is defined by the user. This file contains input cards with parameters such as geometry,
+moderator and construction materials isotopic composition, neutron population, criticality cycles, total heating power, and boundary conditions.
+After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{.bumat1}) and stores the depleted
+composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic composition of the fuel stream,
+which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a multi-zone simplified assembly, or a full core.
+This flexibiliity allows the user to perform simulations of varying fidelity and computational intensity.
+
+SaltProc can manage as many material streams as desired. It also may work with multiple depletion materials. At the end of a each depletion
+step, SaltProc reads the depleted compositions and tracks each material stream individually. Following this, it applies chemical
+separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database
+and prints into the SERPENT 2 composition file for the next depletion calculation.
+
+Saltproc datasets are timseries, meaning that every value is recorded every timestep. The datasets SaltProc produces are listed below,
+where the values inside the parenthesis are the dataset sizes:
+
+\begin{itemize}
+    \item \texttt{core adensity before reproc} (number of isotopes X timesteps)
+    \item \texttt{core adensity after reproc} (number of isotopes X timesteps)
+    \item \texttt{Keff_BOC} (1 X timesteps)
+    \item \texttt{Keff_EOC} (1 X timesteps)
+    \item \texttt{Th tank adensity} (number of isotopes X timesteps)
+    \item \texttt{iso codes} (number of isotopes X 1)
+\end{itemize}
+
+Liquid-fueled \gls{MSBR} design in this thesis focuses on the state of the core at an equilibrium condition, after fission products have
+built up in the fuel salt during years if operation. Isotopic composition of the fuel salt continues change slightly even after decades
+of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration
+(e.g., vary less than 1\% over several years). In contrast, from the startup of an \gls{MSBR} until the equilibrium condition,
+the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile
+materials number density). During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an
+equilibrium state. A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates,
+fission product removal rates, and corresponding core safety parameters are constant in time.
+
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
+  \vspace{-0.3em}
+  \includegraphics[width=\textwidth]{saltproc_flowchart.pdf}
+  \caption{Flow chart for the Saltproc python-based tools.}
+  \vspace{-1.0em}
+  \label{fig:saltproc_flow}
+\end{figure}
+\FloatBarrier
+
+In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts. These rates need not be
+constant in SaltProc. They can be defined as piecewise functions or set to respond conditions in the core. For instance, SaltProc might increase the
+fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
+These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc focused
+on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor
+fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.

### 2018-07-07 methods.tex
.gitignore is now working

--- 2018-05-10 methods.tex
@@
 
-% Material and methods
+Liquid-fueled system modeling with contemporary reactor physics codes is difficult because most of these codes were developed for analyzing solid-fueled reactors.
+In fact, world-wide commercial reactors fleet today is represented by systems with solid fuel.
+Liquid-fueled systems ability to continuously remove fission products and add fissile and/or fertile elements is the main challenge for depletion simulations.
+SaltProc takes into account online separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and depletion code.
 
-% Provide sufficient details to allow the work to be reproduced by an
-% independent researcher. Methods that are already published should be
-% summarized, and indicated by a reference. If quoting directly from a previously
-% published method, use quotation marks and also cite the source. Any
-% modifications to existing methods should also be described.
+\subsection{Molten Salt Breeder Reactor design and model}
+The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
+It contains a molten fluoride fuel-salt mixture that generates heat in the active core region and transports that heat to the primary heat exchanger by way of the primary salt pump.
+In the active core region, the salt flows through channels in moderating and reflecting graphite blocks.
+Salt at about 565$^{\circ}$C enters the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows upward through channels in the lower plenum graphite.
+The fuel salt exits at the top at about 704$^{\circ}$C through four equally spaced nozzles which connect to the salt-suction pipes leading to primary circulation pumps.
+The fuel salt drain lines connect to the bottom of the reactor vessel inlet manifold.
 
-% Theory/calculation 
-% A Theory section should extend, not repeat, the background to the article
-% already dealt with in the Introduction and lay the foundation for further work.
-% In contrast, a Calculation section represents a practical development from a
-% theoretical basis.
+Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel.
+The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall.
+The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
+Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{These rods needed for emergency shutdown only.} rods.
+The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
+Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}).
+This space for fuel is necessary for injection and flow of molten salt.
+
+Since reactor graphite experiences significant dimensional changes due to neutron irradiation, the reactor core was designed for periodic replacement.
+Based on the irradiation experimental data from \gls{MSRE}, core graphite lifetime is about 4 years and reflector graphite lifetime is 30 years \cite{robertson_conceptual_1971}.
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{view_serpent.png}
+  \caption{Plan and elevation view of SERPENT 2 \gls{MSBR} model developed in this work.}
+  \label{fig:serpent_plan_view}
+\end{figure}
+
+Moreover, it was decided to remove and install the core graphite as an assembly rather than by individual blocks, because it is relatively easier for maintenance personnel and has lower probability of radioactive elements escape due to used blocks damage during removal.
+In addition, handling the core as an assembly also allows the replacement core to be carefully preassembled and tested under factory conditions.
+
+There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, one of which is illustrated in Figure~\ref{fig:serpent_zoneII}.
+The holes in the centers are for the core lifting rods used during the core replacement operations.
+These holes also allow a portion of the fuel salt to flow to the top of the vessel for cooling the top head and axial reflector.
+Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
+This annulus constists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
+In this work, all figures of the core were generated using the built-in SERPENT plotter.
+
+\begin{figure}[t!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{ser_zone_II.png}
+  \caption{Detailed view of \gls{MSBR} zone II model.}
+  \label{fig:serpent_zoneII}
+\end{figure}
+
+\subsubsection{Core zone I}
+The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
+In zone I, 13\% of the volume is fuel salt and 87\% is graphite.
+Zone I is composed of 1,320 graphite cells and 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
+
+These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements.
+Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Zone I is well-moderated to achieve the desired fission power density.
+Figure~\ref{fig:I_element_ref} demonstrates the elevation and sectional views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+
+\subsubsection{Core zone II}
+Zone II which is undermoderated, surrounds zone I.
+Combined with the bounding radial reflector, zone II serves to diminish neutron leakage.
+This zone is formed of two kinds of elements: large-diameter fuel channels (zone II-A) and radial graphite slats (zone II-B).
+
+Zone II has 37\% fuel salt by volume and each element has a fuel channel diameter of 6.604cm.
+The graphite elements for zone II-A are prismatic and have elliptical-shaped dowels running axially between the prisms and needed to isolate the fuel salt flow in zone I from that in zone II.
+Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite elements and their SERPENT model.
+Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
+The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:detail_plan_view}.
+Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
+The neutron energy spectrum in zone II is made harder to enhance the rate of thorium resonance capture relative to the fission rate, thus limiting the neutron flux in the outer core zone and reducing the neutron leakage \cite{robertson_conceptual_1971}.
+
+The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
+From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels (figure~\ref{fig:detail_plan_view}).
+These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
+Figure~\ref{fig:serpent_zoneII} illustrates this core region in the SERPENT model.
+The volume of fuel salt in zone II was kept exactly 37\%, so that this simplification did not considerably change the core neutronics.
+This is the only simplification made to the \gls{MSBR} geometry in this work.
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
+  \vspace{-0.3em}
+  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
+  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \vspace{-0.6em}
+  \label{fig:I_element_ref}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
+  \vspace{-0.3em}
+  \includegraphics[width=\textwidth]{zone_II_element_ref.png}
+  \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \vspace{-0.6em}
+  \label{fig:II_element_ref}
+\end{figure}
+\FloatBarrier
+
+\subsubsection{Material composition and normalization parameters}
+The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
+The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole \%) as the \gls{MSBR} design\cite{robertson_conceptual_1971}.
+The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
+
+For cross section generation, JEFF-3.1.2 neutron library was employed \cite{oecd/nea_data_bank_jeff-3.1.2_2014}.
+The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when SERPENT generates the problem-dependent nuclear data library.
+The isotopic composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to SERPENT model without any modification.
+Table~\ref{tab:msbr_tab} is a summary of the major \gls{MSBR} parameters used by this model \cite{robertson_conceptual_1971}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h!]
+        %\centering
+        \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
+        \begin{tabularx}{\textwidth}{ s  x}
+        \hline
+                Thermal capacity of reactor           & 2250 MW(t)
+                \\ 
+                Net electrical output                 & 1000 MW(e) 
+                \\  
+                Net thermal efficiency        & 44.4\%
+                \\  
+                Salt volume fraction in central core zone     & 0.13
+                \\ 
+                Salt volume fraction in outer core zone       & 0.37
+                \\ 
+                Fuel salt inventory (Zone I)                  & 8.2 m$^3$	
+                \\ 
+                Fuel salt inventory (Zone II)                 & 10.8 m$^3$	
+                \\ 
+                Fuel salt inventory (annulus)                 & 3.8 m$^3$	
+                \\  
+                Total fuel salt inventory                     & 48.7 m$^3$	
+                \\ 
+                Fissile mass in fuel salt                   & 1303.7 kg	
+                \\ 
+                Fuel salt components                  & 
+                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	
+                \\  
+                Fuel salt composition                 & 
+                71.85-16-12-0.25 mole\%
+                \\
+                Fuel salt density                    & 
+                3.35 g/cm$^3$
+                \\ \hline
+        \end{tabularx}
+        \label{tab:msbr_tab}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
+This section contains \gls{MSBR} chemical processing plant and gas separation system brief overview.
+
+\begin{itemize}
+        \item \gls{MSBR} design description.
+	\item SERPENT2 very short overview (couple paragraphs).
+	\item Full-core model description.
+	\item Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.
+\end{itemize}

### 2018-07-07 methods.tex
Methods except Teddy's part finished

@@
 
-\subsection{Molten Salt Breeder Reactor design and model}
+\subsection{Molten Salt Breeder Reactor design and model description}
 The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
@@
 Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
-This annulus constists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
-In this work, all figures of the core were generated using the built-in SERPENT plotter.
+This annulus consists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
+In this work, all figures of the core were generated using the built-in SERPENT 2 plotter.
+All calculations presented in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
 
@@
 The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
-In zone I, 13\% of the volume is fuel salt and 87\% is graphite.
-Zone I is composed of 1,320 graphite cells and 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
+Zone I has 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
 
@@
 Zone I is well-moderated to achieve the desired fission power density.
-Figure~\ref{fig:I_element_ref} demonstrates the elevation and sectional views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
+  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \label{fig:I_element_ref}
+\end{figure}
 
@@
 Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
-The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:detail_plan_view}.
+The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}.
 Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
@@
 The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
-From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels (figure~\ref{fig:detail_plan_view}).
+From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels.
 These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
@@
 
-\begin{figure}[hbp!] % replace 't' with 'b' to 
+\begin{figure}[ht!] % replace 't' with 'b' to 
   \centering
-  \vspace{-0.3em}
-  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
-  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
-  \vspace{-0.6em}
-  \label{fig:I_element_ref}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[hbp!] % replace 't' with 'b' to 
-  \centering
-  \vspace{-0.3em}
   \includegraphics[width=\textwidth]{zone_II_element_ref.png}
   \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
-  \vspace{-0.6em}
   \label{fig:II_element_ref}
 \end{figure}
-\FloatBarrier
 
@@
 The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
-The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole \%) as the \gls{MSBR} design\cite{robertson_conceptual_1971}.
+The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.75-16-12-0.25 mole \%) as the \gls{MSBR} design \cite{robertson_conceptual_1971}.
 The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
@@
         \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
-        \begin{tabularx}{\textwidth}{ s  x}
+        \begin{tabularx}{\textwidth}{ s  s}
         \hline
@@
                 Fuel salt composition                 & 
-                71.85-16-12-0.25 mole\%
+                71.75-16-12-0.25 mole\%
                 \\
@@
 
+\subsection{Online reprocessing method}
 Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
-This section contains \gls{MSBR} chemical processing plant and gas separation system brief overview.
 
-\begin{itemize}
-        \item \gls{MSBR} design description.
-	\item SERPENT2 very short overview (couple paragraphs).
-	\item Full-core model description.
-	\item Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.
-\end{itemize}
+\textbf{Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.}

### 2018-07-08 methods.tex
Update methods.tex

--- 2018-07-02 methods.tex
@@
 
-\begin{itemize}
-        \item \gls{MSBR} design description.
-	\item SERPENT2 very short overview (couple paragraphs).
-	\item Full-core model description.
-	\item Online reprocessing method. Advantages and disadvantages of batch-wise approach. SaltProc capabilities description.
-\end{itemize}
-
-\subsection{Saltproc}
+\subsection{The SaltProc modeling and simulation code}
 
 The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
-The python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
 for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 

### 2018-07-08 methods.tex
reflected comments

@@
 
-The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
+The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_201*} is designed to expand SERPENT 2
+ depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
 The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
@@
 
-The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE developed in \gls{ORNL} \cite{powers_new_2013}.
-SaltProc is coupled with Monte Carlo SERPENT 2 software which allows to simulate online reprocessing for irregular full-core geometry with high level of fidelity.
-The primary function of SaltProc is to manage material streams while SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion calculations.
-Each material stream represents a fluid in the core design and has specific parameters (e.g.
-isotopic composition, reprocessing interval, mass rate, removal efficacy, etc).
-In addition, SaltProc provides a set of functions for each stream: read and write isotopic data in/from database, separate out specific isotopes from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant number density of specific nuclide in the core.
-These attributes and functions are crucial to simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for myriad reactor systems.
+The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
+developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
+software which allows to simulate online reprocessing for irregular full-core geometry with 
+high level of fidelity.  The primary function of SaltProc is to manage material streams while
+SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
+calculations. Saltproc is defined as a 
+python class, where each material stream is defined as a isotopic atomic density
+vector variable. This allows tracking of time-sensitive material streams such as the
+Pa-233 tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
+reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
+for each stream: read and write isotopic data in/from database, separate out specific isotopes 
+from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
+number density of specific nuclide in the core. These attributes and functions are crucial to 
+simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
+myriad reactor systems.
 
-Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the user. This file contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, criticality cycles, total heating power, and boundary conditions.
-After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{.bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a multi-zone simplified assembly, or a full core.
-This flexibiliity allows the user to perform simulations of varying fidelity and computational intensity.
+Saltproc is currently in active development in Github, and has unit tests and
+Travis continuous integration for sustainable development. There is also documentation
+generated through Sphinx document generator for ease of use. We plan to implement
+user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
+and decay modeling in future releases.
 
-SaltProc can manage as many material streams as desired. It also may work with multiple depletion materials. At the end of a each depletion
-step, SaltProc reads the depleted compositions and tracks each material stream individually. Following this, it applies chemical
-separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database
+Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
+coupled SaltProc and SERPENT 2. To perform a depletion step,
+SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
+contains input cards with parameters such as geometry,
+moderator and construction materials isotopic composition, neutron population, criticality 
+cycles, total heating power, and boundary conditions.
+After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
+.bumat1}) and stores the depleted
+composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
+composition of the fuel stream,
+which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
+multi-zone simplified assembly, or a full core.
+This flexibiliity allows the user to perform simulations of varying fidelity and computational 
+intensity.
+
+SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
+materials. At the end of a each depletion
+step, SaltProc reads the depleted compositions and tracks each material stream individually. 
+Following this, it applies chemical
+separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x 
+timesteps) which SaltProc stores in an HDF5 database
 and prints into the SERPENT 2 composition file for the next depletion calculation.
 
-Saltproc datasets are timseries, meaning that every value is recorded every timestep. The datasets SaltProc produces are listed below,
+Saltproc datasets are timseries, meaning that every value is recorded every timestep. The 
+datasets SaltProc produces are listed below,
 where the values inside the parenthesis are the dataset sizes:

### 2018-07-08 methods.tex
github website

@@
 
-Saltproc is currently in active development in Github, and has unit tests and
+Saltproc is currently in active development in Github (https://github.com/arfc/saltproc), and has unit tests and
 Travis continuous integration for sustainable development. There is also documentation

### 2018-07-09 acros.tex

@@
 \newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
-\newacronym{ADS}{ADS}{Accelerator-Driven Systems}
 \newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
@@
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
-\newacronym{ASTRID}{ASTRID}{Advanced Sodium Technological Reactor for Industrial Demonstration}
 \newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
@@
 \newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
-\newacronym{BWR}{BWR}{Boiling Water Reactor}
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
 \newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
+\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
 \newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
@@
 \newacronym{EPA}{EPA}{Environmental Protection Agency}
-\newacronym{EPR}{EPR}{European Pressurized Reactor}
+\newacronym{EPR}{EPR}{European Pressurized Reactors}
 \newacronym{EP}{EP}{Engineering Physics}
@@
 \newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
-\newacronym{FP}{FP}{Fission Products}
+\newacronym{FP}{FP}{Fission Product}
 \newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
@@
 \newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
-\newacronym{MOX}{MOX}{Mixed Oxide Fuel}
+\newacronym{MOSART}{MOSART}{Molten Salt Actinide Recycler and Transmuter}
+\newacronym{MOX}{MOX}{mixed oxide}
+\newacronym{MPI}{MPI}{Message Passing Interface}
 \newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
+\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
 \newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
 \newacronym{MSR}{MSR}{Molten Salt Reactor}
-\newacronym{MWe}{MWe}{Mega Watt electric}
 \newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
@@
 \newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
+\newacronym{NPP}{NPP}{Nuclear Power Plant}
 \newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
@@
 \newacronym{PH}{PRONGHORN}{PRONGHORN}
-\newacronym{PHWR}{Pressurized Heavy Water Reactor}{Pressurized Heavy Water Reactor}
 \newacronym{PRIS}{PRIS}{Power Reactor Information System}
@@
 \newacronym{RD}{R\&D}{Research and Development}
+\newacronym{REE}{REE}{rare earth element}
 \newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
@@
 \newacronym{UML}{UML}{Unified Modeling Language}
-\newacronym{UNF}{UNF}{Used Nuclear Fuel}
-\newacronym{UOX}{UOX}{Uranium Oxide Fuel}
+\newacronym{UOX}{UOX}{uranium oxide}
 \newacronym{UQ}{UQ}{uncertainty quantification}

### 2018-07-09 introduction.tex
.gitignore is now working

@@
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this thesis are described in (6, 7, 8, 9).
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in (6, 7, 8, 9).
 Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
@@
 The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}.
-Note that this thesis leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
+Note that this study leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
 This article only discusses liquid-fueled \glspl{MSR}.
-Discussions of \glspl{MSR} herein refer only to the liquid-fueled variants.
 Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.

### 2018-07-09 methods.tex

@@
 \section{Methods}
+
+Liquid-fueled system modeling with contemporary reactor physics codes is difficult because most of these codes were developed for analyzing solid-fueled reactors.
+In fact, world-wide commercial reactors fleet today is represented by systems with solid fuel.
+Liquid-fueled systems ability to continuously remove fission products and add fissile and/or fertile elements is the main challenge for depletion simulations.
+SaltProc takes into account online separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and depletion code.
+
+\subsection{Molten Salt Breeder Reactor design and model description}
+The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
+It contains a molten fluoride fuel-salt mixture that generates heat in the active core region and transports that heat to the primary heat exchanger by way of the primary salt pump.
+In the active core region, the salt flows through channels in moderating and reflecting graphite blocks.
+Salt at about 565$^{\circ}$C enters the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows upward through channels in the lower plenum graphite.
+The fuel salt exits at the top at about 704$^{\circ}$C through four equally spaced nozzles which connect to the salt-suction pipes leading to primary circulation pumps.
+The fuel salt drain lines connect to the bottom of the reactor vessel inlet manifold.
+
+Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel.
+The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall.
+The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
+Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{These rods needed for emergency shutdown only.} rods.
+The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
+Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}).
+This space for fuel is necessary for injection and flow of molten salt.
+
+Since reactor graphite experiences significant dimensional changes due to neutron irradiation, the reactor core was designed for periodic replacement.
+Based on the irradiation experimental data from \gls{MSRE}, core graphite lifetime is about 4 years and reflector graphite lifetime is 30 years \cite{robertson_conceptual_1971}.
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{view_serpent.png}
+  \caption{Plan and elevation view of SERPENT 2 \gls{MSBR} model developed in this work.}
+  \label{fig:serpent_plan_view}
+\end{figure}
+
+Moreover, it was decided to remove and install the core graphite as an assembly rather than by individual blocks, because it is relatively easier for maintenance personnel and has lower probability of radioactive elements escape due to used blocks damage during removal.
+In addition, handling the core as an assembly also allows the replacement core to be carefully preassembled and tested under factory conditions.
+
+There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, one of which is illustrated in Figure~\ref{fig:serpent_zoneII}.
+The holes in the centers are for the core lifting rods used during the core replacement operations.
+These holes also allow a portion of the fuel salt to flow to the top of the vessel for cooling the top head and axial reflector.
+Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
+This annulus consists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
+In this work, all figures of the core were generated using the built-in SERPENT 2 plotter.
+All calculations presented in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+
+\begin{figure}[t!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{ser_zone_II.png}
+  \caption{Detailed view of \gls{MSBR} zone II model.}
+  \label{fig:serpent_zoneII}
+\end{figure}
+
+\subsubsection{Core zone I}
+The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
+Zone I has 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
+
+These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements.
+Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Zone I is well-moderated to achieve the desired fission power density.
+Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{zone_I_element_ref.png}
+  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \label{fig:I_element_ref}
+\end{figure}
+
+\subsubsection{Core zone II}
+Zone II which is undermoderated, surrounds zone I.
+Combined with the bounding radial reflector, zone II serves to diminish neutron leakage.
+This zone is formed of two kinds of elements: large-diameter fuel channels (zone II-A) and radial graphite slats (zone II-B).
+
+Zone II has 37\% fuel salt by volume and each element has a fuel channel diameter of 6.604cm.
+The graphite elements for zone II-A are prismatic and have elliptical-shaped dowels running axially between the prisms and needed to isolate the fuel salt flow in zone I from that in zone II.
+Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite elements and their SERPENT model.
+Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
+The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}.
+Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
+The neutron energy spectrum in zone II is made harder to enhance the rate of thorium resonance capture relative to the fission rate, thus limiting the neutron flux in the outer core zone and reducing the neutron leakage \cite{robertson_conceptual_1971}.
+
+The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
+From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels.
+These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
+Figure~\ref{fig:serpent_zoneII} illustrates this core region in the SERPENT model.
+The volume of fuel salt in zone II was kept exactly 37\%, so that this simplification did not considerably change the core neutronics.
+This is the only simplification made to the \gls{MSBR} geometry in this work.
+
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{zone_II_element_ref.png}
+  \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \label{fig:II_element_ref}
+\end{figure}
+
+\subsubsection{Material composition and normalization parameters}
+The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
+The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.75-16-12-0.25 mole \%) as the \gls{MSBR} design \cite{robertson_conceptual_1971}.
+The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
+
+For cross section generation, JEFF-3.1.2 neutron library was employed \cite{oecd/nea_data_bank_jeff-3.1.2_2014}.
+The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when SERPENT generates the problem-dependent nuclear data library.
+The isotopic composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to SERPENT model without any modification.
+Table~\ref{tab:msbr_tab} is a summary of the major \gls{MSBR} parameters used by this model \cite{robertson_conceptual_1971}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h!]
+        %\centering
+        \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
+        \begin{tabularx}{\textwidth}{ s  s}
+        \hline
+                Thermal capacity of reactor           & 2250 MW(t)
+                \\ 
+                Net electrical output                 & 1000 MW(e) 
+                \\  
+                Net thermal efficiency        & 44.4\%
+                \\  
+                Salt volume fraction in central core zone     & 0.13
+                \\ 
+                Salt volume fraction in outer core zone       & 0.37
+                \\ 
+                Fuel salt inventory (Zone I)                  & 8.2 m$^3$	
+                \\ 
+                Fuel salt inventory (Zone II)                 & 10.8 m$^3$	
+                \\ 
+                Fuel salt inventory (annulus)                 & 3.8 m$^3$	
+                \\  
+                Total fuel salt inventory                     & 48.7 m$^3$	
+                \\ 
+                Fissile mass in fuel salt                   & 1303.7 kg	
+                \\ 
+                Fuel salt components                  & 
+                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	
+                \\  
+                Fuel salt composition                 & 
+                71.75-16-12-0.25 mole\%
+                \\
+                Fuel salt density                    & 
+                3.35 g/cm$^3$
+                \\ \hline
+        \end{tabularx}
+        \label{tab:msbr_tab}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Online reprocessing method}
+Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
 

### 2018-07-09 methods.tex
Reprocessing logic and table added

@@
                 \\  
-                Salt volume fraction in central core zone     & 0.13
+                Salt volume fraction in central zone I		& 0.13
                 \\ 
-                Salt volume fraction in outer core zone       & 0.37
+                Salt volume fraction in outer zone II       & 0.37
                 \\ 
@@
 Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
+All liquid-fueled \gls{MSR} designs involve varying levels of online fuel processing.
+Minimally, volatile gaseous fission products (e.g.
+Kr, Xe) escape from the fuel salt during routine reactor operation and must be captured.
+Additional systems might be used to enhance removal of those elements.
+Most designs also call for the removal of noble and rare earth metals from the core since these metals act as neutron poisons.
+Some designs suggest a more complex list of elements to process (figure ~\ref{fig:periodic_tab}), including the temporary removal of protactinium from the salt or other regulation of the actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
 
-\subsection{The SaltProc modeling and simulation code}
-
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_201*} is designed to expand SERPENT 2
- depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
-The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
-for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
-simulate continuous feeds and removals in the \gls{MSR}.
-
-The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
-developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
-software which allows to simulate online reprocessing for irregular full-core geometry with 
-high level of fidelity.  The primary function of SaltProc is to manage material streams while
-SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
-calculations. Saltproc is defined as a 
-python class, where each material stream is defined as a isotopic atomic density
-vector variable. This allows tracking of time-sensitive material streams such as the
-Pa-233 tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
-reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
-for each stream: read and write isotopic data in/from database, separate out specific isotopes 
-from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
-number density of specific nuclide in the core. These attributes and functions are crucial to 
-simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
-myriad reactor systems.
-
-Saltproc is currently in active development in Github (https://github.com/arfc/saltproc), and has unit tests and
-Travis continuous integration for sustainable development. There is also documentation
-generated through Sphinx document generator for ease of use. We plan to implement
-user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
-and decay modeling in future releases.
-
-Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
-coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
-contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, criticality 
-cycles, total heating power, and boundary conditions.
-After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
-.bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
-composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
-multi-zone simplified assembly, or a full core.
-This flexibiliity allows the user to perform simulations of varying fidelity and computational 
-intensity.
-
-SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
-materials. At the end of a each depletion
-step, SaltProc reads the depleted compositions and tracks each material stream individually. 
-Following this, it applies chemical
-separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x 
-timesteps) which SaltProc stores in an HDF5 database
-and prints into the SERPENT 2 composition file for the next depletion calculation.
-
-Saltproc datasets are timseries, meaning that every value is recorded every timestep. The 
-datasets SaltProc produces are listed below,
-where the values inside the parenthesis are the dataset sizes:
-
-\begin{itemize}
-    \item \texttt{core adensity before reproc} (number of isotopes X timesteps)
-    \item \texttt{core adensity after reproc} (number of isotopes X timesteps)
-    \item \texttt{Keff_BOC} (1 X timesteps)
-    \item \texttt{Keff_EOC} (1 X timesteps)
-    \item \texttt{Th tank adensity} (number of isotopes X timesteps)
-    \item \texttt{iso codes} (number of isotopes X 1)
-\end{itemize}
-
-Liquid-fueled \gls{MSBR} design in this thesis focuses on the state of the core at an equilibrium condition, after fission products have
-built up in the fuel salt during years if operation. Isotopic composition of the fuel salt continues change slightly even after decades
-of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration
-(e.g., vary less than 1\% over several years). In contrast, from the startup of an \gls{MSBR} until the equilibrium condition,
-the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile
-materials number density). During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an
-equilibrium state. A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates,
-fission product removal rates, and corresponding core safety parameters are constant in time.
+In the single-fluid \gls{MSBR} considered in this work, thorium, uranium, protactinium, and fission products are all mixed together in a single fluoride salt (FLiBe).
+Separation of thorium from lanthanide (atomic numbers 57 through 71) fission products is rather challenging because of their chemical similarities.
 
@@
   \centering
-  \vspace{-0.3em}
-  \includegraphics[width=\textwidth]{saltproc_flowchart.pdf}
-  \caption{Flow chart for the Saltproc python-based tools.}
-  \vspace{-1.0em}
-  \label{fig:saltproc_flow}
+  \includegraphics[width=\textwidth]{periodic_map.png}
+  \caption{Processing options for \gls{MSR} fuels \cite{ahmad_neutronics_2015}.}
+  \label{fig:periodic_tab}
 \end{figure}
-\FloatBarrier
 
-In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts. These rates need not be
-constant in SaltProc. They can be defined as piecewise functions or set to respond conditions in the core. For instance, SaltProc might increase the
-fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
-These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc focused
-on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor
-fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.
+\subsubsection{Fuel material flows}
+The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U.
+Furthermore, the \gls{MSBR} design requires online reprocessing to remove all poisons (e.g.
+$^{135}$Xe), noble metals, and gases (e.g.
+$^{75}$Se, $^{85}$Kr) every 20 seconds.
+Protactinium presents a challenge, since it has a large absorption cross section in the thermal energy spectrum.
+Accordingly, $^{233}$Pa is continuously removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U without poisoning the reactor.
+The reactor reprocessing system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop.
+This feature allows the reactor to avoid neutron losses to protactinium, keeps fission products to a very low level, and increases the efficiency of $^{233}$U breeding.
+Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and the cycle times used for modeling salt treatment and separations \cite{robertson_conceptual_1971}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht!]
+        \centering
+        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
+        \begin{tabularx}{\textwidth}{ x | s | x }
+        \hline 
+        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
+        Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
+        \qquad & Eu & 500 days \\ 
+        Noble metals & Se, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
+        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
+        Gases & Kr, Xe & 20 sec \\ 
+        Volatile fluorides & Br, I & 60 days \\
+        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
+        Salt discard & Th, Li, Be, F & 3435 days \\ 
+        Protactinium & $^{233}$Pa & 3 days \\ 
+        Higher nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\ 
+        \end{tabularx}
+        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only.
+Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
+        \label{tab:reprocessing_list}
+\end{table}
+Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations.
+If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition.
+On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured.
+To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.
+
+\subsubsection{The SaltProc modeling and simulation code}

### 2018-07-21 methods.tex
Results section, keff, spectrum finished

--- 2018-07-09 methods.tex
@@
   \includegraphics[width=\textwidth]{view_serpent.png}
-  \caption{Plan and elevation view of SERPENT 2 \gls{MSBR} model developed in this work.}
+  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in this work.}
   \label{fig:serpent_plan_view}
@@
 Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
+All liquid-fueled \gls{MSR} designs involve varying levels of online fuel processing.
+Minimally, volatile gaseous fission products (e.g.
+Kr, Xe) escape from the fuel salt during routine reactor operation and must be captured.
+Additional systems might be used to enhance removal of those elements.
+Most designs also call for the removal of noble and rare earth metals from the core since these metals act as neutron poisons.
+Some designs suggest a more complex list of elements to process (figure ~\ref{fig:periodic_tab}), including the temporary removal of protactinium from the salt or other regulation of the actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
 
-\subsection{The SaltProc modeling and simulation code}
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{periodic_map.png}
+  \caption{Processing options for \gls{MSR} fuels \cite{ahmad_neutronics_2015}.}
+  \label{fig:periodic_tab}
+\end{figure}
 
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_201*} is designed to expand SERPENT 2
+\subsubsection{Fuel material flows}
+The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U.
+Furthermore, the \gls{MSBR} design requires online reprocessing to remove all poisons (e.g.
+$^{135}$Xe), noble metals, and gases (e.g.
+$^{75}$Se, $^{85}$Kr) every 20 seconds.
+Protactinium presents a challenge, since it has a large absorption cross section in the thermal energy spectrum.
+Accordingly, $^{233}$Pa is continuously removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U without poisoning the reactor.
+The reactor reprocessing system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop.
+This feature allows the reactor to avoid neutron losses to protactinium, keeps fission products to a very low level, and increases the efficiency of $^{233}$U breeding.
+Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and the cycle times used for modeling salt treatment and separations \cite{robertson_conceptual_1971}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht!]
+        \centering
+        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
+        \begin{tabularx}{\textwidth}{ x | s | x }
+        \hline 
+        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
+        Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
+        \qquad & Eu & 500 days \\ 
+        Noble metals & Se, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
+        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
+        Gases & Kr, Xe & 20 sec \\ 
+        Volatile fluorides & Br, I & 60 days \\
+        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
+        Salt discard & Th, Li, Be, F & 3435 days \\ 
+        Protactinium & $^{233}$Pa & 3 days \\ 
+        Higher nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
+        \end{tabularx}
+        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only.
+Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
+        \label{tab:reprocessing_list}
+\end{table}
+Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations.
+If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition.
+On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured.
+To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.
+
+\subsubsection{The SaltProc modeling and simulation code}
+The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to expand SERPENT 2
  depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
-The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
 for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
@@
 vector variable. This allows tracking of time-sensitive material streams such as the
-Pa-233 tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
+$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
 reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
@@
 
-Saltproc is currently in active development in Github (https://github.com/arfc/saltproc), and has unit tests and
-Travis continuous integration for sustainable development. There is also documentation
+Saltproc is currently in active development in Github (https://github.com/ arfc/saltproc), and has unit tests and Travis continuous integration for sustainable development. There is also documentation
 generated through Sphinx document generator for ease of use. We plan to implement
@@
 
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
+  \caption{Flow chart for the Saltproc python-based tools.}
+  \label{fig:saltproc_flow}
+\end{figure}
+
 SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
@@
 \begin{itemize}
-    \item \texttt{core adensity before reproc} (number of isotopes X timesteps)
-    \item \texttt{core adensity after reproc} (number of isotopes X timesteps)
-    \item \texttt{Keff_BOC} (1 X timesteps)
-    \item \texttt{Keff_EOC} (1 X timesteps)
-    \item \texttt{Th tank adensity} (number of isotopes X timesteps)
-    \item \texttt{iso codes} (number of isotopes X 1)
+    \item \texttt{core adensity before reproc} (number of isotopes x timesteps)
+    \item \texttt{core adensity after reproc} (number of isotopes x timesteps)
+    \item \texttt{Keff\_BOC} (1 x timesteps)
+    \item \texttt{Keff\_EOC} (1 x timesteps)
+    \item \texttt{Th tank adensity} (number of isotopes x timesteps)
+    \item \texttt{iso codes} (number of isotopes x 1)
 \end{itemize}
 
-Liquid-fueled \gls{MSBR} design in this thesis focuses on the state of the core at an equilibrium condition, after fission products have
-built up in the fuel salt during years if operation. Isotopic composition of the fuel salt continues change slightly even after decades
-of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration
-(e.g., vary less than 1\% over several years). In contrast, from the startup of an \gls{MSBR} until the equilibrium condition,
-the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile
-materials number density). During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an
-equilibrium state. A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates,
-fission product removal rates, and corresponding core safety parameters are constant in time.
+Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core at an equilibrium condition, after fission products have built up in the fuel salt during years if operation.
+Isotopic composition of the fuel salt continues change slightly even after decades of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration (e.g., vary less than 1\% over several years).
+In contrast, from the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile materials number density).
+During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an equilibrium state.
+A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates, fission product removal rates, and corresponding core safety parameters are constant in time.
 
-\begin{figure}[htp!] % replace 't' with 'b' to 
-  \centering
-  \vspace{-0.3em}
-  \includegraphics[width=\textwidth]{saltproc_flowchart.pdf}
-  \caption{Flow chart for the Saltproc python-based tools.}
-  \vspace{-1.0em}
-  \label{fig:saltproc_flow}
-\end{figure}
-\FloatBarrier
-
-In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts. These rates need not be
-constant in SaltProc. They can be defined as piecewise functions or set to respond conditions in the core. For instance, SaltProc might increase the
-fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
-These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc focused
-on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor
-fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.
+In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts.
+These rates need not be constant in SaltProc.
+They can be defined as piecewise functions or set to respond conditions in the core.
+For instance, SaltProc might increase the fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
+These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}.
+In summary, the development approach of SaltProc focused on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.

### 2018-07-21 results.tex
Results section, keff, spectrum finished

@@
 \section{Results}
+The SaltProc online reprocessing simulation code is demonstrated in four applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion, (2) studying operational and safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated outer core zone II works as a virtual ``blanket", reduces neutron leakage and improves breeding ratio due to neutron energy spectral shift, and (4) determining the effect of fission product removal on the core neutronics.
+
+The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm for effective multiplication factor) and computational time.
+The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
+The total computational time for achieving equilibrium composition was approximately 9,900 node-hours (18 core-years.)
+
+\subsection{Effective multiplication factor}
+Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
+The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
+The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{keff.png}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
+  \label{fig:keff}
+\end{figure}
+\FloatBarrier
+First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
+Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
+The corresponding effective multiplication factor is much smaller than the previous one.
+Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
+Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
+
+Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
+In fact, removal of these elements every 3435 days causes the multiplication factor to jump by approximately 450 pcm, and limits using the batch approach for online reprocessing simulation.
+Overall, the effective multiplication factor gradually decreases from 1.075 to $k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of irradiation.
+
+The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
+Figure~\ref{fig:adens_eq} shows major nuclides which have a strong influence on the reactor core physics normalized separately for each isotope by average atomic density, at the beginning of each depletion time step.
+Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
+Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equlibrium state was achieved after 16 years of reactor operation.
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
+  \caption{Number density of major nuclides during 60 years of reactor operation.}
+  \label{fig:adens_eq}
+\end{figure}
+In contrast, a wide variety of nuclides, including fissile isotopes (e.g.
+$^{235}$U) and non-fissile strong absorbers (e.g.
+$^{234}$U), keep accumulating in the core.
+Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core.
+In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm).
+Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm.
+Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
+  \includegraphics[width=\textwidth]{fissile_short.png}
+  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
+  \label{fig:fissile_short}
+\end{figure}
+\subsection{Neutron spectrum}
+Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV.
+The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
+\begin{figure}[t!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum.png} 
+  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
+  \label{fig:spectrum}
+\end{figure}
+
+Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal neutrons than zone II, indicating that the majority of fissions occured in the central part of the core.
+In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.
+Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV.
+Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the neutron energy spectrum in this range.
+Furthermore, in the central core region (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years of reactor operation.
+In contrast, in the outer core region (zone II) a similar spectral shift takes place at a reduced scale.
+This resuls is in a good agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core steady-state study \cite{park_whole_2015}.
+
+It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV.
+Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
+Thus, a signficant amount fissile material will be needed to make the reactor critical.
+
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum_zones.png} 
+  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+  \label{fig:spectrum_zones}
+\end{figure}
+
+\subsection{Neutron flux}
+Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition.
+The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum.
+A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons.
+This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
+Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
+
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{radial_flux.png} 
+  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
+  \label{fig:radial_flux}
+\end{figure}
+\FloatBarrier
+
+\subsection{Power and breeding distribution}
+Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for initial and equilibrium fuel composition.
+Figure~\ref{fig:pow_den} demonstrates the normalized power distribution of the \gls{MSBR} quater core at both states.
+For both the initial and equilibrium compositions, fission primarly occurs in the center of the core, namely zone I.
+The spectral shift during reactor operation results in different power fractions at startup and equilibrium, but most of the power is still generated in zone I.
+Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states.
+The distribution reflects the spatial distribution of $^{233}$Th production in the core.
+The thorium-232 then $\beta$-decays to $^{233}$Pa which is the precursor for $^{233}$U production.
+Accordingly, this characteristic represents the breeding distribution in the \gls{MSBR} core.
+Spectral shift does not cause significant changes in power nor in breeding distribution.
+Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II, which is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht!]
+  \centering
+  \caption{Power generation fraction in each zone for initial and equilibrium state.}
+\begin{tabularx}{\textwidth}{ m | s | s } \hline
+Core region      & Initial      & Equilibrium   \\   
+Zone I           & 97.91\%      & 98.12\%   \\
+Zone II          & 2.09\%       & 1.88\%   \\
+\end{tabularx}
+  \label{tab:powgen_fraction}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{power_distribution.png} 
+  \caption{Normalized power density for initial (top) and equilibrium (bottom) fuel salt composition.}
+  \label{fig:pow_den}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{breeding_distribution.png} 
+  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for initial (top) and equilibrium (bottom) fuel salt composition.}
+  \label{fig:breeding_den}
+\end{figure}
+\FloatBarrier
+
+\subsection{Temperature coefficient of reactivity}
+Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}.
+Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}.
+The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated.
+When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite.
+When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt.
+To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K.
+Three different cases were considered:
+\begin{enumerate}
+  \item Temperature of fuel salt rising from 900K to 1000K.
+  \item Temperature of graphite rising from 900K to 1000K.
+  \item Whole reactor temperature rising from 900K to 1000K.
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht!]
+  \centering
+  \caption{Temperature coefficients of reactivity for initial and equilibrium state.}
+\begin{tabularx}{\textwidth}{ m | s | s | s } \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  
+Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
+Moderator        & $+1.61\pm0.044$ & $+0.97\pm0.046$ & $+2.35$  \\
+Total            & $-3.1\pm0.04$   & $-0.97\pm0.046$ & $-0.87$  \\
+\end{tabularx}
+  \label{tab:tcoef}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the first case, changes in the fuel temperature only impact fuel density.
+In this case, the geometry is unchanged because the fuel is a liquid.
+However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector.
+Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
+A new geometry input was created based on this information.
+
+The fuel temperature coefficient (FTC) is negative for both initial and equilibrium fuel compositon due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with earlier research \cite{robertson_conceptual_1971,park_whole_2015}.
+The moderator temperature coefficient (MTC) is positive for startup composition and decreases during reactor operation because of spectrum hardening with fuel depletion.
+Finally, the total temperature coefficient of reactivity is negative for both cases, but decreases during reactor operation due to spectral shift.
+In summary, even after 20 years of operation the total temperature coefficient of reactivity is relatively large and negative during reactor operation, despite positive MTC, and affords excellent reactor stability and control.
+
+\subsection{Reactivity control system rod worth}
+Table~\ref{tab:rod_worth} summarizes the reactivity control system worth.
+During normal operation the control (graphite) rods are fully inserted, and the safety (B$_4$C) rods are fully withdrawn.
+To insert negative reactivity into the core, the graphite rods are gradually withdrawn from the core.
+In an accident, the safety rods would fall down into the core.
+The integral rod worths were calculated for various positions to separately estimate control (graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system worth.
+Control rod integral worth is approximately 28 cents and stays almost constant during reactor operation.
+The safety rod integral worth decreases by  16.2\% during 20 years of operation because of neutron spectrum hardening and absorber accumulation in proximity to reactivity control system rods.
+This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[hb!]
+  \centering
+  \caption{Control system rod worth for initial and equilibrium fuel composition.}
+\begin{tabularx}{\textwidth}{ m | s | s } \hline
+\qquad\qquad Reactivity parameter  & \quad Initial      & \enspace Equilibrium      \\
+Control (graphite) rod integral worth (cents)               & $\ 28.2\pm0.8$     & $\ 29.0\pm0.8$ \\ 
+Safety (B$_4$C) rod integral worth (cents)                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
+Total reactivity control system worth (cents)               & $505.8\pm0.7$    & $424.9\pm0.8$ \\
+\end{tabularx}
+  \label{tab:rod_worth}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Six Factor Analysis}
+The effective multiplication factor could be expressed using formula:
+\begin{align*}
+k_{eff} = k_{inf} P_f  P_t \\
+ = \eta \epsilon p f P_f P_t
+\end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht!]
+  \centering
+  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
+\begin{tabularx}{\textwidth}{ m | s | s } \hline
+	   \qquad\qquad\qquad Factors  & \qquad Initial      & \qquad Equilibrium   \\ 
+Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
+Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
+Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
+Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
+Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
+Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ 
+\end{tabularx}
+  \label{tab:six_factor}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and equilibrium fuel salt composition.
+The non-leakage probability for both fast and thermal neutrons does not change during reactor operation because these values are not largely affected by the neutron spectrum shift.
+In contrast, neutron reproduction factor ($\eta$), resonance escape probability (p), and fast fission factor ($\epsilon$) are considerably different between startup and equilibrium.
+As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the initial state.
+Neutron spectrum hardening causes the fast fission to increase through the core lifetime.
+The opposite is true for the resonance escape probability.
+Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
+
+\subsection{Thorium refill rate}
+As was mentioned in Methods the only external feed material flow for this \gls{MSBR} reprocessing scheme is $^{232}$Th.
+Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 20 years of reactor operation.
+Figure~\ref{fig:th_refill_spike} shows the large spikes up to 36 kg/day in a thorium consumption every 3435 days.
+This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
+The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
+As indicated in Figure~\ref{fig:th_refill}, the average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
+As a result, the average $^{232}$Th feed rate over 20 years of operation is about 2.39 kg/day.
+This results is in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017} which reported thorium-232 refill rate for single-cell online reprocessing of 2.45 kg/day.
+
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate.png} 
+  \caption{$^{232}$Th feed rate over 20 years of \gls{MSBR} operation.}
+  \label{fig:th_refill}
+\end{figure}
+\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate_spike.png} 
+  \caption{Typical $^{232}$Th feed rate spike caused by strong absorbers (Rb, Sr, Cs, Ba) removal.}
+  \label{fig:th_refill_spike}
+\end{figure}
+\FloatBarrier
 

### 2018-07-27 results.tex
Results finished

@@
 
-The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm for effective multiplication factor) and computational time.
+The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective multiplication factor) and computational time.
 The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
@@
 The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
-\begin{figure}[hbp!] % replace 't' with 'b' to 
+
+First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
+Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
+The corresponding effective multiplication factor is much smaller than the previous one.
+Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
+Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
+\begin{figure}[ht!] % replace 't' with 'b' to 
   \centering
@@
 \end{figure}
-\FloatBarrier
-First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
-Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
-The corresponding effective multiplication factor is much smaller than the previous one.
-Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
-Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
-
 Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
@@
 Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
-Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equlibrium state was achieved after 16 years of reactor operation.
-\begin{figure}[htp!] % replace 't' with 'b' to 
+Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
+\begin{figure}[ht!] % replace 't' with 'b' to 
   \centering
@@
 \end{figure}
+
 \subsection{Neutron spectrum}
@@
 The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
-\begin{figure}[t!] % replace 't' with 'b' to force it to 
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
   \centering
@@
 \end{figure}
-
 Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal neutrons than zone II, indicating that the majority of fissions occured in the central part of the core.
@@
 Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
-Thus, a signficant amount fissile material will be needed to make the reactor critical.
-
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{spectrum_zones.png} 
-  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
-  \label{fig:spectrum_zones}
-\end{figure}
+Thus, a significant amount fissile material will be needed to make the reactor critical.
 
@@
 Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
-
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum_zones.png} 
+  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+  \label{fig:spectrum_zones}
+\end{figure}
+\begin{figure}[hb!] % replace 't' with 'b' to force it to 
   \centering
@@
 \end{figure}
-\FloatBarrier
-
 \subsection{Power and breeding distribution}
 Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for initial and equilibrium fuel composition.
-Figure~\ref{fig:pow_den} demonstrates the normalized power distribution of the \gls{MSBR} quater core at both states.
-For both the initial and equilibrium compositions, fission primarly occurs in the center of the core, namely zone I.
+Figure~\ref{fig:pow_den} reflects the normalized power distribution of the \gls{MSBR} quarter core which is the same at both states.
+For both the initial and equilibrium compositions, fission primarily occurs in the center of the core, namely zone I.
 The spectral shift during reactor operation results in different power fractions at startup and equilibrium, but most of the power is still generated in zone I.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[hb!]
+  \centering
+  \caption{Power generation fraction in each zone for initial and equilibrium state.}
+\begin{tabularx}{\textwidth}{ m | s | s } \hline
+Core region      & Initial      & Equilibrium   \\   \hline
+Zone I           & 97.91\%      & 98.12\%   \\
+Zone II          & 2.09\%       & 1.88\%   \\ \hline
+\end{tabularx}
+  \label{tab:powgen_fraction}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states.
@@
 Spectral shift does not cause significant changes in power nor in breeding distribution.
-Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II, which is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[ht!]
+Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.
+\begin{figure}[hb!] % replace 't' with 'b' to force it to 
   \centering
-  \caption{Power generation fraction in each zone for initial and equilibrium state.}
-\begin{tabularx}{\textwidth}{ m | s | s } \hline
-Core region      & Initial      & Equilibrium   \\   
-Zone I           & 97.91\%      & 98.12\%   \\
-Zone II          & 2.09\%       & 1.88\%   \\
-\end{tabularx}
-  \label{tab:powgen_fraction}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{power_distribution.png} 
-  \caption{Normalized power density for initial (top) and equilibrium (bottom) fuel salt composition.}
+  \includegraphics[width=\textwidth]{power_distribution_eq.png} 
+  \caption{Normalized power density for both initial and equilibrium fuel salt composition.}
   \label{fig:pow_den}
 \end{figure}
-\FloatBarrier
-
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
   \centering
-  \includegraphics[width=\textwidth]{breeding_distribution.png} 
-  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for initial (top) and equilibrium (bottom) fuel salt composition.}
+  \includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
+  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
   \label{fig:breeding_den}
 \end{figure}
-\FloatBarrier
-
 \subsection{Temperature coefficient of reactivity}
@@
 \end{enumerate}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{Temperature coefficients of reactivity for initial and equilibrium state.}
-\begin{tabularx}{\textwidth}{ m | s | s | s } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  
+\begin{tabularx}{\textwidth}{ s | s | s | x } \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  \hline
 Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
 Moderator        & $+1.61\pm0.044$ & $+0.97\pm0.046$ & $+2.35$  \\
-Total            & $-3.1\pm0.04$   & $-0.97\pm0.046$ & $-0.87$  \\
+Total            & $-3.1\pm0.04$   & $-0.97\pm0.046$ & $-0.87$  \\ \hline
 \end{tabularx}
@@
 This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[hb!]
+\begin{table}[ht!]
   \centering
   \caption{Control system rod worth for initial and equilibrium fuel composition.}
-\begin{tabularx}{\textwidth}{ m | s | s } \hline
-\qquad\qquad Reactivity parameter  & \quad Initial      & \enspace Equilibrium      \\
-Control (graphite) rod integral worth (cents)               & $\ 28.2\pm0.8$     & $\ 29.0\pm0.8$ \\ 
-Safety (B$_4$C) rod integral worth (cents)                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
-Total reactivity control system worth (cents)               & $505.8\pm0.7$    & $424.9\pm0.8$ \\
+\begin{tabularx}{\textwidth}{ b | x | x } \hline
+Reactivity parameter [cents]  &  Initial      &  Equilibrium      \\ \hline
+Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 29.0\pm0.8$ \\ 
+Safety (B$_4$C) rod integral worth                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
+Total reactivity control system worth               & $505.8\pm0.7$    & $424.9\pm0.8$ \\ \hline
 \end{tabularx}
@@
 \begin{align*}
-k_{eff} = k_{inf} P_f  P_t \\
- = \eta \epsilon p f P_f P_t
+k_{eff} = k_{inf} P_f  P_t = \eta \epsilon p f P_f P_t
 \end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[ht!]
-  \centering
-  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
-\begin{tabularx}{\textwidth}{ m | s | s } \hline
-	   \qquad\qquad\qquad Factors  & \qquad Initial      & \qquad Equilibrium   \\ 
-Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
-Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
-Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
-Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
-Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
-Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ 
-\end{tabularx}
-  \label{tab:six_factor}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[hb!]
+  \centering
+  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
+\begin{tabularx}{\textwidth}{ b | s | s } \hline
+Factor  & Initial      & Equilibrium   \\ \hline
+Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
+Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
+Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
+Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
+Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
+Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ \hline
+\end{tabularx}
+  \label{tab:six_factor}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Thorium refill rate}
-As was mentioned in Methods the only external feed material flow for this \gls{MSBR} reprocessing scheme is $^{232}$Th.
-Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 20 years of reactor operation.
-Figure~\ref{fig:th_refill_spike} shows the large spikes up to 36 kg/day in a thorium consumption every 3435 days.
+In \gls{MSBR} reprocessing scheme the only external feed material flow  is $^{232}$Th.
+Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 60 years of reactor operation.
+The the $^{232}$Th feed rate fluctuates significantly as a result of the batch-wise nature of this online reprocessing approach.
+For example, the large spikes up to 36 kg/day in a thorium consumption occurs every 3435 days.
 This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
 The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
-As indicated in Figure~\ref{fig:th_refill}, the average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
-As a result, the average $^{232}$Th feed rate over 20 years of operation is about 2.39 kg/day.
-This results is in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017} which reported thorium-232 refill rate for single-cell online reprocessing of 2.45 kg/day.
-
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
   \centering
   \includegraphics[width=\textwidth]{Th_refill_rate.png} 
-  \caption{$^{232}$Th feed rate over 20 years of \gls{MSBR} operation.}
+  \caption{$^{232}$Th feed rate over 60 years of \gls{MSBR} operation.}
   \label{fig:th_refill}
 \end{figure}
-\begin{figure}[htp!] % replace 't' with 'b' to force it to 
+
+The average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
+As a result, the average $^{232}$Th feed rate over 60 years of operation is about 2.40 kg/day.
+This results are in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017}.
+
+\subsection{The effect of removing fission product from fuel salt}
+Loading initial fuel salt composition into the \gls{MSBR} core leads to supercritical configuration (Figure ~\ref{fig:fp_removal}).
+After reactor startup the effective multiplication factor for the case with volatile gases and noble metals removal is approximately 7500 pcm  higher than for case with no fission products removal.
+This significant impact on the reactor core achieved due to immediate removal (20 sec cycle time) and high absorption cross section of Xe, Kr, Mo, and other noble metals removed.
+The effect of rare earth element removal considerable after few month from startup and achieves approximately 5500 pcm after 10 years of operation.
+The rare earth elements are removed with slower rate (50 days cycle time).
+The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
+The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime.
+Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
   \centering
-  \includegraphics[width=\textwidth]{Th_refill_rate_spike.png} 
-  \caption{Typical $^{232}$Th feed rate spike caused by strong absorbers (Rb, Sr, Cs, Ba) removal.}
-  \label{fig:th_refill_spike}
+  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
+  \label{fig:fp_removal}
 \end{figure}
-\FloatBarrier
-
-\begin{itemize}
-  \item K-eff over 40 years of simulation with $<$15pcm uncertainty.
-  \item Dynamics isotope composition from initial to equilibrium composition.
-  \item Dynamics of fissile vs non-fissile isotopes over 40 years.
-  \item Neutron spectrum for both states and separately for Zone I and Zone II (probably, even Zone II-A and II-B).
-  \item Power distribution plot (without breeding, too much pics).
-  \item Control rod worth \& Six factor analysis \& temperature coefficients.
-  \item $^{232}$Th refill rate.
-  \item Bried discussion (2-3 paragraph).
-\end{itemize}

### 2018-07-28 conclusion.tex
Conclusion and discussion section finished

--- 2018-05-10 conclusion.tex
@@
-\section{Conclusion}
+\section{Discussion and conclusions}
 
-% The main conclusions of the study may be presented in a short Conclusions
-% section, which may stand alone or form a subsection of a Discussion or Results
-% and Discussion section.
+This work introduces the open source \gls{MSR} simulation code SaltProc.
+The SaltProc modeling and simulation tool expands the capability of a continuous-energy Monte Carlo Burnup calculation code SERPENT 2 for analyzing liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
+Benefits of SaltProc include generic geometry modeling, multi-flow capabilities, time-dependent feed and removal rates, and the ability to specify removal efficiency.
+The main goal has been to demonstrate the ability of this tool to find equilibrium fuel salt composition (when the number densities of major isotopes vary less than 1\% over several years).
+A secondary goal has been to compare predicted operational and safety parameters (e.g., neutron energy spectrum, power and breeding distribution, temperature coefficients of reactivity) of the \gls{MSBR} at startup and equilibrium state.
+A tertiary goal has been to demonstrate benefits of continuous fission products removal for thermal \gls{MSR} design.
 
-\FloatBarrier
+Toward these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} was implemented in SERPENT 2.
+The purpose of the full-core model instead of simplified single-cell model \cite{betzler_molten_2017, rykhlevskii_online_2017, betzler_fuel_2018} was to precisely describe the two-region \gls{MSBR} concept design sufficiently to accurately represent breeding in the ``blanket" (outer core zone).
+When running depletion calculations, the most important fission products and $^{233}$Pa are removed and fertile/fissile materials are added to fuel salt every 3 days, while the removal interval for the rare earths, volatile fluorides and seminoble metals was more than month which causes effective multiplication factor fluctuation.
+
+\subsection{Equilibrium state search}
+The results of this study indicate that the effective multiplication factor slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 6 years of operation.
+At the same time, concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, $^{232}$Pa stabilizes after approximately 2500 days of operation.
+Particularly, $^{233}$U number density fluctuates less than 0.8\% from 16 to 20 years of operation.
+Consequently, the core reaches the quasi-equilibrium state after 16 years of operation.
+On the other hand, a wide diversity of nuclides, including fissile isotopes (e.g.
+$^{233}$U, $^{239}$Pu) and non-fissile strong absorbers (e.g.
+$^{234}$U), keep accumulating in the core.
+Current work results show that a true equilibrium composition cannot exist but the balance between negative effects of strong absorber accumulation and new fissile material production can be achieved to keep the reactor critical.
+
+\subsection{Spectral shift}
+Another finding to emerge from the analysis of initial and equilibrium isotopic composition is that the neutron energy spectrum is harder for the equilibrium state because significant amount of heavy fission products were accumulated in the \gls{MSBR} core.
+Moreover, the neutron energy spectrum in the central core region is much softer than in the outer core region due to lower moderator-to-fuel ratio in the outer zone, and this distribution remains stable during reactor operation.
+Finally, the epithermal or thermal spectrum is needed to effectively breed $^{233}$U from $^{232}$Th because radiative capture cross section of thorium-232 monotonically decreases from $10^{-10}$ MeV to $10^{-5}$ MeV.
+A harder spectrum in the outer core region tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and structural materials.
+
+The spatial power distribution in the \gls{MSBR} shows that 98\% of the fission power is generated in central zone I, and neutron energy spectral shift did not cause any notable changes in a power distribution.
+The neutron capture reaction rate spatial distribution for fertile $^{232}$Th, corresponding to breeding in the core, confirms that most of the breeding occurs in an outer, undermoderated, region of the \gls{MSBR} core.
+Finally, the average $^{232}$Th refill rate throughout 60 years of operation is approximately 2.40 kg/day or 100 g/GWh$_e$.
+
+Comparisons of the safety parameters were made for the initial fuel loading and equilibrium compositions with the SERPENT 2 Monte Carlo code.
+It is noted that neutron energy spectrum hardening over the fuel depletion and this spectral shift causes changes in the reactor behavior.
+The total temperature coefficient is large and negative at startup and equilibrium but the magnitude decreases throughout reactor operation from $-3.10$ to $-0.94$ pcm/K.
+The moderator temperature coefficient is positive and also decreases during fuel depletion.
+From reactivity control system efficiency analysis, the safety rod integral worth decreases by approximately 16.2\% over 16 years of operation, while graphite rod integral worth remains constant.
+Summing up, neutron energy spectrum hardening during fuel salt depletion has an undesirable impact on \gls{MSBR} stability and controllability, and should be taken into consideration in further analysis of accident transient scenarios.
+
+\subsection{Benefits of fission products removal}
+Specific chemical elements separation from molten salt is a sophisticated engineering problem that requires    extensive R\&D work (designing separation plant, bypass flow system) and has significant economical costs.
+Moreover, storing and handling separated radioactive material that might be in solid, liquid and gaseous form, presents an engineering challenge.
+On the other hand, keeping all fission products in the molten salt  also impossible because some elements are chemically antagonistic with the molten fuel salt components.
+In fact, some \gls{MSR} designs include removals of only few elements (e.g., volatile gases sparging).
+Other fission products removal is economical problem: the increase of core performance should outweigh the cost of removal.
+
+For thermal spectrum \gls{MSBR} removal of volatile gases, noble metals, and rare earths from a fuel salt has significant core performance benefit.
+Moreover, immediate removal of volatile gases (e.g., xenon) and noble metals had positive effect on reactivity approximately 7500 pcm over 10-years timeframe.
+In contrast, the effect of relatively slower removal of rare earths elements (every 50 days cycle instead of 3 days) has less impact (5500 pcm) on the core reactivity after 10 years of operation.
+In sum, additional study needed to carefully estimate neutronics benefits of removing each element with understanding of chemical separation performance and costs.
+
+\subsection{Future work}
+Continued research into SaltProc-SERPENT and related topics could progress in a number of different directions.
+First and foremost, efforts should be made to enable optimization of reprocessing parameters (e.g.
+time step, feeding rate, protactinium removal rate) to achieve the best fuel utilization, breeding ratio or safety characteristics.
+This might be performed with a parameter sweeping outer loop which would change an input parameter by a small increment, run the simulation and analyze output to determine optimal configuration.
+Furthermore, the existing RAVEN optimization framework might be employed for this optimization study \cite{alfonsi_raven_2013}.
+
+Only the batch-wise online reprocessing approach has been treated in this thesis.
+However, the SERPENT 2 Monte Carlo code was recently extended for continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}.
+This extension must be verified against existing SaltProc/SERPENT or ChemTriton/SCALE packages, and could be employed for immediate removal of fission product gases (e.g., Xe, Kr) which have a strong negative impact on core lifetime and breeding efficiency.
+Finally, using the built-in SERPENT 2 Monte Carlo code online reprocessing \& refueling material burnup routine would significantly speed up computer-intensive full-core depletion simulations.
+
+Lastly, an additional area to explore is the accident safety analysis which requires development a multi-physics model of the \gls{MSBR} with the coupled neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}.
+The existing full-core SERPENT 2 model and equilibrium fuel material composition would be employed to generate problem-oriented nuclear data libraries for further usage in accident transient analysis.
+The final goal of this effort is to develop a fast-running computational model which could study the dynamic behavior of generic \glspl{MSR}, performing detailed safety analysis and design optimization for a variety of reactor concepts.

### 2018-07-28 results.tex
Conclusion and discussion section finished

@@
 The rare earth elements are removed with slower rate (50 days cycle time).
+Moreover, Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day step even strong absorbers did not necessarily leads to fluctuation in results but rare earth elements removal every 50 days causes approximately 600 pcm jump in reactivity.
+
 The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
@@
   \includegraphics[width=\textwidth]{keff_rem_cases.png} 
-  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.
+The confidence interval $\pm\sigma	$ is shaded.}
   \label{fig:fp_removal}

### 2018-07-29 cover-letter/cover-letter.tex
Conclusion and discussion section finished
Graph abstract, cover letter and highlighs finished

@@
 Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
-Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor'' which Mr. 
-Andrei Rykhlevskii and I are submitting for exclusive consideration of 
+Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor'' which Mr. 
+Andrei Rykhlevskii, Mr. Jin Whan Bae and I are submitting for exclusive consideration of 
 publication as a research article in Annals of Nuclear Energy.

### 2018-07-29 introduction.tex
Graph abstract, cover letter and highlighs finished

@@
 \begin{tabularx}{\textwidth}{ x | s | s | m | x } 
-\# & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
+\hline & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
 \hline
@@
 \hline
-4 & SERPENT 2 \cite{leppanen_serpent_2015}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
+4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
 \hline
@@
 \hline
-9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\
+9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
 \end{tabularx}
@@
 
-The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
+The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
 It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}.

### 2018-07-29 abstract.tex
Abstract added

@@
 \begin{abstract}
-        % motivation
-        % problem statement
-        % approach
-        % results
-        % conclusions
+
+Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced demand in building the tools to analyze these systems.
+This paper introduces a Python script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt.
+SaltProc couples with the Monte Carlo code, SERPENT 2, for neutron transport and depletion calculations.
+SaltProc capabilities was illuminated for full-core depletion in the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could be achieved after 16 years and (2) the multiplication factor stabilizes after 6 years of operation.
+Fuel salt irradiation with online reprocessing causes considerable neutron energy spectrum hardening; this spectral shift has a problematic impact on safety parameters (e.g., temperature reactivity feedback, reactivity control system worth).
+Volatile gases and noble metals removal has positive effect on the core performance approximately 7500 pcm over 10-years timeframe; rare earth elements removal has slower rate and less impact on reactivity (5500 pcm).
+Finally, the average $^{232}$Th feed rate throughout 60 years of operation is 100 g/GWh$_e$ which is a good agreement with other recent research.
+Problematic effects of neutron energy spectrum hardening during \gls{MSBR} operation should be taken into account for neutronics, multi-physics, and fuel cycle performance analysis.
+
 \end{abstract}

### 2018-07-29 introduction.tex
Abstract added

@@
  In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e.
-UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
 This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
@@
 The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium.
-With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{$^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
+With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
 Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}.

### 2018-07-29 results.tex
Abstract added

@@
 Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
-The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
+The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
 The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
@@
 
+\subsection{Fuel salt composition dynamics}
 The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
@@
 Thus, a significant amount fissile material will be needed to make the reactor critical.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum_zones.png} 
+  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+  \label{fig:spectrum_zones}
+\end{figure}
 
@@
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{spectrum_zones.png} 
-  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
-  \label{fig:spectrum_zones}
-\end{figure}
-\begin{figure}[hb!] % replace 't' with 'b' to force it to 
   \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[hb!]
+\begin{table}[ht!]
   \centering
@@
 Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.
-\begin{figure}[hb!] % replace 't' with 'b' to force it to 
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
   \centering

### 2018-08-02 acks.tex
Conclusion and discussion section finished

@@
 and/or tables, performed the computation work, contributed to the software 
-product, and reviewed drafts of the paper. Mr. Rykhlevskii is supported by the 
-Department of Nuclear, Plasma, and Radiological Engineering.
+product, and reviewed drafts of the paper. Jin Whan Bae conceived and designed 
+the simulations, wrote the paper, contributed to the software 
+product, and reviewed drafts of the paper. Andrei Rykhlevskii and Jin Whan Bae 
+is supported by the Department of Nuclear, Plasma, and Radiological Engineering.
 

### 2018-08-02 graph-abs/graph-abs.tex
Conclusion and discussion section finished

@@
 
-\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
-\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
-\graphicspath{ {images/} }
+%\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
+%\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
+\graphicspath{ {../figures/} }
 
@@
 \title{Graphical Abstract\\
-Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
+Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor}
 \date{}                     %% if you don't need date to appear
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{./highlight.png}
+        \includegraphics[width=\textwidth]{view_serpent.png}
     \end{center}
-    \caption{A very fancy image important to the paper.}
+    \caption{Plan and elevation views of SERPENT 2 Molten Salt Breeder Reactor model developed in this work.}
     \label{fig:graph-abs}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+        \includegraphics[width=\textwidth]{ser_zone_II.png}
+    \end{center}
+    \caption{Detailed view of Molten Salt Breeder Reactor zone II model.}
+    \label{fig:serpent-zoneII}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+        \includegraphics[width=\textwidth]{zone_I_element_ref.png}
+    \end{center}
+    \caption{Graphite moderator elements for zone I.}
+  	\label{fig:I_element_ref}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{zone_II_element_ref.png}
+    \end{center}
+	\caption{Graphite moderator elements for zone II-A.}
+	\label{fig:II_element_ref}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{periodic_map.png}
+    \end{center}
+	\caption{Processing options for Molten Salt Reactor fuels.}
+	\label{fig:periodic_tab}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
+    \end{center}
+  \caption{Flow chart for the Saltproc python-based tools.}
+  \label{fig:saltproc_flow}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{keff.png}
+    \end{center}
+	\caption{Effective multiplication factor dynamics for full-core model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
+	\label{fig:keff}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{major_isotopes_adens.png}
+    \end{center}
+	\caption{Number density of major nuclides during 60 years of reactor operation.}
+	\label{fig:adens_eq}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{fissile_short.png}
+    \end{center}
+	\caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
+	\label{fig:fissile_short}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{spectrum.png} 
+    \end{center}
+	\caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
+	\label{fig:spectrum}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{spectrum_zones.png} 
+    \end{center}
+	\caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+	\label{fig:spectrum_zones}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{radial_flux.png} 
+    \end{center}
+	\caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
+	\label{fig:radial_flux}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{power_distribution_eq.png} 
+    \end{center}
+	\caption{Normalized power density for both initial and equilibrium fuel salt composition.}
+	\label{fig:pow_den}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
+    \end{center}
+	\caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
+	\label{fig:breeding_den}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{Th_refill_rate.png} 
+    \end{center}
+	\caption{$^{232}$Th feed rate over 60 years of Molten Salt Breeder Reactor operation.}
+	\label{fig:th-rate}
+\end{figure}
+\begin{figure}[htbp!]
+    \begin{center}
+		\includegraphics[width=\textwidth]{keff_rem_cases.png} 
+    \end{center}
+	\caption{Calculated effective multiplication factor for full-core model with removal of different fission product groups over 10 years of operation. The confidence interval $\pm\sigma$ is shaded.}
+	\label{fig:fp-removal}
 \end{figure}

### 2018-08-02 highlights/highlights.tex

@@
 \begin{frontmatter}
-\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
+\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor}
 \end{frontmatter}
@@
 \begin{itemize}
-       \item Highlight 1
-       \item Highlight 2
-       \item Highlight 3
+       \item Python script, SaltProc, and SERPENT are used to simulate material feeds and removals during depletion in MSBR.
+       \item Analysis of the startup of a thorium-fueled MSBR to find equilibrium fuel composition.
+       \item Effects of the fuel salt irradiation with online reprocessing on MSBR operations.
+       \item Fission products online removal benefits for thermal spectrum MSBR.
 \end{itemize}

### 2018-08-02 methods.tex
Results finished

@@
 The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{These rods needed for emergency shutdown only.} rods.
+Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods needed for emergency shutdown only.} rods.
 The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
@@
 Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
-
 \begin{figure}[ht!] % replace 't' with 'b' to 
@@
 intensity.
-
-\begin{figure}[htp!] % replace 't' with 'b' to 
+\begin{figure}[ht!] % replace 't' with 'b' to 
   \centering
@@
 \end{figure}
-
 SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
-materials. At the end of a each depletion
-step, SaltProc reads the depleted compositions and tracks each material stream individually. 
-Following this, it applies chemical
-separation functions to fuel stream vectors. These vectors then form a matrix (isotopics x 
-timesteps) which SaltProc stores in an HDF5 database
-and prints into the SERPENT 2 composition file for the next depletion calculation.
+materials.
+At the end of a each depletion step, SaltProc reads the depleted compositions and tracks each material stream individually.
+Following this, it applies chemical separation functions to fuel stream vectors.
+These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition file for the next depletion calculation.
 

### 2018-08-02 conclusion.tex
hard wraps all the lines

@@
 
-This work introduces the open source \gls{MSR} simulation code SaltProc.
-The SaltProc modeling and simulation tool expands the capability of a continuous-energy Monte Carlo Burnup calculation code SERPENT 2 for analyzing liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
-Benefits of SaltProc include generic geometry modeling, multi-flow capabilities, time-dependent feed and removal rates, and the ability to specify removal efficiency.
-The main goal has been to demonstrate the ability of this tool to find equilibrium fuel salt composition (when the number densities of major isotopes vary less than 1\% over several years).
-A secondary goal has been to compare predicted operational and safety parameters (e.g., neutron energy spectrum, power and breeding distribution, temperature coefficients of reactivity) of the \gls{MSBR} at startup and equilibrium state.
-A tertiary goal has been to demonstrate benefits of continuous fission products removal for thermal \gls{MSR} design.
+This work introduces the open source \gls{MSR} simulation code SaltProc. The 
+SaltProc modeling and simulation tool expands the capability of a 
+continuous-energy Monte Carlo Burnup calculation code SERPENT 2 for analyzing 
+liquid-fueled \gls{MSR} operation 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
+generic geometry modeling, multi-flow capabilities, time-dependent feed and 
+removal rates, and the ability to specify removal efficiency. The main goal has 
+been to demonstrate the ability of this tool to find equilibrium fuel salt 
+composition (when the number densities of major isotopes vary less than 1\% 
+over several years). A secondary goal has been to compare predicted operational 
+and safety parameters (e.g., neutron energy spectrum, power and breeding 
+distribution, temperature coefficients of reactivity) of the \gls{MSBR} at 
+startup and equilibrium state. A tertiary goal has been to demonstrate benefits 
+of continuous fission products removal for thermal \gls{MSR} design.
 
-Toward these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} was implemented in SERPENT 2.
-The purpose of the full-core model instead of simplified single-cell model \cite{betzler_molten_2017, rykhlevskii_online_2017, betzler_fuel_2018} was to precisely describe the two-region \gls{MSBR} concept design sufficiently to accurately represent breeding in the ``blanket" (outer core zone).
-When running depletion calculations, the most important fission products and $^{233}$Pa are removed and fertile/fissile materials are added to fuel salt every 3 days, while the removal interval for the rare earths, volatile fluorides and seminoble metals was more than month which causes effective multiplication factor fluctuation.
+Toward these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} 
+was implemented in SERPENT 2. The purpose of the full-core model instead of 
+simplified single-cell model \cite{betzler_molten_2017, 
+rykhlevskii_online_2017, betzler_fuel_2018} was to precisely describe the 
+two-region \gls{MSBR} concept design sufficiently to accurately represent 
+breeding in the ``blanket" (outer core zone). When running depletion 
+calculations, the most important fission products and $^{233}$Pa are removed 
+and fertile/fissile materials are added to fuel salt every 3 days, while the 
+removal interval for the rare earths, volatile fluorides and seminoble metals 
+was more than month which causes effective multiplication factor fluctuation.
 
 \subsection{Equilibrium state search}
-The results of this study indicate that the effective multiplication factor slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 6 years of operation.
-At the same time, concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, $^{232}$Pa stabilizes after approximately 2500 days of operation.
-Particularly, $^{233}$U number density fluctuates less than 0.8\% from 16 to 20 years of operation.
-Consequently, the core reaches the quasi-equilibrium state after 16 years of operation.
-On the other hand, a wide diversity of nuclides, including fissile isotopes (e.g.
-$^{233}$U, $^{239}$Pu) and non-fissile strong absorbers (e.g.
-$^{234}$U), keep accumulating in the core.
-Current work results show that a true equilibrium composition cannot exist but the balance between negative effects of strong absorber accumulation and new fissile material production can be achieved to keep the reactor critical.
+The results of this study indicate that the effective multiplication factor 
+slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 
+6 years of operation. At the same time, concentration of $^{233}$U, $^{232}$Th, 
+$^{233}$Pa, $^{232}$Pa stabilizes after approximately 2500 days of operation. 
+Particularly, $^{233}$U number density fluctuates less than 0.8\% from 16 to 20 
+years of operation. Consequently, the core reaches the quasi-equilibrium state 
+after 16 years of operation. On the other hand, a wide diversity of nuclides, 
+including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
+absorbers (e.g. $^{234}$U), keep accumulating in the core. Current work results 
+show that a true equilibrium composition cannot exist but the balance between 
+negative effects of strong absorber accumulation and new fissile material 
+production can be achieved to keep the reactor critical.
 
 \subsection{Spectral shift}
-Another finding to emerge from the analysis of initial and equilibrium isotopic composition is that the neutron energy spectrum is harder for the equilibrium state because significant amount of heavy fission products were accumulated in the \gls{MSBR} core.
-Moreover, the neutron energy spectrum in the central core region is much softer than in the outer core region due to lower moderator-to-fuel ratio in the outer zone, and this distribution remains stable during reactor operation.
-Finally, the epithermal or thermal spectrum is needed to effectively breed $^{233}$U from $^{232}$Th because radiative capture cross section of thorium-232 monotonically decreases from $10^{-10}$ MeV to $10^{-5}$ MeV.
-A harder spectrum in the outer core region tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and structural materials.
+Another finding to emerge from the analysis of initial and equilibrium isotopic 
+composition is that the neutron energy spectrum is harder for the equilibrium 
+state because significant amount of heavy fission products were accumulated in 
+the \gls{MSBR} core. Moreover, the neutron energy spectrum in the central core 
+region is much softer than in the outer core region due to lower 
+moderator-to-fuel ratio in the outer zone, and this distribution remains stable 
+during reactor operation. Finally, the epithermal or thermal spectrum is needed 
+to effectively breed $^{233}$U from $^{232}$Th because radiative capture cross 
+section of thorium-232 monotonically decreases from $10^{-10}$ MeV to $10^{-5}$ 
+MeV. A harder spectrum in the outer core region tends to significantly increase 
+resonance absorption in thorium and decrease the absorptions in fissile and 
+structural materials.
 
-The spatial power distribution in the \gls{MSBR} shows that 98\% of the fission power is generated in central zone I, and neutron energy spectral shift did not cause any notable changes in a power distribution.
-The neutron capture reaction rate spatial distribution for fertile $^{232}$Th, corresponding to breeding in the core, confirms that most of the breeding occurs in an outer, undermoderated, region of the \gls{MSBR} core.
-Finally, the average $^{232}$Th refill rate throughout 60 years of operation is approximately 2.40 kg/day or 100 g/GWh$_e$.
+The spatial power distribution in the \gls{MSBR} shows that 98\% of the fission 
+power is generated in central zone I, and neutron energy spectral shift did not 
+cause any notable changes in a power distribution. The neutron capture reaction 
+rate spatial distribution for fertile $^{232}$Th, corresponding to breeding in 
+the core, confirms that most of the breeding occurs in an outer, 
+undermoderated, region of the \gls{MSBR} core. Finally, the average $^{232}$Th 
+refill rate throughout 60 years of operation is approximately 2.40 kg/day or 
+100 g/GWh$_e$.
 
-Comparisons of the safety parameters were made for the initial fuel loading and equilibrium compositions with the SERPENT 2 Monte Carlo code.
-It is noted that neutron energy spectrum hardening over the fuel depletion and this spectral shift causes changes in the reactor behavior.
-The total temperature coefficient is large and negative at startup and equilibrium but the magnitude decreases throughout reactor operation from $-3.10$ to $-0.94$ pcm/K.
-The moderator temperature coefficient is positive and also decreases during fuel depletion.
-From reactivity control system efficiency analysis, the safety rod integral worth decreases by approximately 16.2\% over 16 years of operation, while graphite rod integral worth remains constant.
-Summing up, neutron energy spectrum hardening during fuel salt depletion has an undesirable impact on \gls{MSBR} stability and controllability, and should be taken into consideration in further analysis of accident transient scenarios.
+Comparisons of the safety parameters were made for the initial fuel loading and 
+equilibrium compositions with the SERPENT 2 Monte Carlo code. It is noted that 
+neutron energy spectrum hardening over the fuel depletion and this spectral 
+shift causes changes in the reactor behavior. The total temperature coefficient 
+is large and negative at startup and equilibrium but the magnitude decreases 
+throughout reactor operation from $-3.10$ to $-0.94$ pcm/K. The moderator 
+temperature coefficient is positive and also decreases during fuel depletion. 
+From reactivity control system efficiency analysis, the safety rod integral 
+worth decreases by approximately 16.2\% over 16 years of operation, while 
+graphite rod integral worth remains constant. Summing up, neutron energy 
+spectrum hardening during fuel salt depletion has an undesirable impact on 
+\gls{MSBR} stability and controllability, and should be taken into 
+consideration in further analysis of accident transient scenarios.
 
 \subsection{Benefits of fission products removal}
-Specific chemical elements separation from molten salt is a sophisticated engineering problem that requires    extensive R\&D work (designing separation plant, bypass flow system) and has significant economical costs.
-Moreover, storing and handling separated radioactive material that might be in solid, liquid and gaseous form, presents an engineering challenge.
-On the other hand, keeping all fission products in the molten salt  also impossible because some elements are chemically antagonistic with the molten fuel salt components.
-In fact, some \gls{MSR} designs include removals of only few elements (e.g., volatile gases sparging).
-Other fission products removal is economical problem: the increase of core performance should outweigh the cost of removal.
+Specific chemical elements separation from molten salt is a sophisticated 
+engineering problem that requires    extensive R\&D work (designing separation 
+plant, bypass flow system) and has significant economical costs. Moreover, 
+storing and handling separated radioactive material that might be in solid, 
+liquid and gaseous form, presents an engineering challenge. On the other hand, 
+keeping all fission products in the molten salt  also impossible because some 
+elements are chemically antagonistic with the molten fuel salt components. In 
+fact, some \gls{MSR} designs include removals of only few elements (e.g., 
+volatile gases sparging). Other fission products removal is economical problem: 
+the increase of core performance should outweigh the cost of removal.
 
-For thermal spectrum \gls{MSBR} removal of volatile gases, noble metals, and rare earths from a fuel salt has significant core performance benefit.
-Moreover, immediate removal of volatile gases (e.g., xenon) and noble metals had positive effect on reactivity approximately 7500 pcm over 10-years timeframe.
-In contrast, the effect of relatively slower removal of rare earths elements (every 50 days cycle instead of 3 days) has less impact (5500 pcm) on the core reactivity after 10 years of operation.
-In sum, additional study needed to carefully estimate neutronics benefits of removing each element with understanding of chemical separation performance and costs.
+For thermal spectrum \gls{MSBR} removal of volatile gases, noble metals, and 
+rare earths from a fuel salt has significant core performance benefit. 
+Moreover, immediate removal of volatile gases (e.g., xenon) and noble metals 
+had positive effect on reactivity approximately 7500 pcm over 10-years 
+timeframe. In contrast, the effect of relatively slower removal of rare earths 
+elements (every 50 days cycle instead of 3 days) has less impact (5500 pcm) on 
+the core reactivity after 10 years of operation. In sum, additional study 
+needed to carefully estimate neutronics benefits of removing each element with 
+understanding of chemical separation performance and costs.
 
 \subsection{Future work}
-Continued research into SaltProc-SERPENT and related topics could progress in a number of different directions.
-First and foremost, efforts should be made to enable optimization of reprocessing parameters (e.g.
-time step, feeding rate, protactinium removal rate) to achieve the best fuel utilization, breeding ratio or safety characteristics.
-This might be performed with a parameter sweeping outer loop which would change an input parameter by a small increment, run the simulation and analyze output to determine optimal configuration.
-Furthermore, the existing RAVEN optimization framework might be employed for this optimization study \cite{alfonsi_raven_2013}.
+Continued research into SaltProc-SERPENT and related topics could progress in a 
+number of different directions. First and foremost, efforts should be made to 
+enable optimization of reprocessing parameters (e.g. time step, feeding rate, 
+protactinium removal rate) to achieve the best fuel utilization, breeding ratio 
+or safety characteristics. This might be performed with a parameter sweeping 
+outer loop which would change an input parameter by a small increment, run the 
+simulation and analyze output to determine optimal configuration. Furthermore, 
+the existing RAVEN optimization framework might be employed for this 
+optimization study \cite{alfonsi_raven_2013}.
 
-Only the batch-wise online reprocessing approach has been treated in this thesis.
-However, the SERPENT 2 Monte Carlo code was recently extended for continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}.
-This extension must be verified against existing SaltProc/SERPENT or ChemTriton/SCALE packages, and could be employed for immediate removal of fission product gases (e.g., Xe, Kr) which have a strong negative impact on core lifetime and breeding efficiency.
-Finally, using the built-in SERPENT 2 Monte Carlo code online reprocessing \& refueling material burnup routine would significantly speed up computer-intensive full-core depletion simulations.
+Only the batch-wise online reprocessing approach has been treated in this 
+thesis. However, the SERPENT 2 Monte Carlo code was recently extended for 
+continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
+This extension must be verified against existing SaltProc/SERPENT or 
+ChemTriton/SCALE packages, and could be employed for immediate removal of 
+fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
+core lifetime and breeding efficiency. Finally, using the built-in SERPENT 2 
+Monte Carlo code online reprocessing \& refueling material burnup routine would 
+significantly speed up computer-intensive full-core depletion simulations.
 
-Lastly, an additional area to explore is the accident safety analysis which requires development a multi-physics model of the \gls{MSBR} with the coupled neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}.
-The existing full-core SERPENT 2 model and equilibrium fuel material composition would be employed to generate problem-oriented nuclear data libraries for further usage in accident transient analysis.
-The final goal of this effort is to develop a fast-running computational model which could study the dynamic behavior of generic \glspl{MSR}, performing detailed safety analysis and design optimization for a variety of reactor concepts.
+Lastly, an additional area to explore is the accident safety analysis which 
+requires development a multi-physics model of the \gls{MSBR} with the coupled 
+neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}. 
+The existing full-core SERPENT 2 model and equilibrium fuel material 
+composition would be employed to generate problem-oriented nuclear data 
+libraries for further usage in accident transient analysis. The final goal of 
+this effort is to develop a fast-running computational model which could study 
+the dynamic behavior of generic \glspl{MSR}, performing detailed safety 
+analysis and design optimization for a variety of reactor concepts.

### 2018-08-02 introduction.tex
hard wraps all the lines

@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
-More recently, \gls{MSR} was included in the six advanced reactor concepts that have been chosen by the Generation IV International Forum (GIF) for further research and development.
-\glspl{MSR} offer significant improvements ``in the four broad areas of sustainability, economics, safety and reliability, and proliferation resistance and physical protection" \cite{doe_technology_2002}.
-To achieve the goals formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and improve inherent safety by using liquid coolant which is also a fuel.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} 
+in the 1950s and was operated in the 1960s. More recently, \gls{MSR} was 
+included in the six advanced reactor concepts that have been chosen by the 
+Generation IV International Forum (GIF) for further research and development. 
+\glspl{MSR} offer significant improvements ``in the four broad areas of 
+sustainability, economics, safety and reliability, and proliferation resistance 
+and physical protection" \cite{doe_technology_2002}. To achieve the goals 
+formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
+improve inherent safety by using liquid coolant which is also a fuel.
 
- In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e.
-UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
-This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
-These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
-The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium.
-With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
-Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}.
-The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
-In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle.
-Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.
+ In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
+ materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
+ elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is 
+ circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
+ This innovation leads to immediate advantages over traditional, solid-fueled, 
+ reactors. These include near-atmospheric pressure in the primary loop, 
+ relatively high coolant temperature, outstanding neutron economy, a high level 
+ of inherent safety, reduced fuel preprocessing, and the ability to 
+ continuously remove fission products and add fissile and/or fertile elements 
+ \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
+ early 1970s by \gls{ORNL} specifically to realize the promise of the thorium 
+ fuel cycle, which uses natural thorium instead of enriched uranium. With 
+ continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively 
+ realize advantages of the thorium fuel cycle because the $^{233}$U bred from 
+ $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
+ $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
+ ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
+ ($\tau_{1/2}$=26.967d).} being recycled back to the core 
+ \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a 
+ melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
+ and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
+ In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
+ quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
+ cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
+ for transmutation of spent fuel from current \glspl{LWR}.
 
-Modeling liquid-fueled systems with existing neutron transport and depletion tools is challenging because most of these tools are designed for the solid-fueled reactors simulation.
-The fuel material flows and potential online separations or feeds of specific elements or nuclides are the main challenges
-of liquid-fueled systems.
-Furthermore, no established tool for liquid-fueled \gls{MSR} neutronics and fuel cycle evaluation exist, though internally developed tools from universities and research institutions can approximate online refueling \cite{serp_molten_2014}.
-The foundation for these tools was based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.
-More recent research efforts in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis and couple external tools to neutron transport and depletion codes take into account continuous feeds and removals in \glspl{MSR}.
-Four of these efforts are listed in table~\ref{tab:fs_codes}.
+Modeling liquid-fueled systems with existing neutron transport and depletion 
+tools is challenging because most of these tools are designed for the 
+solid-fueled reactors simulation. The fuel material flows and potential online 
+separations or feeds of specific elements or nuclides are the main challenges
+of liquid-fueled systems. Furthermore, no established tool for liquid-fueled 
+\gls{MSR} neutronics and fuel cycle evaluation exist, though internally 
+developed tools from universities and research institutions can approximate 
+online refueling \cite{serp_molten_2014}. The foundation for these tools was 
+based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated 
+neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into 
+operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and 
+reprocessing system design. More recent research efforts in Europe and Asia 
+mainly focus on fast spectrum reactor fuel cycle analysis and couple external 
+tools to neutron transport and depletion codes take into account continuous 
+feeds and removals in \glspl{MSR}. Four of these efforts are listed in 
+table~\ref{tab:fs_codes}.
 
@@
 \caption{Tools and methods for fast spectrum system fuel cycle analysis.}
-\begin{tabularx}{\textwidth}{ x | s | s | m | x } 
-\hline & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
+\begin{tabularx}{\textwidth}{ x | s | s | m | x } \hline & Neutronic code  & 
+Depletion code    & \qquad Authors & Spectra   \\
 \hline
-1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM \cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
+1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM 
+\cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et 
+al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
 \hline
-2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
+2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et 
+al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
 \hline
-3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
+3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     
+& Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
 \hline
-4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
+4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et 
+al.}, 2013 \cite{aufiero_extended_2013} & fast \\
 \hline
-5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
+5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & 
+Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
 \hline
-6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
+6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et 
+al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, 
+jeong_equilibrium_2016}& thermal\\
 \hline
-7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton \cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
+7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton 
+\cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 
+2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& 
+thermal\\
 \hline
-8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
+8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 
+\cite{rykhlevskii_online_2017} & thermal\\
 \hline
-9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
+9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} 
+\cite{nuttin_potential_2005}&thermal  \\ \hline
 \end{tabularx}
@@
 
-Most of these methods are also applicable to thermal spectrum \glspl{MSR}. Additional tools developed specifically for thermal \gls{MSR} applications are also listed in table~\ref{tab:fs_codes}.
+Most of these methods are also applicable to thermal spectrum \glspl{MSR}. 
+Additional tools developed specifically for thermal \gls{MSR} applications are 
+also listed in table~\ref{tab:fs_codes}.
 
-Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 5, 6, 8, 9) use a set of all nuclides in depletion calculations.
+Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 
+5, 6, 8, 9) use a set of all nuclides in depletion calculations.
 
-Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch).
-To account for batch discharge, a depletion tool must remove some or all material at specified intervals.
-This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
-Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations.
-In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation.
-Methods (1, 4, 8) model true continuous feeds and removals, while other methods employ a batch-wise approach.
-\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing.
-This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
+Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where 
+material is moved to or from the core at all times (continuous) or at specific 
+time steps (batch). To account for batch discharge, a depletion tool must 
+remove some or all material at specified intervals. This requires the burn-up 
+simulation to stop at a given time and restart with a new liquid fuel 
+composition (after removal of discarded materials and addition of 
+fissile/fertile materials). Accounting for a continuous removal or addition is 
+more difficult because it requires adding a term to the Bateman equations. In 
+SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set 
+of Bateman equations using spectrum-averaged fluxes and cross sections 
+generated from a deterministic transport calculation. Methods (1, 4, 8) model 
+true continuous feeds and removals, while other methods employ a batch-wise 
+approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based 
+script for SCALE/TRITON which uses a semi-continuous batch process to simulate 
+a continuous reprocessing. This tool models salt treatment, separations, 
+discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small 
+time steps to simulate continuous reprocessing and deplete the fuel salt 
+\cite{powers_new_2013}.
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in (6, 7, 8, 9).
-Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
+described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
+simplified unit-cell geometry because depletion computations for a many-year 
+fuel cycle are computationally expesive even for simple models.
 
-Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: one for salt channels, one for two salt plena above and below the core and the last cell for the annulus, consequently, two-region reactor core was approximated by one region with averaged fuel/moderator ratio \cite{nuttin_potential_2005}.
-A similar approach was used by Powers \emph{et al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and clearly misrepresent the two-region breeder reactor concept.
-The unit-cell or one-region models may produce reliable results for homogeneous reactor cores (i.e.
-\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e.
-\gls{MSRE}).
-A two-region \gls{MSBR} must be simulated using a whole-core model to represent different neutron transport in the inner and outer regions of the core, because most fissions happens in the inner region while breeding occurs in the outer zone.
+Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: 
+one for salt channels, one for two salt plena above and below the core and the 
+last cell for the annulus, consequently, two-region reactor core was 
+approximated by one region with averaged fuel/moderator ratio 
+\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
+al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
+\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
+betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and 
+clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
+one-region models may produce reliable results for homogeneous reactor cores 
+(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
+(i.e. \gls{MSRE}). A two-region \gls{MSBR} must be simulated using a whole-core 
+model to represent different neutron transport in the inner and outer regions 
+of the core, because most fissions happens in the inner region while breeding 
+occurs in the outer zone.
 
-Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and employed it to study the material isotopic evolution of the \gls{MSFR}.
-The developed extension directly takes into account the effects of online fuel reprocessing on depletion calculations and features a reactivity control algorithm.
-The extended version of SERPENT 2 was assessed against a dedicated version of the deterministic ERANOS-based EQL3D procedure \cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt isotopic evolution.
-We employed this extended SERPENT 2 for a simplified unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained results which contradict existing \gls{MSBR} depletion simulations \cite{jeong_equilibrium_2016}.
+Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
+employed it to study the material isotopic evolution of the \gls{MSFR}. The 
+developed extension directly takes into account the effects of online fuel 
+reprocessing on depletion calculations and features a reactivity control 
+algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
+version of the deterministic ERANOS-based EQL3D procedure 
+\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
+isotopic evolution. We employed this extended SERPENT 2 for a simplified 
+unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
+results which contradict existing \gls{MSBR} depletion simulations 
+\cite{jeong_equilibrium_2016}.
 
-The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
-It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}.
-The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion.
-The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states.
-Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.
+The present work introduces the online reprocessing simulation code, SaltProc, 
+which expands the capability of the continuous-energy Monte Carlo Burnup 
+calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
+liquid-fueled \gls{MSR} operation 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the 
+application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which 
+represents the continuation of the work presented in 
+\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
+of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
+the equilibrium core composition and core depletion. The additional objective 
+is to compare predicted operational and safety parameters of the \gls{MSBR} at 
+both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
+determined and \gls{MSBR} fuel cycle performance will be analyzed.
 
-The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}.
-Note that this study leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
-This article only discusses liquid-fueled \glspl{MSR}.
-Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.
+The \gls{MSBR} complex geometry is hard to describe in software input, and, 
+usually, researchers make significant geometric simplifications to model it 
+\cite{park_whole_2015}. Note that this study leverages extensive computational 
+resources to avoid these geometric approximations and accurately capture 
+breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
+Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
+related to circulating liquid fuel, is not treated here.

### 2018-08-02 results.tex
hard wraps all the lines

@@
 \section{Results}
-The SaltProc online reprocessing simulation code is demonstrated in four applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion, (2) studying operational and safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated outer core zone II works as a virtual ``blanket", reduces neutron leakage and improves breeding ratio due to neutron energy spectral shift, and (4) determining the effect of fission product removal on the core neutronics.
+The SaltProc online reprocessing simulation code is demonstrated in four 
+applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the 
+equilibrium core composition and core depletion, (2) studying operational and 
+safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that 
+in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated 
+outer core zone II works as a virtual ``blanket", reduces neutron leakage and 
+improves breeding ratio due to neutron energy spectral shift, and (4) 
+determining the effect of fission product removal on the core neutronics.
 
-The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective multiplication factor) and computational time.
-The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
-The total computational time for achieving equilibrium composition was approximately 9,900 node-hours (18 core-years.)
+The neutron population per cycle and the number of active/inactive cycles were 
+chosen to obtain balance between reasonable uncertainty for a transport problem 
+($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective 
+multiplication factor) and computational time. The \gls{MSBR} depletion and 
+safety parameter computations were performed on 64 Blue Waters XK7 nodes (two 
+AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per 
+node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
+total computational time for achieving equilibrium composition was 
+approximately 9,900 node-hours (18 core-years.)
 
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
-The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
-The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
+Figure~\ref{fig:keff} demonstrates the effective multiplication factors 
+obtained using SaltProc and SERPENT 2. The effective multiplication factors are 
+calculated after removing fission products listed in 
+Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
+``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
+        amount of time required to remove 100\% of a target nuclide from a fuel 
+salt.} which was fixed at 3 days for this work. The effective multiplication 
+factor fluctuates significantly as a result of the batch-wise nature of this 
+online reprocessing strategy.
 
-First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
-Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
-The corresponding effective multiplication factor is much smaller than the previous one.
-Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
-Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
-\begin{figure}[ht!] % replace 't' with 'b' to 
-  \centering
+First, SERPENT calculates the effective multiplication factor for the beginning 
+of cycle time (fresh fuel composition for the first step). Next, it computes 
+the new fuel salt composition for the end of a 3-day depletion step. The 
+corresponding effective multiplication factor is much smaller than the previous 
+one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
+applying feeds and removals, and this increases accordingly since major reactor 
+poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
+from the protactinium decay tank is added.  \begin{figure}[ht!] % replace 't' 
+        with 'b' to \centering
   \includegraphics[width=\textwidth]{keff.png}
-  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
+  model for a 60-year reactor operation. The confidence interval 
+  $\sigma=\pm15pcm$ is shaded.}
   \label{fig:keff}
 \end{figure}
-Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
-In fact, removal of these elements every 3435 days causes the multiplication factor to jump by approximately 450 pcm, and limits using the batch approach for online reprocessing simulation.
-Overall, the effective multiplication factor gradually decreases from 1.075 to $k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of irradiation.
+Additionally, the presence of rubidium, strontium, cesium, and barium in the 
+core are disadvantageous to reactor physics. In fact, removal of these elements 
+every 3435 days causes the multiplication factor to jump by approximately 450 
+pcm, and limits using the batch approach for online reprocessing simulation. 
+Overall, the effective multiplication factor gradually decreases from 1.075 to 
+$k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of 
+irradiation.
 
 \subsection{Fuel salt composition dynamics}
-The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
-Figure~\ref{fig:adens_eq} shows major nuclides which have a strong influence on the reactor core physics normalized separately for each isotope by average atomic density, at the beginning of each depletion time step.
-Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
-Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
-\begin{figure}[ht!] % replace 't' with 'b' to 
-  \centering
+The analysis of the fuel salt composition evolution provides more comprehensive 
+information about the equilibrium state. Figure~\ref{fig:adens_eq} shows major 
+nuclides which have a strong influence on the reactor core physics normalized 
+separately for each isotope by average atomic density, at the beginning of each 
+depletion time step. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and 
+$^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of 
+operation. Particularly, $^{233}$U number density fluctuates less than 0.8\% in 
+the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium 
+state was achieved after 16 years of reactor operation.
+\begin{figure}[ht!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{major_isotopes_adens.png}
-  \caption{Number density of major nuclides during 60 years of reactor operation.}
+  \caption{Number density of major nuclides during 60 years of reactor 
+  operation.}
   \label{fig:adens_eq}
@@
 In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
-$^{235}$U) and non-fissile strong absorbers (e.g.
-$^{234}$U), keep accumulating in the core.
-Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core.
-In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm).
-Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm.
-Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
-\begin{figure}[htp!] % replace 't' with 'b' to 
-  \centering
+$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
+in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile 
+isotopes in the core. In the end of considered operational time the core 
+contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
+atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
+isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
+production of new fissile materials in the core as well as $^{233}$U breeding 
+make it possible to compensate for negative effects of strong absorber 
+accumulation and keep the reactor critical.
+\begin{figure}[htp!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{fissile_short.png}
-  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
+  \caption{Number density of fissile in epithermal spectrum nuclides 
+  accumulation during the reactor operation.}
   \label{fig:fissile_short}
@@
 \subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV.
-The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{spectrum.png} 
-  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
+Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
+full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
+neutron energy spectrum at equilibrium is harder than at startup due to 
+$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
+the core during reactor operation.  \begin{figure}[ht!] % replace 't' with 'b' 
+        to force it to \centering
+  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
+  spectrum normalized by unit lethargy for initial and equilibrium fuel salt 
+  composition.}
   \label{fig:spectrum}
 \end{figure}
-Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal neutrons than zone II, indicating that the majority of fissions occured in the central part of the core.
-In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.
-Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV.
-Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the neutron energy spectrum in this range.
-Furthermore, in the central core region (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years of reactor operation.
-In contrast, in the outer core region (zone II) a similar spectral shift takes place at a reduced scale.
-This resuls is in a good agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core steady-state study \cite{park_whole_2015}.
+Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal 
+neutrons than zone II, indicating that the majority of fissions occured in the 
+central part of the core. In the undermoderated zone II, the neutron energy 
+spectrum is harder which leads to more capture of neutrons by $^{232}$Th and 
+helps a achieve relatively high breeding ratio. Moreover, the (n,$\gamma$) 
+resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV. 
+Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the 
+neutron energy spectrum in this range. Furthermore, in the central core region 
+(zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years 
+of reactor operation. In contrast, in the outer core region (zone II) a similar 
+spectral shift takes place at a reduced scale. This resuls is in a good 
+agreement with original ORNL report \cite{robertson_conceptual_1971} and most 
+recent whole-core steady-state study \cite{park_whole_2015}.
 
-It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV.
-Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
-Thus, a significant amount fissile material will be needed to make the reactor critical.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{spectrum_zones.png} 
-  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+It is important to obtain the epithermal and thermal spectra to produce 
+$^{233}$U from $^{232}$Th because the radiative capture cross section of 
+thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening 
+the spectrum tends to significantly increase resonance absorption in thorium 
+and decrease the absorptions in fissile and construction materials. Thus, a 
+significant amount fissile material will be needed to make the reactor 
+critical.  \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{spectrum_zones.png} \caption{Neutron flux 
+  energy spectrum in different core regions normalized by unit lethargy for the 
+  initial and equilibrium fuel salt composition.}
   \label{fig:spectrum_zones}
@@
 \subsection{Neutron flux}
-Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition.
-The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum.
-A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons.
-This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
-Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{radial_flux.png} 
-  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
+Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
+neutron flux for both initial and equilibrium composition. The neutron flux has 
+the same shape for both compositions but the equilibrium case has a harder 
+spectrum. A significant spectral shift was observed for the central region of 
+the core (zone I) when for the outer region (zone II) it is negligible for fast 
+but notable for thermal neutrons. This neutron flux radial distribution is in a 
+good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
+Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
+studied for designing the reactivity control system.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
+  flux distribution for initial and equilibrium fuel salt composition.}
   \label{fig:radial_flux}
@@
 \subsection{Power and breeding distribution}
-Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for initial and equilibrium fuel composition.
-Figure~\ref{fig:pow_den} reflects the normalized power distribution of the \gls{MSBR} quarter core which is the same at both states.
-For both the initial and equilibrium compositions, fission primarily occurs in the center of the core, namely zone I.
-The spectral shift during reactor operation results in different power fractions at startup and equilibrium, but most of the power is still generated in zone I.
+Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for 
+initial and equilibrium fuel composition. Figure~\ref{fig:pow_den} reflects the 
+normalized power distribution of the \gls{MSBR} quarter core which is the same 
+at both states. For both the initial and equilibrium compositions, fission 
+primarily occurs in the center of the core, namely zone I. The spectral shift 
+during reactor operation results in different power fractions at startup and 
+equilibrium, but most of the power is still generated in zone I. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Power generation fraction in each zone for initial and equilibrium state.}
+  \caption{Power generation fraction in each zone for initial and equilibrium 
+  state.}
 \begin{tabularx}{\textwidth}{ m | s | s } \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states.
-The distribution reflects the spatial distribution of $^{233}$Th production in the core.
-The thorium-232 then $\beta$-decays to $^{233}$Pa which is the precursor for $^{233}$U production.
-Accordingly, this characteristic represents the breeding distribution in the \gls{MSBR} core.
-Spectral shift does not cause significant changes in power nor in breeding distribution.
-Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
+Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate 
+distribution for $^{232}$Th normalized by the total neutron flux for initial 
+and equilibrium states. The distribution reflects the spatial distribution of 
+$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
+$^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this 
+characteristic represents the breeding distribution in the \gls{MSBR} core. 
+Spectral shift does not cause significant changes in power nor in breeding 
+distribution. Even after 20 years of operation, most of the power still is 
+generated in zone I though the majority of $^{233}$Th is produced in zone II.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
   \includegraphics[width=\textwidth]{power_distribution_eq.png} 
-  \caption{Normalized power density for both initial and equilibrium fuel salt composition.}
+  \caption{Normalized power density for both initial and equilibrium fuel salt 
+  composition.}
   \label{fig:pow_den}
 \end{figure}
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
   \includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
-  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
+  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux 
+  for both initial and equilibrium fuel salt composition.}
   \label{fig:breeding_den}
@@
 \subsection{Temperature coefficient of reactivity}
-Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}.
-Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated.
-When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite.
-When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt.
-To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K.
-Three different cases were considered:
+Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated 
+in this work for both initial and equilibrium fuel composition, and compared 
+with original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
+Uncertainty for each temperature coefficient also appears in 
+Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
+temperature feedback is an expansion of matterial that is heated. When the fuel 
+salt temperature increases, the density of the salt decreases, but at the same 
+time, the total volume of fuel salt in the core remains constant because it is 
+bounded by the graphite. When the graphite temperature increases, the density 
+of graphite decreases creating additional space for fuel salt. To determine 
+temperature coefficients, the cross section temperatures for fuel and moderator 
+were changed from 900K to 1000K. Three different cases were considered:
 \begin{enumerate}
@@
   \centering
-  \caption{Temperature coefficients of reactivity for initial and equilibrium state.}
+  \caption{Temperature coefficients of reactivity for initial and equilibrium 
+  state.}
 \begin{tabularx}{\textwidth}{ s | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
+        \cite{robertson_conceptual_1971} \\  \hline
 Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the first case, changes in the fuel temperature only impact fuel density.
-In this case, the geometry is unchanged because the fuel is a liquid.
-However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector.
-Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
-A new geometry input was created based on this information.
+In the first case, changes in the fuel temperature only impact fuel density. In 
+this case, the geometry is unchanged because the fuel is a liquid. However, 
+when the moderator heats up, both the density and the geometry change due to 
+thermal expansion of the solid graphite blocks and reflector. Accordingly, the 
+new graphite density was calculated using a linear temperature expansion 
+coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 
+geometry input was created based on this information.
 
-The fuel temperature coefficient (FTC) is negative for both initial and equilibrium fuel compositon due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with earlier research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient (MTC) is positive for startup composition and decreases during reactor operation because of spectrum hardening with fuel depletion.
-Finally, the total temperature coefficient of reactivity is negative for both cases, but decreases during reactor operation due to spectral shift.
-In summary, even after 20 years of operation the total temperature coefficient of reactivity is relatively large and negative during reactor operation, despite positive MTC, and affords excellent reactor stability and control.
+The fuel temperature coefficient (FTC) is negative for both initial and 
+equilibrium fuel compositon due to thermal Doppler broadening of the resonance 
+capture cross sections in the thorium and is in a good agreement with earlier 
+research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
+temperature coefficient (MTC) is positive for startup composition and decreases 
+during reactor operation because of spectrum hardening with fuel depletion. 
+Finally, the total temperature coefficient of reactivity is negative for both 
+cases, but decreases during reactor operation due to spectral shift. In 
+summary, even after 20 years of operation the total temperature coefficient of 
+reactivity is relatively large and negative during reactor operation, despite 
+positive MTC, and affords excellent reactor stability and control.
 
@@
 Table~\ref{tab:rod_worth} summarizes the reactivity control system worth. 
-During normal operation the control (graphite) rods are fully inserted, and the safety (B$_4$C) rods are fully withdrawn.
-To insert negative reactivity into the core, the graphite rods are gradually withdrawn from the core.
-In an accident, the safety rods would fall down into the core.
-The integral rod worths were calculated for various positions to separately estimate control (graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system worth.
-Control rod integral worth is approximately 28 cents and stays almost constant during reactor operation.
-The safety rod integral worth decreases by  16.2\% during 20 years of operation because of neutron spectrum hardening and absorber accumulation in proximity to reactivity control system rods.
-This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
+During normal operation the control (graphite) rods are fully inserted, and the 
+safety (B$_4$C) rods are fully withdrawn. To insert negative reactivity into 
+the core, the graphite rods are gradually withdrawn from the core. In an 
+accident, the safety rods would fall down into the core. The integral rod 
+worths were calculated for various positions to separately estimate control 
+(graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system 
+worth. Control rod integral worth is approximately 28 cents and stays almost 
+constant during reactor operation. The safety rod integral worth decreases by  
+16.2\% during 20 years of operation because of neutron spectrum hardening and 
+absorber accumulation in proximity to reactivity control system rods. This 16\% 
+decline in control system worth should be taken into account in \gls{MSBR} 
+accident analysis and safety justification.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Control system rod worth for initial and equilibrium fuel composition.}
+  \caption{Control system rod worth for initial and equilibrium fuel 
+  composition.}
 \begin{tabularx}{\textwidth}{ b | x | x } \hline
 Reactivity parameter [cents]  &  Initial      &  Equilibrium      \\ \hline
-Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 29.0\pm0.8$ \\ 
-Safety (B$_4$C) rod integral worth                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
-Total reactivity control system worth               & $505.8\pm0.7$    & $424.9\pm0.8$ \\ \hline
+Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 
+        29.0\pm0.8$ \\ Safety (B$_4$C) rod integral worth                  & 
+        $251.8\pm0.8$    & $211.0\pm0.8$  \\
+Total reactivity control system worth               & $505.8\pm0.7$    & 
+        $424.9\pm0.8$ \\ \hline
 \end{tabularx}
@@
 
-Table~\ref{tab:six_factor} summarizes the six factors for both initial and equilibrium fuel salt composition.
-The non-leakage probability for both fast and thermal neutrons does not change during reactor operation because these values are not largely affected by the neutron spectrum shift.
-In contrast, neutron reproduction factor ($\eta$), resonance escape probability (p), and fast fission factor ($\epsilon$) are considerably different between startup and equilibrium.
-As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the initial state.
-Neutron spectrum hardening causes the fast fission to increase through the core lifetime.
-The opposite is true for the resonance escape probability.
-Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
+equilibrium fuel salt composition. The non-leakage probability for both fast 
+and thermal neutrons does not change during reactor operation because these 
+values are not largely affected by the neutron spectrum shift. In contrast, 
+neutron reproduction factor ($\eta$), resonance escape probability (p), and 
+fast fission factor ($\epsilon$) are considerably different between startup and 
+equilibrium. As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is 
+softer for the initial state. Neutron spectrum hardening causes the fast 
+fission to increase through the core lifetime. The opposite is true for the 
+resonance escape probability. Finally, the neutron reproduction factor 
+decreases during reactor operation due to accumulation of fissile plutonium 
+isotopes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
+  \caption{Six factors for the full-core \gls{MSBR} model for initial and 
+  equilibrium fuel composition.}
 \begin{tabularx}{\textwidth}{ b | s | s } \hline
 Factor  & Initial      & Equilibrium   \\ \hline
-Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
-Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
-Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
-Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
-Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
-Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ \hline
+Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & 
+        $1.3778\pm.00005$ \\ Thermal utilization factor (f)           & 
+        $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
+Resonance escape probability (p)         & $0.6044\pm.000039$     & 
+        $0.5761\pm.00004$ \\
+Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & 
+        $1.3609\pm.00004$ \\
+Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & 
+        $0.9999\pm.000004$ \\
+Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & 
+        $0.9912\pm.00005$ \\ \hline
 \end{tabularx}
@@
 \subsection{Thorium refill rate}
-In \gls{MSBR} reprocessing scheme the only external feed material flow  is $^{232}$Th.
-Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 60 years of reactor operation.
-The the $^{232}$Th feed rate fluctuates significantly as a result of the batch-wise nature of this online reprocessing approach.
-For example, the large spikes up to 36 kg/day in a thorium consumption occurs every 3435 days.
-This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
-The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{Th_refill_rate.png} 
-  \caption{$^{232}$Th feed rate over 60 years of \gls{MSBR} operation.}
+In \gls{MSBR} reprocessing scheme the only external feed material flow  is 
+$^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
+calculated for 60 years of reactor operation. The the $^{232}$Th feed rate 
+fluctuates significantly as a result of the batch-wise nature of this online 
+reprocessing approach. For example, the large spikes up to 36 kg/day in a 
+thorium consumption occurs every 3435 days. This is required due to batch-wise 
+removal of strong absorbers (Rb, Sr, Cs, Ba). The corresponding effective 
+multiplication factor increase (Figure~\ref{fig:keff}) and breeding 
+intensification leads to additional $^{232}$Th consumption.  
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate.png} \caption{$^{232}$Th 
+  feed rate over 60 years of \gls{MSBR} operation.}
   \label{fig:th_refill}
@@
 
-The average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
-As a result, the average $^{232}$Th feed rate over 60 years of operation is about 2.40 kg/day.
-This results are in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017}.
+The average thorium feed rate increases during the first 500 days of operation 
+and than steadily decreases due to spectrum hardening and accumulation of 
+absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
+years of operation is about 2.40 kg/day. This results are in a good agreement 
+with a recent online reprocessing study by \gls{ORNL} 
+\cite{betzler_molten_2017}.
 
 \subsection{The effect of removing fission product from fuel salt}
-Loading initial fuel salt composition into the \gls{MSBR} core leads to supercritical configuration (Figure ~\ref{fig:fp_removal}).
-After reactor startup the effective multiplication factor for the case with volatile gases and noble metals removal is approximately 7500 pcm  higher than for case with no fission products removal.
-This significant impact on the reactor core achieved due to immediate removal (20 sec cycle time) and high absorption cross section of Xe, Kr, Mo, and other noble metals removed.
-The effect of rare earth element removal considerable after few month from startup and achieves approximately 5500 pcm after 10 years of operation.
-The rare earth elements are removed with slower rate (50 days cycle time).
-Moreover, Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day step even strong absorbers did not necessarily leads to fluctuation in results but rare earth elements removal every 50 days causes approximately 600 pcm jump in reactivity.
+Loading initial fuel salt composition into the \gls{MSBR} core leads to 
+supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
+startup the effective multiplication factor for the case with volatile gases 
+and noble metals removal is approximately 7500 pcm  higher than for case with 
+no fission products removal. This significant impact on the reactor core 
+achieved due to immediate removal (20 sec cycle time) and high absorption cross 
+section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
+element removal considerable after few month from startup and achieves 
+approximately 5500 pcm after 10 years of operation. The rare earth elements are 
+removed with slower rate (50 days cycle time). Moreover, 
+Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day 
+step even strong absorbers did not necessarily leads to fluctuation in results 
+but rare earth elements removal every 50 days causes approximately 600 pcm jump 
+in reactivity.
 
-The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
-The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime.
-Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
-  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.
-The confidence interval $\pm\sigma	$ is shaded.}
+The effective multiplication factor of the core reduces gradually over 
+operation time because the fissile material ($^{233}$U) continuously depletes 
+from the fuel salt due to fission and, at the same time, fission products 
+accumulates in the fuel salt.	Eventually, without fission products removal, 
+the reactivity decreases to the subcritical state after approximately 500 and 
+1300 days of operation for cases with no removal and volatile gases \& noble 
+metals removal, respectively. The time when the simulated core reaches 
+subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
+Therefore, removing fission products provides with significant neutronic 
+benefit because allows achieve longer core lifetime.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{keff_rem_cases.png} \caption{Calculated 
+  effective multiplication factor for full-core \gls{MSBR} model with removal 
+  of different fission product groups over 10 years of operation. The 
+  confidence interval $\pm\sigma	$ is shaded.}
   \label{fig:fp_removal}

### 2018-08-03 abstract.tex

@@
 
-Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced demand in building the tools to analyze these systems.
-This paper introduces a Python script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt.
-SaltProc couples with the Monte Carlo code, SERPENT 2, for neutron transport and depletion calculations.
-SaltProc capabilities was illuminated for full-core depletion in the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could be achieved after 16 years and (2) the multiplication factor stabilizes after 6 years of operation.
-Fuel salt irradiation with online reprocessing causes considerable neutron energy spectrum hardening; this spectral shift has a problematic impact on safety parameters (e.g., temperature reactivity feedback, reactivity control system worth).
-Volatile gases and noble metals removal has positive effect on the core performance approximately 7500 pcm over 10-years timeframe; rare earth elements removal has slower rate and less impact on reactivity (5500 pcm).
-Finally, the average $^{232}$Th feed rate throughout 60 years of operation is 100 g/GWh$_e$ which is a good agreement with other recent research.
-Problematic effects of neutron energy spectrum hardening during \gls{MSBR} operation should be taken into account for neutronics, multi-physics, and fuel cycle performance analysis.
+Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced 
+demand for tools to analyze these systems. This paper introduces a Python 
+script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
+changing isotopic composition of an irradiated fuel salt. SaltProc couples with 
+the Monte Carlo code, SERPENT 2, for neutron transport and depletion 
+calculations. SaltProc capabilities was illuminated for full-core depletion in 
+the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could 
+be achieved after 16 years and (2) the multiplication factor stabilizes after 6 
+years of operation. Fuel salt irradiation with online reprocessing causes 
+considerable neutron energy spectrum hardening; this spectral shift has a 
+problematic impact on safety parameters (e.g., temperature reactivity feedback, 
+reactivity control system worth). Volatile gases and noble metals removal has 
+positive effect on the core performance approximately 7500 pcm over 10-years 
+timeframe; rare earth elements removal has slower rate and less impact on 
+reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 
+years of operation is 100 g/GWh$_e$ which is a good agreement with other recent 
+research. Problematic effects of neutron energy spectrum hardening during 
+\gls{MSBR} operation should be taken into account for neutronics, 
+multi-physics, and fuel cycle performance analysis.
 

### 2018-08-03 methods.tex

@@
 
-Liquid-fueled system modeling with contemporary reactor physics codes is difficult because most of these codes were developed for analyzing solid-fueled reactors.
-In fact, world-wide commercial reactors fleet today is represented by systems with solid fuel.
-Liquid-fueled systems ability to continuously remove fission products and add fissile and/or fertile elements is the main challenge for depletion simulations.
-SaltProc takes into account online separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and depletion code.
+Liquid-fueled system modeling with contemporary reactor physics codes is 
+difficult because most of these codes were developed for analyzing solid-fueled 
+reactors. In fact, world-wide commercial reactors fleet today is represented by 
+systems with solid fuel. Liquid-fueled systems ability to continuously remove 
+fission products and add fissile and/or fertile elements is the main challenge 
+for depletion simulations. SaltProc takes into account online separations and 
+feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and 
+depletion code.
 
 \subsection{Molten Salt Breeder Reactor design and model description}
-The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
-It contains a molten fluoride fuel-salt mixture that generates heat in the active core region and transports that heat to the primary heat exchanger by way of the primary salt pump.
-In the active core region, the salt flows through channels in moderating and reflecting graphite blocks.
-Salt at about 565$^{\circ}$C enters the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows upward through channels in the lower plenum graphite.
-The fuel salt exits at the top at about 704$^{\circ}$C through four equally spaced nozzles which connect to the salt-suction pipes leading to primary circulation pumps.
-The fuel salt drain lines connect to the bottom of the reactor vessel inlet manifold.
+The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm. It 
+contains a molten fluoride fuel-salt mixture that generates heat in the active 
+core region and transports that heat to the primary heat exchanger by way of 
+the primary salt pump. In the active core region, the salt flows through 
+channels in moderating and reflecting graphite blocks. Salt at about 
+565$^{\circ}$C enters the central manifold at the bottom via four 
+40.64-cm-diameter nozzles and flows upward through channels in the lower plenum 
+graphite. The fuel salt exits at the top at about 704$^{\circ}$C through four 
+equally spaced nozzles which connect to the salt-suction pipes leading to 
+primary circulation pumps. The fuel salt drain lines connect to the bottom of 
+the reactor vessel inlet manifold.
 
-Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel.
-The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall.
-The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods needed for emergency shutdown only.} rods.
-The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
-Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}).
-This space for fuel is necessary for injection and flow of molten salt.
+Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the 
+\gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" 
+(zone II) regions inside the vessel. The core has two radial zones bounded by a 
+solid cylindrical graphite reflector and the vessel wall. The central zone, 
+zone I, in which 13\% of the volume is fuel salt and 87\% graphite. Zone I 
+composed of 1,320 graphite cells, 2 graphite control rods, and 2 
+safety\footnote{ These rods needed for emergency shutdown only.} rods. The 
+under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, 
+surrounds the zone I core region and serves to diminish neutron leakage. Zones 
+I and II are surrounded radially and axially by fuel salt 
+(figure~\ref{fig:serpent_zoneII}). This space for fuel is necessary for 
+injection and flow of molten salt.
 
-Since reactor graphite experiences significant dimensional changes due to neutron irradiation, the reactor core was designed for periodic replacement.
-Based on the irradiation experimental data from \gls{MSRE}, core graphite lifetime is about 4 years and reflector graphite lifetime is 30 years \cite{robertson_conceptual_1971}.
+Since reactor graphite experiences significant dimensional changes due to 
+neutron irradiation, the reactor core was designed for periodic replacement. 
+Based on the irradiation experimental data from \gls{MSRE}, core graphite 
+lifetime is about 4 years and reflector graphite lifetime is 30 years 
+\cite{robertson_conceptual_1971}.
 
-\begin{figure}[hbp!] % replace 't' with 'b' to 
-  \centering
+\begin{figure}[hbp!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{view_serpent.png}
-  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in this work.}
+  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in 
+  this work.}
   \label{fig:serpent_plan_view}
@@
 
-Moreover, it was decided to remove and install the core graphite as an assembly rather than by individual blocks, because it is relatively easier for maintenance personnel and has lower probability of radioactive elements escape due to used blocks damage during removal.
-In addition, handling the core as an assembly also allows the replacement core to be carefully preassembled and tested under factory conditions.
+Moreover, it was decided to remove and install the core graphite as an assembly 
+rather than by individual blocks, because it is relatively easier for 
+maintenance personnel and has lower probability of radioactive elements escape 
+due to used blocks damage during removal. In addition, handling the core as an 
+assembly also allows the replacement core to be carefully preassembled and 
+tested under factory conditions.
 
-There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, one of which is illustrated in Figure~\ref{fig:serpent_zoneII}.
-The holes in the centers are for the core lifting rods used during the core replacement operations.
-These holes also allow a portion of the fuel salt to flow to the top of the vessel for cooling the top head and axial reflector.
-Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
-This annulus consists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
-In this work, all figures of the core were generated using the built-in SERPENT 2 plotter.
-All calculations presented in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, 
+one of which is illustrated in Figure~\ref{fig:serpent_zoneII}. The holes in 
+the centers are for the core lifting rods used during the core replacement 
+operations. These holes also allow a portion of the fuel salt to flow to the 
+top of the vessel for cooling the top head and axial reflector. 
+Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular 
+space between the removable core graphite in zone II-B and the permanently 
+mounted reflector graphite. This annulus consists entirely of fuel salt, 
+provides space for moving the core assembly, helps compensate the elliptical 
+dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
+surface of the graphite reflector blocks. In this work, all figures of the core 
+were generated using the built-in SERPENT 2 plotter. All calculations presented 
+in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 
+nodes.
 
-\begin{figure}[t!] % replace 't' with 'b' to 
-  \centering
+\begin{figure}[t!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{ser_zone_II.png}
@@
 \subsubsection{Core zone I}
-The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
-Zone I has 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
+The central region of the core, called zone I, is made up of graphite elements, 
+each $10.16$cm$\times$10.16cm$\times$396.24cm. Zone I has 4 channels for 
+control rods: two for graphite rods which both regulate and shim during normal 
+operation, and two for backup safety rods consisting of boron carbide clad to 
+assure sufficient negative reactivity for emergency situations.
 
-These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements.
-Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Zone I is well-moderated to achieve the desired fission power density.
-Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
-\begin{figure}[ht!] % replace 't' with 'b' to 
-  \centering
+These graphite elements have a mostly rectangular shape with lengthwise ridges 
+at each corner that leave space for salt flow elements. Various element sizes 
+reduce the peak damage flux and power density in the center of the core to 
+prevent local graphite damage. Zone I is well-moderated to achieve the desired 
+fission power density. Figure~\ref{fig:I_element_ref} demonstrates the 
+elevation and plan views of graphite elements of zone I 
+\cite{robertson_conceptual_1971} and their SERPENT model 
+\cite{rykhlevskii_full-core_2017}.
+\begin{figure}[ht!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{zone_I_element_ref.png}
-  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \caption{Graphite moderator elements for zone I 
+  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:I_element_ref}
@@
 \subsubsection{Core zone II}
-Zone II which is undermoderated, surrounds zone I.
-Combined with the bounding radial reflector, zone II serves to diminish neutron leakage.
-This zone is formed of two kinds of elements: large-diameter fuel channels (zone II-A) and radial graphite slats (zone II-B).
+Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
+radial reflector, zone II serves to diminish neutron leakage. This zone is 
+formed of two kinds of elements: large-diameter fuel channels (zone II-A) and 
+radial graphite slats (zone II-B).
 
-Zone II has 37\% fuel salt by volume and each element has a fuel channel diameter of 6.604cm.
-The graphite elements for zone II-A are prismatic and have elliptical-shaped dowels running axially between the prisms and needed to isolate the fuel salt flow in zone I from that in zone II.
-Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite elements and their SERPENT model.
-Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
-The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}.
-Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
-The neutron energy spectrum in zone II is made harder to enhance the rate of thorium resonance capture relative to the fission rate, thus limiting the neutron flux in the outer core zone and reducing the neutron leakage \cite{robertson_conceptual_1971}.
+Zone II has 37\% fuel salt by volume and each element has a fuel channel 
+diameter of 6.604cm. The graphite elements for zone II-A are prismatic and have 
+elliptical-shaped dowels running axially between the prisms and needed to 
+isolate the fuel salt flow in zone I from that in zone II. 
+Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite 
+elements and their SERPENT model. Zone II-B elements are rectangular slats 
+spaced far enough apart to provide the 0.37 fuel salt volume fraction. The 
+reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension 
+(average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}. Zone II 
+serves as a blanket to achieve the best performance: a high breeding ratio and 
+a low fissile inventory. The neutron energy spectrum in zone II is made harder 
+to enhance the rate of thorium resonance capture relative to the fission rate, 
+thus limiting the neutron flux in the outer core zone and reducing the neutron 
+leakage \cite{robertson_conceptual_1971}.
 
-The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
-From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels.
-These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
-Figure~\ref{fig:serpent_zoneII} illustrates this core region in the SERPENT model.
-The volume of fuel salt in zone II was kept exactly 37\%, so that this simplification did not considerably change the core neutronics.
-This is the only simplification made to the \gls{MSBR} geometry in this work.
+The main challenge was to accurately represent zone II-B because it has 
+irregular elements with sophisticated shapes. From the \gls{ORNL} report 
+\cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 
+irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels. 
+These graphite elements were simplified into right-circular cylindrical shapes  
+with central channels. Figure~\ref{fig:serpent_zoneII} illustrates this core 
+region in the SERPENT model. The volume of fuel salt in zone II was kept 
+exactly 37\%, so that this simplification did not considerably change the core 
+neutronics. This is the only simplification made to the \gls{MSBR} geometry in 
+this work.
 
-\begin{figure}[ht!] % replace 't' with 'b' to 
-  \centering
+\begin{figure}[ht!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{zone_II_element_ref.png}
-  \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \caption{Graphite moderator elements for zone II-A 
+  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:II_element_ref}
@@
 \subsubsection{Material composition and normalization parameters}
-The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
-The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.75-16-12-0.25 mole \%) as the \gls{MSBR} design \cite{robertson_conceptual_1971}.
-The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
+The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ 
+Hastelloy-N is very common in reactors now but have been studied and developed 
+at \gls{ORNL} in a program that started in 1950s.} are materials unique of the 
+\gls{MSBR} and were created at \gls{ORNL}. The initial fuel salt used the same 
+density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
+(71.75-16-12-0.25 mole \%) as the \gls{MSBR} design 
+\cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
+enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
+becomes tritium upon neutron capture.
 
-For cross section generation, JEFF-3.1.2 neutron library was employed \cite{oecd/nea_data_bank_jeff-3.1.2_2014}.
-The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when SERPENT generates the problem-dependent nuclear data library.
-The isotopic composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to SERPENT model without any modification.
-Table~\ref{tab:msbr_tab} is a summary of the major \gls{MSBR} parameters used by this model \cite{robertson_conceptual_1971}.
+For cross section generation, JEFF-3.1.2 neutron library was employed 
+\cite{oecd/nea_data_bank_jeff-3.1.2_2014}. The specific temperature was fixed 
+for each material to correctly model the Doppler-broadening of resonance peaks 
+when SERPENT generates the problem-dependent nuclear data library. The isotopic 
+composition of each material at the initial state was described in detail in 
+the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been 
+applied to SERPENT model without any modification. Table~\ref{tab:msbr_tab} is 
+a summary of the major \gls{MSBR} parameters used by this model 
+\cite{robertson_conceptual_1971}.
 
@@
         %\centering
-        \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
+        \caption{Summary of principal data for MSBR 
+        \cite{robertson_conceptual_1971}.}
         \begin{tabularx}{\textwidth}{ s  s}
@@
                 Thermal capacity of reactor           		& 2250 MW(t)
+                \\ Net electrical output                 		& 1000 
+        MW(e) \\  Net thermal efficiency        				
+        & 44.4\%
+                \\  Salt volume fraction in central zone I		& 0.13
+                \\ Salt volume fraction in outer zone II       & 0.37
+                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
+        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
+        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
+        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
+        salt                   & 1303.7 kg	\\ Fuel salt components                  
+                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
+        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                 \\
-                Net electrical output                 		& 1000 MW(e) 
-                \\  
-                Net thermal efficiency        				& 44.4\%
-                \\  
-                Salt volume fraction in central zone I		& 0.13
-                \\ 
-                Salt volume fraction in outer zone II       & 0.37
-                \\ 
-                Fuel salt inventory (Zone I)                & 8.2 m$^3$	
-                \\ 
-                Fuel salt inventory (Zone II)               & 10.8 m$^3$	
-                \\ 
-                Fuel salt inventory (annulus)               & 3.8 m$^3$	
-                \\  
-                Total fuel salt inventory                   & 48.7 m$^3$	
-                \\ 
-                Fissile mass in fuel salt                   & 1303.7 kg	
-                \\ 
-                Fuel salt components                  & 
-                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	
-                \\  
-                Fuel salt composition                 & 
-                71.75-16-12-0.25 mole\%
-                \\
-                Fuel salt density                    & 
-                3.35 g/cm$^3$
+                Fuel salt density                    & 3.35 g/cm$^3$
                 \\ \hline
@@
 \subsection{Online reprocessing method}
-Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
-All liquid-fueled \gls{MSR} designs involve varying levels of online fuel processing.
-Minimally, volatile gaseous fission products (e.g.
-Kr, Xe) escape from the fuel salt during routine reactor operation and must be captured.
-Additional systems might be used to enhance removal of those elements.
-Most designs also call for the removal of noble and rare earth metals from the core since these metals act as neutron poisons.
-Some designs suggest a more complex list of elements to process (figure ~\ref{fig:periodic_tab}), including the temporary removal of protactinium from the salt or other regulation of the actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
+Removing specific chemical elements from a molten salt is a complicated task 
+that requires intelligent design (e.g., chemical separations equipment design, 
+fuel salt flows to equipment) and has a considerable economic cost. All 
+liquid-fueled \gls{MSR} designs involve varying levels of online fuel 
+processing. Minimally, volatile gaseous fission products (e.g. Kr, Xe) escape 
+from the fuel salt during routine reactor operation and must be captured. 
+Additional systems might be used to enhance removal of those elements. Most 
+designs also call for the removal of noble and rare earth metals from the core 
+since these metals act as neutron poisons. Some designs suggest a more complex 
+list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
+temporary removal of protactinium from the salt or other regulation of the 
+actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
 
-\begin{figure}[htp!] % replace 't' with 'b' to 
-  \centering
+\begin{figure}[htp!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{periodic_map.png}
-  \caption{Processing options for \gls{MSR} fuels \cite{ahmad_neutronics_2015}.}
+  \caption{Processing options for \gls{MSR} fuels 
+  \cite{ahmad_neutronics_2015}.}
   \label{fig:periodic_tab}
@@
 \subsubsection{Fuel material flows}
-The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U.
-Furthermore, the \gls{MSBR} design requires online reprocessing to remove all poisons (e.g.
-$^{135}$Xe), noble metals, and gases (e.g.
-$^{75}$Se, $^{85}$Kr) every 20 seconds.
-Protactinium presents a challenge, since it has a large absorption cross section in the thermal energy spectrum.
-Accordingly, $^{233}$Pa is continuously removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U without poisoning the reactor.
-The reactor reprocessing system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop.
-This feature allows the reactor to avoid neutron losses to protactinium, keeps fission products to a very low level, and increases the efficiency of $^{233}$U breeding.
-Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and the cycle times used for modeling salt treatment and separations \cite{robertson_conceptual_1971}.
+The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
+which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
+design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
+noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
+Protactinium presents a challenge, since it has a large absorption cross 
+section in the thermal energy spectrum. Accordingly, $^{233}$Pa is continuously 
+removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
+to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
+system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 
+days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
+primary loop. This feature allows the reactor to avoid neutron losses to 
+protactinium, keeps fission products to a very low level, and increases the 
+efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
+full list of nuclides and the cycle times used for modeling salt treatment and 
+separations \cite{robertson_conceptual_1971}.
 
@@
         \centering
-        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
+        \caption{The effective cycle times for protactinium and fission 
+        products removal (reproduced from \cite{robertson_conceptual_1971}).}
         \begin{tabularx}{\textwidth}{ x | s | x }
-        \hline 
-        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
-        Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
-        \qquad & Eu & 500 days \\ 
-        Noble metals & Se, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
+        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
+                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
+                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
+                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
         Seminoble metals & Zr, Cd, In, Sn & 200 days \\
-        Gases & Kr, Xe & 20 sec \\ 
-        Volatile fluorides & Br, I & 60 days \\
-        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
-        Salt discard & Th, Li, Be, F & 3435 days \\ 
-        Protactinium & $^{233}$Pa & 3 days \\ 
-        Higher nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
+        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
+        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
+                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
+                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
         \end{tabularx}
-        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only.
-Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
+        %\footnotetext{Chemical processing plant and gas separation system 
+        %removing chemical elements (not isotopes) only. Isotopes instead of 
+        %elements listed because other isotopes are short-lived and might be 
+        %ignored.}
         \label{tab:reprocessing_list}
 \end{table}
-Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations.
-If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition.
-On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured.
-To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.
+Th removal rates vary among nuclides in this reactor concept which dictate the 
+necessary resolution of depletion calculations. If the depletion time intervals 
+are very short, an enormous number of depletion steps are required to obtain 
+the equilibrium composition. On the other hand, if the depletion  calculation 
+time interval is too long, the impact of short-lived fission products is not 
+captured. To compromise, the time interval for depletion calculations in this 
+model was selected as 3 days to correlate with the removal interval of 
+$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
+fraction of $^{232}$Th.
 
 \subsubsection{The SaltProc modeling and simulation code}
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to expand SERPENT 2
- depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
-The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
-for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
-simulate continuous feeds and removals in the \gls{MSR}.
+The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to 
+expand SERPENT 2
+ depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous 
+ reprocessing.
+The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store 
+data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+for SEPRENT output file parsing and nuclide naming. It is an open-source tool 
+that uses a semi-continuous approach to simulate continuous feeds and removals 
+in the \gls{MSR}.
 
-The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
-developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
-software which allows to simulate online reprocessing for irregular full-core geometry with 
-high level of fidelity.  The primary function of SaltProc is to manage material streams while
-SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
-calculations. Saltproc is defined as a 
-python class, where each material stream is defined as a isotopic atomic density
-vector variable. This allows tracking of time-sensitive material streams such as the
-$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
-reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
-for each stream: read and write isotopic data in/from database, separate out specific isotopes 
-from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
-number density of specific nuclide in the core. These attributes and functions are crucial to 
-simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
-myriad reactor systems.
+The tool structure and capabilities of SaltProc are similar to ChemTriton tool 
+for SCALE
+developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte 
+Carlo SERPENT 2
+software which allows to simulate online reprocessing for irregular full-core 
+geometry with high level of fidelity.  The primary function of SaltProc is to 
+manage material streams while
+SERPENT 2 performs most of the computationally heavy work, namely neutron 
+transport and depletion
+calculations. Saltproc is defined as a python class, where each material stream 
+is defined as a isotopic atomic density
+vector variable. This allows tracking of time-sensitive material streams such 
+as the
+$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
+parameters, such as the reprocessing interval and removal efficiency.  In 
+addition, SaltProc provides a set of functions for each stream: read and write 
+isotopic data in/from database, separate out specific isotopes from stream with 
+defined efficiency, feed in specific isotopes to stream, and maintain constant 
+number density of specific nuclide in the core. These attributes and functions 
+are crucial to simulate the operation of a complex, multi-zone, multi-fluid 
+\gls{MSR} and are universal for myriad reactor systems.
 
-Saltproc is currently in active development in Github (https://github.com/ arfc/saltproc), and has unit tests and Travis continuous integration for sustainable development. There is also documentation
-generated through Sphinx document generator for ease of use. We plan to implement
-user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
+Saltproc is currently in active development in Github (https://github.com/ 
+arfc/saltproc), and has unit tests and Travis continuous integration for 
+sustainable development. There is also documentation
+generated through Sphinx document generator for ease of use. We plan to 
+implement
+user-defined reprocessing scheme definition, two-region \gls{MSR} modeling 
+capabilities,
 and decay modeling in future releases.
 
-Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
-coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
-contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, criticality 
-cycles, total heating power, and boundary conditions.
-After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
+Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation 
+algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
+SaltProc reads an external SERPENT 2 template file which is defined by the 
+user. This file contains input cards with parameters such as geometry,
+moderator and construction materials isotopic composition, neutron population, 
+criticality cycles, total heating power, and boundary conditions.
+After the depletion calculation, SaltProc reads the depleted fuel composition 
+file (\texttt{
 .bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
-composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
-multi-zone simplified assembly, or a full core.
-This flexibiliity allows the user to perform simulations of varying fidelity and computational 
-intensity.
-\begin{figure}[ht!] % replace 't' with 'b' to 
-  \centering
+composition isotopic vector in an HDF5 database. SaltProc only stores and edits 
+the isotopic composition of the fuel stream,
+which makes SaltProc a flexible tool to model any geometry: an infinite medium, 
+a unit cell, a multi-zone simplified assembly, or a full core.
+This flexibiliity allows the user to perform simulations of varying fidelity 
+and computational intensity.
+\begin{figure}[ht!] % replace 't' with 'b' to \centering
   \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
@@
 \end{figure}
-SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
-materials.
-At the end of a each depletion step, SaltProc reads the depleted compositions and tracks each material stream individually.
-Following this, it applies chemical separation functions to fuel stream vectors.
-These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition file for the next depletion calculation.
+SaltProc can manage as many material streams as desired. It also may work with 
+multiple depletion materials. At the end of a each depletion step, SaltProc 
+reads the depleted compositions and tracks each material stream individually. 
+Following this, it applies chemical separation functions to fuel stream 
+vectors. These vectors then form a matrix (isotopics x timesteps) which 
+SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition 
+file for the next depletion calculation.
 
-Saltproc datasets are timseries, meaning that every value is recorded every timestep. The 
-datasets SaltProc produces are listed below,
+Saltproc datasets are timseries, meaning that every value is recorded every 
+timestep. The datasets SaltProc produces are listed below,
 where the values inside the parenthesis are the dataset sizes:
@@
 
-Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core at an equilibrium condition, after fission products have built up in the fuel salt during years if operation.
-Isotopic composition of the fuel salt continues change slightly even after decades of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration (e.g., vary less than 1\% over several years).
-In contrast, from the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile materials number density).
-During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an equilibrium state.
-A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates, fission product removal rates, and corresponding core safety parameters are constant in time.
+Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core 
+at an equilibrium condition, after fission products have built up in the fuel 
+salt during years if operation. Isotopic composition of the fuel salt continues 
+change slightly even after decades of operation, but the dominant nuclides that 
+have significant impact to the neutronic behavior tend to reach an equilibrium 
+concentration (e.g., vary less than 1\% over several years). In contrast, from 
+the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt 
+composition undergoes significant changes (e.g., changes in fission products, 
+minor actinides, and fissile materials number density). During this period, the 
+material feeds and removals should be optimized for the fastest \gls{MSBR} 
+transition to an equilibrium state. A faster transition simplifies the reactor 
+operation because, at equilibrium, the fissile and fertile feed rates, fission 
+product removal rates, and corresponding core safety parameters are constant in 
+time.
 
-In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts.
-These rates need not be constant in SaltProc.
-They can be defined as piecewise functions or set to respond conditions in the core.
-For instance, SaltProc might increase the fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
-These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}.
-In summary, the development approach of SaltProc focused on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.
+In addition, SaltProc is able to define time-dependent material feed and 
+removal rates to investigate the their impacts. These rates need not be 
+constant in SaltProc. They can be defined as piecewise functions or set to 
+respond conditions in the core. For instance, SaltProc might increase the 
+fissile material feeding rate if the effective multiplication factor, 
+$k_{eff}$, falls below a specific limit (e.g., 1.002).
+These capabilities allow SaltProc to analyze fuel cycle of a generic 
+liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc 
+focused on producing a generic, flexible and expandable tool to give the 
+SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel 
+cycle analysis as well as simulate a myriad of online refueling and fuel 
+reprocessing systems.

### 2018-08-13 introduction.tex
grammar and whatnot

@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} 
-in the 1950s and was operated in the 1960s. More recently, \gls{MSR} was 
-included in the six advanced reactor concepts that have been chosen by the 
-Generation IV International Forum (GIF) for further research and development. 
+The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
+in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
+\glspl{MSR} amon the six advanced reactor concepts promising for further 
+research and development.
 \glspl{MSR} offer significant improvements ``in the four broad areas of 
@@
 formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
-improve inherent safety by using liquid coolant which is also a fuel.
+improve inherent safety by using liquid fuel.
 
@@
  materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
- elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is 
- circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
- This innovation leads to immediate advantages over traditional, solid-fueled, 
- reactors. These include near-atmospheric pressure in the primary loop, 
- relatively high coolant temperature, outstanding neutron economy, a high level 
- of inherent safety, reduced fuel preprocessing, and the ability to 
+ elements}F$_3$) combine with carrier salts to form a liquid fuel that 
+ circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}.  
+ Immediate advantages over traditional, solid-fueled, reactors include 
+ near-atmospheric pressure in the primary loop, 
+ relatively high coolant temperature, outstanding neutron economy, improved 
+ safety parameters, reduced fuel preprocessing, and the ability to 
  continuously remove fission products and add fissile and/or fertile elements 
  \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
- early 1970s by \gls{ORNL} specifically to realize the promise of the thorium 
+ early 1970s by \gls{ORNL} to explore the promise of the thorium 
  fuel cycle, which uses natural thorium instead of enriched uranium. With 
- continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively 
- realize advantages of the thorium fuel cycle because the $^{233}$U bred from 
+ continuous fuel reprocessing, the \gls{MSBR}
+ realizes the advantages of the thorium fuel cycle because the $^{233}$U bred from 
  $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
@@
  ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
- ($\tau_{1/2}$=26.967d).} being recycled back to the core 
- \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a 
- melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
+ ($\tau_{1/2}$=26.967d).} recycled back to the core 
+ \cite{betzler_modeling_2016}. The chosen fuel salt, 
+ LiF-BeF$_2$-ThF$_4$-UF$_4$, has a $499^\circ$C melting point, a low vapor 
+ pressure at operating temperatures, 
  and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 

### 2018-08-13 introduction.tex
huff edits

@@
 
-Modeling liquid-fueled systems with existing neutron transport and depletion 
-tools is challenging because most of these tools are designed for the 
-solid-fueled reactors simulation. The fuel material flows and potential online 
-separations or feeds of specific elements or nuclides are the main challenges
-of liquid-fueled systems. Furthermore, no established tool for liquid-fueled 
-\gls{MSR} neutronics and fuel cycle evaluation exist, though internally 
-developed tools from universities and research institutions can approximate 
-online refueling \cite{serp_molten_2014}. The foundation for these tools was 
-based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated 
-neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into 
-operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and 
-reprocessing system design. More recent research efforts in Europe and Asia 
-mainly focus on fast spectrum reactor fuel cycle analysis and couple external 
-tools to neutron transport and depletion codes take into account continuous 
-feeds and removals in \glspl{MSR}. Four of these efforts are listed in 
-table~\ref{tab:fs_codes}.
+Liquid-fueled systems present a challenge to existing neutron transport and 
+depletion tools which are typically designed to simulate solid-fueled reactors.  
+To handle the material flows and potential online removal and feed of 
+liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
+integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
+\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
+\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
+this approach, recent tools from universities and research institutions can 
+approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
+in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis 
+and couple external tools to neutron transport and depletion codes take into 
+account continuous feeds and removals in \glspl{MSR}. Four of these efforts are 
+listed in table~\ref{tab:fs_codes}.
 

### 2018-08-13 introduction.tex
huff edits

@@
 approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
-in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis 
-and couple external tools to neutron transport and depletion codes take into 
-account continuous feeds and removals in \glspl{MSR}. Four of these efforts are 
-listed in table~\ref{tab:fs_codes}.
+in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis. 
+These  couple external tools to neutron transport while depletion codes take into 
+account continuous feeds and removals in \glspl{MSR}. A summary of recent 
+efforts are listed in table~\ref{tab:fs_codes}.
 

### 2018-08-13 introduction.tex
grammar mostly

@@
 
-Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 
+Methods (1, 3, 4) simulate some form of reactivity control, and methods (1, 4, 
 5, 6, 8, 9) use a set of all nuclides in depletion calculations.
 
-Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where 
-material is moved to or from the core at all times (continuous) or at specific 
+Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which 
+material moves to and from the core at all times (continuous) or at specific 
 time steps (batch). To account for batch discharge, a depletion tool must 
@@
 composition (after removal of discarded materials and addition of 
-fissile/fertile materials). Accounting for a continuous removal or addition is 
-more difficult because it requires adding a term to the Bateman equations. In 
-SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set 
-of Bateman equations using spectrum-averaged fluxes and cross sections 
-generated from a deterministic transport calculation. Methods (1, 4, 8) model 
-true continuous feeds and removals, while other methods employ a batch-wise 
-approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based 
-script for SCALE/TRITON which uses a semi-continuous batch process to simulate 
-a continuous reprocessing. This tool models salt treatment, separations, 
-discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small 
-time steps to simulate continuous reprocessing and deplete the fuel salt 
-\cite{powers_new_2013}.
+fissile/fertile materials). Accounting for continuous removal or addition  
+presents a greater challenge since it requires adding a term to the Bateman 
+equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} 
+solves a set of Bateman equations using spectrum-averaged fluxes and cross 
+sections generated from a deterministic transport calculation. Methods (1, 4, 
+8) model true continuous feeds and removals, while other methods employ a 
+batch-wise approach. \gls{ORNL} researchers have developed ChemTriton, a 
+Python-based script for SCALE/TRITON which uses a semi-continuous batch process 
+to simulate a continuous reprocessing. ChemTriton models salt treatment, 
+separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON 
+model over small time steps to simulate continuous reprocessing and deplete the 
+fuel salt \cite{powers_new_2013}.
 
@@
 simplified unit-cell geometry because depletion computations for a many-year 
-fuel cycle are computationally expesive even for simple models.
+fuel cycle are computationally expensive even for simple models.
 
-Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: 
-one for salt channels, one for two salt plena above and below the core and the 
-last cell for the annulus, consequently, two-region reactor core was 
+Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
+one for salt channels, one for the salt plena above and below the core and the 
+last cell for the annulus, consequently, the two-region reactor core was 
 approximated by one region with averaged fuel/moderator ratio 
@@
 \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
-betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and 
+betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
 clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
@@
 (i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
-(i.e. \gls{MSRE}). A two-region \gls{MSBR} must be simulated using a whole-core 
-model to represent different neutron transport in the inner and outer regions 
-of the core, because most fissions happens in the inner region while breeding 
-occurs in the outer zone.
+(i.e. \gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
+model to capture different neutron transport characteristics in the inner and 
+outer regions of the core. In particular, most fissions happens in the inner 
+region while breeding occurs in the outer zone.
 
@@
 employed it to study the material isotopic evolution of the \gls{MSFR}. The 
-developed extension directly takes into account the effects of online fuel 
+developed extension directly accounts for the effects of online fuel 
 reprocessing on depletion calculations and features a reactivity control 
@@
 liquid-fueled \gls{MSR} operation 
-\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the 
-application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which 
-represents the continuation of the work presented in 
-\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
-of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
-the equilibrium core composition and core depletion. The additional objective 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
+application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
+extension of the work presented in 
+\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
+analyze \gls{MSBR} neutronics and fuel cycle to find 
+the equilibrium core composition. The additional objective 
 is to compare predicted operational and safety parameters of the \gls{MSBR} at 
@@
 
-The \gls{MSBR} complex geometry is hard to describe in software input, and, 
+The complex \gls{MSBR} geometry is challenging to describe in software input, and, 
 usually, researchers make significant geometric simplifications to model it 
-\cite{park_whole_2015}. Note that this study leverages extensive computational 
-resources to avoid these geometric approximations and accurately capture 
-breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
-Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
-related to circulating liquid fuel, is not treated here.
+\cite{park_whole_2015}. This study leverages extensive computational 
+resources to avoid these geometric approximations in order to accurately capture 
+breeding behavior.

### 2018-08-14 methods.tex
proper citation

@@
 systems with solid fuel. Liquid-fueled systems ability to continuously remove 
-fission products and add fissile and/or fertile elements is the main challenge 
+fission products and add fissile and/or fertile elements is sthe main challenge 
 for depletion simulations. SaltProc takes into account online separations and 
-feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and 
-depletion code.
+feeds using the SERPENT 2 continuous-energy Monte Carlo neutron transport and 
+depletion code.  All calculations presented in this study were performed using 
+SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
 
@@
 core region and transports that heat to the primary heat exchanger by way of 
-the primary salt pump. In the active core region, the salt flows through 
-channels in moderating and reflecting graphite blocks. Salt at about 
+the primary salt pump. In the active core region, the fuel salt flows through 
+channels in moderating and reflecting graphite blocks. Fuel salt at
 565$^{\circ}$C enters the central manifold at the bottom via four 
@@
 
-Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the 
-\gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" 
+Figure~\ref{fig:serpent_plan_view} shows the configuration of the 
+\gls{MSBR} vessel, including the ``fission" (zone I) and ``breeding" 
 (zone II) regions inside the vessel. The core has two radial zones bounded by a 
 solid cylindrical graphite reflector and the vessel wall. The central zone, 
-zone I, in which 13\% of the volume is fuel salt and 87\% graphite. Zone I 
+zone I, in which 13\% of the volume is fuel salt and 87\% graphite, is
 composed of 1,320 graphite cells, 2 graphite control rods, and 2 
@@
 
-Since reactor graphite experiences significant dimensional changes due to 
-neutron irradiation, the reactor core was designed for periodic replacement. 
-Based on the irradiation experimental data from \gls{MSRE}, core graphite 
-lifetime is about 4 years and reflector graphite lifetime is 30 years 
-\cite{robertson_conceptual_1971}.
-
 \begin{figure}[hbp!] % replace 't' with 'b' to \centering
@@
 
-Moreover, it was decided to remove and install the core graphite as an assembly 
-rather than by individual blocks, because it is relatively easier for 
-maintenance personnel and has lower probability of radioactive elements escape 
-due to used blocks damage during removal. In addition, handling the core as an 
-assembly also allows the replacement core to be carefully preassembled and 
-tested under factory conditions.
+\begin{figure}[t!] % replace 't' with 'b' to \centering
+  \includegraphics[width=\textwidth]{ser_zone_II.png}
+  \caption{Detailed view of \gls{MSBR} zone II model.  
+          Yellow represents fuel salt, purple represents graphite, and aqua represents the reactor vessel.}
+  \label{fig:serpent_zoneII}
+\end{figure}
+
+Since reactor graphite experiences significant dimensional changes due to 
+neutron irradiation, the reactor core was designed for periodic replacement. 
+Based on the experimental irradiation data from \gls{MSRE}, the core graphite 
+lifetime is about 4 years and reflector graphite lifetime is 30 years 
+\cite{robertson_conceptual_1971}.
 
@@
 top of the vessel for cooling the top head and axial reflector. 
-Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular 
+Figure~\ref{fig:serpent_zoneII} also shows :w
+the 5.08-cm-wide annular 
 space between the removable core graphite in zone II-B and the permanently 
 mounted reflector graphite. This annulus consists entirely of fuel salt, 
-provides space for moving the core assembly, helps compensate the elliptical 
+provides space for moving the core assembly, helps compensate for the elliptical 
 dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
 surface of the graphite reflector blocks. In this work, all figures of the core 
-were generated using the built-in SERPENT 2 plotter. All calculations presented 
-in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 
-nodes.
-
-\begin{figure}[t!] % replace 't' with 'b' to \centering
-  \includegraphics[width=\textwidth]{ser_zone_II.png}
-  \caption{Detailed view of \gls{MSBR} zone II model.}
-  \label{fig:serpent_zoneII}
-\end{figure}
+were generated using the built-in SERPENT 2 plotter.
 
@@
 reduce the peak damage flux and power density in the center of the core to 
-prevent local graphite damage. Zone I is well-moderated to achieve the desired 
-fission power density. Figure~\ref{fig:I_element_ref} demonstrates the 
+prevent local graphite damage.  Figure~\ref{fig:I_element_ref} shows the 
 elevation and plan views of graphite elements of zone I 
@@
 \cite{rykhlevskii_full-core_2017}.
+
 \begin{figure}[ht!] % replace 't' with 'b' to \centering
@@
   \caption{Graphite moderator elements for zone I 
-  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.  Yellow 
+  represents fuel salt, purple represents graphite, and aqua represents the 
+  reactor vessel.}
   \label{fig:I_element_ref}
@@
 Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
-radial reflector, zone II serves to diminish neutron leakage. This zone is 
-formed of two kinds of elements: large-diameter fuel channels (zone II-A) and 
+radial reflector, zone II serves to diminish neutron leakage. Two kinds of 
+elements form this zone: large-diameter fuel channels (zone II-A) and 
 radial graphite slats (zone II-B).
@@
 Zone II has 37\% fuel salt by volume and each element has a fuel channel 
-diameter of 6.604cm. The graphite elements for zone II-A are prismatic and have 
-elliptical-shaped dowels running axially between the prisms and needed to 
+diameter of 6.604cm. The graphite elements for zone II-A are prismatic with
+elliptical dowels running axially between the prisms. These dowels
 isolate the fuel salt flow in zone I from that in zone II. 
-Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite 
+Figure~\ref{fig:II_element_ref} shows the shapes and dimensions of these graphite 
 elements and their SERPENT model. Zone II-B elements are rectangular slats 
@@
 serves as a blanket to achieve the best performance: a high breeding ratio and 
-a low fissile inventory. The neutron energy spectrum in zone II is made harder 
-to enhance the rate of thorium resonance capture relative to the fission rate, 
+a low fissile inventory. The harder neutron energy spectrum in zone II 
+enhances the rate of thorium resonance capture relative to the fission rate, 
 thus limiting the neutron flux in the outer core zone and reducing the neutron 
@@
 
-The main challenge was to accurately represent zone II-B because it has 
-irregular elements with sophisticated shapes. From the \gls{ORNL} report 
-\cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 
-irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels. 
+The sophisticated, irregular shapes of the fuel elements challenge an accurate 
+representation of zone II-B.  
+The suggested design \cite{robertson_conceptual_1971} of zone II-B has 8 
+irregularly-shaped graphite elements as well as dozens of salt channels. 
 These graphite elements were simplified into right-circular cylindrical shapes  
@@
 exactly 37\%, so that this simplification did not considerably change the core 
-neutronics. This is the only simplification made to the \gls{MSBR} geometry in 
-this work.
+neutronics. Simplyfying the eight edge channels was te only simplification made 
+to the \gls{MSBR} geometry in this work.
 
@@
   \caption{Graphite moderator elements for zone II-A 
-  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.  Yellow 
+  represents fuel salt and purple represents graphite.}
   \label{fig:II_element_ref}
@@
 \subsubsection{Material composition and normalization parameters}
-The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ 
+The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
 Hastelloy-N is very common in reactors now but have been studied and developed 
-at \gls{ORNL} in a program that started in 1950s.} are materials unique of the 
-\gls{MSBR} and were created at \gls{ORNL}. The initial fuel salt used the same 
+at \gls{ORNL} in a program that started in 1950s.} 
+are all materials created at \gls{ORNL} specifically for the \gls{MSBR}.
+The initial fuel salt used the same 
 density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
@@
 
-For cross section generation, JEFF-3.1.2 neutron library was employed 
-\cite{oecd/nea_data_bank_jeff-3.1.2_2014}. The specific temperature was fixed 
+The JEFF-3.1.2 neutron library provided cross section generation, 
+\cite{oecd/nea_data_bank_jeff-3.1.2_2014}. 
+The specific temperature was fixed 
 for each material to correctly model the Doppler-broadening of resonance peaks 
@@
 the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been 
-applied to SERPENT model without any modification. Table~\ref{tab:msbr_tab} is 
+applied to the SERPENT model without any modification. Table~\ref{tab:msbr_tab} is 
 a summary of the major \gls{MSBR} parameters used by this model 
@@
 \subsection{Online reprocessing method}
-Removing specific chemical elements from a molten salt is a complicated task 
-that requires intelligent design (e.g., chemical separations equipment design, 
+Removing specific chemical elements from a molten salt 
+requires intelligent design (e.g., chemical separations equipment design, 
 fuel salt flows to equipment) and has a considerable economic cost. All 
@@
 list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
-temporary removal of protactinium from the salt or other regulation of the 
-actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
+temporary removal of protactinium or other regulation of the 
+actinide inventory \cite{ahmad_neutronics_2015}.
 
@@
   \includegraphics[width=\textwidth]{periodic_map.png}
-  \caption{Processing options for \gls{MSR} fuels 
-  \cite{ahmad_neutronics_2015}.}
+  \caption{Processing options for \gls{MSR} fuels. 
+          Reproduced from \cite{ahmad_neutronics_2015} where it was adapted 
+          from a chart courtesy of Nicolas 
+          Raymond, www.freestock.ca.}
   \label{fig:periodic_tab}
@@
 
-The tool structure and capabilities of SaltProc are similar to ChemTriton tool 
-for SCALE
-developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte 
+The tool structure and capabilities of SaltProc are similar to the ChemTriton tool 
+developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled with Monte 
 Carlo SERPENT 2

### 2018-08-14 methods.tex
fixing stuff

@@
 to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
-system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 
+system must separate $^{233}$Pa from the molten-salt fuel over 3 
 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
 primary loop. This feature allows the reactor to avoid neutron losses to 
-protactinium, keeps fission products to a very low level, and increases the 
+protactinium, lowers in-core fission product inventory, and increases the 
 efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 

### 2018-08-14 methods.tex
grammar

@@
 The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store 
-data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
-for SEPRENT output file parsing and nuclide naming. It is an open-source tool 
+data, and the PyNE Nuclear Engineering Toolkit \cite{scopatz_pyne:_2012}
+for SEPRENT output file parsing and nuclide naming. SaltProc is an open-source tool 
 that uses a semi-continuous approach to simulate continuous feeds and removals 
-in the \gls{MSR}.
+in \glspl{MSR}.
 

### 2018-08-14 results.tex
grammar in results section

@@
 \section{Results}
-The SaltProc online reprocessing simulation code is demonstrated in four 
+The SaltProc online reprocessing simulation package is demonstrated in four 
 applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the 
@@
 node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
-total computational time for achieving equilibrium composition was 
+total computational time for calculating the equilibrium composition was 
 approximately 9,900 node-hours (18 core-years.)
@@
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} demonstrates the effective multiplication factors 
+Figure~\ref{fig:keff} shows the effective multiplication factors 
 obtained using SaltProc and SERPENT 2. The effective multiplication factors are 
@@
 Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
-``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
+cycle time\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
         amount of time required to remove 100\% of a target nuclide from a fuel 
@@
 online reprocessing strategy.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=\textwidth]{keff.png}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
+  model for a 60-year reactor operation. The confidence interval 
+  $\sigma=\pm15pcm$ is shaded.}
+  \label{fig:keff}
+\end{figure}
 
@@
 one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
-applying feeds and removals, and this increases accordingly since major reactor 
+applying feeds and removals. $K_{eff}$ this increases accordingly since major reactor 
 poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
-from the protactinium decay tank is added.  \begin{figure}[ht!] % replace 't' 
-        with 'b' to \centering
-  \includegraphics[width=\textwidth]{keff.png}
-  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
-  model for a 60-year reactor operation. The confidence interval 
-  $\sigma=\pm15pcm$ is shaded.}
-  \label{fig:keff}
-\end{figure}
+from the protactinium decay tank is added.
+
 Additionally, the presence of rubidium, strontium, cesium, and barium in the 
@@
 separately for each isotope by average atomic density, at the beginning of each 
-depletion time step. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and 
+depletion time step. The concentrations of $^{233}$U, $^{232}$Th, $^{233}$Pa, and 
 $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of 
 operation. Particularly, $^{233}$U number density fluctuates less than 0.8\% in 
-the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium 
+the time interval from 16 to 20 years of operation. Hence, a quasi-equilibrium 
 state was achieved after 16 years of reactor operation.
@@
 $^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
-in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile 
-isotopes in the core. In the end of considered operational time the core 
+in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
+isotopes in the core. In the end of the considered operational time, the core 
 contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
@@
 resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV. 
-Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the 
-neutron energy spectrum in this range. Furthermore, in the central core region 
+Furthermore, in the central core region 
 (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years 
-of reactor operation. In contrast, in the outer core region (zone II) a similar 
-spectral shift takes place at a reduced scale. This resuls is in a good 
+of reactor operation. Meanwhile, in the outer core region (zone II) a similar 
+spectral shift takes place at a reduced scale. This results is in a good 
 agreement with original ORNL report \cite{robertson_conceptual_1971} and most 
@@
 \end{figure}
+
 \subsection{Power and breeding distribution}
@@
 normalized power distribution of the \gls{MSBR} quarter core which is the same 
-at both states. For both the initial and equilibrium compositions, fission 
+at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 
 primarily occurs in the center of the core, namely zone I. The spectral shift 
 during reactor operation results in different power fractions at startup and 
-equilibrium, but most of the power is still generated in zone I. 
+equilibrium, but most of the power is still generated in zone I at equilibrium. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
-temperature feedback is an expansion of matterial that is heated. When the fuel 
+temperature feedback is an expansion of material that is heated. When the fuel 
 salt temperature increases, the density of the salt decreases, but at the same 
@@
 The fuel temperature coefficient (FTC) is negative for both initial and 
-equilibrium fuel compositon due to thermal Doppler broadening of the resonance 
+equilibrium fuel composition due to thermal Doppler broadening of the resonance 
 capture cross sections in the thorium and is in a good agreement with earlier 
@@
 worths were calculated for various positions to separately estimate control 
-(graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system 
-worth. Control rod integral worth is approximately 28 cents and stays almost 
-constant during reactor operation. The safety rod integral worth decreases by  
-16.2\% during 20 years of operation because of neutron spectrum hardening and 
-absorber accumulation in proximity to reactivity control system rods. This 16\% 
-decline in control system worth should be taken into account in \gls{MSBR} 
-accident analysis and safety justification.
+graphite moderator rods\footnote{In \cite{robertson_conceptual_1971}, the 
+graphite rods are referred to as ``control'' rods.}, safety (B$_4$C) rod, and 
+the whole reactivity control system worth. Control rod integral worth is 
+approximately 28 cents and stays almost constant during reactor operation. The 
+safety rod integral worth decreases by  16.2\% during 20 years of operation 
+because of neutron spectrum hardening and absorber accumulation in proximity to 
+reactivity control system rods. This 16\% decline in control system worth 
+should be taken into account in \gls{MSBR} accident analysis and safety 
+justification.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 equilibrium. As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is 
-softer for the initial state. Neutron spectrum hardening causes the fast 
+softer at the beginning of reactor life. Neutron spectrum hardening causes the fast 
 fission to increase through the core lifetime. The opposite is true for the 
@@
 $^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
-calculated for 60 years of reactor operation. The the $^{232}$Th feed rate 
+calculated for 60 years of reactor operation. The $^{232}$Th feed rate 
 fluctuates significantly as a result of the batch-wise nature of this online 

### 2018-08-15 introduction.tex
proper citation
amon --> among

@@
 in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
-\glspl{MSR} amon the six advanced reactor concepts promising for further 
+\glspl{MSR} among the six advanced reactor concepts promising for further 
 research and development.
@@
 betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
-clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
+approach misrepresents the two-region breeder reactor concept. The unit-cell or 
 one-region models may produce reliable results for homogeneous reactor cores 

### 2018-08-15 abstract.tex

@@
 demand for tools to analyze these systems. This paper introduces a Python 
-script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
+package, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
 changing isotopic composition of an irradiated fuel salt. SaltProc couples with 
-the Monte Carlo code, SERPENT 2, for neutron transport and depletion 
+the Monte Carlo neutron transport software, SERPENT 2, for neutron transport and depletion 
 calculations. SaltProc capabilities was illuminated for full-core depletion in 

### 2018-08-15 acks.tex

@@
 Kathryn D. Huff directed and 
-supervised the work, conceived and designed the simulations, wrote the paper, 
+supervised the work, conceived and designed the simulations, 
 contributed to the software product, and reviewed drafts of the paper.  Prof. 

### 2018-08-15 conclusion.tex

--- 2018-05-18 conclusion.tex
@@
-\section{Conclusion}
+\section{Discussion and conclusions}
 
-Condensed copy-paste of the thesis conclusion.
-\begin{itemize}
-    \item Full-core model which is better the most exists. Importance of full-core approach for multi-region designs.
-    \item K-eff dynamics and explanation of this dynamics.
-    \item Spectral shift explanation.
-    \item Why spectral shift causes safety parameters worsening and power profile changes.
-    \item $^{232}$Th rate is in a good agreement with references.
-\end{itemize}
+This work introduces the open source \gls{MSR} simulation package SaltProc. 
+SaltProc expands the capability of SERPENT 2, the continuous-energy Monte Carlo 
+code to include online reprocessing in liquid-fueled \gls{MSR} operation 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
+generic geometry modeling, multi-flow capabilities, time-dependent feed and 
+removal rates, and the ability to specify removal efficiency. The main goal of 
+this work has 
+been to demonstrate the SaltProc capability to find the equilibrium fuel salt 
+composition (where equilibrium is defined as when the number densities of major 
+isotopes vary less than 1\% over several years). A secondary goal has been to 
+compare predicted operational and safety parameters (e.g., neutron energy 
+spectrum, power and breeding distribution, temperature coefficients of 
+reactivity) of the \gls{MSBR} at startup and equilibrium state. A tertiary goal 
+has been to demonstrate benefits of continuous fission products removal for 
+thermal \gls{MSR} design.
 
-\FloatBarrier
+Toward these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} 
+was implemented in SERPENT 2. The purpose of the full-core model instead of 
+the simplified single-cell model \cite{betzler_molten_2017, 
+rykhlevskii_online_2017, betzler_fuel_2018} was to precisely describe the 
+two-region \gls{MSBR} concept design sufficiently to accurately represent 
+breeding in the outer core zone. When running depletion calculations, the most 
+important fission products and $^{233}$Pa are removed and fertile/fissile 
+materials are added to the fuel salt every 3 days.  Meanwhile, the removal 
+interval for the rare earths, volatile fluorides, and seminoble metals was more 
+than month which causes effective multiplication factor fluctuation.
+
+\subsection{Equilibrium state search}
+The results of this study indicate that the effective multiplication factor 
+slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 
+6 years of operation. At the same time, the concentration of $^{233}$U, $^{232}$Th, 
+$^{233}$Pa, $^{232}$Pa stabilizes after approximately 2500 days of operation. 
+Particularly, $^{233}$U number density equilibrates\footnote{fluctuates less 
+than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state 
+after 16 years of operation. On the other hand, a wide diversity of nuclides, 
+including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
+absorbers (e.g. $^{234}$U), continue accumulating in the core. The current work results 
+show that a true equilibrium composition cannot exist but the balance
+between strong absorber accumulation and new fissile material 
+production can be achieved to keep the reactor critical.
+
+\subsection{Spectral shift}
+We also found that the neutron energy spectrum grows harder as equilibrium 
+approaches because significant heavy fission products accumulate in 
+the \gls{MSBR} core. Moreover, the neutron energy spectrum in the central core 
+region is much softer than in the outer core region due to lower 
+moderator-to-fuel ratio in the outer zone, and this distribution remains stable 
+during reactor operation. Finally, the epithermal or thermal spectrum is needed 
+to effectively breed $^{233}$U from $^{232}$Th because radiative capture cross 
+section of thorium-232 monotonically decreases from $10^{-10}$ MeV to $10^{-5}$ 
+MeV. A harder spectrum in the outer core region tends to significantly increase 
+resonance absorption in thorium and decrease the absorptions in fissile and 
+structural materials.
+
+The spatial power distribution in the \gls{MSBR} shows that 98\% of the fission 
+power is generated in central zone I, and neutron energy spectral shift did not 
+cause any notable changes in a power distribution. The spatial distribution of 
+neutron capture reaction rate for fertile $^{232}$Th, corresponding to breeding in 
+the core, confirms that most of the breeding occurs in an outer, 
+undermoderated, region of the \gls{MSBR} core. Finally, the average $^{232}$Th 
+refill rate throughout 60 years of operation is approximately 2.40 kg/day or 
+100 g/GWh$_e$.
+
+We compared the safety parameters for the initial fuel loading and 
+equilibrium compositions using the SERPENT 2 Monte Carlo code. 
+The total temperature coefficient 
+is large and negative at startup and equilibrium but the magnitude decreases 
+throughout reactor operation from $-3.10$ to $-0.94$ pcm/K as the spectrum 
+hardens. The moderator 
+temperature coefficient is positive and also decreases during fuel depletion. 
+From reactivity control system efficiency analysis, showed the safety rod integral 
+worth decreases by approximately 16.2\% over 16 years of operation, while 
+graphite rod integral worth remains constant. Summing up, neutron energy 
+spectrum hardening during fuel salt depletion has an undesirable impact on 
+\gls{MSBR} stability and controllability, and should be taken into 
+consideration in further analysis of accident transient scenarios.
+
+\subsection{Benefits of fission product removal}
+
+For thermal spectrum \gls{MSBR} removal of volatile gases, noble metals, and 
+rare earths from a fuel salt benefits core performance.
+Moreover, immediate removal of volatile gases (e.g., xenon) and noble metals 
+increased reactivity by approximately 7500 pcm over a 10-year 
+timeframe. In contrast, the effect of relatively slower removal of rare earth 
+elements (every 50 days cycle instead of 3 days) has less impact (5500 pcm) on 
+the core reactivity after 10 years of operation. In sum, additional study 
+is needed to establish neutronic  and economic tradeoffs of removing each element.
+
+\subsection{Future work}
+Continued SaltProc-SERPENT coupled simulation efforts could progress in a 
+number of different directions. First optimization of reprocessing parameters (e.g. time step, feeding rate, 
+protactinium removal rate) could establish the best fuel utilization, breeding 
+ratio, or safety characteristics for various designs. This might be performed with a parameter sweeping 
+outer loop which would change an input parameter by a small increment, run the 
+simulation and analyze output to determine optimal configuration. Alternatively, 
+the existing RAVEN optimization framework \cite{alfonsi_raven_2013} might be 
+employed for such optimization studies.
+
+Only the batch-wise online reprocessing approach has been treated in this 
+work. However, the SERPENT 2 Monte Carlo code was recently extended for 
+continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
+This extension must be verified against existing SaltProc/SERPENT or 
+ChemTriton/SCALE packages, and could be employed for simulating immediate removal of 
+fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
+core lifetime and breeding efficiency. Finally, using the built-in SERPENT 2 
+Monte Carlo code online reprocessing \& refueling material burnup routine would 
+significantly speed up computer-intensive full-core depletion simulations.
+
+Lastly, this work enables accident safety analysis such as multi-physics 
+simulation of the \gls{MSBR} with the coupled 
+neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}. 
+The existing full-core SERPENT 2 model and equilibrium fuel material 
+composition would be employed to generate problem-oriented nuclear data 
+libraries for further usage in accident transient analysis. The final goal of 
+this effort is to develop a fast-running computational model which could study 
+the dynamic behavior of generic \glspl{MSR}, performing detailed safety 
+analysis and design optimization for a variety of reactor concepts.

### 2018-08-15 methods.tex

@@
 The tool structure and capabilities of SaltProc are similar to the ChemTriton tool 
-developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled with Monte 
-Carlo SERPENT 2
-software which allows to simulate online reprocessing for irregular full-core 
-geometry with high level of fidelity.  The primary function of SaltProc is to 
+developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled 
+with the Monte Carlo SERPENT 2
+software to simulate online reprocessing for irregular full-core 
+geometry with high fidelity.  The primary function of SaltProc is to 
 manage material streams while
-SERPENT 2 performs most of the computationally heavy work, namely neutron 
+SERPENT 2 performs the computationally heavy work, namely neutron 
 transport and depletion
@@
 number density of specific nuclide in the core. These attributes and functions 
-are crucial to simulate the operation of a complex, multi-zone, multi-fluid 
-\gls{MSR} and are universal for myriad reactor systems.
+are crucial to simulating the operation of a complex, multi-zone, multi-fluid 
+\gls{MSR} and sufficiently general to represent myriad reactor systems.
 
-Saltproc is currently in active development in Github (https://github.com/ 
-arfc/saltproc), and has unit tests and Travis continuous integration for 
+SaltProc, currently in active development in Github (https://github.com/ 
+arfc/saltproc), leverages unit tests and continuous integration for 
 sustainable development. There is also documentation
-generated through Sphinx document generator for ease of use. We plan to 
+generated through Sphinx document generator for ease of use. In future 
+releases, we plan to 
 implement
-user-defined reprocessing scheme definition, two-region \gls{MSR} modeling 
+support for entirely user-customized reprocessing strategies, two-region \gls{MSR} modeling 
 capabilities,
-and decay modeling in future releases.
+and decay modeling.
 
 Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation 
-algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the 
-user. This file contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, 
-criticality cycles, total heating power, and boundary conditions.
+algorithm coupling SaltProc and SERPENT 2. To perform a depletion step, 
+SaltProc reads a user-defined SERPENT 2 template file. This file contains input 
+cards with parameters such as geometry, material, isotopic composition, neutron 
+population, criticality cycles, total heating power, and boundary conditions.  
 After the depletion calculation, SaltProc reads the depleted fuel composition 
-file (\texttt{
-.bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits 
-the isotopic composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, 
-a unit cell, a multi-zone simplified assembly, or a full core.
+file (\texttt{ .bumat1}) and stores the depleted composition isotopic vector in 
+an HDF5 database.
+
+SaltProc only stores and edits the isotopic composition of 
+the fuel stream, which makes SaltProc a flexible tool to model any geometry: an 
+infinite medium, a unit cell, a multi-zone simplified assembly, or a full core.
 This flexibiliity allows the user to perform simulations of varying fidelity 
 and computational intensity.
+
 \begin{figure}[ht!] % replace 't' with 'b' to \centering
   \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
-  \caption{Flow chart for the Saltproc python-based tools.}
+  \caption{Flow chart for the Saltproc python package.}
   \label{fig:saltproc_flow}
@@
 In addition, SaltProc is able to define time-dependent material feed and 
-removal rates to investigate the their impacts. These rates need not be 
+removal rates to investigate their impacts. These rates need not be 
 constant in SaltProc. They can be defined as piecewise functions or set to 
-respond conditions in the core. For instance, SaltProc might increase the 
+respond to conditions in the core. For instance, SaltProc might increase the 
 fissile material feeding rate if the effective multiplication factor, 

### 2018-08-15 results.tex

@@
   effective multiplication factor for full-core \gls{MSBR} model with removal 
-  of different fission product groups over 10 years of operation. The 
+  of various fission product groups over 10 years of operation. The 
   confidence interval $\pm\sigma	$ is shaded.}

### 2018-08-17 introduction.tex
Resolved issue #8 . Number and depletion code removed from Table 1. Numbers in text substituted with references

--- 2018-08-13 introduction.tex
@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
-in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
-\glspl{MSR} amon the six advanced reactor concepts promising for further 
-research and development.
-\glspl{MSR} offer significant improvements ``in the four broad areas of 
-sustainability, economics, safety and reliability, and proliferation resistance 
-and physical protection" \cite{doe_technology_2002}. To achieve the goals 
-formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
-improve inherent safety by using liquid fuel.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
+More recently, \gls{MSR} was included in the six advanced reactor concepts that have been chosen by the Generation IV International Forum (GIF) for further research and development.
+\glspl{MSR} offer significant improvements ``in the four broad areas of sustainability, economics, safety and reliability, and proliferation resistance and physical protection" \cite{doe_technology_2002}.
+To achieve the goals formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and improve inherent safety by using liquid coolant which is also a fuel.
 
- In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
- materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
- elements}F$_3$) combine with carrier salts to form a liquid fuel that 
- circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}.  
- Immediate advantages over traditional, solid-fueled, reactors include 
- near-atmospheric pressure in the primary loop, 
- relatively high coolant temperature, outstanding neutron economy, improved 
- safety parameters, reduced fuel preprocessing, and the ability to 
- continuously remove fission products and add fissile and/or fertile elements 
- \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
- early 1970s by \gls{ORNL} to explore the promise of the thorium 
- fuel cycle, which uses natural thorium instead of enriched uranium. With 
- continuous fuel reprocessing, the \gls{MSBR}
- realizes the advantages of the thorium fuel cycle because the $^{233}$U bred from 
- $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
- $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
- ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
- ($\tau_{1/2}$=26.967d).} recycled back to the core 
- \cite{betzler_modeling_2016}. The chosen fuel salt, 
- LiF-BeF$_2$-ThF$_4$-UF$_4$, has a $499^\circ$C melting point, a low vapor 
- pressure at operating temperatures, 
- and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
- In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
- quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
- cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
- for transmutation of spent fuel from current \glspl{LWR}.
+ In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e.
+UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
+These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
+The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium.
+With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
+Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}.
+The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle.
+Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.
 
-Liquid-fueled systems present a challenge to existing neutron transport and 
-depletion tools which are typically designed to simulate solid-fueled reactors.  
-To handle the material flows and potential online removal and feed of 
-liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
-integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
-\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
-\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
-this approach, recent tools from universities and research institutions can 
-approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
-in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis. 
-These  couple external tools to neutron transport while depletion codes take into 
-account continuous feeds and removals in \glspl{MSR}. A summary of recent 
-efforts are listed in table~\ref{tab:fs_codes}.
+Modeling liquid-fueled systems with existing neutron transport and depletion tools is challenging because most of these tools are designed for the solid-fueled reactors simulation.
+The fuel material flows and potential online separations or feeds of specific elements or nuclides are the main challenges
+of liquid-fueled systems.
+Furthermore, no established tool for liquid-fueled \gls{MSR} neutronics and fuel cycle evaluation exist, though internally developed tools from universities and research institutions can approximate online refueling \cite{serp_molten_2014}.
+The foundation for these tools was based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.
+More recent research efforts in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis and couple external tools to neutron transport and depletion codes take into account continuous feeds and removals in \glspl{MSR}.
+Four of these efforts are listed in table~\ref{tab:fs_codes}.
 
@@
 \caption{Tools and methods for fast spectrum system fuel cycle analysis.}
-\begin{tabularx}{\textwidth}{ x | s | s | m | x } \hline & Neutronic code  & 
-Depletion code    & \qquad Authors & Spectra   \\
+\begin{tabularx}{\textwidth}{ m | b | x } 
+\hline Neutronic code    & \qquad Authors & Spectra   \\
 \hline
-1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM 
-\cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et 
-al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
+\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
 \hline
-2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et 
-al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
+ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
 \hline
-3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     
-& Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
+KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
 \hline
-4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et 
-al.}, 2013 \cite{aufiero_extended_2013} & fast \\
+SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
 \hline
-5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & 
-Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
+MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
 \hline
-6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et 
-al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, 
-jeong_equilibrium_2016}& thermal\\
+\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
 \hline
-7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton 
-\cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 
-2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& 
-thermal\\
+SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
 \hline
-8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 
-\cite{rykhlevskii_online_2017} & thermal\\
+SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
 \hline
-9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} 
-\cite{nuttin_potential_2005}&thermal  \\ \hline
+\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
 \end{tabularx}
@@
 
-Most of these methods are also applicable to thermal spectrum \glspl{MSR}. 
-Additional tools developed specifically for thermal \gls{MSR} applications are 
-also listed in table~\ref{tab:fs_codes}.
+Most of these methods are also applicable to thermal spectrum \glspl{MSR}. Additional tools developed specifically for thermal \gls{MSR} applications are also listed in table~\ref{tab:fs_codes}.
 
-Methods (1, 3, 4) provide some form of reactivity control, and methods (1, 4, 
-5, 6, 8, 9) use a set of all nuclides in depletion calculations.
+References \cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,aufiero_extended_2013} provide some form of reactivity control, and methods \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,ahmad_neutronics_2015, park_whole_2015, jeong_equilibrium_2016,rykhlevskii_online_2017,nuttin_potential_2005} use a set of all nuclides in depletion calculations.
 
-Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where 
-material is moved to or from the core at all times (continuous) or at specific 
-time steps (batch). To account for batch discharge, a depletion tool must 
-remove some or all material at specified intervals. This requires the burn-up 
-simulation to stop at a given time and restart with a new liquid fuel 
-composition (after removal of discarded materials and addition of 
-fissile/fertile materials). Accounting for a continuous removal or addition is 
-more difficult because it requires adding a term to the Bateman equations. In 
-SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set 
-of Bateman equations using spectrum-averaged fluxes and cross sections 
-generated from a deterministic transport calculation. Methods (1, 4, 8) model 
-true continuous feeds and removals, while other methods employ a batch-wise 
-approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based 
-script for SCALE/TRITON which uses a semi-continuous batch process to simulate 
-a continuous reprocessing. This tool models salt treatment, separations, 
-discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small 
-time steps to simulate continuous reprocessing and deplete the fuel salt 
-\cite{powers_new_2013}.
+Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch).
+To account for batch discharge, a depletion tool must remove some or all material at specified intervals.
+This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
+Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations.
+In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation.
+Methods listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013, rykhlevskii_online_2017} model true continuous feeds and removals, while other methods employ a batch-wise approach.
+\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing.
+This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
-described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
-simplified unit-cell geometry because depletion computations for a many-year 
-fuel cycle are computationally expesive even for simple models.
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in \cite{park_whole_2015, jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}.
+Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
 
-Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: 
-one for salt channels, one for two salt plena above and below the core and the 
-last cell for the annulus, consequently, two-region reactor core was 
-approximated by one region with averaged fuel/moderator ratio 
-\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
-al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
-\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
-betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and 
-clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
-one-region models may produce reliable results for homogeneous reactor cores 
-(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
-(i.e. \gls{MSRE}). A two-region \gls{MSBR} must be simulated using a whole-core 
-model to represent different neutron transport in the inner and outer regions 
-of the core, because most fissions happens in the inner region while breeding 
-occurs in the outer zone.
+Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: one for salt channels, one for two salt plena above and below the core and the last cell for the annulus, consequently, two-region reactor core was approximated by one region with averaged fuel/moderator ratio \cite{nuttin_potential_2005}.
+A similar approach was used by Powers \emph{et al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and clearly misrepresent the two-region breeder reactor concept.
+The unit-cell or one-region models may produce reliable results for homogeneous reactor cores (i.e.
+\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e.
+\gls{MSRE}).
+A two-region \gls{MSBR} must be simulated using a whole-core model to represent different neutron transport in the inner and outer regions of the core, because most fissions happens in the inner region while breeding occurs in the outer zone.
 
-Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
-employed it to study the material isotopic evolution of the \gls{MSFR}. The 
-developed extension directly takes into account the effects of online fuel 
-reprocessing on depletion calculations and features a reactivity control 
-algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
-version of the deterministic ERANOS-based EQL3D procedure 
-\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
-isotopic evolution. We employed this extended SERPENT 2 for a simplified 
-unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
-results which contradict existing \gls{MSBR} depletion simulations 
-\cite{jeong_equilibrium_2016}.
+Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and employed it to study the material isotopic evolution of the \gls{MSFR}.
+The developed extension directly takes into account the effects of online fuel reprocessing on depletion calculations and features a reactivity control algorithm.
+The extended version of SERPENT 2 was assessed against a dedicated version of the deterministic ERANOS-based EQL3D procedure \cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt isotopic evolution.
+We employed this extended SERPENT 2 for a simplified unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained results which contradict existing \gls{MSBR} depletion simulations \cite{jeong_equilibrium_2016}.
 
-The present work introduces the online reprocessing simulation code, SaltProc, 
-which expands the capability of the continuous-energy Monte Carlo Burnup 
-calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
-liquid-fueled \gls{MSR} operation 
-\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the 
-application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which 
-represents the continuation of the work presented in 
-\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
-of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
-the equilibrium core composition and core depletion. The additional objective 
-is to compare predicted operational and safety parameters of the \gls{MSBR} at 
-both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
-determined and \gls{MSBR} fuel cycle performance will be analyzed.
+The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
+It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}.
+The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion.
+The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states.
+Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.
 
-The \gls{MSBR} complex geometry is hard to describe in software input, and, 
-usually, researchers make significant geometric simplifications to model it 
-\cite{park_whole_2015}. Note that this study leverages extensive computational 
-resources to avoid these geometric approximations and accurately capture 
-breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
-Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
-related to circulating liquid fuel, is not treated here.
+The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}.
+Note that this study leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
+This article only discusses liquid-fueled \glspl{MSR}.
+Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.

### 2018-08-21 introduction.tex
Paragraph about batch-wise and truly continuous approaches rewritten to resove issue #9

@@
 
-Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch).
-To account for batch discharge, a depletion tool must remove some or all material at specified intervals.
-This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
+Liquid-fueled \gls{MSR} designs have online separations and feeds, where material is moved to or from the core at specific time steps (batch) or continuously.
+In batch-wise approach the burn-up simulation stops at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
+\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which the batch-wise to simulate a continuous reprocessing.
+This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON depletion simulation over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
+Methods listed in references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} and current work employ a batch-wise approach.
+
 Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations.
 In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation.
-Methods listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013, rykhlevskii_online_2017} model true continuous feeds and removals, while other methods employ a batch-wise approach.
-\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing.
-This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
+Approaches listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} model true continuous feeds and removals.
 

### 2018-08-21 methods.tex
First METHODS paragraph reduced and state only main challenge of MSR modeling and our tool. Closed issue #10

--- 2018-08-14 methods.tex
@@
 
-Liquid-fueled system modeling with contemporary reactor physics codes is 
-difficult because most of these codes were developed for analyzing solid-fueled 
-reactors. In fact, world-wide commercial reactors fleet today is represented by 
-systems with solid fuel. Liquid-fueled systems ability to continuously remove 
-fission products and add fissile and/or fertile elements is sthe main challenge 
-for depletion simulations. SaltProc takes into account online separations and 
-feeds using the SERPENT 2 continuous-energy Monte Carlo neutron transport and 
-depletion code.  All calculations presented in this study were performed using 
-SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+Liquid-fueled systems ability to continuously remove fission products and add fissile and/or fertile elements is the main challenge for depletion simulations.
+Introduced in this work Python-package, SaltProc, takes into account online separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and depletion code.
 
 \subsection{Molten Salt Breeder Reactor design and model description}
-The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm. It 
-contains a molten fluoride fuel-salt mixture that generates heat in the active 
-core region and transports that heat to the primary heat exchanger by way of 
-the primary salt pump. In the active core region, the fuel salt flows through 
-channels in moderating and reflecting graphite blocks. Fuel salt at
-565$^{\circ}$C enters the central manifold at the bottom via four 
-40.64-cm-diameter nozzles and flows upward through channels in the lower plenum 
-graphite. The fuel salt exits at the top at about 704$^{\circ}$C through four 
-equally spaced nozzles which connect to the salt-suction pipes leading to 
-primary circulation pumps. The fuel salt drain lines connect to the bottom of 
-the reactor vessel inlet manifold.
+The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
+It contains a molten fluoride fuel-salt mixture that generates heat in the active core region and transports that heat to the primary heat exchanger by way of the primary salt pump.
+In the active core region, the salt flows through channels in moderating and reflecting graphite blocks.
+Salt at about 565$^{\circ}$C enters the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows upward through channels in the lower plenum graphite.
+The fuel salt exits at the top at about 704$^{\circ}$C through four equally spaced nozzles which connect to the salt-suction pipes leading to primary circulation pumps.
+The fuel salt drain lines connect to the bottom of the reactor vessel inlet manifold.
 
-Figure~\ref{fig:serpent_plan_view} shows the configuration of the 
-\gls{MSBR} vessel, including the ``fission" (zone I) and ``breeding" 
-(zone II) regions inside the vessel. The core has two radial zones bounded by a 
-solid cylindrical graphite reflector and the vessel wall. The central zone, 
-zone I, in which 13\% of the volume is fuel salt and 87\% graphite, is
-composed of 1,320 graphite cells, 2 graphite control rods, and 2 
-safety\footnote{ These rods needed for emergency shutdown only.} rods. The 
-under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, 
-surrounds the zone I core region and serves to diminish neutron leakage. Zones 
-I and II are surrounded radially and axially by fuel salt 
-(figure~\ref{fig:serpent_zoneII}). This space for fuel is necessary for 
-injection and flow of molten salt.
+Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel.
+The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall.
+The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
+Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods needed for emergency shutdown only.} rods.
+The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
+Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}).
+This space for fuel is necessary for injection and flow of molten salt.
 
-\begin{figure}[hbp!] % replace 't' with 'b' to \centering
+Since reactor graphite experiences significant dimensional changes due to neutron irradiation, the reactor core was designed for periodic replacement.
+Based on the irradiation experimental data from \gls{MSRE}, core graphite lifetime is about 4 years and reflector graphite lifetime is 30 years \cite{robertson_conceptual_1971}.
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{view_serpent.png}
-  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in 
-  this work.}
+  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in this work.}
   \label{fig:serpent_plan_view}
@@
 
-\begin{figure}[t!] % replace 't' with 'b' to \centering
+Moreover, it was decided to remove and install the core graphite as an assembly rather than by individual blocks, because it is relatively easier for maintenance personnel and has lower probability of radioactive elements escape due to used blocks damage during removal.
+In addition, handling the core as an assembly also allows the replacement core to be carefully preassembled and tested under factory conditions.
+
+There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, one of which is illustrated in Figure~\ref{fig:serpent_zoneII}.
+The holes in the centers are for the core lifting rods used during the core replacement operations.
+These holes also allow a portion of the fuel salt to flow to the top of the vessel for cooling the top head and axial reflector.
+Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
+This annulus consists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
+In this work, all figures of the core were generated using the built-in SERPENT 2 plotter.
+All calculations presented in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+
+\begin{figure}[t!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{ser_zone_II.png}
-  \caption{Detailed view of \gls{MSBR} zone II model.  
-          Yellow represents fuel salt, purple represents graphite, and aqua represents the reactor vessel.}
+  \caption{Detailed view of \gls{MSBR} zone II model.}
   \label{fig:serpent_zoneII}
@@
 
-Since reactor graphite experiences significant dimensional changes due to 
-neutron irradiation, the reactor core was designed for periodic replacement. 
-Based on the experimental irradiation data from \gls{MSRE}, the core graphite 
-lifetime is about 4 years and reflector graphite lifetime is 30 years 
-\cite{robertson_conceptual_1971}.
+\subsubsection{Core zone I}
+The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
+Zone I has 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
 
-There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, 
-one of which is illustrated in Figure~\ref{fig:serpent_zoneII}. The holes in 
-the centers are for the core lifting rods used during the core replacement 
-operations. These holes also allow a portion of the fuel salt to flow to the 
-top of the vessel for cooling the top head and axial reflector. 
-Figure~\ref{fig:serpent_zoneII} also shows :w
-the 5.08-cm-wide annular 
-space between the removable core graphite in zone II-B and the permanently 
-mounted reflector graphite. This annulus consists entirely of fuel salt, 
-provides space for moving the core assembly, helps compensate for the elliptical 
-dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
-surface of the graphite reflector blocks. In this work, all figures of the core 
-were generated using the built-in SERPENT 2 plotter.
-
-\subsubsection{Core zone I}
-The central region of the core, called zone I, is made up of graphite elements, 
-each $10.16$cm$\times$10.16cm$\times$396.24cm. Zone I has 4 channels for 
-control rods: two for graphite rods which both regulate and shim during normal 
-operation, and two for backup safety rods consisting of boron carbide clad to 
-assure sufficient negative reactivity for emergency situations.
-
-These graphite elements have a mostly rectangular shape with lengthwise ridges 
-at each corner that leave space for salt flow elements. Various element sizes 
-reduce the peak damage flux and power density in the center of the core to 
-prevent local graphite damage.  Figure~\ref{fig:I_element_ref} shows the 
-elevation and plan views of graphite elements of zone I 
-\cite{robertson_conceptual_1971} and their SERPENT model 
-\cite{rykhlevskii_full-core_2017}.
-
-\begin{figure}[ht!] % replace 't' with 'b' to \centering
+These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements.
+Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Zone I is well-moderated to achieve the desired fission power density.
+Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{zone_I_element_ref.png}
-  \caption{Graphite moderator elements for zone I 
-  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.  Yellow 
-  represents fuel salt, purple represents graphite, and aqua represents the 
-  reactor vessel.}
+  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:I_element_ref}
@@
 \subsubsection{Core zone II}
-Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
-radial reflector, zone II serves to diminish neutron leakage. Two kinds of 
-elements form this zone: large-diameter fuel channels (zone II-A) and 
-radial graphite slats (zone II-B).
+Zone II which is undermoderated, surrounds zone I.
+Combined with the bounding radial reflector, zone II serves to diminish neutron leakage.
+This zone is formed of two kinds of elements: large-diameter fuel channels (zone II-A) and radial graphite slats (zone II-B).
 
-Zone II has 37\% fuel salt by volume and each element has a fuel channel 
-diameter of 6.604cm. The graphite elements for zone II-A are prismatic with
-elliptical dowels running axially between the prisms. These dowels
-isolate the fuel salt flow in zone I from that in zone II. 
-Figure~\ref{fig:II_element_ref} shows the shapes and dimensions of these graphite 
-elements and their SERPENT model. Zone II-B elements are rectangular slats 
-spaced far enough apart to provide the 0.37 fuel salt volume fraction. The 
-reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension 
-(average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}. Zone II 
-serves as a blanket to achieve the best performance: a high breeding ratio and 
-a low fissile inventory. The harder neutron energy spectrum in zone II 
-enhances the rate of thorium resonance capture relative to the fission rate, 
-thus limiting the neutron flux in the outer core zone and reducing the neutron 
-leakage \cite{robertson_conceptual_1971}.
+Zone II has 37\% fuel salt by volume and each element has a fuel channel diameter of 6.604cm.
+The graphite elements for zone II-A are prismatic and have elliptical-shaped dowels running axially between the prisms and needed to isolate the fuel salt flow in zone I from that in zone II.
+Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite elements and their SERPENT model.
+Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
+The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}.
+Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
+The neutron energy spectrum in zone II is made harder to enhance the rate of thorium resonance capture relative to the fission rate, thus limiting the neutron flux in the outer core zone and reducing the neutron leakage \cite{robertson_conceptual_1971}.
 
-The sophisticated, irregular shapes of the fuel elements challenge an accurate 
-representation of zone II-B.  
-The suggested design \cite{robertson_conceptual_1971} of zone II-B has 8 
-irregularly-shaped graphite elements as well as dozens of salt channels. 
-These graphite elements were simplified into right-circular cylindrical shapes  
-with central channels. Figure~\ref{fig:serpent_zoneII} illustrates this core 
-region in the SERPENT model. The volume of fuel salt in zone II was kept 
-exactly 37\%, so that this simplification did not considerably change the core 
-neutronics. Simplyfying the eight edge channels was te only simplification made 
-to the \gls{MSBR} geometry in this work.
+The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
+From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels.
+These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
+Figure~\ref{fig:serpent_zoneII} illustrates this core region in the SERPENT model.
+The volume of fuel salt in zone II was kept exactly 37\%, so that this simplification did not considerably change the core neutronics.
+This is the only simplification made to the \gls{MSBR} geometry in this work.
 
-\begin{figure}[ht!] % replace 't' with 'b' to \centering
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{zone_II_element_ref.png}
-  \caption{Graphite moderator elements for zone II-A 
-  \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.  Yellow 
-  represents fuel salt and purple represents graphite.}
+  \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:II_element_ref}
@@
 \subsubsection{Material composition and normalization parameters}
-The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
-Hastelloy-N is very common in reactors now but have been studied and developed 
-at \gls{ORNL} in a program that started in 1950s.} 
-are all materials created at \gls{ORNL} specifically for the \gls{MSBR}.
-The initial fuel salt used the same 
-density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
-(71.75-16-12-0.25 mole \%) as the \gls{MSBR} design 
-\cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
-enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
-becomes tritium upon neutron capture.
+The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
+The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.75-16-12-0.25 mole \%) as the \gls{MSBR} design \cite{robertson_conceptual_1971}.
+The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
 
-The JEFF-3.1.2 neutron library provided cross section generation, 
-\cite{oecd/nea_data_bank_jeff-3.1.2_2014}. 
-The specific temperature was fixed 
-for each material to correctly model the Doppler-broadening of resonance peaks 
-when SERPENT generates the problem-dependent nuclear data library. The isotopic 
-composition of each material at the initial state was described in detail in 
-the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been 
-applied to the SERPENT model without any modification. Table~\ref{tab:msbr_tab} is 
-a summary of the major \gls{MSBR} parameters used by this model 
-\cite{robertson_conceptual_1971}.
+For cross section generation, JEFF-3.1.2 neutron library was employed \cite{oecd/nea_data_bank_jeff-3.1.2_2014}.
+The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when SERPENT generates the problem-dependent nuclear data library.
+The isotopic composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to SERPENT model without any modification.
+Table~\ref{tab:msbr_tab} is a summary of the major \gls{MSBR} parameters used by this model \cite{robertson_conceptual_1971}.
 
@@
         %\centering
-        \caption{Summary of principal data for MSBR 
-        \cite{robertson_conceptual_1971}.}
+        \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
         \begin{tabularx}{\textwidth}{ s  s}
@@
                 Thermal capacity of reactor           		& 2250 MW(t)
-                \\ Net electrical output                 		& 1000 
-        MW(e) \\  Net thermal efficiency        				
-        & 44.4\%
-                \\  Salt volume fraction in central zone I		& 0.13
-                \\ Salt volume fraction in outer zone II       & 0.37
-                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
-        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
-        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
-        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
-        salt                   & 1303.7 kg	\\ Fuel salt components                  
-                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
-        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                 \\ 
-                Fuel salt density                    & 3.35 g/cm$^3$
+                Net electrical output                 		& 1000 MW(e) 
+                \\  
+                Net thermal efficiency        				& 44.4\%
+                \\  
+                Salt volume fraction in central zone I		& 0.13
+                \\ 
+                Salt volume fraction in outer zone II       & 0.37
+                \\ 
+                Fuel salt inventory (Zone I)                & 8.2 m$^3$	
+                \\ 
+                Fuel salt inventory (Zone II)               & 10.8 m$^3$	
+                \\ 
+                Fuel salt inventory (annulus)               & 3.8 m$^3$	
+                \\  
+                Total fuel salt inventory                   & 48.7 m$^3$	
+                \\ 
+                Fissile mass in fuel salt                   & 1303.7 kg	
+                \\ 
+                Fuel salt components                  & 
+                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	
+                \\  
+                Fuel salt composition                 & 
+                71.75-16-12-0.25 mole\%
+                \\
+                Fuel salt density                    & 
+                3.35 g/cm$^3$
                 \\ \hline
@@
 \subsection{Online reprocessing method}
-Removing specific chemical elements from a molten salt 
-requires intelligent design (e.g., chemical separations equipment design, 
-fuel salt flows to equipment) and has a considerable economic cost. All 
-liquid-fueled \gls{MSR} designs involve varying levels of online fuel 
-processing. Minimally, volatile gaseous fission products (e.g. Kr, Xe) escape 
-from the fuel salt during routine reactor operation and must be captured. 
-Additional systems might be used to enhance removal of those elements. Most 
-designs also call for the removal of noble and rare earth metals from the core 
-since these metals act as neutron poisons. Some designs suggest a more complex 
-list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
-temporary removal of protactinium or other regulation of the 
-actinide inventory \cite{ahmad_neutronics_2015}.
+Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
+All liquid-fueled \gls{MSR} designs involve varying levels of online fuel processing.
+Minimally, volatile gaseous fission products (e.g.
+Kr, Xe) escape from the fuel salt during routine reactor operation and must be captured.
+Additional systems might be used to enhance removal of those elements.
+Most designs also call for the removal of noble and rare earth metals from the core since these metals act as neutron poisons.
+Some designs suggest a more complex list of elements to process (figure ~\ref{fig:periodic_tab}), including the temporary removal of protactinium from the salt or other regulation of the actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
 
-\begin{figure}[htp!] % replace 't' with 'b' to \centering
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{periodic_map.png}
-  \caption{Processing options for \gls{MSR} fuels. 
-          Reproduced from \cite{ahmad_neutronics_2015} where it was adapted 
-          from a chart courtesy of Nicolas 
-          Raymond, www.freestock.ca.}
+  \caption{Processing options for \gls{MSR} fuels \cite{ahmad_neutronics_2015}.}
   \label{fig:periodic_tab}
@@
 \subsubsection{Fuel material flows}
-The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
-which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
-design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
-noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
-Protactinium presents a challenge, since it has a large absorption cross 
-section in the thermal energy spectrum. Accordingly, $^{233}$Pa is continuously 
-removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
-system must separate $^{233}$Pa from the molten-salt fuel over 3 
-days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
-primary loop. This feature allows the reactor to avoid neutron losses to 
-protactinium, lowers in-core fission product inventory, and increases the 
-efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
-full list of nuclides and the cycle times used for modeling salt treatment and 
-separations \cite{robertson_conceptual_1971}.
+The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U.
+Furthermore, the \gls{MSBR} design requires online reprocessing to remove all poisons (e.g.
+$^{135}$Xe), noble metals, and gases (e.g.
+$^{75}$Se, $^{85}$Kr) every 20 seconds.
+Protactinium presents a challenge, since it has a large absorption cross section in the thermal energy spectrum.
+Accordingly, $^{233}$Pa is continuously removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U without poisoning the reactor.
+The reactor reprocessing system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop.
+This feature allows the reactor to avoid neutron losses to protactinium, keeps fission products to a very low level, and increases the efficiency of $^{233}$U breeding.
+Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and the cycle times used for modeling salt treatment and separations \cite{robertson_conceptual_1971}.
 
@@
         \centering
-        \caption{The effective cycle times for protactinium and fission 
-        products removal (reproduced from \cite{robertson_conceptual_1971}).}
+        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
         \begin{tabularx}{\textwidth}{ x | s | x }
-        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
-                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
-                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
-                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
+        \hline 
+        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
+        Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
+        \qquad & Eu & 500 days \\ 
+        Noble metals & Se, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
         Seminoble metals & Zr, Cd, In, Sn & 200 days \\
-        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
-        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
-                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
-                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
+        Gases & Kr, Xe & 20 sec \\ 
+        Volatile fluorides & Br, I & 60 days \\
+        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
+        Salt discard & Th, Li, Be, F & 3435 days \\ 
+        Protactinium & $^{233}$Pa & 3 days \\ 
+        Higher nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
         \end{tabularx}
-        %\footnotetext{Chemical processing plant and gas separation system 
-        %removing chemical elements (not isotopes) only. Isotopes instead of 
-        %elements listed because other isotopes are short-lived and might be 
-        %ignored.}
+        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only.
+Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
         \label{tab:reprocessing_list}
 \end{table}
-Th removal rates vary among nuclides in this reactor concept which dictate the 
-necessary resolution of depletion calculations. If the depletion time intervals 
-are very short, an enormous number of depletion steps are required to obtain 
-the equilibrium composition. On the other hand, if the depletion  calculation 
-time interval is too long, the impact of short-lived fission products is not 
-captured. To compromise, the time interval for depletion calculations in this 
-model was selected as 3 days to correlate with the removal interval of 
-$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
-fraction of $^{232}$Th.
+Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations.
+If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition.
+On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured.
+To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.
 
 \subsubsection{The SaltProc modeling and simulation code}
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to 
-expand SERPENT 2
- depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous 
- reprocessing.
-The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store 
-data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
-for SEPRENT output file parsing and nuclide naming. It is an open-source tool 
-that uses a semi-continuous approach to simulate continuous feeds and removals 
-in the \gls{MSR}.
+The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to expand SERPENT 2
+ depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
+The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
+simulate continuous feeds and removals in the \gls{MSR}.
 
-The tool structure and capabilities of SaltProc are similar to the ChemTriton tool 
-developed in \gls{ORNL} for SCALE \cite{powers_new_2013}. SaltProc is coupled with Monte 
-Carlo SERPENT 2
-software which allows to simulate online reprocessing for irregular full-core 
-geometry with high level of fidelity.  The primary function of SaltProc is to 
-manage material streams while
-SERPENT 2 performs most of the computationally heavy work, namely neutron 
-transport and depletion
-calculations. Saltproc is defined as a python class, where each material stream 
-is defined as a isotopic atomic density
-vector variable. This allows tracking of time-sensitive material streams such 
-as the
-$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
-parameters, such as the reprocessing interval and removal efficiency.  In 
-addition, SaltProc provides a set of functions for each stream: read and write 
-isotopic data in/from database, separate out specific isotopes from stream with 
-defined efficiency, feed in specific isotopes to stream, and maintain constant 
-number density of specific nuclide in the core. These attributes and functions 
-are crucial to simulate the operation of a complex, multi-zone, multi-fluid 
-\gls{MSR} and are universal for myriad reactor systems.
+The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
+developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
+software which allows to simulate online reprocessing for irregular full-core geometry with 
+high level of fidelity.  The primary function of SaltProc is to manage material streams while
+SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
+calculations. Saltproc is defined as a 
+python class, where each material stream is defined as a isotopic atomic density
+vector variable. This allows tracking of time-sensitive material streams such as the
+$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
+reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
+for each stream: read and write isotopic data in/from database, separate out specific isotopes 
+from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
+number density of specific nuclide in the core. These attributes and functions are crucial to 
+simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
+myriad reactor systems.
 
-Saltproc is currently in active development in Github (https://github.com/ 
-arfc/saltproc), and has unit tests and Travis continuous integration for 
-sustainable development. There is also documentation
-generated through Sphinx document generator for ease of use. We plan to 
-implement
-user-defined reprocessing scheme definition, two-region \gls{MSR} modeling 
-capabilities,
+Saltproc is currently in active development in Github (https://github.com/ arfc/saltproc), and has unit tests and Travis continuous integration for sustainable development. There is also documentation
+generated through Sphinx document generator for ease of use. We plan to implement
+user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
 and decay modeling in future releases.
 
-Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation 
-algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the 
-user. This file contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, 
-criticality cycles, total heating power, and boundary conditions.
-After the depletion calculation, SaltProc reads the depleted fuel composition 
-file (\texttt{
+Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
+coupled SaltProc and SERPENT 2. To perform a depletion step,
+SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
+contains input cards with parameters such as geometry,
+moderator and construction materials isotopic composition, neutron population, criticality 
+cycles, total heating power, and boundary conditions.
+After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
 .bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits 
-the isotopic composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, 
-a unit cell, a multi-zone simplified assembly, or a full core.
-This flexibiliity allows the user to perform simulations of varying fidelity 
-and computational intensity.
-\begin{figure}[ht!] % replace 't' with 'b' to \centering
+composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
+composition of the fuel stream,
+which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
+multi-zone simplified assembly, or a full core.
+This flexibiliity allows the user to perform simulations of varying fidelity and computational 
+intensity.
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=0.75\textwidth]{saltproc_flowchart.pdf}
@@
 \end{figure}
-SaltProc can manage as many material streams as desired. It also may work with 
-multiple depletion materials. At the end of a each depletion step, SaltProc 
-reads the depleted compositions and tracks each material stream individually. 
-Following this, it applies chemical separation functions to fuel stream 
-vectors. These vectors then form a matrix (isotopics x timesteps) which 
-SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition 
-file for the next depletion calculation.
+SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
+materials.
+At the end of a each depletion step, SaltProc reads the depleted compositions and tracks each material stream individually.
+Following this, it applies chemical separation functions to fuel stream vectors.
+These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition file for the next depletion calculation.
 
-Saltproc datasets are timseries, meaning that every value is recorded every 
-timestep. The datasets SaltProc produces are listed below,
+Saltproc datasets are timseries, meaning that every value is recorded every timestep. The 
+datasets SaltProc produces are listed below,
 where the values inside the parenthesis are the dataset sizes:
@@
 
-Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core 
-at an equilibrium condition, after fission products have built up in the fuel 
-salt during years if operation. Isotopic composition of the fuel salt continues 
-change slightly even after decades of operation, but the dominant nuclides that 
-have significant impact to the neutronic behavior tend to reach an equilibrium 
-concentration (e.g., vary less than 1\% over several years). In contrast, from 
-the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt 
-composition undergoes significant changes (e.g., changes in fission products, 
-minor actinides, and fissile materials number density). During this period, the 
-material feeds and removals should be optimized for the fastest \gls{MSBR} 
-transition to an equilibrium state. A faster transition simplifies the reactor 
-operation because, at equilibrium, the fissile and fertile feed rates, fission 
-product removal rates, and corresponding core safety parameters are constant in 
-time.
+Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core at an equilibrium condition, after fission products have built up in the fuel salt during years if operation.
+Isotopic composition of the fuel salt continues change slightly even after decades of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration (e.g., vary less than 1\% over several years).
+In contrast, from the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile materials number density).
+During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an equilibrium state.
+A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates, fission product removal rates, and corresponding core safety parameters are constant in time.
 
-In addition, SaltProc is able to define time-dependent material feed and 
-removal rates to investigate the their impacts. These rates need not be 
-constant in SaltProc. They can be defined as piecewise functions or set to 
-respond conditions in the core. For instance, SaltProc might increase the 
-fissile material feeding rate if the effective multiplication factor, 
-$k_{eff}$, falls below a specific limit (e.g., 1.002).
-These capabilities allow SaltProc to analyze fuel cycle of a generic 
-liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc 
-focused on producing a generic, flexible and expandable tool to give the 
-SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel 
-cycle analysis as well as simulate a myriad of online refueling and fuel 
-reprocessing systems.
+In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts.
+These rates need not be constant in SaltProc.
+They can be defined as piecewise functions or set to respond conditions in the core.
+For instance, SaltProc might increase the fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
+These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}.
+In summary, the development approach of SaltProc focused on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.

### 2018-08-22 methods.tex
deleted paragraph out of place

--- 2018-08-15 methods.tex
@@
 
-Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core 
-at an equilibrium condition, after fission products have built up in the fuel 
-salt during years if operation. Isotopic composition of the fuel salt continues 
-change slightly even after decades of operation, but the dominant nuclides that 
-have significant impact to the neutronic behavior tend to reach an equilibrium 
-concentration (e.g., vary less than 1\% over several years). In contrast, from 
-the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt 
-composition undergoes significant changes (e.g., changes in fission products, 
-minor actinides, and fissile materials number density). During this period, the 
-material feeds and removals should be optimized for the fastest \gls{MSBR} 
-transition to an equilibrium state. A faster transition simplifies the reactor 
-operation because, at equilibrium, the fissile and fertile feed rates, fission 
-product removal rates, and corresponding core safety parameters are constant in 
-time.
-
 In addition, SaltProc is able to define time-dependent material feed and 

### 2018-08-22 results.tex
Figure 8 has number density with no normalization #12

--- 2018-08-02 results.tex
@@
 \section{Results}
-The SaltProc online reprocessing simulation code is demonstrated in four 
-applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the 
-equilibrium core composition and core depletion, (2) studying operational and 
-safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that 
-in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated 
-outer core zone II works as a virtual ``blanket", reduces neutron leakage and 
-improves breeding ratio due to neutron energy spectral shift, and (4) 
-determining the effect of fission product removal on the core neutronics.
+The SaltProc online reprocessing simulation code is demonstrated in four applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion, (2) studying operational and safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated outer core zone II works as a virtual ``blanket", reduces neutron leakage and improves breeding ratio due to neutron energy spectral shift, and (4) determining the effect of fission product removal on the core neutronics.
 
-The neutron population per cycle and the number of active/inactive cycles were 
-chosen to obtain balance between reasonable uncertainty for a transport problem 
-($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective 
-multiplication factor) and computational time. The \gls{MSBR} depletion and 
-safety parameter computations were performed on 64 Blue Waters XK7 nodes (two 
-AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per 
-node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
-total computational time for achieving equilibrium composition was 
-approximately 9,900 node-hours (18 core-years.)
+The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective multiplication factor) and computational time.
+The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
+The total computational time for achieving equilibrium composition was approximately 9,900 node-hours (18 core-years.)
 
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} demonstrates the effective multiplication factors 
-obtained using SaltProc and SERPENT 2. The effective multiplication factors are 
-calculated after removing fission products listed in 
-Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
-``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
-        amount of time required to remove 100\% of a target nuclide from a fuel 
-salt.} which was fixed at 3 days for this work. The effective multiplication 
-factor fluctuates significantly as a result of the batch-wise nature of this 
-online reprocessing strategy.
+Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
+The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
+The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
 
-First, SERPENT calculates the effective multiplication factor for the beginning 
-of cycle time (fresh fuel composition for the first step). Next, it computes 
-the new fuel salt composition for the end of a 3-day depletion step. The 
-corresponding effective multiplication factor is much smaller than the previous 
-one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
-applying feeds and removals, and this increases accordingly since major reactor 
-poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
-from the protactinium decay tank is added.  \begin{figure}[ht!] % replace 't' 
-        with 'b' to \centering
+First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
+Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
+The corresponding effective multiplication factor is much smaller than the previous one.
+Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
+Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{keff.png}
-  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
-  model for a 60-year reactor operation. The confidence interval 
-  $\sigma=\pm15pcm$ is shaded.}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
   \label{fig:keff}
 \end{figure}
-Additionally, the presence of rubidium, strontium, cesium, and barium in the 
-core are disadvantageous to reactor physics. In fact, removal of these elements 
-every 3435 days causes the multiplication factor to jump by approximately 450 
-pcm, and limits using the batch approach for online reprocessing simulation. 
-Overall, the effective multiplication factor gradually decreases from 1.075 to 
-$k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of 
-irradiation.
+Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
+In fact, removal of these elements every 3435 days causes the multiplication factor to jump by approximately 450 pcm, and limits using the batch approach for online reprocessing simulation.
+Overall, the effective multiplication factor gradually decreases from 1.075 to $k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of irradiation.
 
 \subsection{Fuel salt composition dynamics}
-The analysis of the fuel salt composition evolution provides more comprehensive 
-information about the equilibrium state. Figure~\ref{fig:adens_eq} shows major 
-nuclides which have a strong influence on the reactor core physics normalized 
-separately for each isotope by average atomic density, at the beginning of each 
-depletion time step. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and 
-$^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of 
-operation. Particularly, $^{233}$U number density fluctuates less than 0.8\% in 
-the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium 
-state was achieved after 16 years of reactor operation.
-\begin{figure}[ht!] % replace 't' with 'b' to \centering
+The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
+Figure~\ref{fig:adens_eq} shows number density of major nuclides which have a strong influence on the reactor core physics.
+Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
+Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
+\begin{figure}[ht!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{major_isotopes_adens.png}
-  \caption{Number density of major nuclides during 60 years of reactor 
-  operation.}
+  \caption{Number density of major nuclides during 60 years of reactor operation.}
   \label{fig:adens_eq}
@@
 In contrast, a wide variety of nuclides, including fissile isotopes (e.g.
-$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
-in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile 
-isotopes in the core. In the end of considered operational time the core 
-contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
-($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
-atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
-isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
-production of new fissile materials in the core as well as $^{233}$U breeding 
-make it possible to compensate for negative effects of strong absorber 
-accumulation and keep the reactor critical.
-\begin{figure}[htp!] % replace 't' with 'b' to \centering
+$^{235}$U) and non-fissile strong absorbers (e.g.
+$^{234}$U), keep accumulating in the core.
+Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core.
+In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm).
+Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm.
+Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{fissile_short.png}
-  \caption{Number density of fissile in epithermal spectrum nuclides 
-  accumulation during the reactor operation.}
+  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
   \label{fig:fissile_short}
@@
 \subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
-full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
-neutron energy spectrum at equilibrium is harder than at startup due to 
-$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
-the core during reactor operation.  \begin{figure}[ht!] % replace 't' with 'b' 
-        to force it to \centering
-  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
-  spectrum normalized by unit lethargy for initial and equilibrium fuel salt 
-  composition.}
+Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV.
+The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum.png} 
+  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
   \label{fig:spectrum}
 \end{figure}
-Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal 
-neutrons than zone II, indicating that the majority of fissions occured in the 
-central part of the core. In the undermoderated zone II, the neutron energy 
-spectrum is harder which leads to more capture of neutrons by $^{232}$Th and 
-helps a achieve relatively high breeding ratio. Moreover, the (n,$\gamma$) 
-resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV. 
-Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the 
-neutron energy spectrum in this range. Furthermore, in the central core region 
-(zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years 
-of reactor operation. In contrast, in the outer core region (zone II) a similar 
-spectral shift takes place at a reduced scale. This resuls is in a good 
-agreement with original ORNL report \cite{robertson_conceptual_1971} and most 
-recent whole-core steady-state study \cite{park_whole_2015}.
+Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal neutrons than zone II, indicating that the majority of fissions occured in the central part of the core.
+In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.
+Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV.
+Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the neutron energy spectrum in this range.
+Furthermore, in the central core region (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years of reactor operation.
+In contrast, in the outer core region (zone II) a similar spectral shift takes place at a reduced scale.
+This resuls is in a good agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core steady-state study \cite{park_whole_2015}.
 
-It is important to obtain the epithermal and thermal spectra to produce 
-$^{233}$U from $^{232}$Th because the radiative capture cross section of 
-thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening 
-the spectrum tends to significantly increase resonance absorption in thorium 
-and decrease the absorptions in fissile and construction materials. Thus, a 
-significant amount fissile material will be needed to make the reactor 
-critical.  \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
-  \includegraphics[width=\textwidth]{spectrum_zones.png} \caption{Neutron flux 
-  energy spectrum in different core regions normalized by unit lethargy for the 
-  initial and equilibrium fuel salt composition.}
+It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV.
+Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
+Thus, a significant amount fissile material will be needed to make the reactor critical.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{spectrum_zones.png} 
+  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
   \label{fig:spectrum_zones}
@@
 \subsection{Neutron flux}
-Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
-neutron flux for both initial and equilibrium composition. The neutron flux has 
-the same shape for both compositions but the equilibrium case has a harder 
-spectrum. A significant spectral shift was observed for the central region of 
-the core (zone I) when for the outer region (zone II) it is negligible for fast 
-but notable for thermal neutrons. This neutron flux radial distribution is in a 
-good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
-Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
-studied for designing the reactivity control system.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
-  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
-  flux distribution for initial and equilibrium fuel salt composition.}
+Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition.
+The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum.
+A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons.
+This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
+Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{radial_flux.png} 
+  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
   \label{fig:radial_flux}
@@
 \subsection{Power and breeding distribution}
-Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for 
-initial and equilibrium fuel composition. Figure~\ref{fig:pow_den} reflects the 
-normalized power distribution of the \gls{MSBR} quarter core which is the same 
-at both states. For both the initial and equilibrium compositions, fission 
-primarily occurs in the center of the core, namely zone I. The spectral shift 
-during reactor operation results in different power fractions at startup and 
-equilibrium, but most of the power is still generated in zone I. 
+Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for initial and equilibrium fuel composition.
+Figure~\ref{fig:pow_den} reflects the normalized power distribution of the \gls{MSBR} quarter core which is the same at both states.
+For both the initial and equilibrium compositions, fission primarily occurs in the center of the core, namely zone I.
+The spectral shift during reactor operation results in different power fractions at startup and equilibrium, but most of the power is still generated in zone I.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Power generation fraction in each zone for initial and equilibrium 
-  state.}
+  \caption{Power generation fraction in each zone for initial and equilibrium state.}
 \begin{tabularx}{\textwidth}{ m | s | s } \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate 
-distribution for $^{232}$Th normalized by the total neutron flux for initial 
-and equilibrium states. The distribution reflects the spatial distribution of 
-$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
-$^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this 
-characteristic represents the breeding distribution in the \gls{MSBR} core. 
-Spectral shift does not cause significant changes in power nor in breeding 
-distribution. Even after 20 years of operation, most of the power still is 
-generated in zone I though the majority of $^{233}$Th is produced in zone II.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states.
+The distribution reflects the spatial distribution of $^{233}$Th production in the core.
+The thorium-232 then $\beta$-decays to $^{233}$Pa which is the precursor for $^{233}$U production.
+Accordingly, this characteristic represents the breeding distribution in the \gls{MSBR} core.
+Spectral shift does not cause significant changes in power nor in breeding distribution.
+Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
   \includegraphics[width=\textwidth]{power_distribution_eq.png} 
-  \caption{Normalized power density for both initial and equilibrium fuel salt 
-  composition.}
+  \caption{Normalized power density for both initial and equilibrium fuel salt composition.}
   \label{fig:pow_den}
 \end{figure}
-\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
   \includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
-  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux 
-  for both initial and equilibrium fuel salt composition.}
+  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
   \label{fig:breeding_den}
@@
 \subsection{Temperature coefficient of reactivity}
-Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated 
-in this work for both initial and equilibrium fuel composition, and compared 
-with original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
-Uncertainty for each temperature coefficient also appears in 
-Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
-temperature feedback is an expansion of matterial that is heated. When the fuel 
-salt temperature increases, the density of the salt decreases, but at the same 
-time, the total volume of fuel salt in the core remains constant because it is 
-bounded by the graphite. When the graphite temperature increases, the density 
-of graphite decreases creating additional space for fuel salt. To determine 
-temperature coefficients, the cross section temperatures for fuel and moderator 
-were changed from 900K to 1000K. Three different cases were considered:
+Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}.
+Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}.
+The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated.
+When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite.
+When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt.
+To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K.
+Three different cases were considered:
 \begin{enumerate}
@@
   \centering
-  \caption{Temperature coefficients of reactivity for initial and equilibrium 
-  state.}
+  \caption{Temperature coefficients of reactivity for initial and equilibrium state.}
 \begin{tabularx}{\textwidth}{ s | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
-        \cite{robertson_conceptual_1971} \\  \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  \hline
 Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the first case, changes in the fuel temperature only impact fuel density. In 
-this case, the geometry is unchanged because the fuel is a liquid. However, 
-when the moderator heats up, both the density and the geometry change due to 
-thermal expansion of the solid graphite blocks and reflector. Accordingly, the 
-new graphite density was calculated using a linear temperature expansion 
-coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 
-geometry input was created based on this information.
+In the first case, changes in the fuel temperature only impact fuel density.
+In this case, the geometry is unchanged because the fuel is a liquid.
+However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector.
+Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
+A new geometry input was created based on this information.
 
-The fuel temperature coefficient (FTC) is negative for both initial and 
-equilibrium fuel compositon due to thermal Doppler broadening of the resonance 
-capture cross sections in the thorium and is in a good agreement with earlier 
-research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
-temperature coefficient (MTC) is positive for startup composition and decreases 
-during reactor operation because of spectrum hardening with fuel depletion. 
-Finally, the total temperature coefficient of reactivity is negative for both 
-cases, but decreases during reactor operation due to spectral shift. In 
-summary, even after 20 years of operation the total temperature coefficient of 
-reactivity is relatively large and negative during reactor operation, despite 
-positive MTC, and affords excellent reactor stability and control.
+The fuel temperature coefficient (FTC) is negative for both initial and equilibrium fuel compositon due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with earlier research \cite{robertson_conceptual_1971,park_whole_2015}.
+The moderator temperature coefficient (MTC) is positive for startup composition and decreases during reactor operation because of spectrum hardening with fuel depletion.
+Finally, the total temperature coefficient of reactivity is negative for both cases, but decreases during reactor operation due to spectral shift.
+In summary, even after 20 years of operation the total temperature coefficient of reactivity is relatively large and negative during reactor operation, despite positive MTC, and affords excellent reactor stability and control.
 
@@
 Table~\ref{tab:rod_worth} summarizes the reactivity control system worth.
-During normal operation the control (graphite) rods are fully inserted, and the 
-safety (B$_4$C) rods are fully withdrawn. To insert negative reactivity into 
-the core, the graphite rods are gradually withdrawn from the core. In an 
-accident, the safety rods would fall down into the core. The integral rod 
-worths were calculated for various positions to separately estimate control 
-(graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system 
-worth. Control rod integral worth is approximately 28 cents and stays almost 
-constant during reactor operation. The safety rod integral worth decreases by  
-16.2\% during 20 years of operation because of neutron spectrum hardening and 
-absorber accumulation in proximity to reactivity control system rods. This 16\% 
-decline in control system worth should be taken into account in \gls{MSBR} 
-accident analysis and safety justification.
+During normal operation the control (graphite) rods are fully inserted, and the safety (B$_4$C) rods are fully withdrawn.
+To insert negative reactivity into the core, the graphite rods are gradually withdrawn from the core.
+In an accident, the safety rods would fall down into the core.
+The integral rod worths were calculated for various positions to separately estimate control (graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system worth.
+Control rod integral worth is approximately 28 cents and stays almost constant during reactor operation.
+The safety rod integral worth decreases by  16.2\% during 20 years of operation because of neutron spectrum hardening and absorber accumulation in proximity to reactivity control system rods.
+This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Control system rod worth for initial and equilibrium fuel 
-  composition.}
+  \caption{Control system rod worth for initial and equilibrium fuel composition.}
 \begin{tabularx}{\textwidth}{ b | x | x } \hline
 Reactivity parameter [cents]  &  Initial      &  Equilibrium      \\ \hline
-Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 
-        29.0\pm0.8$ \\ Safety (B$_4$C) rod integral worth                  & 
-        $251.8\pm0.8$    & $211.0\pm0.8$  \\
-Total reactivity control system worth               & $505.8\pm0.7$    & 
-        $424.9\pm0.8$ \\ \hline
+Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 29.0\pm0.8$ \\ 
+Safety (B$_4$C) rod integral worth                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
+Total reactivity control system worth               & $505.8\pm0.7$    & $424.9\pm0.8$ \\ \hline
 \end{tabularx}
@@
 
-Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
-equilibrium fuel salt composition. The non-leakage probability for both fast 
-and thermal neutrons does not change during reactor operation because these 
-values are not largely affected by the neutron spectrum shift. In contrast, 
-neutron reproduction factor ($\eta$), resonance escape probability (p), and 
-fast fission factor ($\epsilon$) are considerably different between startup and 
-equilibrium. As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is 
-softer for the initial state. Neutron spectrum hardening causes the fast 
-fission to increase through the core lifetime. The opposite is true for the 
-resonance escape probability. Finally, the neutron reproduction factor 
-decreases during reactor operation due to accumulation of fissile plutonium 
-isotopes.
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and equilibrium fuel salt composition.
+The non-leakage probability for both fast and thermal neutrons does not change during reactor operation because these values are not largely affected by the neutron spectrum shift.
+In contrast, neutron reproduction factor ($\eta$), resonance escape probability (p), and fast fission factor ($\epsilon$) are considerably different between startup and equilibrium.
+As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the initial state.
+Neutron spectrum hardening causes the fast fission to increase through the core lifetime.
+The opposite is true for the resonance escape probability.
+Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Six factors for the full-core \gls{MSBR} model for initial and 
-  equilibrium fuel composition.}
+  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
 \begin{tabularx}{\textwidth}{ b | s | s } \hline
 Factor  & Initial      & Equilibrium   \\ \hline
-Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & 
-        $1.3778\pm.00005$ \\ Thermal utilization factor (f)           & 
-        $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
-Resonance escape probability (p)         & $0.6044\pm.000039$     & 
-        $0.5761\pm.00004$ \\
-Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & 
-        $1.3609\pm.00004$ \\
-Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & 
-        $0.9999\pm.000004$ \\
-Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & 
-        $0.9912\pm.00005$ \\ \hline
+Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
+Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
+Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
+Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
+Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
+Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ \hline
 \end{tabularx}
@@
 \subsection{Thorium refill rate}
-In \gls{MSBR} reprocessing scheme the only external feed material flow  is 
-$^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
-calculated for 60 years of reactor operation. The the $^{232}$Th feed rate 
-fluctuates significantly as a result of the batch-wise nature of this online 
-reprocessing approach. For example, the large spikes up to 36 kg/day in a 
-thorium consumption occurs every 3435 days. This is required due to batch-wise 
-removal of strong absorbers (Rb, Sr, Cs, Ba). The corresponding effective 
-multiplication factor increase (Figure~\ref{fig:keff}) and breeding 
-intensification leads to additional $^{232}$Th consumption.  
-\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
-  \includegraphics[width=\textwidth]{Th_refill_rate.png} \caption{$^{232}$Th 
-  feed rate over 60 years of \gls{MSBR} operation.}
+In \gls{MSBR} reprocessing scheme the only external feed material flow  is $^{232}$Th.
+Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 60 years of reactor operation.
+The the $^{232}$Th feed rate fluctuates significantly as a result of the batch-wise nature of this online reprocessing approach.
+For example, the large spikes up to 36 kg/day in a thorium consumption occurs every 3435 days.
+This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
+The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate.png} 
+  \caption{$^{232}$Th feed rate over 60 years of \gls{MSBR} operation.}
   \label{fig:th_refill}
@@
 
-The average thorium feed rate increases during the first 500 days of operation 
-and than steadily decreases due to spectrum hardening and accumulation of 
-absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
-years of operation is about 2.40 kg/day. This results are in a good agreement 
-with a recent online reprocessing study by \gls{ORNL} 
-\cite{betzler_molten_2017}.
+The average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
+As a result, the average $^{232}$Th feed rate over 60 years of operation is about 2.40 kg/day.
+This results are in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017}.
 
 \subsection{The effect of removing fission product from fuel salt}
-Loading initial fuel salt composition into the \gls{MSBR} core leads to 
-supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
-startup the effective multiplication factor for the case with volatile gases 
-and noble metals removal is approximately 7500 pcm  higher than for case with 
-no fission products removal. This significant impact on the reactor core 
-achieved due to immediate removal (20 sec cycle time) and high absorption cross 
-section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
-element removal considerable after few month from startup and achieves 
-approximately 5500 pcm after 10 years of operation. The rare earth elements are 
-removed with slower rate (50 days cycle time). Moreover, 
-Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day 
-step even strong absorbers did not necessarily leads to fluctuation in results 
-but rare earth elements removal every 50 days causes approximately 600 pcm jump 
-in reactivity.
+Loading initial fuel salt composition into the \gls{MSBR} core leads to supercritical configuration (Figure ~\ref{fig:fp_removal}).
+After reactor startup the effective multiplication factor for the case with volatile gases and noble metals removal is approximately 7500 pcm  higher than for case with no fission products removal.
+This significant impact on the reactor core achieved due to immediate removal (20 sec cycle time) and high absorption cross section of Xe, Kr, Mo, and other noble metals removed.
+The effect of rare earth element removal considerable after few month from startup and achieves approximately 5500 pcm after 10 years of operation.
+The rare earth elements are removed with slower rate (50 days cycle time).
+Moreover, Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day step even strong absorbers did not necessarily leads to fluctuation in results but rare earth elements removal every 50 days causes approximately 600 pcm jump in reactivity.
 
-The effective multiplication factor of the core reduces gradually over 
-operation time because the fissile material ($^{233}$U) continuously depletes 
-from the fuel salt due to fission and, at the same time, fission products 
-accumulates in the fuel salt.	Eventually, without fission products removal, 
-the reactivity decreases to the subcritical state after approximately 500 and 
-1300 days of operation for cases with no removal and volatile gases \& noble 
-metals removal, respectively. The time when the simulated core reaches 
-subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
-Therefore, removing fission products provides with significant neutronic 
-benefit because allows achieve longer core lifetime.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
-  \includegraphics[width=\textwidth]{keff_rem_cases.png} \caption{Calculated 
-  effective multiplication factor for full-core \gls{MSBR} model with removal 
-  of different fission product groups over 10 years of operation. The 
-  confidence interval $\pm\sigma	$ is shaded.}
+The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
+The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime.
+Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to 
+  \centering
+  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.
+The confidence interval $\pm\sigma	$ is shaded.}
   \label{fig:fp_removal}

### 2018-08-22 results.tex
Fixed confusing statement about thermal neutron in zone I #13

@@
 \end{figure}
-Figure~\ref{fig:spectrum_zones} shows that zone I produced much more thermal neutrons than zone II, indicating that the majority of fissions occured in the central part of the core.
+Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons than zone II, corresponding to a majority of fissions occuring in the central part of the core.
 In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.

### 2018-08-25 results.tex
Resolve issue #14
Figure 16 caption fixed #16

@@
 Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
-Thus, a significant amount fissile material will be needed to make the reactor critical.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{keff_rem_cases.png} 
-  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.
-The confidence interval $\pm\sigma	$ is shaded.}
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
   \label{fig:fp_removal}

### 2018-08-25 conclusion.tex
Final sentences about multiphysics removed #17

--- 2018-07-28 conclusion.tex
@@
 Finally, using the built-in SERPENT 2 Monte Carlo code online reprocessing \& refueling material burnup routine would significantly speed up computer-intensive full-core depletion simulations.
-
-Lastly, an additional area to explore is the accident safety analysis which requires development a multi-physics model of the \gls{MSBR} with the coupled neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}.
-The existing full-core SERPENT 2 model and equilibrium fuel material composition would be employed to generate problem-oriented nuclear data libraries for further usage in accident transient analysis.
-The final goal of this effort is to develop a fast-running computational model which could study the dynamic behavior of generic \glspl{MSR}, performing detailed safety analysis and design optimization for a variety of reactor concepts.

### 2018-08-25 abstract.tex
Abstract have been re-written #5

--- 2018-08-03 abstract.tex
@@
 
-Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced 
-demand for tools to analyze these systems. This paper introduces a Python 
-script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
-changing isotopic composition of an irradiated fuel salt. SaltProc couples with 
-the Monte Carlo code, SERPENT 2, for neutron transport and depletion 
-calculations. SaltProc capabilities was illuminated for full-core depletion in 
-the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could 
-be achieved after 16 years and (2) the multiplication factor stabilizes after 6 
-years of operation. Fuel salt irradiation with online reprocessing causes 
-considerable neutron energy spectrum hardening; this spectral shift has a 
-problematic impact on safety parameters (e.g., temperature reactivity feedback, 
-reactivity control system worth). Volatile gases and noble metals removal has 
-positive effect on the core performance approximately 7500 pcm over 10-years 
-timeframe; rare earth elements removal has slower rate and less impact on 
-reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 
-years of operation is 100 g/GWh$_e$ which is a good agreement with other recent 
-research. Problematic effects of neutron energy spectrum hardening during 
-\gls{MSBR} operation should be taken into account for neutronics, 
-multi-physics, and fuel cycle performance analysis.
+Nowadays climate change pushes humankind in search new ways to generate carbon-free, reliable, nonintermittent base load power.
+That is reason why interest in advanced nuclear energy and, particularly \glspl{MSR} has resurged, with multiple new companies pursuing commercialization of \gls{MSR} designs\footnote{Examples include both liquid-fueled and solid-fueled molten salt designs from
+Transatomic, Terrapower, Terrestrial, Moltex Energy, and Thorcon.}.
+To further develop these \gls{MSR} concepts researchers need tools for analyzing liquid fueled molten salt reactor depletion and fuel processing.
+However, most contemporary nuclear reactor physics software is unable to perform high-fidelity full-core depletion calculations in an online reprocessing regime.
+This paper introduces a Python script, SaltProc, which couples with the Monte Carlo code, SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt.
+SaltProc capabilities was demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} concept and compared well to previous results from lower fidelity analyses.
 

### 2018-08-25 conclusion.tex

--- 2018-08-15 conclusion.tex
@@
 Only the batch-wise online reprocessing approach has been treated in this 
-work. However, the SERPENT 2 Monte Carlo code was recently extended for 
+thesis. However, the SERPENT 2 Monte Carlo code was recently extended for 
 continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
 This extension must be verified against existing SaltProc/SERPENT or 
-ChemTriton/SCALE packages, and could be employed for simulating immediate removal of 
+ChemTriton/SCALE packages, and could be employed for immediate removal of 
 fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
@@
 significantly speed up computer-intensive full-core depletion simulations.
-
-Lastly, this work enables accident safety analysis such as multi-physics 
-simulation of the \gls{MSBR} with the coupled 
-neutronics/thermal-hydraulics code, Moltres \cite{lindsay_introduction_2018}. 
-The existing full-core SERPENT 2 model and equilibrium fuel material 
-composition would be employed to generate problem-oriented nuclear data 
-libraries for further usage in accident transient analysis. The final goal of 
-this effort is to develop a fast-running computational model which could study 
-the dynamic behavior of generic \glspl{MSR}, performing detailed safety 
-analysis and design optimization for a variety of reactor concepts.

### 2018-08-25 introduction.tex

--- 2018-08-15 introduction.tex
@@
 
-Methods (1, 3, 4) simulate some form of reactivity control, and methods (1, 4, 
-5, 6, 8, 9) use a set of all nuclides in depletion calculations.
+References \cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,
+aufiero_extended_2013} provide some form of reactivity control, and methods 
+\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,
+ahmad_neutronics_2015, park_whole_2015, jeong_equilibrium_2016,rykhlevskii_online_2017,
+nuttin_potential_2005} use a set of all nuclides in depletion calculations.
 
-Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which 
-material moves to and from the core at all times (continuous) or at specific 
-time steps (batch). To account for batch discharge, a depletion tool must 
-remove some or all material at specified intervals. This requires the burn-up 
-simulation to stop at a given time and restart with a new liquid fuel 
-composition (after removal of discarded materials and addition of 
-fissile/fertile materials). Accounting for continuous removal or addition  
-presents a greater challenge since it requires adding a term to the Bateman 
-equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} 
-solves a set of Bateman equations using spectrum-averaged fluxes and cross 
-sections generated from a deterministic transport calculation. Methods (1, 4, 
-8) model true continuous feeds and removals, while other methods employ a 
-batch-wise approach. \gls{ORNL} researchers have developed ChemTriton, a 
-Python-based script for SCALE/TRITON which uses a semi-continuous batch process 
-to simulate a continuous reprocessing. ChemTriton models salt treatment, 
-separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON 
-model over small time steps to simulate continuous reprocessing and deplete the 
-fuel salt \cite{powers_new_2013}.
+Liquid-fueled \gls{MSR} designs have online separations and feeds, where material 
+is moved to or from the core at specific time steps (batch) or continuously. In 
+batch-wise approach the burn-up simulation stops at a given time and restart with
+a new liquid fuel composition (after removal of discarded materials and addition 
+of fissile/fertile materials). \gls{ORNL} researchers have developed ChemTriton, 
+a Python-based script for SCALE/TRITON which the batch-wise to simulate a continuous 
+reprocessing. This tool models salt treatment, separations, discharge, and refill 
+using a unit-cell \gls{MSR} SCALE/TRITON depletion simulation over small time steps 
+to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}. 
+Methods listed in references \cite{fiorina_investigation_2013,sheu_depletion_2013,
+park_whole_2015, jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,
+rykhlevskii_online_2017} and current work employ a batch-wise approach.
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
-described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only 
-simplified unit-cell geometry because depletion computations for a many-year 
-fuel cycle are computationally expensive even for simple models.
+Accounting for a continuous removal or addition is more difficult because it requires
+adding a term to the Bateman equations. In SCALE \cite{bowman_scale_2011}, 
+ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using 
+spectrum-averaged fluxes and cross sections generated from a deterministic transport 
+calculation. Approaches listed in references \cite{doligez_coupled_2014,heuer_towards_2014,
+aufiero_extended_2013,nuttin_potential_2005} model true continuous feeds and removals.
+
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in 
+\cite{park_whole_2015, jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, 
+betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}. Nevertheless, most of 
+these efforts considered only simplified unit-cell geometry because depletion computations 
+for a many-year fuel cycle are computationally expesive even for simple models.
 

### 2018-08-25 methods.tex

@@
 
-Liquid-fueled system modeling with contemporary reactor physics codes is 
-difficult because most of these codes were developed for analyzing solid-fueled 
-reactors. In fact, world-wide commercial reactors fleet today is represented by 
-systems with solid fuel. Liquid-fueled systems ability to continuously remove 
-fission products and add fissile and/or fertile elements is sthe main challenge 
-for depletion simulations. SaltProc takes into account online separations and 
-feeds using the SERPENT 2 continuous-energy Monte Carlo neutron transport and 
-depletion code.  All calculations presented in this study were performed using 
-SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+Liquid-fueled systems ability to continuously remove fission products and add 
+fissile and/or fertile elements is the main challenge for depletion simulations. 
+Introduced in this work Python-package, SaltProc, takes into account online 
+separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron 
+transport and depletion code.
 

### 2018-08-25 results.tex

@@
 \section{Results}
-The SaltProc online reprocessing simulation code is demonstrated in four applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion, (2) studying operational and safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated outer core zone II works as a virtual ``blanket", reduces neutron leakage and improves breeding ratio due to neutron energy spectral shift, and (4) determining the effect of fission product removal on the core neutronics.
+The SaltProc online reprocessing simulation package is demonstrated in four 
+applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the 
+equilibrium core composition and core depletion, (2) studying operational and 
+safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that 
+in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated 
+outer core zone II works as a virtual ``blanket", reduces neutron leakage and 
+improves breeding ratio due to neutron energy spectral shift, and (4) 
+determining the effect of fission product removal on the core neutronics.
 
-The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective multiplication factor) and computational time.
-The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
-The total computational time for achieving equilibrium composition was approximately 9,900 node-hours (18 core-years.)
+The neutron population per cycle and the number of active/inactive cycles were 
+chosen to obtain balance between reasonable uncertainty for a transport problem 
+($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective 
+multiplication factor) and computational time. The \gls{MSBR} depletion and 
+safety parameter computations were performed on 64 Blue Waters XK7 nodes (two 
+AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per 
+node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
+total computational time for calculating the equilibrium composition was 
+approximately 9,900 node-hours (18 core-years.)
 
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
-The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
-The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
+Figure~\ref{fig:keff} shows the effective multiplication factors 
+obtained using SaltProc and SERPENT 2. The effective multiplication factors are 
+calculated after removing fission products listed in 
+Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
+cycle time\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
+        amount of time required to remove 100\% of a target nuclide from a fuel 
+salt.} which was fixed at 3 days for this work. The effective multiplication 
+factor fluctuates significantly as a result of the batch-wise nature of this 
+online reprocessing strategy.
 
-First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
-Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
-The corresponding effective multiplication factor is much smaller than the previous one.
-Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
-Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
-\begin{figure}[ht!] % replace 't' with 'b' to 
+\begin{figure}[ht!] 
   \centering
   \includegraphics[width=\textwidth]{keff.png}
-  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
+  model for a 60-year reactor operation. The confidence interval 
+  $\sigma=\pm15pcm$ is shaded.}
   \label{fig:keff}
 \end{figure}
-Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
-In fact, removal of these elements every 3435 days causes the multiplication factor to jump by approximately 450 pcm, and limits using the batch approach for online reprocessing simulation.
-Overall, the effective multiplication factor gradually decreases from 1.075 to $k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of irradiation.
+
+First, SERPENT calculates the effective multiplication factor for the beginning 
+of cycle time (fresh fuel composition for the first step). Next, it computes 
+the new fuel salt composition for the end of a 3-day depletion step. The 
+corresponding effective multiplication factor is much smaller than the previous 
+one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
+applying feeds and removals. $K_{eff}$ this increases accordingly since major reactor 
+poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
+from the protactinium decay tank is added.
+
+Additionally, the presence of rubidium, strontium, cesium, and barium in the 
+core are disadvantageous to reactor physics. In fact, removal of these elements 
+every 3435 days causes the multiplication factor to jump by approximately 450 
+pcm, and limits using the batch approach for online reprocessing simulation. 
+Overall, the effective multiplication factor gradually decreases from 1.075 to 
+$k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of 
+irradiation.
 
 \subsection{Fuel salt composition dynamics}
-The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
-Figure~\ref{fig:adens_eq} shows number density of major nuclides which have a strong influence on the reactor core physics.
-Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
-Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
+
+The analysis of the fuel salt composition evolution provides more comprehensive 
+information about the equilibrium state. Figure~\ref{fig:adens_eq} shows number 
+density of major nuclides which have a strong influence on the reactor core 
+physics. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
+fuel salt change insignificantly after approximately 2500 days of operation. 
+Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time 
+interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was 
+achieved after 16 years of reactor operation.
 \begin{figure}[ht!] % replace 't' with 'b' to 
@@
   \includegraphics[width=\textwidth]{major_isotopes_adens.png}
-  \caption{Number density of major nuclides during 60 years of reactor operation.}
+  \caption{Number density of major nuclides during 60 years of reactor 
+  operation.}
   \label{fig:adens_eq}
@@
 In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
-$^{235}$U) and non-fissile strong absorbers (e.g.
-$^{234}$U), keep accumulating in the core.
-Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core.
-In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm).
-Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm.
-Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
-\begin{figure}[htp!] % replace 't' with 'b' to 
-  \centering
+$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
+in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
+isotopes in the core. In the end of the considered operational time, the core 
+contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
+atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
+isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
+production of new fissile materials in the core as well as $^{233}$U breeding 
+make it possible to compensate for negative effects of strong absorber 
+accumulation and keep the reactor critical.
+\begin{figure}[htp!] % replace 't' with 'b' to \centering
   \includegraphics[width=\textwidth]{fissile_short.png}
-  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
+  \caption{Number density of fissile in epithermal spectrum nuclides 
+  accumulation during the reactor operation.}
   \label{fig:fissile_short}
@@
 \subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV.
-The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{spectrum.png} 
-  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
+Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
+full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
+neutron energy spectrum at equilibrium is harder than at startup due to 
+$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
+the core during reactor operation.  \begin{figure}[ht!] % replace 't' with 'b' 
+        to force it to \centering
+  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
+  spectrum normalized by unit lethargy for initial and equilibrium fuel salt 
+  composition.}
   \label{fig:spectrum}
 \end{figure}
-Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons than zone II, corresponding to a majority of fissions occuring in the central part of the core.
-In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.
-Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV.
-Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the neutron energy spectrum in this range.
-Furthermore, in the central core region (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years of reactor operation.
-In contrast, in the outer core region (zone II) a similar spectral shift takes place at a reduced scale.
-This resuls is in a good agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core steady-state study \cite{park_whole_2015}.
 
-It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV.
-Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
+Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons 
+than zone II, corresponding to a majority of fissions occuring in the central part 
+of the core. In the undermoderated zone II, the neutron energy spectrum is harder 
+which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively 
+high breeding ratio. Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th 
+is from 10$^{-4}$ to 10$^{-2}$ MeV. Therefore, the moderator-to-fuel ratio for zone 
+II was chosen to shift the neutron energy spectrum in this range. Furthermore, in the 
+central core region (zone I), the neutron energy spectrum shifts to a harder spectrum 
+over 20 years of reactor operation. In contrast, in the outer core region (zone II) a 
+similar spectral shift takes place at a reduced scale. This resuls is in a good 
+agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent 
+whole-core steady-state study \cite{park_whole_2015}.
+
+It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from 
+$^{232}$Th because the radiative capture cross section of thorium decreases monotonically 
+from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly 
+increase resonance absorption in thorium and decrease the absorptions in fissile and 
+construction materials. 
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
 \subsection{Neutron flux}
-Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition.
-The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum.
-A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons.
-This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
-Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{radial_flux.png} 
-  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
+Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
+neutron flux for both initial and equilibrium composition. The neutron flux has 
+the same shape for both compositions but the equilibrium case has a harder 
+spectrum. A significant spectral shift was observed for the central region of 
+the core (zone I) when for the outer region (zone II) it is negligible for fast 
+but notable for thermal neutrons. This neutron flux radial distribution is in a 
+good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
+Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
+studied for designing the reactivity control system.
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
+  flux distribution for initial and equilibrium fuel salt composition.}
   \label{fig:radial_flux}
 \end{figure}
+
 \subsection{Power and breeding distribution}
-Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for initial and equilibrium fuel composition.
-Figure~\ref{fig:pow_den} reflects the normalized power distribution of the \gls{MSBR} quarter core which is the same at both states.
-For both the initial and equilibrium compositions, fission primarily occurs in the center of the core, namely zone I.
-The spectral shift during reactor operation results in different power fractions at startup and equilibrium, but most of the power is still generated in zone I.
+Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for 
+initial and equilibrium fuel composition. Figure~\ref{fig:pow_den} reflects the 
+normalized power distribution of the \gls{MSBR} quarter core which is the same 
+at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 
+primarily occurs in the center of the core, namely zone I. The spectral shift 
+during reactor operation results in different power fractions at startup and 
+equilibrium, but most of the power is still generated in zone I at equilibrium. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Temperature coefficient of reactivity}
-Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}.
-Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated.
-When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite.
-When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt.
-To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K.
-Three different cases were considered:
+Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated 
+in this work for both initial and equilibrium fuel composition, and compared 
+with original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
+Uncertainty for each temperature coefficient also appears in 
+Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
+temperature feedback is an expansion of material that is heated. When the fuel 
+salt temperature increases, the density of the salt decreases, but at the same 
+time, the total volume of fuel salt in the core remains constant because it is 
+bounded by the graphite. When the graphite temperature increases, the density 
+of graphite decreases creating additional space for fuel salt. To determine 
+temperature coefficients, the cross section temperatures for fuel and moderator 
+were changed from 900K to 1000K. Three different cases were considered:
 \begin{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the first case, changes in the fuel temperature only impact fuel density.
-In this case, the geometry is unchanged because the fuel is a liquid.
-However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector.
-Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
-A new geometry input was created based on this information.
+In the first case, changes in the fuel temperature only impact fuel density. In 
+this case, the geometry is unchanged because the fuel is a liquid. However, 
+when the moderator heats up, both the density and the geometry change due to 
+thermal expansion of the solid graphite blocks and reflector. Accordingly, the 
+new graphite density was calculated using a linear temperature expansion 
+coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 
+geometry input was created based on this information.
 
-The fuel temperature coefficient (FTC) is negative for both initial and equilibrium fuel compositon due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with earlier research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient (MTC) is positive for startup composition and decreases during reactor operation because of spectrum hardening with fuel depletion.
-Finally, the total temperature coefficient of reactivity is negative for both cases, but decreases during reactor operation due to spectral shift.
-In summary, even after 20 years of operation the total temperature coefficient of reactivity is relatively large and negative during reactor operation, despite positive MTC, and affords excellent reactor stability and control.
+The fuel temperature coefficient (FTC) is negative for both initial and 
+equilibrium fuel composition due to thermal Doppler broadening of the resonance 
+capture cross sections in the thorium and is in a good agreement with earlier 
+research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
+temperature coefficient (MTC) is positive for startup composition and decreases 
+during reactor operation because of spectrum hardening with fuel depletion. 
+Finally, the total temperature coefficient of reactivity is negative for both 
+cases, but decreases during reactor operation due to spectral shift. In 
+summary, even after 20 years of operation the total temperature coefficient of 
+reactivity is relatively large and negative during reactor operation, despite 
+positive MTC, and affords excellent reactor stability and control.
 
@@
 Table~\ref{tab:rod_worth} summarizes the reactivity control system worth. 
-During normal operation the control (graphite) rods are fully inserted, and the safety (B$_4$C) rods are fully withdrawn.
-To insert negative reactivity into the core, the graphite rods are gradually withdrawn from the core.
-In an accident, the safety rods would fall down into the core.
-The integral rod worths were calculated for various positions to separately estimate control (graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system worth.
-Control rod integral worth is approximately 28 cents and stays almost constant during reactor operation.
-The safety rod integral worth decreases by  16.2\% during 20 years of operation because of neutron spectrum hardening and absorber accumulation in proximity to reactivity control system rods.
-This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
+During normal operation the control (graphite) rods are fully inserted, and the 
+safety (B$_4$C) rods are fully withdrawn. To insert negative reactivity into 
+the core, the graphite rods are gradually withdrawn from the core. In an 
+accident, the safety rods would fall down into the core. The integral rod 
+worths were calculated for various positions to separately estimate control 
+graphite moderator rods\footnote{In \cite{robertson_conceptual_1971}, the 
+graphite rods are referred to as ``control'' rods.}, safety (B$_4$C) rod, and 
+the whole reactivity control system worth. Control rod integral worth is 
+approximately 28 cents and stays almost constant during reactor operation. The 
+safety rod integral worth decreases by  16.2\% during 20 years of operation 
+because of neutron spectrum hardening and absorber accumulation in proximity to 
+reactivity control system rods. This 16\% decline in control system worth 
+should be taken into account in \gls{MSBR} accident analysis and safety 
+justification.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Table~\ref{tab:six_factor} summarizes the six factors for both initial and equilibrium fuel salt composition.
-The non-leakage probability for both fast and thermal neutrons does not change during reactor operation because these values are not largely affected by the neutron spectrum shift.
-In contrast, neutron reproduction factor ($\eta$), resonance escape probability (p), and fast fission factor ($\epsilon$) are considerably different between startup and equilibrium.
-As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the initial state.
-Neutron spectrum hardening causes the fast fission to increase through the core lifetime.
-The opposite is true for the resonance escape probability.
-Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
+equilibrium fuel salt composition. The non-leakage probability for both fast 
+and thermal neutrons does not change during reactor operation because these 
+values are not largely affected by the neutron spectrum shift. In contrast, 
+neutron reproduction factor ($\eta$), resonance escape probability (p), and 
+fast fission factor ($\epsilon$) are considerably different between startup and 
+equilibrium. As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is 
+softer at the beginning of reactor life. Neutron spectrum hardening causes the fast 
+fission to increase through the core lifetime. The opposite is true for the 
+resonance escape probability. Finally, the neutron reproduction factor 
+decreases during reactor operation due to accumulation of fissile plutonium 
+isotopes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Thorium refill rate}
-In \gls{MSBR} reprocessing scheme the only external feed material flow  is $^{232}$Th.
-Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 60 years of reactor operation.
-The the $^{232}$Th feed rate fluctuates significantly as a result of the batch-wise nature of this online reprocessing approach.
-For example, the large spikes up to 36 kg/day in a thorium consumption occurs every 3435 days.
-This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
-The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
-\begin{figure}[ht!] % replace 't' with 'b' to force it to 
-  \centering
-  \includegraphics[width=\textwidth]{Th_refill_rate.png} 
-  \caption{$^{232}$Th feed rate over 60 years of \gls{MSBR} operation.}
+In \gls{MSBR} reprocessing scheme the only external feed material flow  is 
+$^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
+calculated for 60 years of reactor operation. The $^{232}$Th feed rate 
+fluctuates significantly as a result of the batch-wise nature of this online 
+reprocessing approach. For example, the large spikes up to 36 kg/day in a 
+thorium consumption occurs every 3435 days. This is required due to batch-wise 
+removal of strong absorbers (Rb, Sr, Cs, Ba). The corresponding effective 
+multiplication factor increase (Figure~\ref{fig:keff}) and breeding 
+intensification leads to additional $^{232}$Th consumption.  
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate.png} \caption{$^{232}$Th 
+  feed rate over 60 years of \gls{MSBR} operation.}
   \label{fig:th_refill}
@@
 
-The average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
-As a result, the average $^{232}$Th feed rate over 60 years of operation is about 2.40 kg/day.
-This results are in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017}.
+The average thorium feed rate increases during the first 500 days of operation 
+and than steadily decreases due to spectrum hardening and accumulation of 
+absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
+years of operation is about 2.40 kg/day. This results are in a good agreement 
+with a recent online reprocessing study by \gls{ORNL} 
+\cite{betzler_molten_2017}.
 
 \subsection{The effect of removing fission product from fuel salt}
-Loading initial fuel salt composition into the \gls{MSBR} core leads to supercritical configuration (Figure ~\ref{fig:fp_removal}).
-After reactor startup the effective multiplication factor for the case with volatile gases and noble metals removal is approximately 7500 pcm  higher than for case with no fission products removal.
-This significant impact on the reactor core achieved due to immediate removal (20 sec cycle time) and high absorption cross section of Xe, Kr, Mo, and other noble metals removed.
-The effect of rare earth element removal considerable after few month from startup and achieves approximately 5500 pcm after 10 years of operation.
-The rare earth elements are removed with slower rate (50 days cycle time).
-Moreover, Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day step even strong absorbers did not necessarily leads to fluctuation in results but rare earth elements removal every 50 days causes approximately 600 pcm jump in reactivity.
+Loading initial fuel salt composition into the \gls{MSBR} core leads to 
+supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
+startup the effective multiplication factor for the case with volatile gases 
+and noble metals removal is approximately 7500 pcm  higher than for case with 
+no fission products removal. This significant impact on the reactor core 
+achieved due to immediate removal (20 sec cycle time) and high absorption cross 
+section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
+element removal considerable after few month from startup and achieves 
+approximately 5500 pcm after 10 years of operation. The rare earth elements are 
+removed with slower rate (50 days cycle time). Moreover, 
+Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day 
+step even strong absorbers did not necessarily leads to fluctuation in results 
+but rare earth elements removal every 50 days causes approximately 600 pcm jump 
+in reactivity.
 
-The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
-The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime.
-Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
+The effective multiplication factor of the core reduces gradually over 
+operation time because the fissile material ($^{233}$U) continuously depletes 
+from the fuel salt due to fission and, at the same time, fission products 
+accumulates in the fuel salt.	Eventually, without fission products removal, 
+the reactivity decreases to the subcritical state after approximately 500 and 
+1300 days of operation for cases with no removal and volatile gases \& noble 
+metals removal, respectively. The time when the simulated core reaches 
+subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
+Therefore, removing fission products provides with significant neutronic benefit 
+because allows achieve longer core lifetime.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 

### 2018-08-25 introduction.tex
Word hard wrap 80 col

--- 2018-08-21 introduction.tex
@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
-More recently, \gls{MSR} was included in the six advanced reactor concepts that have been chosen by the Generation IV International Forum (GIF) for further research and development.
-\glspl{MSR} offer significant improvements ``in the four broad areas of sustainability, economics, safety and reliability, and proliferation resistance and physical protection" \cite{doe_technology_2002}.
-To achieve the goals formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and improve inherent safety by using liquid coolant which is also a fuel.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} 
+in the 1950s and was operated in the 1960s. More recently, \gls{MSR} was 
+included in the six advanced reactor concepts that have been chosen by the 
+Generation IV International Forum (GIF) for further research and development. 
+\glspl{MSR} offer significant improvements ``in the four broad areas of 
+sustainability, economics, safety and reliability, and proliferation resistance 
+and physical protection" \cite{doe_technology_2002}. To achieve the goals 
+formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
+improve inherent safety by using liquid coolant which is also a fuel.
 
- In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e.
-UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
-This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
-These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
-The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium.
-With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron.
-Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}.
-The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
-In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle.
-Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.
+ In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
+materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
+elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is 
+circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
+This innovation leads to immediate advantages over traditional, solid-fueled, 
+reactors. These include near-atmospheric pressure in the primary loop, 
+relatively high coolant temperature, outstanding neutron economy, a high level 
+of inherent safety, reduced fuel preprocessing, and the ability to continuously 
+remove fission products and add fissile and/or fertile elements 
+\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
+early 1970s by \gls{ORNL} specifically to realize the promise of the thorium 
+fuel cycle, which uses natural thorium instead of enriched uranium. With 
+continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively 
+realize advantages of the thorium fuel cycle because the $^{233}$U bred from 
+$^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
+$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
+($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
+($\tau_{1/2}$=26.967d).} being recycled back to the core 
+\cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a 
+melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
+and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
+the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
+of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
+Finally, the \gls{MSR} also could be employed as a converter reactor for 
+transmutation of spent fuel from current \glspl{LWR}.
 
-Modeling liquid-fueled systems with existing neutron transport and depletion tools is challenging because most of these tools are designed for the solid-fueled reactors simulation.
-The fuel material flows and potential online separations or feeds of specific elements or nuclides are the main challenges
-of liquid-fueled systems.
-Furthermore, no established tool for liquid-fueled \gls{MSR} neutronics and fuel cycle evaluation exist, though internally developed tools from universities and research institutions can approximate online refueling \cite{serp_molten_2014}.
-The foundation for these tools was based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.
-More recent research efforts in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis and couple external tools to neutron transport and depletion codes take into account continuous feeds and removals in \glspl{MSR}.
-Four of these efforts are listed in table~\ref{tab:fs_codes}.
+Modeling liquid-fueled systems with existing neutron transport and depletion 
+tools is challenging because most of these tools are designed for the 
+solid-fueled reactors simulation. The fuel material flows and potential online 
+separations or feeds of specific elements or nuclides are the main challenges
+of liquid-fueled systems. Furthermore, no established tool for liquid-fueled 
+\gls{MSR} neutronics and fuel cycle evaluation exist, though internally 
+developed tools from universities and research institutions can approximate 
+online refueling \cite{serp_molten_2014}. The foundation for these tools was 
+based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated 
+neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into 
+operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and 
+reprocessing system design. More recent research efforts in Europe and Asia 
+mainly focus on fast spectrum reactor fuel cycle analysis and couple external 
+tools to neutron transport and depletion codes take into account continuous 
+feeds and removals in \glspl{MSR}. Four of these efforts are listed in 
+table~\ref{tab:fs_codes}.
 
@@
 \hline
-\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
+\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
+\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
+\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
 \hline
-ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
+ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
+\cite{fiorina_investigation_2013}            & fast \\
 \hline
-KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
+KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
+\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
 \hline
-SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
+SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 
+\cite{aufiero_extended_2013} & fast \\
 \hline
-MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
+MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
+2015 \cite{ahmad_neutronics_2015}   & thermal  \\
 \hline
-\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
+\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
+Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
+thermal\\
 \hline
-SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
+SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
+2014; Betzler \emph{et al.}, 2017 
+\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
 \hline
-SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
+SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
+thermal\\
 \hline
-\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
+\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
+\hline
 \end{tabularx}
@@
 
-Most of these methods are also applicable to thermal spectrum \glspl{MSR}. Additional tools developed specifically for thermal \gls{MSR} applications are also listed in table~\ref{tab:fs_codes}.
+Most of these methods are also applicable to thermal spectrum \glspl{MSR}. 
+Additional tools developed specifically for thermal \gls{MSR} applications are 
+also listed in table~\ref{tab:fs_codes}.
 
-References \cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,aufiero_extended_2013} provide some form of reactivity control, and methods \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,ahmad_neutronics_2015, park_whole_2015, jeong_equilibrium_2016,rykhlevskii_online_2017,nuttin_potential_2005} use a set of all nuclides in depletion calculations.
+References 
+\cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,aufiero_extended_2013} 
+provide some form of reactivity control, and methods 
+\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,ahmad_neutronics_2015, 
+park_whole_2015, 
+jeong_equilibrium_2016,rykhlevskii_online_2017,nuttin_potential_2005} use a set 
+of all nuclides in depletion calculations.
 
-Liquid-fueled \gls{MSR} designs have online separations and feeds, where material is moved to or from the core at specific time steps (batch) or continuously.
-In batch-wise approach the burn-up simulation stops at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials).
-\gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which the batch-wise to simulate a continuous reprocessing.
-This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON depletion simulation over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.
-Methods listed in references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} and current work employ a batch-wise approach.
+Liquid-fueled \gls{MSR} designs have online separations and feeds, where 
+material is moved to or from the core at specific time steps (batch) or 
+continuously. In batch-wise approach the burn-up simulation stops at a given 
+time and restart with a new liquid fuel composition (after removal of discarded 
+materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
+have developed ChemTriton, a Python-based script for SCALE/TRITON which the 
+batch-wise to simulate a continuous reprocessing. This tool models salt 
+treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
+SCALE/TRITON depletion simulation over small time steps to simulate continuous 
+reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
+references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
+jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
+and current work employ a batch-wise approach.
 
-Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations.
-In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation.
-Approaches listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} model true continuous feeds and removals.
+Accounting for a continuous removal or addition is more difficult because it 
+requires adding a term to the Bateman equations. In SCALE 
+\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
+Bateman equations using spectrum-averaged fluxes and cross sections generated 
+from a deterministic transport calculation. Approaches listed in references 
+\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
+model true continuous feeds and removals.
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in \cite{park_whole_2015, jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}.
-Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
+described in \cite{park_whole_2015, 
+jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, 
+betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}. 
+Nevertheless, most of these efforts considered only simplified unit-cell 
+geometry because depletion computations for a many-year fuel cycle are 
+computationally expesive even for simple models.
 
-Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: one for salt channels, one for two salt plena above and below the core and the last cell for the annulus, consequently, two-region reactor core was approximated by one region with averaged fuel/moderator ratio \cite{nuttin_potential_2005}.
-A similar approach was used by Powers \emph{et al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and clearly misrepresent the two-region breeder reactor concept.
-The unit-cell or one-region models may produce reliable results for homogeneous reactor cores (i.e.
+Nuttin \emph{et al.} broke up reactor core geometry into tree \gls{MCNP} cells: 
+one for salt channels, one for two salt plena above and below the core and the 
+last cell for the annulus, consequently, two-region reactor core was 
+approximated by one region with averaged fuel/moderator ratio 
+\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
+al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
+\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
+betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} and clearly 
+misrepresent the two-region breeder reactor concept. The unit-cell or one-region 
+models may produce reliable results for homogeneous reactor cores (i.e. 
 \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
-\gls{MSRE}).
-A two-region \gls{MSBR} must be simulated using a whole-core model to represent different neutron transport in the inner and outer regions of the core, because most fissions happens in the inner region while breeding occurs in the outer zone.
+\gls{MSRE}). A two-region \gls{MSBR} must be simulated using a whole-core model 
+to represent different neutron transport in the inner and outer regions of the 
+core, because most fissions happens in the inner region while breeding occurs in 
+the outer zone.
 
-Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and employed it to study the material isotopic evolution of the \gls{MSFR}.
-The developed extension directly takes into account the effects of online fuel reprocessing on depletion calculations and features a reactivity control algorithm.
-The extended version of SERPENT 2 was assessed against a dedicated version of the deterministic ERANOS-based EQL3D procedure \cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt isotopic evolution.
-We employed this extended SERPENT 2 for a simplified unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained results which contradict existing \gls{MSBR} depletion simulations \cite{jeong_equilibrium_2016}.
+Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
+employed it to study the material isotopic evolution of the \gls{MSFR}. The 
+developed extension directly takes into account the effects of online fuel 
+reprocessing on depletion calculations and features a reactivity control 
+algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
+version of the deterministic ERANOS-based EQL3D procedure 
+\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
+isotopic evolution. We employed this extended SERPENT 2 for a simplified 
+unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
+results which contradict existing \gls{MSBR} depletion simulations 
+\cite{jeong_equilibrium_2016}.
 
-The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}.
-It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}.
-The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion.
-The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states.
-Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.
+The present work introduces the online reprocessing simulation code, SaltProc, 
+which expands the capability of the continuous-energy Monte Carlo Burnup 
+calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
+liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}. 
+It is also reports the application of the coupled SaltProc-SERPENT 2 system to 
+the \gls{MSBR}, which represents the continuation of the work presented in 
+\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
+of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
+the equilibrium core composition and core depletion. The additional objective is 
+to compare predicted operational and safety parameters of the \gls{MSBR} at both 
+the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
+determined and \gls{MSBR} fuel cycle performance will be analyzed.
 
-The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}.
-Note that this study leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior.
-This article only discusses liquid-fueled \glspl{MSR}.
-Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.
+The \gls{MSBR} complex geometry is hard to describe in software input, and, 
+usually, researchers make significant geometric simplifications to model it 
+\cite{park_whole_2015}. Note that this study leverages extensive computational 
+resources to avoid these geometric approximations and accurately capture 
+breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
+Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
+related to circulating liquid fuel, is not treated here.

### 2018-08-25 methods.tex
Word hard wrap 80 col

--- 2018-08-21 methods.tex
@@
 
-Liquid-fueled systems ability to continuously remove fission products and add fissile and/or fertile elements is the main challenge for depletion simulations.
-Introduced in this work Python-package, SaltProc, takes into account online separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron transport and depletion code.
+Liquid-fueled systems ability to continuously remove fission products and add 
+fissile and/or fertile elements is the main challenge for depletion simulations. 
+Introduced in this work Python-package, SaltProc, takes into account online 
+separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron 
+transport and depletion code.
 
 \subsection{Molten Salt Breeder Reactor design and model description}
-The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm.
-It contains a molten fluoride fuel-salt mixture that generates heat in the active core region and transports that heat to the primary heat exchanger by way of the primary salt pump.
-In the active core region, the salt flows through channels in moderating and reflecting graphite blocks.
-Salt at about 565$^{\circ}$C enters the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows upward through channels in the lower plenum graphite.
-The fuel salt exits at the top at about 704$^{\circ}$C through four equally spaced nozzles which connect to the salt-suction pipes leading to primary circulation pumps.
-The fuel salt drain lines connect to the bottom of the reactor vessel inlet manifold.
+The \gls{MSBR} vessel has a diameter of 680 cm and a height of 610 cm. It 
+contains a molten fluoride fuel-salt mixture that generates heat in the active 
+core region and transports that heat to the primary heat exchanger by way of the 
+primary salt pump. In the active core region, the salt flows through channels in 
+moderating and reflecting graphite blocks. Salt at about 565$^{\circ}$C enters 
+the central manifold at the bottom via four 40.64-cm-diameter nozzles and flows 
+upward through channels in the lower plenum graphite. The fuel salt exits at the 
+top at about 704$^{\circ}$C through four equally spaced nozzles which connect to 
+the salt-suction pipes leading to primary circulation pumps. The fuel salt drain 
+lines connect to the bottom of the reactor vessel inlet manifold.
 
-Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the \gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone II) regions inside the vessel.
-The core has two radial zones bounded by a solid cylindrical graphite reflector and the vessel wall.
-The central zone, zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-Zone I composed of 1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods needed for emergency shutdown only.} rods.
-The under-moderated zone, zone II, with 37\% fuel salt, and radial reflector, surrounds the zone I core region and serves to diminish neutron leakage.
-Zones I and II are surrounded radially and axially by fuel salt (figure~\ref{fig:serpent_zoneII}).
-This space for fuel is necessary for injection and flow of molten salt.
+Figure~\ref{fig:serpent_plan_view} demonstrate the configuration of the 
+\gls{MSBR} vessel, core configuration, ``fission" (zone I) and ``breeding" (zone 
+II) regions inside the vessel. The core has two radial zones bounded by a solid 
+cylindrical graphite reflector and the vessel wall. The central zone, zone I, in 
+which 13\% of the volume is fuel salt and 87\% graphite. Zone I composed of 
+1,320 graphite cells, 2 graphite control rods, and 2 safety\footnote{ These rods 
+needed for emergency shutdown only.} rods. The under-moderated zone, zone II, 
+with 37\% fuel salt, and radial reflector, surrounds the zone I core region and 
+serves to diminish neutron leakage. Zones I and II are surrounded radially and 
+axially by fuel salt (figure~\ref{fig:serpent_zoneII}). This space for fuel is 
+necessary for injection and flow of molten salt.
 
-Since reactor graphite experiences significant dimensional changes due to neutron irradiation, the reactor core was designed for periodic replacement.
-Based on the irradiation experimental data from \gls{MSRE}, core graphite lifetime is about 4 years and reflector graphite lifetime is 30 years \cite{robertson_conceptual_1971}.
+Since reactor graphite experiences significant dimensional changes due to 
+neutron irradiation, the reactor core was designed for periodic replacement. 
+Based on the irradiation experimental data from \gls{MSRE}, core graphite 
+lifetime is about 4 years and reflector graphite lifetime is 30 years 
+\cite{robertson_conceptual_1971}.
 
@@
   \includegraphics[width=\textwidth]{view_serpent.png}
-  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in this work.}
+  \caption{Plan and elevation views of SERPENT 2 \gls{MSBR} model developed in 
+this work.}
   \label{fig:serpent_plan_view}
@@
 
-Moreover, it was decided to remove and install the core graphite as an assembly rather than by individual blocks, because it is relatively easier for maintenance personnel and has lower probability of radioactive elements escape due to used blocks damage during removal.
-In addition, handling the core as an assembly also allows the replacement core to be carefully preassembled and tested under factory conditions.
+Moreover, it was decided to remove and install the core graphite as an assembly 
+rather than by individual blocks, because it is relatively easier for 
+maintenance personnel and has lower probability of radioactive elements escape 
+due to used blocks damage during removal. In addition, handling the core as an 
+assembly also allows the replacement core to be carefully preassembled and 
+tested under factory conditions.
 
-There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, one of which is illustrated in Figure~\ref{fig:serpent_zoneII}.
-The holes in the centers are for the core lifting rods used during the core replacement operations.
-These holes also allow a portion of the fuel salt to flow to the top of the vessel for cooling the top head and axial reflector.
-Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space between the removable core graphite in zone II-B and the permanently mounted reflector graphite.
-This annulus consists entirely of fuel salt, provides space for moving the core assembly, helps compensate the elliptical dimensions of the reactor vessel, and serves to reduce the damaging flux at the surface of the graphite reflector blocks.
-In this work, all figures of the core were generated using the built-in SERPENT 2 plotter.
-All calculations presented in this study were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
+There are eight symmetric graphite slabs with a width of 15.24 cm in zone II, 
+one of which is illustrated in Figure~\ref{fig:serpent_zoneII}. The holes in the 
+centers are for the core lifting rods used during the core replacement 
+operations. These holes also allow a portion of the fuel salt to flow to the top 
+of the vessel for cooling the top head and axial reflector. 
+Figure~\ref{fig:serpent_zoneII} also demonstrates the 5.08-cm-wide annular space 
+between the removable core graphite in zone II-B and the permanently mounted 
+reflector graphite. This annulus consists entirely of fuel salt, provides space 
+for moving the core assembly, helps compensate the elliptical dimensions of the 
+reactor vessel, and serves to reduce the damaging flux at the surface of the 
+graphite reflector blocks. In this work, all figures of the core were generated 
+using the built-in SERPENT 2 plotter. All calculations presented in this study 
+were performed using SERPENT 2 version 2.1.30 on Blue Waters’ XE6 nodes.
 
@@
 \subsubsection{Core zone I}
-The central region of the core, called zone I, is made up of graphite elements, each $10.16$cm$\times$10.16cm$\times$396.24cm.
-Zone I has 4 channels for control rods: two for graphite rods which both regulate and shim during normal operation, and two for backup safety rods consisting of boron carbide clad to assure sufficient negative reactivity for emergency situations.
+The central region of the core, called zone I, is made up of graphite elements, 
+each $10.16$cm$\times$10.16cm$\times$396.24cm. Zone I has 4 channels for control 
+rods: two for graphite rods which both regulate and shim during normal 
+operation, and two for backup safety rods consisting of boron carbide clad to 
+assure sufficient negative reactivity for emergency situations.
 
-These graphite elements have a mostly rectangular shape with lengthwise ridges at each corner that leave space for salt flow elements.
-Various element sizes reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Zone I is well-moderated to achieve the desired fission power density.
-Figure~\ref{fig:I_element_ref} demonstrates the elevation and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} and their SERPENT model \cite{rykhlevskii_full-core_2017}.
+These graphite elements have a mostly rectangular shape with lengthwise ridges 
+at each corner that leave space for salt flow elements. Various element sizes 
+reduce the peak damage flux and power density in the center of the core to 
+prevent local graphite damage. Zone I is well-moderated to achieve the desired 
+fission power density. Figure~\ref{fig:I_element_ref} demonstrates the elevation 
+and plan views of graphite elements of zone I \cite{robertson_conceptual_1971} 
+and their SERPENT model \cite{rykhlevskii_full-core_2017}.
 \begin{figure}[ht!] % replace 't' with 'b' to 
@@
   \includegraphics[width=\textwidth]{zone_I_element_ref.png}
-  \caption{Graphite moderator elements for zone I \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \caption{Graphite moderator elements for zone I 
+\cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:I_element_ref}
@@
 \subsubsection{Core zone II}
-Zone II which is undermoderated, surrounds zone I.
-Combined with the bounding radial reflector, zone II serves to diminish neutron leakage.
-This zone is formed of two kinds of elements: large-diameter fuel channels (zone II-A) and radial graphite slats (zone II-B).
+Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
+radial reflector, zone II serves to diminish neutron leakage. This zone is 
+formed of two kinds of elements: large-diameter fuel channels (zone II-A) and 
+radial graphite slats (zone II-B).
 
-Zone II has 37\% fuel salt by volume and each element has a fuel channel diameter of 6.604cm.
-The graphite elements for zone II-A are prismatic and have elliptical-shaped dowels running axially between the prisms and needed to isolate the fuel salt flow in zone I from that in zone II.
-Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite elements and their SERPENT model.
-Zone II-B elements are rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
-The reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}.
-Zone II serves as a blanket to achieve the best performance: a high breeding ratio and a low fissile inventory.
-The neutron energy spectrum in zone II is made harder to enhance the rate of thorium resonance capture relative to the fission rate, thus limiting the neutron flux in the outer core zone and reducing the neutron leakage \cite{robertson_conceptual_1971}.
+Zone II has 37\% fuel salt by volume and each element has a fuel channel 
+diameter of 6.604cm. The graphite elements for zone II-A are prismatic and have 
+elliptical-shaped dowels running axially between the prisms and needed to 
+isolate the fuel salt flow in zone I from that in zone II. 
+Figure~\ref{fig:II_element_ref} shows shape and dimensions of these graphite 
+elements and their SERPENT model. Zone II-B elements are rectangular slats 
+spaced far enough apart to provide the 0.37 fuel salt volume fraction. The 
+reactor zone II-B graphite 5.08cm-thick slats vary in the radial dimension 
+(average width is 26.67cm) as shown in figure~\ref{fig:serpent_zoneII}. Zone II 
+serves as a blanket to achieve the best performance: a high breeding ratio and a 
+low fissile inventory. The neutron energy spectrum in zone II is made harder to 
+enhance the rate of thorium resonance capture relative to the fission rate, thus 
+limiting the neutron flux in the outer core zone and reducing the neutron 
+leakage \cite{robertson_conceptual_1971}.
 
-The main challenge was to accurately represent zone II-B because it has irregular elements with sophisticated shapes.
-From the \gls{ORNL} report \cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels.
-These graphite elements were simplified into right-circular cylindrical shapes  with central channels.
-Figure~\ref{fig:serpent_zoneII} illustrates this core region in the SERPENT model.
-The volume of fuel salt in zone II was kept exactly 37\%, so that this simplification did not considerably change the core neutronics.
-This is the only simplification made to the \gls{MSBR} geometry in this work.
+The main challenge was to accurately represent zone II-B because it has 
+irregular elements with sophisticated shapes. From the \gls{ORNL} report 
+\cite{robertson_conceptual_1971}, the suggested design of zone II-B has 8 
+irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels. 
+These graphite elements were simplified into right-circular cylindrical shapes  
+with central channels. Figure~\ref{fig:serpent_zoneII} illustrates this core 
+region in the SERPENT model. The volume of fuel salt in zone II was kept exactly 
+37\%, so that this simplification did not considerably change the core 
+neutronics. This is the only simplification made to the \gls{MSBR} geometry in 
+this work.
 
@@
   \includegraphics[width=\textwidth]{zone_II_element_ref.png}
-  \caption{Graphite moderator elements for zone II-A \cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
+  \caption{Graphite moderator elements for zone II-A 
+\cite{robertson_conceptual_1971,rykhlevskii_full-core_2017}.}
   \label{fig:II_element_ref}
@@
 \subsubsection{Material composition and normalization parameters}
-The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ Hastelloy-N is very common in reactors now but have been studied and developed at \gls{ORNL} in a program that started in 1950s.} are materials unique of the \gls{MSBR} and were created at \gls{ORNL}.
-The initial fuel salt used the same density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.75-16-12-0.25 mole \%) as the \gls{MSBR} design \cite{robertson_conceptual_1971}.
-The lithium in the molten salt fuel is fully enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
+The fuel salt, the reactor graphite, and the modified Hastelloy-N\footnote{ 
+Hastelloy-N is very common in reactors now but have been studied and developed 
+at \gls{ORNL} in a program that started in 1950s.} are materials unique of the 
+\gls{MSBR} and were created at \gls{ORNL}. The initial fuel salt used the same 
+density (3.35 g/cm$^3$) and composition LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ 
+(71.75-16-12-0.25 mole \%) as the \gls{MSBR} design 
+\cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
+enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
+becomes tritium upon neutron capture.
 
-For cross section generation, JEFF-3.1.2 neutron library was employed \cite{oecd/nea_data_bank_jeff-3.1.2_2014}.
-The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when SERPENT generates the problem-dependent nuclear data library.
-The isotopic composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to SERPENT model without any modification.
-Table~\ref{tab:msbr_tab} is a summary of the major \gls{MSBR} parameters used by this model \cite{robertson_conceptual_1971}.
+For cross section generation, JEFF-3.1.2 neutron library was employed 
+\cite{oecd/nea_data_bank_jeff-3.1.2_2014}. The specific temperature was fixed 
+for each material to correctly model the Doppler-broadening of resonance peaks 
+when SERPENT generates the problem-dependent nuclear data library. The isotopic 
+composition of each material at the initial state was described in detail in the 
+MSBR conceptual design study \cite{robertson_conceptual_1971} and has been 
+applied to SERPENT model without any modification. Table~\ref{tab:msbr_tab} is a 
+summary of the major \gls{MSBR} parameters used by this model 
+\cite{robertson_conceptual_1971}.
 
@@
         %\centering
-        \caption{Summary of principal data for MSBR \cite{robertson_conceptual_1971}.}
+        \caption{Summary of principal data for MSBR 
+\cite{robertson_conceptual_1971}.}
         \begin{tabularx}{\textwidth}{ s  s}
@@
 \subsection{Online reprocessing method}
-Removing specific chemical elements from a molten salt is a complicated task that requires intelligent design (e.g., chemical separations equipment design, fuel salt flows to equipment) and has a considerable economic cost.
-All liquid-fueled \gls{MSR} designs involve varying levels of online fuel processing.
-Minimally, volatile gaseous fission products (e.g.
-Kr, Xe) escape from the fuel salt during routine reactor operation and must be captured.
-Additional systems might be used to enhance removal of those elements.
-Most designs also call for the removal of noble and rare earth metals from the core since these metals act as neutron poisons.
-Some designs suggest a more complex list of elements to process (figure ~\ref{fig:periodic_tab}), including the temporary removal of protactinium from the salt or other regulation of the actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
+Removing specific chemical elements from a molten salt is a complicated task 
+that requires intelligent design (e.g., chemical separations equipment design, 
+fuel salt flows to equipment) and has a considerable economic cost. All 
+liquid-fueled \gls{MSR} designs involve varying levels of online fuel 
+processing. Minimally, volatile gaseous fission products (e.g. Kr, Xe) escape 
+from the fuel salt during routine reactor operation and must be captured. 
+Additional systems might be used to enhance removal of those elements. Most 
+designs also call for the removal of noble and rare earth metals from the core 
+since these metals act as neutron poisons. Some designs suggest a more complex 
+list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
+temporary removal of protactinium from the salt or other regulation of the 
+actinide inventory in the fuel salt \cite{ahmad_neutronics_2015}.
 
@@
 \subsubsection{Fuel material flows}
-The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U.
-Furthermore, the \gls{MSBR} design requires online reprocessing to remove all poisons (e.g.
-$^{135}$Xe), noble metals, and gases (e.g.
-$^{75}$Se, $^{85}$Kr) every 20 seconds.
-Protactinium presents a challenge, since it has a large absorption cross section in the thermal energy spectrum.
-Accordingly, $^{233}$Pa is continuously removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U without poisoning the reactor.
-The reactor reprocessing system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop.
-This feature allows the reactor to avoid neutron losses to protactinium, keeps fission products to a very low level, and increases the efficiency of $^{233}$U breeding.
-Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and the cycle times used for modeling salt treatment and separations \cite{robertson_conceptual_1971}.
+The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
+which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} design 
+requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), noble 
+metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. Protactinium 
+presents a challenge, since it has a large absorption cross section in the 
+thermal energy spectrum. Accordingly, $^{233}$Pa is continuously removed from 
+the fuel salt into a protactinium decay tank to allow $^{233}$Pa to decay to 
+$^{233}$U without poisoning the reactor. The reactor reprocessing system is 
+designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, hold it 
+while $^{233}$Pa decays into $^{233}$U, and return it back to the primary loop. 
+This feature allows the reactor to avoid neutron losses to protactinium, keeps 
+fission products to a very low level, and increases the efficiency of $^{233}$U 
+breeding. Table~\ref{tab:reprocessing_list} summarizes full list of nuclides and 
+the cycle times used for modeling salt treatment and separations 
+\cite{robertson_conceptual_1971}.
 
@@
         \centering
-        \caption{The effective cycle times for protactinium and fission products removal (reproduced from \cite{robertson_conceptual_1971}).}
+        \caption{The effective cycle times for protactinium and fission products 
+removal (reproduced from \cite{robertson_conceptual_1971}).}
         \begin{tabularx}{\textwidth}{ x | s | x }
         \hline 
-        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full power) \\ \hline 
+        Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at full 
+power) \\ \hline 
         Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, Gd & 50 days \\ 
@@
         \end{tabularx}
-        %\footnotetext{Chemical processing plant and gas separation system removing chemical elements (not isotopes) only.
-Isotopes instead of elements listed because other isotopes are short-lived and might be ignored.}
         \label{tab:reprocessing_list}
 \end{table}
-Th removal rates vary among nuclides in this reactor concept which dictate the necessary resolution of depletion calculations.
-If the depletion time intervals are very short, an enormous number of depletion steps are required to obtain the equilibrium composition.
-On the other hand, if the depletion  calculation time interval is too long, the impact of short-lived fission products is not captured.
-To compromise, the time interval for depletion calculations in this model was selected as 3 days to correlate with the removal interval of $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass fraction of $^{232}$Th.
+Th removal rates vary among nuclides in this reactor concept which dictate the 
+necessary resolution of depletion calculations. If the depletion time intervals 
+are very short, an enormous number of depletion steps are required to obtain the 
+equilibrium composition. On the other hand, if the depletion  calculation time 
+interval is too long, the impact of short-lived fission products is not 
+captured. To compromise, the time interval for depletion calculations in this 
+model was selected as 3 days to correlate with the removal interval of 
+$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
+fraction of $^{232}$Th.
 
 \subsubsection{The SaltProc modeling and simulation code}
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to expand SERPENT 2
- depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
-The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
-for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
+The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to 
+expand SERPENT 2
+ depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous 
+reprocessing.
+The Python package uses HDF5 \cite{the_hdf_group_hierarchical_1997} to store 
+data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
+for SEPRENT output file parsing and nuclide naming. It is an open-source tool 
+that uses a semi-continuous approach to 
 simulate continuous feeds and removals in the \gls{MSR}.
 
-The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
-developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
-software which allows to simulate online reprocessing for irregular full-core geometry with 
-high level of fidelity.  The primary function of SaltProc is to manage material streams while
-SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
+The tool structure and capabilities of SaltProc are similar to ChemTriton tool 
+for SCALE
+developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte 
+Carlo SERPENT 2
+software which allows to simulate online reprocessing for irregular full-core 
+geometry with 
+high level of fidelity.  The primary function of SaltProc is to manage material 
+streams while
+SERPENT 2 performs most of the computationally heavy work, namely neutron 
+transport and depletion
 calculations. Saltproc is defined as a 
 python class, where each material stream is defined as a isotopic atomic density
-vector variable. This allows tracking of time-sensitive material streams such as the
-$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
-reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
-for each stream: read and write isotopic data in/from database, separate out specific isotopes 
-from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
-number density of specific nuclide in the core. These attributes and functions are crucial to 
-simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
+vector variable. This allows tracking of time-sensitive material streams such as 
+the
+$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
+parameters, such as the 
+reprocessing interval and removal efficiency.  In addition, SaltProc provides a 
+set of functions 
+for each stream: read and write isotopic data in/from database, separate out 
+specific isotopes 
+from stream with defined efficiency, feed in specific isotopes to stream, and 
+maintain constant 
+number density of specific nuclide in the core. These attributes and functions 
+are crucial to 
+simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are 
+universal for 
 myriad reactor systems.
 
-Saltproc is currently in active development in Github (https://github.com/ arfc/saltproc), and has unit tests and Travis continuous integration for sustainable development. There is also documentation
-generated through Sphinx document generator for ease of use. We plan to implement
-user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
+Saltproc is currently in active development in Github (https://github.com/ 
+arfc/saltproc), and has unit tests and Travis continuous integration for 
+sustainable development. There is also documentation
+generated through Sphinx document generator for ease of use. We plan to 
+implement
+user-defined reprocessing scheme definition, two-region \gls{MSR} modeling 
+capabilities,
 and decay modeling in future releases.
 
-Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
+Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation 
+algorithm the 
 coupled SaltProc and SERPENT 2. To perform a depletion step,
-SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
+SaltProc reads an external SERPENT 2 template file which is defined by the user. 
+This file 
 contains input cards with parameters such as geometry,
-moderator and construction materials isotopic composition, neutron population, criticality 
+moderator and construction materials isotopic composition, neutron population, 
+criticality 
 cycles, total heating power, and boundary conditions.
-After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
+After the depletion calculation, SaltProc reads the depleted fuel composition 
+file (\texttt{
 .bumat1}) and stores the depleted
-composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
+composition isotopic vector in an HDF5 database. SaltProc only stores and edits 
+the isotopic 
 composition of the fuel stream,
-which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
+which makes SaltProc a flexible tool to model any geometry: an infinite medium, 
+a unit cell, a 
 multi-zone simplified assembly, or a full core.
-This flexibiliity allows the user to perform simulations of varying fidelity and computational 
+This flexibiliity allows the user to perform simulations of varying fidelity and 
+computational 
 intensity.
@@
 \end{figure}
-SaltProc can manage as many material streams as desired. It also may work with multiple depletion 
-materials.
-At the end of a each depletion step, SaltProc reads the depleted compositions and tracks each material stream individually.
-Following this, it applies chemical separation functions to fuel stream vectors.
-These vectors then form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database and prints into the SERPENT 2 composition file for the next depletion calculation.
+SaltProc can manage as many material streams as desired. It also may work with 
+multiple depletion 
+materials. At the end of a each depletion step, SaltProc reads the depleted 
+compositions and tracks each material stream individually. Following this, it 
+applies chemical separation functions to fuel stream vectors. These vectors then 
+form a matrix (isotopics x timesteps) which SaltProc stores in an HDF5 database 
+and prints into the SERPENT 2 composition file for the next depletion 
+calculation.
 
-Saltproc datasets are timseries, meaning that every value is recorded every timestep. The 
+Saltproc datasets are timseries, meaning that every value is recorded every 
+timestep. The 
 datasets SaltProc produces are listed below,
@@
 
-Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core at an equilibrium condition, after fission products have built up in the fuel salt during years if operation.
-Isotopic composition of the fuel salt continues change slightly even after decades of operation, but the dominant nuclides that have significant impact to the neutronic behavior tend to reach an equilibrium concentration (e.g., vary less than 1\% over several years).
-In contrast, from the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt composition undergoes significant changes (e.g., changes in fission products, minor actinides, and fissile materials number density).
-During this period, the material feeds and removals should be optimized for the fastest \gls{MSBR} transition to an equilibrium state.
-A faster transition simplifies the reactor operation because, at equilibrium, the fissile and fertile feed rates, fission product removal rates, and corresponding core safety parameters are constant in time.
+Liquid-fueled \gls{MSBR} design in this work focuses on the state of the core at 
+an equilibrium condition, after fission products have built up in the fuel salt 
+during years if operation. Isotopic composition of the fuel salt continues 
+change slightly even after decades of operation, but the dominant nuclides that 
+have significant impact to the neutronic behavior tend to reach an equilibrium 
+concentration (e.g., vary less than 1\% over several years). In contrast, from 
+the startup of an \gls{MSBR} until the equilibrium condition, the fuel salt 
+composition undergoes significant changes (e.g., changes in fission products, 
+minor actinides, and fissile materials number density). During this period, the 
+material feeds and removals should be optimized for the fastest \gls{MSBR} 
+transition to an equilibrium state. A faster transition simplifies the reactor 
+operation because, at equilibrium, the fissile and fertile feed rates, fission 
+product removal rates, and corresponding core safety parameters are constant in 
+time.
 
-In addition, SaltProc is able to define time-dependent material feed and removal rates to investigate the their impacts.
-These rates need not be constant in SaltProc.
-They can be defined as piecewise functions or set to respond conditions in the core.
-For instance, SaltProc might increase the fissile material feeding rate if the effective multiplication factor, $k_{eff}$, falls below a specific limit (e.g., 1.002).
-These capabilities allow SaltProc to analyze fuel cycle of a generic liquid-fueled \gls{MSR}.
-In summary, the development approach of SaltProc focused on producing a generic, flexible and expandable tool to give the SERPENT 2 Monte Carlo code the ability to conduct advanced in-reactor fuel cycle analysis as well as simulate a myriad of online refueling and fuel reprocessing systems.
+In addition, SaltProc is able to define time-dependent material feed and removal 
+rates to investigate the their impacts. These rates need not be constant in 
+SaltProc. They can be defined as piecewise functions or set to respond 
+conditions in the core. For instance, SaltProc might increase the fissile 
+material feeding rate if the effective multiplication factor, $k_{eff}$, falls 
+below a specific limit (e.g., 1.002).
+These capabilities allow SaltProc to analyze fuel cycle of a generic 
+liquid-fueled \gls{MSR}. In summary, the development approach of SaltProc 
+focused on producing a generic, flexible and expandable tool to give the SERPENT 
+2 Monte Carlo code the ability to conduct advanced in-reactor fuel cycle 
+analysis as well as simulate a myriad of online refueling and fuel reprocessing 
+systems.

### 2018-08-25 results.tex
Word hard wrap 80 col

--- 2018-08-25 results.tex
@@
 \section{Results}
-The SaltProc online reprocessing simulation code is demonstrated in four applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion, (2) studying operational and safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated outer core zone II works as a virtual ``blanket", reduces neutron leakage and improves breeding ratio due to neutron energy spectral shift, and (4) determining the effect of fission product removal on the core neutronics.
+The SaltProc online reprocessing simulation code is demonstrated in four 
+applications: (1) analyzing  \gls{MSBR} neutronics and fuel cycle to find the 
+equilibrium core composition and core depletion, (2) studying operational and 
+safety parameters evolution during \gls{MSBR} operation, (3) demonstrating that 
+in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated 
+outer core zone II works as a virtual ``blanket", reduces neutron leakage and 
+improves breeding ratio due to neutron energy spectral shift, and (4) 
+determining the effect of fission product removal on the core neutronics.
 
-The neutron population per cycle and the number of active/inactive cycles were chosen to obtain balance between reasonable uncertainty for a transport problem ($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective multiplication factor) and computational time.
-The \gls{MSBR} depletion and safety parameter computations were performed on 64 Blue Waters XK7 nodes (two AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz).
-The total computational time for achieving equilibrium composition was approximately 9,900 node-hours (18 core-years.)
+The neutron population per cycle and the number of active/inactive cycles were 
+chosen to obtain balance between reasonable uncertainty for a transport problem 
+($\leq$ 15 pcm\footnote{ 1 pcm = 10$^{-5}\Delta k_{eff}/k_{eff}$} for effective 
+multiplication factor) and computational time. The \gls{MSBR} depletion and 
+safety parameter computations were performed on 64 Blue Waters XK7 nodes (two 
+AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per 
+node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
+total computational time for achieving equilibrium composition was approximately 
+9,900 node-hours (18 core-years.)
 
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2.
-The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work.
-The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.
+Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained 
+using SaltProc and SERPENT 2. The effective multiplication factors are 
+calculated after removing fission products listed in 
+Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
+``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
+amount of time required to remove 100\% of a target nuclide from a fuel salt.} 
+which was fixed at 3 days for this work. The effective multiplication factor 
+fluctuates significantly as a result of the batch-wise nature of this online 
+reprocessing strategy.
 
-First, SERPENT calculates the effective multiplication factor for the beginning of cycle time (fresh fuel composition for the first step).
-Next, it computes the new fuel salt composition for the end of a 3-day depletion step.
-The corresponding effective multiplication factor is much smaller than the previous one.
-Finally, SERPENT calculates $k_{eff}$ for the depleted composition after applying feeds and removals, and this increases accordingly since major reactor poisons (e.g.
-Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from the protactinium decay tank is added.
+First, SERPENT calculates the effective multiplication factor for the beginning 
+of cycle time (fresh fuel composition for the first step). Next, it computes the 
+new fuel salt composition for the end of a 3-day depletion step. The 
+corresponding effective multiplication factor is much smaller than the previous 
+one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
+applying feeds and removals, and this increases accordingly since major reactor 
+poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) from 
+the protactinium decay tank is added. 
 \begin{figure}[ht!] % replace 't' with 'b' to 
@@
   \includegraphics[width=\textwidth]{keff.png}
-  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ is shaded.}
+  \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
+model for a 60-year reactor operation. The confidence interval $\sigma=\pm15pcm$ 
+is shaded.}
   \label{fig:keff}
 \end{figure}
-Additionally, the presence of rubidium, strontium, cesium, and barium in the core are disadvantageous to reactor physics.
-In fact, removal of these elements every 3435 days causes the multiplication factor to jump by approximately 450 pcm, and limits using the batch approach for online reprocessing simulation.
-Overall, the effective multiplication factor gradually decreases from 1.075 to $k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of irradiation.
+Additionally, the presence of rubidium, strontium, cesium, and barium in the 
+core are disadvantageous to reactor physics. In fact, removal of these elements 
+every 3435 days causes the multiplication factor to jump by approximately 450 
+pcm, and limits using the batch approach for online reprocessing simulation. 
+Overall, the effective multiplication factor gradually decreases from 1.075 to 
+$k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of 
+irradiation.
 
 \subsection{Fuel salt composition dynamics}
-The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state.
-Figure~\ref{fig:adens_eq} shows number density of major nuclides which have a strong influence on the reactor core physics.
-Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation.
-Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
+The analysis of the fuel salt composition evolution provides more comprehensive 
+information about the equilibrium state. Figure~\ref{fig:adens_eq} shows number 
+density of major nuclides which have a strong influence on the reactor core 
+physics. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
+fuel salt change insignificantly after approximately 2500 days of operation. 
+Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time 
+interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was 
+achieved after 16 years of reactor operation.
 \begin{figure}[ht!] % replace 't' with 'b' to 
@@
   \includegraphics[width=\textwidth]{major_isotopes_adens.png}
-  \caption{Number density of major nuclides during 60 years of reactor operation.}
+  \caption{Number density of major nuclides during 60 years of reactor 
+operation.}
   \label{fig:adens_eq}
@@
 In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
-$^{235}$U) and non-fissile strong absorbers (e.g.
-$^{234}$U), keep accumulating in the core.
-Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core.
-In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm).
-Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm.
-Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
+$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
+in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile 
+isotopes in the core. In the end of considered operational time the core 
+contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
+atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
+isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
+production of new fissile materials in the core as well as $^{233}$U breeding 
+make it possible to compensate for negative effects of strong absorber 
+accumulation and keep the reactor critical.
 \begin{figure}[htp!] % replace 't' with 'b' to 
@@
   \includegraphics[width=\textwidth]{fissile_short.png}
-  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
+  \caption{Number density of fissile in epithermal spectrum nuclides 
+accumulation during the reactor operation.}
   \label{fig:fissile_short}
@@
 \subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV.
-The neutron energy spectrum at equilibrium is harder than at startup due to $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in the core during reactor operation.
+Figure~\ref{fig:spectrum} shows the normalized neutron flux spectrum for the 
+full-core \gls{MSBR} model in the energy range from $10^{-8}$ to $10$ MeV. The 
+neutron energy spectrum at equilibrium is harder than at startup due to 
+$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
+the core during reactor operation. 
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{spectrum.png} 
-  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial and equilibrium fuel salt composition.}
+  \caption{Neutron flux energy spectrum normalized by unit lethargy for initial 
+and equilibrium fuel salt composition.}
   \label{fig:spectrum}
 \end{figure}
-Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons than zone II, corresponding to a majority of fissions occuring in the central part of the core.
-In the undermoderated zone II, the neutron energy spectrum is harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively high breeding ratio.
-Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV.
-Therefore, the moderator-to-fuel ratio for zone II was chosen to shift the neutron energy spectrum in this range.
-Furthermore, in the central core region (zone I), the neutron energy spectrum shifts to a harder spectrum over 20 years of reactor operation.
-In contrast, in the outer core region (zone II) a similar spectral shift takes place at a reduced scale.
-This resuls is in a good agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core steady-state study \cite{park_whole_2015}.
+Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons 
+than zone II, corresponding to a majority of fissions occuring in the central 
+part of the core. In the undermoderated zone II, the neutron energy spectrum is 
+harder which leads to more capture of neutrons by $^{232}$Th and helps a achieve 
+relatively high breeding ratio. Moreover, the (n,$\gamma$) resonance energy 
+range in $^{232}$Th is from 10$^{-4}$ to 10$^{-2}$ MeV. Therefore, the 
+moderator-to-fuel ratio for zone II was chosen to shift the neutron energy 
+spectrum in this range. Furthermore, in the central core region (zone I), the 
+neutron energy spectrum shifts to a harder spectrum over 20 years of reactor 
+operation. In contrast, in the outer core region (zone II) a similar spectral 
+shift takes place at a reduced scale. This resuls is in a good agreement with 
+original ORNL report \cite{robertson_conceptual_1971} and most recent whole-core 
+steady-state study \cite{park_whole_2015}.
 
-It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV.
-Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials.
+It is important to obtain the epithermal and thermal spectra to produce 
+$^{233}$U from $^{232}$Th because the radiative capture cross section of thorium 
+decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the 
+spectrum tends to significantly increase resonance absorption in thorium and 
+decrease the absorptions in fissile and construction materials. 
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{spectrum_zones.png} 
-  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
+  \caption{Neutron flux energy spectrum in different core regions normalized by 
+unit lethargy for the initial and equilibrium fuel salt composition.}
   \label{fig:spectrum_zones}
@@
 \subsection{Neutron flux}
-Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition.
-The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum.
-A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons.
-This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}.
-Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.
+Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
+neutron flux for both initial and equilibrium composition. The neutron flux has 
+the same shape for both compositions but the equilibrium case has a harder 
+spectrum. A significant spectral shift was observed for the central region of 
+the core (zone I) when for the outer region (zone II) it is negligible for fast 
+but notable for thermal neutrons. This neutron flux radial distribution is in a 
+good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
+Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
+studied for designing the reactivity control system.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{radial_flux.png} 
-  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}
+  \caption{Radial neutron flux distribution for initial and equilibrium fuel 
+salt composition.}
   \label{fig:radial_flux}
@@
   \centering
-  \caption{Power generation fraction in each zone for initial and equilibrium state.}
+  \caption{Power generation fraction in each zone for initial and equilibrium 
+state.}
 \begin{tabularx}{\textwidth}{ m | s | s } \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states.
-The distribution reflects the spatial distribution of $^{233}$Th production in the core.
-The thorium-232 then $\beta$-decays to $^{233}$Pa which is the precursor for $^{233}$U production.
-Accordingly, this characteristic represents the breeding distribution in the \gls{MSBR} core.
-Spectral shift does not cause significant changes in power nor in breeding distribution.
-Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.
+Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate 
+distribution for $^{232}$Th normalized by the total neutron flux for initial and 
+equilibrium states. The distribution reflects the spatial distribution of 
+$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
+$^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this 
+characteristic represents the breeding distribution in the \gls{MSBR} core. 
+Spectral shift does not cause significant changes in power nor in breeding 
+distribution. Even after 20 years of operation, most of the power still is 
+generated in zone I though the majority of $^{233}$Th is produced in zone II.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{power_distribution_eq.png} 
-  \caption{Normalized power density for both initial and equilibrium fuel salt composition.}
+  \caption{Normalized power density for both initial and equilibrium fuel salt 
+composition.}
   \label{fig:pow_den}
@@
   \includegraphics[width=\textwidth]{breeding_distribution_eq.png} 
-  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}
+  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for 
+both initial and equilibrium fuel salt composition.}
   \label{fig:breeding_den}
@@
 \subsection{Temperature coefficient of reactivity}
-Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}.
-Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated.
-When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite.
-When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt.
-To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K.
+Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in 
+this work for both initial and equilibrium fuel composition, and compared with 
+original \gls{ORNL} report data \cite{robertson_conceptual_1971}. Uncertainty 
+for each temperature coefficient also appears in Table~\ref{tab:tcoef}. The main 
+physical principle underlying the reactor temperature feedback is an expansion 
+of matterial that is heated. When the fuel salt temperature increases, the 
+density of the salt decreases, but at the same time, the total volume of fuel 
+salt in the core remains constant because it is bounded by the graphite. When 
+the graphite temperature increases, the density of graphite decreases creating 
+additional space for fuel salt. To determine temperature coefficients, the cross 
+section temperatures for fuel and moderator were changed from 900K to 1000K. 
 Three different cases were considered:
@@
   \centering
-  \caption{Temperature coefficients of reactivity for initial and equilibrium state.}
+  \caption{Temperature coefficients of reactivity for initial and equilibrium 
+state.}
 \begin{tabularx}{\textwidth}{ s | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \cite{robertson_conceptual_1971} \\  \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
+\cite{robertson_conceptual_1971} \\  \hline
 Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the first case, changes in the fuel temperature only impact fuel density.
-In this case, the geometry is unchanged because the fuel is a liquid.
-However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector.
-Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
-A new geometry input was created based on this information.
+In the first case, changes in the fuel temperature only impact fuel density. In 
+this case, the geometry is unchanged because the fuel is a liquid. However, when 
+the moderator heats up, both the density and the geometry change due to thermal 
+expansion of the solid graphite blocks and reflector. Accordingly, the new 
+graphite density was calculated using a linear temperature expansion coefficient 
+of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new geometry input 
+was created based on this information.
 
-The fuel temperature coefficient (FTC) is negative for both initial and equilibrium fuel compositon due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with earlier research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient (MTC) is positive for startup composition and decreases during reactor operation because of spectrum hardening with fuel depletion.
-Finally, the total temperature coefficient of reactivity is negative for both cases, but decreases during reactor operation due to spectral shift.
-In summary, even after 20 years of operation the total temperature coefficient of reactivity is relatively large and negative during reactor operation, despite positive MTC, and affords excellent reactor stability and control.
+The fuel temperature coefficient (FTC) is negative for both initial and 
+equilibrium fuel compositon due to thermal Doppler broadening of the resonance 
+capture cross sections in the thorium and is in a good agreement with earlier 
+research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
+temperature coefficient (MTC) is positive for startup composition and decreases 
+during reactor operation because of spectrum hardening with fuel depletion. 
+Finally, the total temperature coefficient of reactivity is negative for both 
+cases, but decreases during reactor operation due to spectral shift. In summary, 
+even after 20 years of operation the total temperature coefficient of reactivity 
+is relatively large and negative during reactor operation, despite positive MTC, 
+and affords excellent reactor stability and control.
 
 \subsection{Reactivity control system rod worth}
-Table~\ref{tab:rod_worth} summarizes the reactivity control system worth.
-During normal operation the control (graphite) rods are fully inserted, and the safety (B$_4$C) rods are fully withdrawn.
-To insert negative reactivity into the core, the graphite rods are gradually withdrawn from the core.
-In an accident, the safety rods would fall down into the core.
-The integral rod worths were calculated for various positions to separately estimate control (graphite) rod, safety (B$_4$C) rod, and the whole reactivity control system worth.
-Control rod integral worth is approximately 28 cents and stays almost constant during reactor operation.
-The safety rod integral worth decreases by  16.2\% during 20 years of operation because of neutron spectrum hardening and absorber accumulation in proximity to reactivity control system rods.
-This 16\% decline in control system worth should be taken into account in \gls{MSBR} accident analysis and safety justification.
+Table~\ref{tab:rod_worth} summarizes the reactivity control system worth. During 
+normal operation the control (graphite) rods are fully inserted, and the safety 
+(B$_4$C) rods are fully withdrawn. To insert negative reactivity into the core, 
+the graphite rods are gradually withdrawn from the core. In an accident, the 
+safety rods would fall down into the core. The integral rod worths were 
+calculated for various positions to separately estimate control (graphite) rod, 
+safety (B$_4$C) rod, and the whole reactivity control system worth. Control rod 
+integral worth is approximately 28 cents and stays almost constant during 
+reactor operation. The safety rod integral worth decreases by  16.2\% during 20 
+years of operation because of neutron spectrum hardening and absorber 
+accumulation in proximity to reactivity control system rods. This 16\% decline 
+in control system worth should be taken into account in \gls{MSBR} accident 
+analysis and safety justification.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Control system rod worth for initial and equilibrium fuel composition.}
+  \caption{Control system rod worth for initial and equilibrium fuel 
+composition.}
 \begin{tabularx}{\textwidth}{ b | x | x } \hline
 Reactivity parameter [cents]  &  Initial      &  Equilibrium      \\ \hline
-Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 29.0\pm0.8$ \\ 
-Safety (B$_4$C) rod integral worth                  & $251.8\pm0.8$    & $211.0\pm0.8$  \\
-Total reactivity control system worth               & $505.8\pm0.7$    & $424.9\pm0.8$ \\ \hline
+Control (graphite) rod integral worth               & $\ 28.2\pm0.8$    & $\ 
+29.0\pm0.8$ \\ 
+Safety (B$_4$C) rod integral worth                  & $251.8\pm0.8$    & 
+$211.0\pm0.8$  \\
+Total reactivity control system worth               & $505.8\pm0.7$    & 
+$424.9\pm0.8$ \\ \hline
 \end{tabularx}
@@
 
-Table~\ref{tab:six_factor} summarizes the six factors for both initial and equilibrium fuel salt composition.
-The non-leakage probability for both fast and thermal neutrons does not change during reactor operation because these values are not largely affected by the neutron spectrum shift.
-In contrast, neutron reproduction factor ($\eta$), resonance escape probability (p), and fast fission factor ($\epsilon$) are considerably different between startup and equilibrium.
-As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the initial state.
-Neutron spectrum hardening causes the fast fission to increase through the core lifetime.
-The opposite is true for the resonance escape probability.
-Finally, the neutron reproduction factor decreases during reactor operation due to accumulation of fissile plutonium isotopes.
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
+equilibrium fuel salt composition. The non-leakage probability for both fast and 
+thermal neutrons does not change during reactor operation because these values 
+are not largely affected by the neutron spectrum shift. In contrast, neutron 
+reproduction factor ($\eta$), resonance escape probability (p), and fast fission 
+factor ($\epsilon$) are considerably different between startup and equilibrium. 
+As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is softer for the 
+initial state. Neutron spectrum hardening causes the fast fission to increase 
+through the core lifetime. The opposite is true for the resonance escape 
+probability. Finally, the neutron reproduction factor decreases during reactor 
+operation due to accumulation of fissile plutonium isotopes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \caption{Six factors for the full-core \gls{MSBR} model for initial and equilibrium fuel composition.}
+  \caption{Six factors for the full-core \gls{MSBR} model for initial and 
+equilibrium fuel composition.}
 \begin{tabularx}{\textwidth}{ b | s | s } \hline
 Factor  & Initial      & Equilibrium   \\ \hline
-Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & $1.3778\pm.00005$ \\ 
-Thermal utilization factor (f)           & $0.9670\pm.000011$     & $0.9706\pm.00001$ \\
-Resonance escape probability (p)         & $0.6044\pm.000039$     & $0.5761\pm.00004$ \\
-Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & $1.3609\pm.00004$ \\
-Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & $0.9999\pm.000004$ \\
-Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & $0.9912\pm.00005$ \\ \hline
+Neutron reproduction factor ($\eta$)     & $1.3960\pm.000052$     & 
+$1.3778\pm.00005$ \\ 
+Thermal utilization factor (f)           & $0.9670\pm.000011$     & 
+$0.9706\pm.00001$ \\
+Resonance escape probability (p)         & $0.6044\pm.000039$     & 
+$0.5761\pm.00004$ \\
+Fast fission factor ($\epsilon$)         & $1.3421\pm.000040$     & 
+$1.3609\pm.00004$ \\
+Fast non-leakage probability (P$_f$)     & $0.9999\pm.000004$     & 
+$0.9999\pm.000004$ \\
+Thermal non-leakage probability (P$_t$)  & $0.9894\pm.000005$     & 
+$0.9912\pm.00005$ \\ \hline
 \end{tabularx}
@@
 \subsection{Thorium refill rate}
-In \gls{MSBR} reprocessing scheme the only external feed material flow  is $^{232}$Th.
-Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated for 60 years of reactor operation.
-The the $^{232}$Th feed rate fluctuates significantly as a result of the batch-wise nature of this online reprocessing approach.
-For example, the large spikes up to 36 kg/day in a thorium consumption occurs every 3435 days.
-This is required due to batch-wise removal of strong absorbers (Rb, Sr, Cs, Ba).
-The corresponding effective multiplication factor increase (Figure~\ref{fig:keff}) and breeding intensification leads to additional $^{232}$Th consumption.
+In \gls{MSBR} reprocessing scheme the only external feed material flow  is 
+$^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate calculated 
+for 60 years of reactor operation. The the $^{232}$Th feed rate fluctuates 
+significantly as a result of the batch-wise nature of this online reprocessing 
+approach. For example, the large spikes up to 36 kg/day in a thorium consumption 
+occurs every 3435 days. This is required due to batch-wise removal of strong 
+absorbers (Rb, Sr, Cs, Ba). The corresponding effective multiplication factor 
+increase (Figure~\ref{fig:keff}) and breeding intensification leads to 
+additional $^{232}$Th consumption. 
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
 
-The average thorium feed rate increases during the first 500 days of operation and than steadily decreases due to spectrum hardening and accumulation of absorbers in the core.
-As a result, the average $^{232}$Th feed rate over 60 years of operation is about 2.40 kg/day.
-This results are in a good agreement with a recent online reprocessing study by \gls{ORNL} \cite{betzler_molten_2017}.
+The average thorium feed rate increases during the first 500 days of operation 
+and than steadily decreases due to spectrum hardening and accumulation of 
+absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
+years of operation is about 2.40 kg/day. This results are in a good agreement 
+with a recent online reprocessing study by \gls{ORNL} 
+\cite{betzler_molten_2017}.
 
 \subsection{The effect of removing fission product from fuel salt}
-Loading initial fuel salt composition into the \gls{MSBR} core leads to supercritical configuration (Figure ~\ref{fig:fp_removal}).
-After reactor startup the effective multiplication factor for the case with volatile gases and noble metals removal is approximately 7500 pcm  higher than for case with no fission products removal.
-This significant impact on the reactor core achieved due to immediate removal (20 sec cycle time) and high absorption cross section of Xe, Kr, Mo, and other noble metals removed.
-The effect of rare earth element removal considerable after few month from startup and achieves approximately 5500 pcm after 10 years of operation.
-The rare earth elements are removed with slower rate (50 days cycle time).
-Moreover, Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day step even strong absorbers did not necessarily leads to fluctuation in results but rare earth elements removal every 50 days causes approximately 600 pcm jump in reactivity.
+Loading initial fuel salt composition into the \gls{MSBR} core leads to 
+supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
+startup the effective multiplication factor for the case with volatile gases and 
+noble metals removal is approximately 7500 pcm  higher than for case with no 
+fission products removal. This significant impact on the reactor core achieved 
+due to immediate removal (20 sec cycle time) and high absorption cross section 
+of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth element 
+removal considerable after few month from startup and achieves approximately 
+5500 pcm after 10 years of operation. The rare earth elements are removed with 
+slower rate (50 days cycle time). Moreover, Figure~\ref{fig:fp_removal} 
+demonstrates that batch-wise removal every 3-day step even strong absorbers did 
+not necessarily leads to fluctuation in results but rare earth elements removal 
+every 50 days causes approximately 600 pcm jump in reactivity.
 
-The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively.
-The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime.
-Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
+The effective multiplication factor of the core reduces gradually over operation 
+time because the fissile material ($^{233}$U) continuously depletes from the 
+fuel salt due to fission and, at the same time, fission products accumulates in 
+the fuel salt.	Eventually, without fission products removal, the reactivity 
+decreases to the subcritical state after approximately 500 and 1300 days of 
+operation for cases with no removal and volatile gases \& noble metals removal, 
+respectively. The time when the simulated core reaches subcriticality 
+($k_{eff}<$1.0) for full-core model) called the core lifetime. Therefore, 
+removing fission products provides with significant neutronic benefit because 
+allows achieve longer core lifetime.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 
@@
   \includegraphics[width=\textwidth]{keff_rem_cases.png} 
-  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} 
+model with removal of different fission product groups over 10 years of 
+operation.}
   \label{fig:fp_removal}

### 2018-08-25 introduction.tex

@@
 calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
-liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}. 
-It is also reports the application of the coupled SaltProc-SERPENT 2 system to 
-the \gls{MSBR}, which represents the continuation of the work presented in 
-\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
-of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
-the equilibrium core composition and core depletion. The additional objective is 
-to compare predicted operational and safety parameters of the \gls{MSBR} at both 
-the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
+liquid-fueled \gls{MSR} operation 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
+application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
+extension of the work presented in 
+\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
+analyze \gls{MSBR} neutronics and fuel cycle to find 
+the equilibrium core composition. The additional objective 
+is to compare predicted operational and safety parameters of the \gls{MSBR} at 
+both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
 determined and \gls{MSBR} fuel cycle performance will be analyzed.
 
-The \gls{MSBR} complex geometry is hard to describe in software input, and, 
+The complex \gls{MSBR} geometry is challenging to describe in software input, 
+and, 
 usually, researchers make significant geometric simplifications to model it 
-\cite{park_whole_2015}. Note that this study leverages extensive computational 
-resources to avoid these geometric approximations and accurately capture 
-breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
-Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
-related to circulating liquid fuel, is not treated here.
+\cite{park_whole_2015}. This study leverages extensive computational 
+resources to avoid these geometric approximations in order to accurately capture 
+breeding behavior.

### 2018-08-25 introduction.tex
Conflicts resolved (hopefully)

--- 2018-08-25 introduction.tex
@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
-in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
-\glspl{MSR} among the six advanced reactor concepts promising for further 
-research and development.
+The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
+in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
+included \glspl{MSR} among the six advanced reactor concepts promising for 
+further research and development. 
 \glspl{MSR} offer significant improvements ``in the four broad areas of 
@@
 relatively high coolant temperature, outstanding neutron economy, improved 
- safety parameters, reduced fuel preprocessing, and the ability to 
- continuously remove fission products and add fissile and/or fertile elements 
+safety parameters, reduced fuel preprocessing, and the ability to continuously 
+remove fission products and add fissile and/or fertile elements 
 \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
- early 1970s by \gls{ORNL} to explore the promise of the thorium 
+early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
- continuous fuel reprocessing, the \gls{MSBR}
- realizes the advantages of the thorium fuel cycle because the $^{233}$U bred from 
+continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
+thorium fuel cycle because the $^{233}$U bred from 
 $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
@@
 ($\tau_{1/2}$=26.967d).} recycled back to the core 
- \cite{betzler_modeling_2016}. The chosen fuel salt, 
- LiF-BeF$_2$-ThF$_4$-UF$_4$, has a $499^\circ$C melting point, a low vapor 
- pressure at operating temperatures, 
- and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
- In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
- quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
- cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
- for transmutation of spent fuel from current \glspl{LWR}.
+\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
+melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
+and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
+the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
+of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
+Finally, the \gls{MSR} also could be employed as a converter reactor for 
+transmutation of spent fuel from current \glspl{LWR}.
 
@@
 
-References \cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,
-aufiero_extended_2013} provide some form of reactivity control, and methods 
-\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,
-ahmad_neutronics_2015, park_whole_2015, jeong_equilibrium_2016,rykhlevskii_online_2017,
-nuttin_potential_2005} use a set of all nuclides in depletion calculations.
+References 
+\cite{doligez_coupled_2014,heuer_towards_2014,sheu_depletion_2013,aufiero_extended_2013} 
+simulate some form of reactivity control, and methods 
+\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,ahmad_neutronics_2015, 
+park_whole_2015, 
+jeong_equilibrium_2016,rykhlevskii_online_2017,nuttin_potential_2005} use a set 
+of all nuclides in depletion calculations.
 
-Liquid-fueled \gls{MSR} designs have online separations and feeds, where material 
-is moved to or from the core at specific time steps (batch) or continuously. In 
-batch-wise approach the burn-up simulation stops at a given time and restart with
-a new liquid fuel composition (after removal of discarded materials and addition 
-of fissile/fertile materials). \gls{ORNL} researchers have developed ChemTriton, 
-a Python-based script for SCALE/TRITON which the batch-wise to simulate a continuous 
-reprocessing. This tool models salt treatment, separations, discharge, and refill 
-using a unit-cell \gls{MSR} SCALE/TRITON depletion simulation over small time steps 
-to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}. 
-Methods listed in references \cite{fiorina_investigation_2013,sheu_depletion_2013,
-park_whole_2015, jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,
-rykhlevskii_online_2017} and current work employ a batch-wise approach.
+Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
+material moves to and from the core at specific time steps (batch) or 
+continuously. In batch-wise approach the burn-up simulation stops at a given 
+time and restart with a new liquid fuel composition (after removal of discarded 
+materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
+have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
+batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
+treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
+SCALE/TRITON depletion simulation over small time steps to simulate continuous 
+reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
+references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
+jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
+and current work employ a batch-wise approach.
 
-Accounting for a continuous removal or addition is more difficult because it requires
-adding a term to the Bateman equations. In SCALE \cite{bowman_scale_2011}, 
-ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using 
-spectrum-averaged fluxes and cross sections generated from a deterministic transport 
-calculation. Approaches listed in references \cite{doligez_coupled_2014,heuer_towards_2014,
-aufiero_extended_2013,nuttin_potential_2005} model true continuous feeds and removals.
+Accounting for continuous removal or addition presents a greater challenge since it 
+requires adding a term to the Bateman equations. In SCALE 
+\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
+Bateman equations using spectrum-averaged fluxes and cross sections generated 
+from a deterministic transport calculation. Approaches listed in references 
+\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
+model true continuous feeds and removals.
 
-Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in 
-\cite{park_whole_2015, jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, 
-betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}. Nevertheless, most of 
-these efforts considered only simplified unit-cell geometry because depletion computations 
-for a many-year fuel cycle are computationally expesive even for simple models.
+Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are 
+described in \cite{park_whole_2015, 
+jeong_equilibrium_2016,powers_new_2013,powers_inventory_2014, 
+betzler_molten_2017,rykhlevskii_online_2017,nuttin_potential_2005}. 
+Nevertheless, most of these efforts considered only simplified unit-cell 
+geometry because depletion computations for a many-year fuel cycle are 
+computationally expensive even for simple models.
 
@@
 \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
-betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
-approach misrepresents the two-region breeder reactor concept. The unit-cell or 
-one-region models may produce reliable results for homogeneous reactor cores 
-(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
-(i.e. \gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
+betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
+misrepresent the two-region breeder reactor concept. The unit-cell or one-region 
+models may produce reliable results for homogeneous reactor cores (i.e. 
+\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
+\gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
 model to capture different neutron transport characteristics in the inner and 
@@
 
-The complex \gls{MSBR} geometry is challenging to describe in software input, and, 
+The complex \gls{MSBR} geometry is challenging to describe in software input, 
+and, 
 usually, researchers make significant geometric simplifications to model it 

### 2018-08-25 results.tex
Conflicts resolved (hopefully)

--- 2018-08-25 results.tex
@@
   \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
-  model for a 60-year reactor operation. The confidence interval 
-  $\sigma=\pm15pcm$ is shaded.}
+  model for a 60-year reactor operation.}
   \label{fig:keff}
@@
 \subsection{Fuel salt composition dynamics}
-
 The analysis of the fuel salt composition evolution provides more comprehensive 
@@
 density of major nuclides which have a strong influence on the reactor core 
-physics. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
+physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
 fuel salt change insignificantly after approximately 2500 days of operation. 
 Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time 
-interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was 
+interval from 16 to 20 years of operation. Hence, a quasi-equilibrium state was 
 achieved after 16 years of reactor operation.
@@
 accumulation and keep the reactor critical.
-\begin{figure}[htp!] % replace 't' with 'b' to \centering
+\begin{figure}[htp!] % replace 't' with 'b' to 
+  \centering
   \includegraphics[width=\textwidth]{fissile_short.png}
@@
 $^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
-the core during reactor operation.  \begin{figure}[ht!] % replace 't' with 'b' 
-        to force it to \centering
+the core during reactor operation.  
+\begin{figure}[ht!] % replace 't' with 'b'         to force it to 
+  \centering
   \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
@@
 central core region (zone I), the neutron energy spectrum shifts to a harder spectrum 
-over 20 years of reactor operation. In contrast, in the outer core region (zone II) a 
-similar spectral shift takes place at a reduced scale. This resuls is in a good 
+over 20 years of reactor operation. Meanwhile, in the outer core region (zone II) a 
+similar spectral shift takes place at a reduced scale. This results is in a good 
 agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent 
@@
   \includegraphics[width=\textwidth]{keff_rem_cases.png} 
-  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
+  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} 
+model with removal of various fission product groups over 10 years of 
+operation.}
   \label{fig:fp_removal}

### 2018-08-26 abstract.tex
Word hard wrap 80 col
Minor grammatical issues were implemented

@@
 
-Nowadays climate change pushes humankind in search new ways to generate carbon-free, reliable, nonintermittent base load power.
-That is reason why interest in advanced nuclear energy and, particularly \glspl{MSR} has resurged, with multiple new companies pursuing commercialization of \gls{MSR} designs\footnote{Examples include both liquid-fueled and solid-fueled molten salt designs from
-Transatomic, Terrapower, Terrestrial, Moltex Energy, and Thorcon.}.
-To further develop these \gls{MSR} concepts researchers need tools for analyzing liquid fueled molten salt reactor depletion and fuel processing.
-However, most contemporary nuclear reactor physics software is unable to perform high-fidelity full-core depletion calculations in an online reprocessing regime.
-This paper introduces a Python script, SaltProc, which couples with the Monte Carlo code, SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt.
-SaltProc capabilities was demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} concept and compared well to previous results from lower fidelity analyses.
+Today climate change pushes humankind in search new ways to generate 
+carbon-free, reliable base load power. Thus,
+interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
+with multiple new companies pursuing commercialization of \gls{MSR} 
+designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
+develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
+fueled molten salt reactor depletion and fuel processing. However, most 
+contemporary nuclear reactor physics software is unable to perform high-fidelity 
+full-core depletion calculations in an online reprocessing regime. This paper 
+introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
+SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing 
+isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
+demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
+concept and compared well to previous results from lower fidelity analyses.
 

### 2018-08-26 introduction.tex
Minor grammatical issues were implemented

@@
 Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
-material moves to and from the core at specific time steps (batch) or 
-continuously. In batch-wise approach the burn-up simulation stops at a given 
-time and restart with a new liquid fuel composition (after removal of discarded 
+material moves to and from the core continuously or at specific time steps 
+(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
+time and restarts with a new liquid fuel composition (after removal of discarded 
 materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
@@
 jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
-and current work employ a batch-wise approach.
+as well as the current work employ a batch-wise approach.
 
@@
 Bateman equations using spectrum-averaged fluxes and cross sections generated 
-from a deterministic transport calculation. Approaches listed in references 
+from a deterministic transport calculation. Meanwhile, approaches listed in references 
 \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
@@
 betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
-misrepresent the two-region breeder reactor concept. The unit-cell or one-region 
+misrepresents the two-region breeder reactor concept. The unit-cell or one-region 
 models may produce reliable results for homogeneous reactor cores (i.e. 

### 2018-08-26 results.tex
Minor grammatical issues were implemented

@@
 physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
-fuel salt change insignificantly after approximately 2500 days of operation. 
-Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time 
+the fuel salt change insignificantly after approximately 2500 days of operation. 
+Particularly, the $^{233}$U number density fluctuates less than 0.8\% in the time 
 interval from 16 to 20 years of operation. Hence, a quasi-equilibrium state was 
@@
 Therefore, removing fission products provides with significant neutronic benefit 
-because allows achieve longer core lifetime.
+and enables a longer core lifetime.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to 

### 2018-08-26 methods.tex
Conflicts resolved (hopefully)

--- 2018-08-25 methods.tex
@@
 
-Liquid-fueled systems ability to continuously remove fission products and add 
+The ability of liquid-fueled systems to continuously remove fission products and add 
 fissile and/or fertile elements is the main challenge for depletion simulations. 
-Introduced in this work Python-package, SaltProc, takes into account online 
-separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron 
+The python package introduced in this work, SaltProc, takes into account online 
+separations and feeds using the SERPENT 2 continuous-energy Monte Carlo neutron 
 transport and depletion code.
@@
         \end{tabularx}
-        %\footnotetext{Chemical processing plant and gas separation system 
-        %removing chemical elements (not isotopes) only. Isotopes instead of 
-        %elements listed because other isotopes are short-lived and might be 
-        %ignored.}
         \label{tab:reprocessing_list}

### 2018-08-30 abstract.tex
Teddy's comments implemented #20

@@
 
-Today climate change pushes humankind in search new ways to generate 
+Today climate change pushes humankind in search of new ways to generate 
 carbon-free, reliable base load power. Thus,
@@
 contemporary nuclear reactor physics software is unable to perform high-fidelity 
-full-core depletion calculations in an online reprocessing regime. This paper 
+full-core depletion calculations for a reactor design with online reprocessing. This paper 
 introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
-SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing 
+SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
 isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
 demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
-concept and compared well to previous results from lower fidelity analyses.
+concept and compared well to previous results from lower-fidelity analyses.
 

### 2018-08-30 conclusion.tex
Thesis --> work
Teddy's comments implemented #20

@@
 than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state 
-after 16 years of operation. On the other hand, a wide diversity of nuclides, 
+after 16 years of operation. On the other hand, a wide variety of nuclides, 
 including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
@@
 
-For thermal spectrum \gls{MSBR} removal of volatile gases, noble metals, and 
+For thermal spectrum \gls{MSBR}, removal of volatile gases, noble metals, and 
 rare earths from a fuel salt benefits core performance.
@@
 Only the batch-wise online reprocessing approach has been treated in this 
-thesis. However, the SERPENT 2 Monte Carlo code was recently extended for 
+work. However, the SERPENT 2 Monte Carlo code was recently extended for 
 continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 

### 2018-08-30 methods.tex
Teddy's comments implemented #20

@@
 top of the vessel for cooling the top head and axial reflector. 
-Figure~\ref{fig:serpent_zoneII} also shows :w
+Figure~\ref{fig:serpent_zoneII} also shows
 the 5.08-cm-wide annular 
@@
 addition, SaltProc provides a set of functions for each stream: read and write 
-isotopic data in/from database, separate out specific isotopes from stream with 
+isotopic data in/from database, separate out specific elements from stream with 
 defined efficiency, feed in specific isotopes to stream, and maintain constant 
@@
 are crucial to simulating the operation of a complex, multi-zone, multi-fluid 
-\gls{MSR} and sufficiently general to represent myriad reactor systems.
+\gls{MSR} and are sufficiently general to represent myriad reactor systems.
 
@@
 support for entirely user-customized reprocessing strategies, two-region \gls{MSR} modeling 
-capabilities,
-and decay modeling.
+capabilities, and decay modeling in tanks.
 

### 2018-08-30 results.tex
Teddy's comments implemented #20

@@
 of cycle time (fresh fuel composition for the first step). Next, it computes 
-the new fuel salt composition for the end of a 3-day depletion step. The 
+the new fuel salt composition at the end of a 3-day depletion step. The 
 corresponding effective multiplication factor is much smaller than the previous 
 one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
-applying feeds and removals. $K_{eff}$ this increases accordingly since major reactor 
+applying feeds and removals. This $K_{eff}$ increases accordingly since major reactor 
 poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
@@
 over 20 years of reactor operation. Meanwhile, in the outer core region (zone II) a 
-similar spectral shift takes place at a reduced scale. This results is in a good 
-agreement with original ORNL report \cite{robertson_conceptual_1971} and most recent 
+similar spectral shift takes place at a reduced scale. These results are in a good 
+agreement with original ORNL report \cite{robertson_conceptual_1971} and the most recent 
 whole-core steady-state study \cite{park_whole_2015}.
@@
 Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
-neutron flux for both initial and equilibrium composition. The neutron flux has 
+neutron flux for the both initial and equilibrium composition. The neutron flux has 
 the same shape for both compositions but the equilibrium case has a harder 
@@
 Table~\ref{tab:powgen_fraction} shows the power fraction in each zone for 
-initial and equilibrium fuel composition. Figure~\ref{fig:pow_den} reflects the 
+initial and equilibrium fuel compositions. Figure~\ref{fig:pow_den} reflects the 
 normalized power distribution of the \gls{MSBR} quarter core which is the same 
@@
 the core, the graphite rods are gradually withdrawn from the core. In an 
-accident, the safety rods would fall down into the core. The integral rod 
+accident, the safety rods would be dropped down into the core. The integral rod 
 worths were calculated for various positions to separately estimate control 
@@
 supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
-startup the effective multiplication factor for the case with volatile gases 
+startup, the effective multiplication factor for the case with volatile gases 
 and noble metals removal is approximately 7500 pcm  higher than for case with 
-no fission products removal. This significant impact on the reactor core 
+no fission products removal. This significant impact on the reactor core is
 achieved due to immediate removal (20 sec cycle time) and high absorption cross 
 section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
-element removal considerable after few month from startup and achieves 
+element removal is considerable after few month from startup and achieves 
 approximately 5500 pcm after 10 years of operation. The rare earth elements are 
-removed with slower rate (50 days cycle time). Moreover, 
+removed with a slower rate (50 days cycle time). Moreover, 
 Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day 
 step even strong absorbers did not necessarily leads to fluctuation in results 
-but rare earth elements removal every 50 days causes approximately 600 pcm jump 
+but rare earth elements removal every 50 days causes an approximately 600 pcm jump 
 in reactivity.
@@
 from the fuel salt due to fission and, at the same time, fission products 
-accumulates in the fuel salt.	Eventually, without fission products removal, 
+accumulate in the fuel salt.	Eventually, without fission products removal, 
 the reactivity decreases to the subcritical state after approximately 500 and 
@@
 metals removal, respectively. The time when the simulated core reaches 
-subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
+subcriticality ($k_{eff}<$1.0) for full-core model) is called the core lifetime. 
 Therefore, removing fission products provides with significant neutronic benefit 

### 2018-08-31 abstract.tex
Ansh edits incorporated #21

@@
 
-Today climate change pushes humankind in search of new ways to generate 
-carbon-free, reliable base load power. Thus,
+Today,  climate change is driving the search for new ways to generate 
+carbon-free, reliable base-load power. Thus,
 interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
@@
 develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
-fueled molten salt reactor depletion and fuel processing. However, most 
+fueled \gls{MSR} depletion and fuel processing. However, most 
 contemporary nuclear reactor physics software is unable to perform high-fidelity 

### 2018-08-31 introduction.tex
Ansh edits incorporated #21

@@
 in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
-included \glspl{MSR} among the six advanced reactor concepts promising for 
+included \glspl{MSR} among the six most promising advanced reactor concepts for 
 further research and development. 
@@
 \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
-early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
+early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
@@
 thorium fuel cycle because the $^{233}$U bred from 
-$^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
+$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
 $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
 ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
-($\tau_{1/2}$=26.967d).} recycled back to the core 
+($\tau_{1/2}$=26.967d).} recycled back into the core 
 \cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
@@
 Liquid-fueled systems present a challenge to existing neutron transport and
-depletion tools which are typically designed to simulate solid-fueled reactors. 
+depletion tools, which are typically designed to simulate solid-fueled reactors. 
 To handle the material flows and potential online removal and feed of 
@@
 this approach, recent tools from universities and research institutions can
-approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
-in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis.
-These  couple external tools to neutron transport while depletion codes take into
-account continuous feeds and removals in \glspl{MSR}. A summary of recent
-efforts are listed in table~\ref{tab:fs_codes}.
+approximate online refueling \cite{serp_molten_2014}. A summary of recent
+efforts is listed in table~\ref{tab:fs_codes}.
 
@@
 \FloatBarrier
-
-Most of these methods are also applicable to thermal spectrum \glspl{MSR}. 
-Additional tools developed specifically for thermal \gls{MSR} applications are 
-also listed in table~\ref{tab:fs_codes}.
 
@@
 one for salt channels, one for the salt plena above and below the core and the 
-last cell for the annulus, consequently, the two-region reactor core was 
+last cell for the annulus. Consequently, the two-region reactor core was 
 approximated by one region with averaged fuel/moderator ratio 
@@
 The complex \gls{MSBR} geometry is challenging to describe in software input, 
-and, 
-usually, researchers make significant geometric simplifications to model it 
+and usually researchers make significant geometric simplifications to model it 
 \cite{park_whole_2015}. This study leverages extensive computational 

### 2018-08-31 methods.tex
Ansh edits incorporated #21

@@
 separations and feeds using the SERPENT 2 continuous-energy Monte Carlo neutron 
-transport and depletion code.
+transport and depletion code. In this work, all figures of the core model
+were generated using the built-in SERPENT 2 plotter.
 
@@
 neutron irradiation, the reactor core was designed for periodic replacement. 
-Based on the experimental irradiation data from \gls{MSRE}, the core graphite 
-lifetime is about 4 years and reflector graphite lifetime is 30 years 
+Based on the experimental irradiation data from the \gls{MSRE}, the core graphite 
+lifetime is about 4 years and the reflector graphite lifetime is 30 years 
 \cite{robertson_conceptual_1971}.
@@
 dimensions of the reactor vessel, and serves to reduce the damaging flux at the 
-surface of the graphite reflector blocks. In this work, all figures of the core 
-were generated using the built-in SERPENT 2 plotter.
+surface of the graphite reflector blocks.
 
@@
 \subsubsection{Core zone II}
-Zone II which is undermoderated, surrounds zone I. Combined with the bounding 
+Zone II, which is undermoderated, surrounds zone I. Combined with the bounding 
 radial reflector, zone II serves to diminish neutron leakage. Two kinds of 
@@
 exactly 37\%, so that this simplification did not considerably change the core 
-neutronics. Simplyfying the eight edge channels was te only simplification made 
+neutronics. Simplyfying the eight edge channels was the only simplification made 
 to the \gls{MSBR} geometry in this work.
@@
 The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
-Hastelloy-N is very common in reactors now but have been studied and developed 
+Hastelloy-N is very common in reactors now but has been studied and developed 
 at \gls{ORNL} in a program that started in 1950s.} 
@@
 \cite{robertson_conceptual_1971}. The lithium in the molten salt fuel is fully 
-enriched in $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
+enriched to 100\% $^{7}$Li because $^{6}$Li is a very strong neutron poison and 
 becomes tritium upon neutron capture.
@@
         %\centering
-        \caption{Summary of principal data for MSBR 
+        \caption{•} of principal data for MSBR 
         \cite{robertson_conceptual_1971}.}
@@
 since these metals act as neutron poisons. Some designs suggest a more complex 
-list of elements to process (figure ~\ref{fig:periodic_tab}), including the 
+list of elements to process (figure~\ref{fig:periodic_tab}), including the 
 temporary removal of protactinium or other regulation of the 
@@
 \end{table}
-Th removal rates vary among nuclides in this reactor concept which dictate the 
+The removal rates vary among nuclides in this reactor concept which dictate the 
 necessary resolution of depletion calculations. If the depletion time intervals 
@@
 geometry with high fidelity.  The primary function of SaltProc is to 
-manage material streams while
-SERPENT 2 performs the computationally heavy work, namely neutron 
-transport and depletion
-calculations. Saltproc is defined as a python class, where each material stream 
-is defined as a isotopic atomic density
+manage material streams while SERPENT 2 performs the neutron 
+transport and depletioncalculations. Saltproc is defined as a python class, where 
+each material stream is defined as a isotopic atomic density
 vector variable. This allows tracking of time-sensitive material streams such 
-as the
-$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
+as the 	$^{233}$Pa tank in the \gls{MSBR}. The user can define the reprocessing 
 parameters, such as the reprocessing interval and removal efficiency.  In 
@@
 
-SaltProc, currently in active development in Github (https://github.com/ 
+SaltProc, currently in active development on Github (https://github.com/ 
 arfc/saltproc), leverages unit tests and continuous integration for 
@@
 SaltProc can manage as many material streams as desired. It also may work with 
-multiple depletion materials. At the end of a each depletion step, SaltProc 
+multiple depletion materials. At the end of each depletion step, SaltProc 
 reads the depleted compositions and tracks each material stream individually. 
@@
 
-Saltproc datasets are timseries, meaning that every value is recorded every 
+Saltproc datasets are time-series, meaning that every value is recorded every 
 timestep. The datasets SaltProc produces are listed below,

### 2018-08-31 conclusion.tex
Gwen's edits implemented @22

@@
 this work has 
-been to demonstrate the SaltProc capability to find the equilibrium fuel salt 
+been to demonstrate SaltProc's capability to find the equilibrium fuel salt 
 composition (where equilibrium is defined as when the number densities of major 
@@
 breeding in the outer core zone. When running depletion calculations, the most 
-important fission products and $^{233}$Pa are removed and fertile/fissile 
+important fission products and $^{233}$Pa are removed while fertile and fissile 
 materials are added to the fuel salt every 3 days.  Meanwhile, the removal 
 interval for the rare earths, volatile fluorides, and seminoble metals was more 
-than month which causes effective multiplication factor fluctuation.
+than month which caused effective multiplication factor fluctuation.
 
@@
 than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state 
-after 16 years of operation. On the other hand, a wide variety of nuclides, 
+after 16 years of operation. However, a wide variety of nuclides, 
 including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
@@
 temperature coefficient is positive and also decreases during fuel depletion. 
-From reactivity control system efficiency analysis, showed the safety rod integral 
+The reactivity control system efficiency analysis showed that the safety rod integral 
 worth decreases by approximately 16.2\% over 16 years of operation, while 
-graphite rod integral worth remains constant. Summing up, neutron energy 
+graphite rod integral worth remains constant. Therefore, neutron energy 
 spectrum hardening during fuel salt depletion has an undesirable impact on 
 \gls{MSBR} stability and controllability, and should be taken into 
-consideration in further analysis of accident transient scenarios.
+consideration in further analysis of transient accident scenarios.
 
@@
 
-For thermal spectrum \gls{MSBR}, removal of volatile gases, noble metals, and 
-rare earths from a fuel salt benefits core performance.
+The \gls{MSBR} core performance benefits from the removal of volatile gases, 
+noble metals, and rare earths from the fuel salt. 
 Moreover, immediate removal of volatile gases (e.g., xenon) and noble metals 
@@
 elements (every 50 days cycle instead of 3 days) has less impact (5500 pcm) on 
-the core reactivity after 10 years of operation. In sum, additional study 
+the core reactivity after 10 years of operation. An additional study 
 is needed to establish neutronic  and economic tradeoffs of removing each element.

### 2018-08-31 results.tex
Gwen's edits implemented @22

@@
         amount of time required to remove 100\% of a target nuclide from a fuel 
-salt.} which was fixed at 3 days for this work. The effective multiplication 
+salt.} (3 days for this work). The effective multiplication 
 factor fluctuates significantly as a result of the batch-wise nature of this 
@@
   \caption{Effective multiplication factor dynamics for full-core \gls{MSBR} 
-  model for a 60-year reactor operation.}
+  model over a 60-year reactor operation lifetime.}
   \label{fig:keff}
@@
 First, SERPENT calculates the effective multiplication factor for the beginning 
-of cycle time (fresh fuel composition for the first step). Next, it computes 
-the new fuel salt composition at the end of a 3-day depletion step. The 
+of cycle time (there is fresh fuel composition at the first step). Next, it 
+computes the new fuel salt composition at the end of a 3-day depletion. The 
 corresponding effective multiplication factor is much smaller than the previous 
 one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
-applying feeds and removals. This $K_{eff}$ increases accordingly since major reactor 
+applying feeds and removals. $K_{eff}$ increases accordingly since major reactor 
 poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
@@
 the fuel salt change insignificantly after approximately 2500 days of operation. 
-Particularly, the $^{233}$U number density fluctuates less than 0.8\% in the time 
-interval from 16 to 20 years of operation. Hence, a quasi-equilibrium state was 
+In particular, the $^{233}$U number density fluctuates less than 0.8\% between
+ 16 and 20 years of operation. Hence, a quasi-equilibrium state was 
 achieved after 16 years of reactor operation.
@@
 isotopes in the core. In the end of the considered operational time, the core 
-contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+contains significant amount of $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
 ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
@@
 the core (zone I) when for the outer region (zone II) it is negligible for fast 
-but notable for thermal neutrons. This neutron flux radial distribution is in a 
+but notable for thermal neutrons. This neutron flux radial distribution is in 
 good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
@@
 Spectral shift does not cause significant changes in power nor in breeding 
-distribution. Even after 20 years of operation, most of the power still is 
-generated in zone I though the majority of $^{233}$Th is produced in zone II.
+distribution. Even after 20 years of operation, most of the power is still 
+generated in zone I with exception to the majority of $^{233}$Th that is 
+produced in zone II.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
@@
 of graphite decreases creating additional space for fuel salt. To determine 
-temperature coefficients, the cross section temperatures for fuel and moderator 
-were changed from 900K to 1000K. Three different cases were considered:
+temperature coefficients, the cross section temperatures for the fuel and 
+moderator were changed from 900K to 1000K. Three different cases were considered:
 \begin{enumerate}
@@
   state.}
-\begin{tabularx}{\textwidth}{ s | s | s | x } \hline
+\begin{tabularx}{\textwidth}{ m | s | s | x } \hline
    Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
@@
 equilibrium fuel composition due to thermal Doppler broadening of the resonance 
-capture cross sections in the thorium and is in a good agreement with earlier 
+capture cross sections in the thorium. This is in good agreement with earlier 
 research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
@@
 graphite moderator rods\footnote{In \cite{robertson_conceptual_1971}, the 
-graphite rods are referred to as ``control'' rods.}, safety (B$_4$C) rod, and 
+graphite rods are referred to as ``control'' rods.}, safety (B$_4$C) rods, and 
 the whole reactivity control system worth. Control rod integral worth is 
@@
 \subsection{Thorium refill rate}
-In \gls{MSBR} reprocessing scheme the only external feed material flow  is 
+In a \gls{MSBR} reprocessing scheme the only external feed material flow  is 
 $^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
@@
 fluctuates significantly as a result of the batch-wise nature of this online 
-reprocessing approach. For example, the large spikes up to 36 kg/day in a 
+reprocessing approach. For example, the large spikes of up to 36 kg/day in a 
 thorium consumption occurs every 3435 days. This is required due to batch-wise 
@@
 The average thorium feed rate increases during the first 500 days of operation 
-and than steadily decreases due to spectrum hardening and accumulation of 
+and steadily decreases due to spectrum hardening and accumulation of 
 absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
-years of operation is about 2.40 kg/day. This results are in a good agreement 
-with a recent online reprocessing study by \gls{ORNL} 
+years of operation is about 2.40 kg/day. This thorium consumption rate is in 
+good agreement with a recent online reprocessing study by \gls{ORNL} 
 \cite{betzler_molten_2017}.
@@
 \subsection{The effect of removing fission product from fuel salt}
-Loading initial fuel salt composition into the \gls{MSBR} core leads to 
+Loading initial fuel salt composition into the \gls{MSBR} core leads to a 
 supercritical configuration (Figure ~\ref{fig:fp_removal}). After reactor 
@@
 section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
-element removal is considerable after few month from startup and achieves 
+element removal is considerable a few months after startup and achieves 
 approximately 5500 pcm after 10 years of operation. The rare earth elements are 
-removed with a slower rate (50 days cycle time). Moreover, 
-Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal every 3-day 
-step even strong absorbers did not necessarily leads to fluctuation in results 
+removed at a slower rate (50-day cycle time). Moreover, 
+Figure~\ref{fig:fp_removal} demonstrates that batch-wise removal of strong 
+absorbers every 3 days did not necessarily leads to fluctuation in results 
 but rare earth elements removal every 50 days causes an approximately 600 pcm jump 
@@
 operation time because the fissile material ($^{233}$U) continuously depletes 
-from the fuel salt due to fission and, at the same time, fission products 
-accumulate in the fuel salt.	Eventually, without fission products removal, 
+from the fuel salt due to fission and, while, fission products 
+accumulate in the fuel salt simultaneously. Eventually, without fission products removal, 
 the reactivity decreases to the subcritical state after approximately 500 and 

### 2018-09-02 results.tex
Park's edits implemented #23

@@
 Figure~\ref{fig:keff} shows the effective multiplication factors 
-obtained using SaltProc and SERPENT 2. The effective multiplication factors are 
+obtained using SaltProc and SERPENT 2. The effective multiplication factors were 
 calculated after removing fission products listed in 
@@
 First, SERPENT calculates the effective multiplication factor for the beginning 
-of cycle time (there is fresh fuel composition at the first step). Next, it 
+of the cycle (there is fresh fuel composition at the first step). Next, it 
 computes the new fuel salt composition at the end of a 3-day depletion. The 
@@
 one. Finally, SERPENT calculates $k_{eff}$ for the depleted composition after 
-applying feeds and removals. $K_{eff}$ increases accordingly since major reactor 
+applying feeds and removals. The $K_{eff}$ increases accordingly since major reactor 
 poisons (e.g. Xe, Kr) are removed, while fresh fissile material ($^{233}$U) 
@@
 Additionally, the presence of rubidium, strontium, cesium, and barium in the 
-core are disadvantageous to reactor physics. In fact, removal of these elements 
+core are disadvantageous to reactor physics. In fact, the removal of these elements 
 every 3435 days causes the multiplication factor to jump by approximately 450 
-pcm, and limits using the batch approach for online reprocessing simulation. 
+pcm, and limits using the batch approach for online reprocessing simulations. 
 Overall, the effective multiplication factor gradually decreases from 1.075 to 
-$k_{eff} \approx 1.02$ at equilibrium after approximately 6 years of 
-irradiation.
+$\approx$1.02 at equilibrium after approximately 6 years of irradiation.
 
@@
 The analysis of the fuel salt composition evolution provides more comprehensive 
-information about the equilibrium state. Figure~\ref{fig:adens_eq} shows number 
-density of major nuclides which have a strong influence on the reactor core 
+information about the equilibrium state. Figure~\ref{fig:adens_eq} shows the number 
+densities of major nuclides which have a strong influence on the reactor core 
 physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
 the fuel salt change insignificantly after approximately 2500 days of operation. 
-In particular, the $^{233}$U number density fluctuates less than 0.8\% between
+In particular, the $^{233}$U number density fluctuates by less than 0.8\% between
  16 and 20 years of operation. Hence, a quasi-equilibrium state was 
@@
   \centering
-  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
+  \includegraphics[scale=•]{•}=\textwidth]{major_isotopes_adens.png}
   \caption{Number density of major nuclides during 60 years of reactor 
@@
 In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
-$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
+$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), kept accumulating 
 in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
 isotopes in the core. In the end of the considered operational time, the core 
-contains significant amount of $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+contained significant amount of $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
 ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
@@
 isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
-production of new fissile materials in the core as well as $^{233}$U breeding 
-make it possible to compensate for negative effects of strong absorber 
+production of new fissile materials in the core, as well as $^{233}$U breeding, 
+made it possible to compensate for negative effects of strong absorber 
 accumulation and keep the reactor critical.
@@
 Figure~\ref{fig:spectrum_zones} shows that zone I produced more thermal neutrons 
-than zone II, corresponding to a majority of fissions occuring in the central part 
-of the core. In the undermoderated zone II, the neutron energy spectrum is harder 
-which leads to more capture of neutrons by $^{232}$Th and helps a achieve relatively 
+than zone II, corresponding to a majority of fissions occurring in the central part 
+of the core. In the undermoderated zone II, the neutron energy spectrum is harder, 
+which leads to more neutrons capture by $^{232}$Th and helps achieve relatively 
 high breeding ratio. Moreover, the (n,$\gamma$) resonance energy range in $^{232}$Th 
@@
 central core region (zone I), the neutron energy spectrum shifts to a harder spectrum 
-over 20 years of reactor operation. Meanwhile, in the outer core region (zone II) a 
+over 20 years of reactor operation. Meanwhile, in the outer core region (zone II), a 
 similar spectral shift takes place at a reduced scale. These results are in a good 
@@
 from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly 
-increase resonance absorption in thorium and decrease the absorptions in fissile and 
+increase resonance absorption in thorium and decrease absorptions in fissile and 
 construction materials. 
@@
 Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
-neutron flux for the both initial and equilibrium composition. The neutron flux has 
-the same shape for both compositions but the equilibrium case has a harder 
-spectrum. A significant spectral shift was observed for the central region of 
-the core (zone I) when for the outer region (zone II) it is negligible for fast 
-but notable for thermal neutrons. This neutron flux radial distribution is in 
+neutron flux for the both initial and equilibrium composition. The neutron fluxes
+have similar shapes for both compositions but the equilibrium case has a harder 
+spectrum. A significant spectral shift was observed in the central region of 
+the core (zone I), while for the outer region (zone II), it is negligible for fast 
+but notable for thermal neutrons. These neutron flux radial distributions is in 
 good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
 Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
-studied for designing the reactivity control system.
+studied when designing the reactivity control system.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
@@
 initial and equilibrium fuel compositions. Figure~\ref{fig:pow_den} reflects the 
-normalized power distribution of the \gls{MSBR} quarter core which is the same 
+normalized power distribution of the \gls{MSBR} quarter core, which is the same 
 at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 
@@
 $^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
-$^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this 
+$^{233}$Pa, which is the precursor for $^{233}$U production. Accordingly, this 
 characteristic represents the breeding distribution in the \gls{MSBR} core. 
@@
 Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated 
-in this work for both initial and equilibrium fuel composition, and compared 
-with original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
+in this work for both initial and equilibrium fuel compositions, compared 
+with the original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
 Uncertainty for each temperature coefficient also appears in 
@@
 bounded by the graphite. When the graphite temperature increases, the density 
-of graphite decreases creating additional space for fuel salt. To determine 
-temperature coefficients, the cross section temperatures for the fuel and 
+of graphite decreases, creating additional space for fuel salt. To determine 
+the temperature coefficients, the cross section temperatures for the fuel and 
 moderator were changed from 900K to 1000K. Three different cases were considered:
@@
 The fuel temperature coefficient (FTC) is negative for both initial and 
-equilibrium fuel composition due to thermal Doppler broadening of the resonance 
+equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
 capture cross sections in the thorium. This is in good agreement with earlier 
 research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
-temperature coefficient (MTC) is positive for startup composition and decreases 
+temperature coefficient (MTC) is positive for the startup composition and decreases 
 during reactor operation because of spectrum hardening with fuel depletion. 
@@
 Table~\ref{tab:rod_worth} summarizes the reactivity control system worth. 
-During normal operation the control (graphite) rods are fully inserted, and the 
+During normal operation, the control (graphite) rods are fully inserted, and the 
 safety (B$_4$C) rods are fully withdrawn. To insert negative reactivity into 
@@
 accident, the safety rods would be dropped down into the core. The integral rod 
-worths were calculated for various positions to separately estimate control 
-graphite moderator rods\footnote{In \cite{robertson_conceptual_1971}, the 
-graphite rods are referred to as ``control'' rods.}, safety (B$_4$C) rods, and 
-the whole reactivity control system worth. Control rod integral worth is 
+worths were calculated for various positions to separately estimate the worth
+of the control graphite rods\footnote{In \cite{robertson_conceptual_1971}, the 
+graphite rods are referred to as ``control'' rods.}, the safety (B$_4$C) rods, 
+and the whole reactivity control system. Control rod integral worth is 
 approximately 28 cents and stays almost constant during reactor operation. The 
@@
 \subsection{Six Factor Analysis}
-The effective multiplication factor could be expressed using formula:
+The effective multiplication factor can be expressed using next formula:
 \begin{align*}
@@
 fast fission factor ($\epsilon$) are considerably different between startup and 
-equilibrium. As indicated in Figure~\ref{fig:spectrum} the neutron spectrum is 
+equilibrium. As indicated in Figure~\ref{fig:spectrum}, the neutron spectrum is 
 softer at the beginning of reactor life. Neutron spectrum hardening causes the fast 
-fission to increase through the core lifetime. The opposite is true for the 
+fission factor to increase through the core lifetime. The opposite is true for the 
 resonance escape probability. Finally, the neutron reproduction factor 
@@
 \subsection{Thorium refill rate}
-In a \gls{MSBR} reprocessing scheme the only external feed material flow  is 
+In a \gls{MSBR} reprocessing scheme, the only external feed material flow  is 
 $^{232}$Th. Figure~\ref{fig:th_refill} shows the $^{232}$Th feed rate 
@@
 
-The average thorium feed rate increases during the first 500 days of operation 
+The average thorium feed rate increases during the first 500 days of operation, 
 and steadily decreases due to spectrum hardening and accumulation of 
@@
 section of Xe, Kr, Mo, and other noble metals removed. The effect of rare earth 
-element removal is considerable a few months after startup and achieves 
-approximately 5500 pcm after 10 years of operation. The rare earth elements are 
+element removal is considerable a few months after startup and reached 
+approximately 5500 pcm after 10 years of operation. The rare earth elements were 
 removed at a slower rate (50-day cycle time). Moreover, 
@@
 operation time because the fissile material ($^{233}$U) continuously depletes 
-from the fuel salt due to fission and, while, fission products 
+from the fuel salt due to fission while fission products 
 accumulate in the fuel salt simultaneously. Eventually, without fission products removal, 

### 2018-09-06 introduction.tex
which was is pointless verbage
MSBR should probably be introduced earlier, but its ok... as is, seems alright.. but should be its own paragraph
word order

@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
-in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
+The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
+in the 1950s and operated in the 1960s. More recently, the \gls{GIF}  
 included \glspl{MSR} among the six most promising advanced reactor concepts for 
@@
 remove fission products and add fissile and/or fertile elements 
-\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
-early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
+\cite{leblanc_molten_2010}.
+
+The thorium-fueled \gls{MSBR} was developed in the 
+early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 

### 2018-09-06 introduction.tex
easy active voice fixes

@@
 melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
-and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
-the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
+and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
+With regard to the nuclear fuel cycle, the thorium cycle produces a reduced quantity 
 of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
@@
 jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
-as well as the current work employ a batch-wise approach.
+as well as the current work similarly employ a batch-wise approach.
 
@@
 
-Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
-one for salt channels, one for the salt plena above and below the core and the 
-last cell for the annulus. Consequently, the two-region reactor core was 
+Nuttin \emph{et al.} broke up the reactor core geometry into three \gls{MCNP} cells: 
+one for salt channels, one for the salt plena above and below the core, and a 
+third cell for the annulus. Consequently, the two-region reactor core was 
 approximated by one region with averaged fuel/moderator ratio 
-\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
+\cite{nuttin_potential_2005}.  Powers \emph{et 
 al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
 \cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
-betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
+betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016} used a 
+similar approach. This approach 
 misrepresents the two-region breeder reactor concept. The unit-cell or one-region 

### 2018-09-06 introduction.tex
rephrasing introduction for more active voice and consistency of tense

@@
 model to capture different neutron transport characteristics in the inner and 
-outer regions of the core. In particular, most fissions happens in the inner 
+outer regions of the core. In particular, most fissions happen in the inner 
 region while breeding occurs in the outer zone.
@@
 Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
-employed it to study the material isotopic evolution of the \gls{MSFR}. The 
+employed it to study the material isotopic evolution of the 
+\gls{MSFR}\cite{aufiero_extended_2013}. The 
 developed extension directly accounts for the effects of online fuel 
@@
 
-The present work introduces the online reprocessing simulation code, SaltProc, 
+The present work introduces the online reprocessing simulation package, SaltProc, 
 which expands the capability of the continuous-energy Monte Carlo Burnup 
@@
 \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
-analyze \gls{MSBR} neutronics and fuel cycle to find 
-the equilibrium core composition. The additional objective 
-is to compare predicted operational and safety parameters of the \gls{MSBR} at 
-both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
-determined and \gls{MSBR} fuel cycle performance will be analyzed.
+analyzed \gls{MSBR} neutronics and fuel cycle to establish its equilibrium core 
+composition. Additionally, we compared predicted operational and safety parameters of the \gls{MSBR} at 
+both the initial and equilibrium states to characterize the evolution of its 
+safety case over time. Finally, these simulations determined the appropriate $^{232}$Th feed rate  
+for maintaining criticality and enabled analysis of the overall \gls{MSBR} fuel 
+cycle performance.
 

### 2018-09-06 methods.tex
Gwen's edits implemented @22
no need for hastelloy footnote

@@
 \subsubsection{Material composition and normalization parameters}
-The fuel salt, reactor graphite, and modified Hastelloy-N\footnote{ 
-Hastelloy-N is very common in reactors now but has been studied and developed 
-at \gls{ORNL} in a program that started in 1950s.} 
+The fuel salt, reactor graphite, and modified Hastelloy-N
 are all materials created at \gls{ORNL} specifically for the \gls{MSBR}.
@@
         %\centering
-        \caption{•} of principal data for MSBR 
+        \caption{Summary of principal data for \gls{MSBR} 
         \cite{robertson_conceptual_1971}.}

### 2018-09-06 methods.tex
maybe more clear?

@@
 
-Saltproc datasets are time-series, meaning that every value is recorded every 
-timestep. The datasets SaltProc produces are listed below,
+SaltProc records every value every timestep. The resulting time series datasets
+produced by SaltProc are listed below,
 where the values inside the parenthesis are the dataset sizes:

### 2018-09-06 results.tex
Typo in includegraphics fixed
maybe more clear?

@@
   \centering
-  \includegraphics[scale=•]{•}=\textwidth]{major_isotopes_adens.png}
+  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
   \caption{Number density of major nuclides during 60 years of reactor 
@@
 isotopes in the core. In the end of the considered operational time, the core 
-contained significant amount of $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
+contained significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
 ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
@@
 the core (zone I), while for the outer region (zone II), it is negligible for fast 
-but notable for thermal neutrons. These neutron flux radial distributions is in 
-good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
+but notable for thermal neutrons. These neutron flux radial distributions 
+agree with the fluxes in the original ORNL report \cite{robertson_conceptual_1971}. 
 Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
@@
 distribution. Even after 20 years of operation, most of the power is still 
-generated in zone I with exception to the majority of $^{233}$Th that is 
+generated in zone I and the majority of $^{233}$Th is 
 produced in zone II.

### 2018-09-06 introduction.tex
Mark's edits implemented #27

--- 2018-09-06 introduction.tex
@@
 % a detailed literature survey or a summary of the results.
-The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
-in the 1950s and operated in the 1960s. More recently, the \gls{GIF}  
+The \gls{MSR} is an advanced nuclear reactor which was developed at \gls{ORNL} 
+in the 1950s and was operated in the 1960s. More recently, the \gls{GIF}  
 included \glspl{MSR} among the six most promising advanced reactor concepts for 
@@
 remove fission products and add fissile and/or fertile elements 
-\cite{leblanc_molten_2010}.
-
-The thorium-fueled \gls{MSBR} was developed in the 
-early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
+\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
+early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
@@
 \begin{tabularx}{\textwidth}{ m | b | x } 
-\hline Neutronic code    & \qquad Authors & Spectra   \\
+\hline Neutronic code    & \qquad Authors & Spectrum   \\
 \hline

### 2018-09-06 methods.tex
Mark's edits implemented #27

--- 2018-08-31 methods.tex
@@
 region in the SERPENT model. The volume of fuel salt in zone II was kept 
-exactly 37\%, so that this simplification did not considerably change the core 
+exactly at 37\%, so that this simplification did not considerably change the core 
 neutronics. Simplyfying the eight edge channels was the only simplification made 
@@
 
-The JEFF-3.1.2 neutron library provided cross section generation, 
+The JEFF-3.1.2 neutron library provided cross section generation 
 \cite{oecd/nea_data_bank_jeff-3.1.2_2014}. 
@@
 After the depletion calculation, SaltProc reads the depleted fuel composition 
-file (\texttt{ .bumat1}) and stores the depleted composition isotopic vector in 
+file and stores the depleted composition isotopic vector in 
 an HDF5 database.

### 2018-09-10 methods.tex
@katyhuff comments implemented

@@
 
-Saltproc datasets are time-series, meaning that every value is recorded every 
-timestep. The datasets SaltProc produces are listed below,
+SaltProc records every value every timestep. The resulting time series datasets 
+produced by SaltProc are listed below are listed below,
 where the values inside the parenthesis are the dataset sizes:

### 2018-09-10 results.tex
maybe all changes handled
Mark's edits implemented #27
@katyhuff comments implemented

@@
 the core (zone I), while for the outer region (zone II), it is negligible for fast 
-but notable for thermal neutrons. These neutron flux radial distributions 
-agree with the fluxes in the original ORNL report \cite{robertson_conceptual_1971}. 
+but notable for thermal neutrons. These neutron flux radial distributions are in 
+good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
 Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
@@
 distribution. Even after 20 years of operation, most of the power is still 
-generated in zone I and the majority of $^{233}$Th is 
+generated in zone I except the majority of $^{233}$Th that is 
 produced in zone II.
@@
 new graphite density was calculated using a linear temperature expansion 
-coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 
+coefficient of 1.3$\times10^{-6}$K$^{-1}$ \cite{robertson_conceptual_1971}. A new 
 geometry input was created based on this information.
@@
 \subsection{Six Factor Analysis}
-The effective multiplication factor can be expressed using next formula:
+The effective multiplication factor can be expressed using the following formula:
 \begin{align*}

### 2018-09-10 introduction.tex
@achubbz comment implemented

@@
 thorium fuel cycle because the $^{233}$U bred from 
-$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
+$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmuted into 
 $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 

### 2018-09-10 graph-abs/graph-abs.tex
Graphic abstact edited to resolve #26

--- 2018-05-10 graph-abs/graph-abs.tex
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{./highlight.png}
+        \includegraphics[width=\textwidth]{graph_abs.pdf}
     \end{center}
-    \caption{A very fancy image important to the paper.}
     \label{fig:graph-abs}

### 2018-09-10 introduction.tex
Lit review words fixed #25

--- 2018-09-10 introduction.tex
@@
 jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
-as well as the current work employ a batch-wise approach.
+as well as the current work also employ a batch-wise approach.
 
 Accounting for continuous removal or addition presents a greater challenge since it 
-requires adding a term to the Bateman equations. In SCALE 
-\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
-Bateman equations using spectrum-averaged fluxes and cross sections generated 
-from a deterministic transport calculation. Meanwhile, approaches listed in references 
-\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
-model true continuous feeds and removals.
+requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
+introduced online fuel reprocessing in the system of equations by adding effective 
+decay and transmutation terms for the different nuclides. In his work SERPENT was 
+used for solution of the matrix exponential derived from the system of the Bateman 
+equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
+continuous feeds and removals using MCNP transport code listed in references 
+\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
 

### 2018-09-10 acks.tex
Word hard wrap 80 col

@@
 
-The authors would like to thank  members of Advanced Reactors and Fuel Cycles
-research group (ARFC) at the University of Illinois - Urbana Champaign who 
-provided valuable code reviews and proofreading.
+The authors would like to thank  members of the \gls{ARFC} group at the 
+University of Illinois - Urbana Champaign who provided valuable code reviews 
+and proofreading.
 
@@
 the simulations, wrote the paper, contributed to the software 
-product, and reviewed drafts of the paper. Andrei Rykhlevskii and Jin Whan Bae 
-is supported by the Department of Nuclear, Plasma, and Radiological Engineering.
+product, and reviewed drafts of the paper. Andrei Rykhlevskii 
+is supported by the Department of Nuclear, Plasma, and Radiological 
+Engineering. Jin Whan Bae is supported by funding received from the DOE Office 
+of Nuclear Energy's Nuclear Energy University Program (Project 16-10512) 
+`Demand-Driven Cycamore Archetypes'.
 

### 2018-09-10 results.tex

@@
 the core (zone I), while for the outer region (zone II), it is negligible for fast 
-but notable for thermal neutrons. These neutron flux radial distributions are in 
-good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
+but notable for thermal neutrons. These neutron flux radial distributions 
+agree with the fluxes in the original ORNL report \cite{robertson_conceptual_1971}. 
 Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
@@
 distribution. Even after 20 years of operation, most of the power is still 
-generated in zone I except the majority of $^{233}$Th that is 
+generated in zone I and the majority of $^{233}$Th is 
 produced in zone II.

### 2018-09-10 abstract.tex

@@
 
-Today,  climate change is driving the search for new ways to generate 
+Today, climate change drives humanity's search for new ways to generate 
 carbon-free, reliable base-load power. Thus,
@@
 SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
-isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
-demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
-concept and compared well to previous results from lower-fidelity analyses.
+isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities
+for a full-core, high-fidelity model of the commercial \gls{MSBR} 
+concept and verifies these results to results in the literature from 
+independent, lower-fidelity analyses.
 

### 2018-09-10 conclusion.tex
Gwen's edits implemented #22

@@
 composition (where equilibrium is defined as when the number densities of major 
-isotopes vary less than 1\% over several years). A secondary goal has been to 
+isotopes vary by less than 1\% over several years). A secondary goal has been to 
 compare predicted operational and safety parameters (e.g., neutron energy 
@@
 
-Toward these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} 
-was implemented in SERPENT 2. The purpose of the full-core model instead of 
+To achieve these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} 
+was implemented in SERPENT 2. The full-core model was used instead of the 
 the simplified single-cell model \cite{betzler_molten_2017, 
-rykhlevskii_online_2017, betzler_fuel_2018} was to precisely describe the 
+rykhlevskii_online_2017, betzler_fuel_2018} to precisely describe the 
 two-region \gls{MSBR} concept design sufficiently to accurately represent 
@@
 materials are added to the fuel salt every 3 days.  Meanwhile, the removal 
-interval for the rare earths, volatile fluorides, and seminoble metals was more 
-than month which caused effective multiplication factor fluctuation.
+interval for the rare earths, volatile fluorides, and seminoble metals was greater 
+than month a (50 days), which caused effective multiplication factor fluctuation.
 
@@
 slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 
-6 years of operation. At the same time, the concentration of $^{233}$U, $^{232}$Th, 
-$^{233}$Pa, $^{232}$Pa stabilizes after approximately 2500 days of operation. 
+6 years of operation. At the same time, the concentrations of $^{233}$U, $^{232}$Th, 
+$^{233}$Pa, $^{232}$Pa stabilized after approximately 2500 days of operation. 
 Particularly, $^{233}$U number density equilibrates\footnote{fluctuates less 
@@
 absorbers (e.g. $^{234}$U), continue accumulating in the core. The current work results 
-show that a true equilibrium composition cannot exist but the balance
+show that a true equilibrium composition cannot exist but balance
 between strong absorber accumulation and new fissile material 
@@
 \subsection{Spectral shift}
-We also found that the neutron energy spectrum grows harder as equilibrium 
-approaches because significant heavy fission products accumulate in 
+We also found that the neutron energy spectrum grew harder as the core  
+approaches equilibrium because significant heavy fission products accumulated in 
 the \gls{MSBR} core. Moreover, the neutron energy spectrum in the central core 
@@
 \subsection{Future work}
-Continued SaltProc-SERPENT coupled simulation efforts could progress in a 
+SaltProc-SERPENT coupled simulation efforts could progress in a 
 number of different directions. First optimization of reprocessing parameters (e.g. time step, feeding rate, 

### 2018-09-10 introduction.tex

--- 2018-09-10 introduction.tex
@@
 jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
-as well as the current work similarly employ a batch-wise approach.
+as well as the current work also employ a batch-wise approach.
 
 Accounting for continuous removal or addition presents a greater challenge since it 
-requires adding a term to the Bateman equations. In SCALE 
-\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
-Bateman equations using spectrum-averaged fluxes and cross sections generated 
-from a deterministic transport calculation. Meanwhile, approaches listed in references 
-\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
-model true continuous feeds and removals.
+requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
+introduced online fuel reprocessing in the system of equations by adding effective 
+decay and transmutation terms for the different nuclides. In his work SERPENT was 
+used for solution of the matrix exponential derived from the system of the Bateman 
+equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
+continuous feeds and removals using MCNP transport code listed in references 
+\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
 

### 2018-09-11 methods.tex
minor final edits

--- 2018-09-06 methods.tex
@@
   \includegraphics[width=\textwidth]{ser_zone_II.png}
-  \caption{Detailed view of \gls{MSBR} zone II model.  
+  \caption{Detailed view of \gls{MSBR} two zone model. 
           Yellow represents fuel salt, purple represents graphite, and aqua represents the reactor vessel.}

### 2018-09-11 graph-abs/graph-abs.tex
minor final edits
closes #26

@@
     \begin{center}
-        \includegraphics[width=\textwidth]{graph_abs.pdf}
+        %\includegraphics[width=0.3\textwidth]{keff_rem_cases.png}
+        \includegraphics[width=0.49\textwidth]{ser_zone_II.png}
+        \includegraphics[width=0.49\textwidth]{spectrum_zones.png}
     \end{center}
     \label{fig:graph-abs}
+    \caption{The Molten Salt Breeder Reactor (left) was modeled in full
+three-dimensional detail.  Yellow represents fuel salt, purple represents
+graphite, and aqua represents the reactor vessel Online liquid fuel processing
+was simulated until a quasi-equillibrium of fuel composiion could be
+established. Reactor physics parameters, such as flux profiles, were evaluated
+during the 10 year evolution.}
 \end{figure}

### 2018-09-11 cover-letter/cover-letter.tex
final cover letter edits

--- 2018-05-10 cover-letter/cover-letter.tex
@@
 Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
-Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor'' which Mr. 
-Andrei Rykhlevskii and I are submitting for exclusive consideration of 
-publication as a research article in Annals of Nuclear Energy.
+Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor'' which I and my 
+coauthors (Mr. Andrei Rykhlevskii and Mr. Jin Whan Bae) are submitting for 
+exclusive consideration of publication as a research article in Annals of 
+Nuclear Energy.
 

### 2018-09-11 highlights/highlights.tex
highlights grammar

--- 2018-05-10 highlights/highlights.tex
@@
 \begin{itemize}
-       \item Highlight 1
-       \item Highlight 2
-       \item Highlight 3
+       \item A python script, SaltProc, is coupled with SERPENT to simulate 
+               material feeds and removals during depletion in MSBR.
+       \item Ten years of depletion and fuel processing in a thorium-fueled 
+               MSBR is simulated to find the equilibrium fuel composition.
+       \item Effects of the fuel salt irradiation with online reprocessing on 
+               MSBR operations are identified.
+       \item Benefits of online fission product removal in the thermal 
+               spectrum MSBR are identified.
 \end{itemize}

### 2018-10-11 acks.tex
as submitted update

@@
 product, and reviewed drafts of the paper. Andrei Rykhlevskii 
-is supported by the Department of Nuclear, Plasma, and Radiological 
-Engineering. Jin Whan Bae is supported by funding received from the DOE Office 
-of Nuclear Energy's Nuclear Energy University Program (Project 16-10512) 
-`Demand-Driven Cycamore Archetypes'.
+is supported by 
+DOE ARPA-E MEITNER program award 1798-1576. 
+Jin Whan
+Bae is supported by funding received from the DOE Nuclear Energy University
+Program (Project 16-10512) `Demand-Driven Cycamore Archetypes'.
 
@@
 of Defense Nuclear Nonproliferation R\&D through the Consortium for Verfication 
-Technologies and the Consortium for Nonproliferation Enabling Capabilities, and 
+Technologies and the Consortium for Nonproliferation Enabling Capabilities,  
 the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
 sponsored by the Japanese Ministry of Education, Culture, Sports, Science and 
-Technology.
+Technology, and DOE ARPA-E MEITNER program award 1798-1576.

### 2018-11-20 revisions/review-responses.tex

%        File: revise.tex
%     Created: Wed Oct 27 02:00 PM 2018 P
% Last Change: Wed Oct 27 02:00 PM 2018 P
%

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled 
        Molten Salt Breeder Reactor\\
\large Response to Review Comments}
\author{Andrei Rykhlevskii, Jin Whan Bae, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your comments have resulted in changes which certainly improved the 
paper.

\begin{questions}
        \section*{Reviewer 1}
        %---------------------------------------------------------------------
        \question <++> 
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Overall, a well written article in a topic area of interest 
        to a number of audiences. Technically very good, well written in the 
        description and analysis.  Well done authors!

        A few minor comments/suggestions/clarifications as follows:
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question  Abstract: Given the recent announcement about TransAtomic 
        Power, you may want to remove them from your list?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 1, page 3: SCALE/TRITON is fast as well as thermal 
        reactor capable.  
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 48: Should read ``...and refill using a single 
        or multiple unit cell ....''
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 55. Also worth noting that the latest SCALE 
        release will have the same functionality using continuous removal (B. 
        R. Betzler, J. J. Powers, N. R. Brown, and B. T. Rearden, ``Molten Salt 
        Reactor Neutronics Tools in SCALE,'' Proc. M\&C 2017 - International 
        Conference on Mathematics \& Computational Methods Applied to Nuclear 
        Science and Engineering, Jeju, Korea, Apr. 16-20 (2017).)
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 8, Fig 2: Appears the image is cut off at the top?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 13, line 209: The description of the Pa removal, 
        although correct, isn't quite fully correct. The reason the Pa is 
        removed from the core and hence flux is to then enable the Pa to decay 
        to U233. If it was left in the core, it would transmute further and 
        hence not be able to produce the U233 that is necessary for this 
        breeding cycle to work.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 3: ``cycle time'' is not defined in the paper. Please 
        add.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 224. The 3 day time step as the ``optimum'' for 
        Th fuel cycles in an MSR was first described and concluded by Powers et 
        al. Please add a reference to their initial work.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 234 onwards: Doesn't SERPENT already have an 
        MSR removal capability? If so, what is different about using SaltProc 
        with SERPENT?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, Figure 7: The figure is hard to interpret or see 
        clearly what is going on. Could an additional figure or a zoomed in 
        portion be added to show what the swing in k is over a much shorter 
        time interval? k seems to be swinging dramatically but over what time 
        period and how would this be controlled in reality? The graph almost 
        suggests that the core is unstable??
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, line 327: Are those elements removed every 3435 
        days, or is it that the entire salt core is discharged?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, line 351: It is more than just the Pu isotopes that 
        makes the spectrum harder? What about the other MAs etc?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Fig 12: units on y-axis?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 24, line 389: Should that be ``233U'' and not ``233Th''?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 5: Please provide some comments on the uncertainties - 
        where do they come from? Also, the ``reference'' results need to state 
        whether ``initial'' or ``equilibrium''
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 26, line 425: ``Relatively large'' compared with what? 
        Perhaps results for an LWR case would be a good basis for comparison?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 27, section 3.8: It needs to be made more clear that 
        these results were calculated, and that they are taken from the code 
        output.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 29, Figure 15: Similar comment to above regarding Fig 7 
        - the results are difficult to see and interpret with such notable 
        swings.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question The paper presents a python script (SaltProc) that can 
        complement the Serpent 2 code capabilities in terms of fuel cycle 
        analysis of MSRs. The paper is well written and the tool might be 
        useful for the nuclear engineering community. However, before 
        publishing the paper, I recommend some revisions.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question The most critical point of the work is that the built-in 
        capabilities for online reprocessing of Serpent 2 have not been used. 
        Their use is mentioned in the future work, but it is not clear why 
        these capabilities have not been used in the current work. To the 
        author's knowledge, they have been available in Serpent 2 since quite a 
        while. The authors should clarify this point at the beginning of the 
        paper, and not only in the ``Future work'' section. Even though the 
        technical work was done without using these capabilities, they should 
        highlight what  SaltProc adds to the built-in Serpent capabilities, and 
        they should at least try to extrapolate on the potential advantages of 
        combining  SaltProc and Serpent capabilities. Based on this, they 
        should slightly restructure the paper in order to prove the claimed 
        advantages over Serpent 2.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question In addition to this major point, I would suggest a few other 
        revisions.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Abstract:
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        - Considering the scope of the journal, mentioning the names of 
        companies and start-up is not appropriate. I would suggest removing 
        them.

        \question Introduction:
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        - The sentence ``Immediate advantages over traditional, solid-fueled, 
        reactors include near-atmospheric pressure in the 15 primary loop, 
        relatively high coolant temperature, outstanding neutron economy, 
        improved safety parameters,'' may suggest improved neutron economy vs 
        solid-fuel fast reactors. This is rarely the case, especially vs 
        Pu-based SFRs. I would suggest reformulating.

        \question The sentence ``With regard to the nuclear fuel cycle, the 
        thorium cycle produces a reduced quantity of plutonium and minor 
        actinides (MAs) compared to the traditional uranium fuel cycle'' is 
        correct, but the fact that this is an advantage is questionable. The 
        pros\&cons of thorium cycle have been long debated and there is no 
        consensus on its advantage in terms of exposure of workers, exposure of 
        public, geological repository, etc. I would suggest removing the 
        sentence.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``Methods listed in references [14, 17, 24, 25, 28, 29, 30] 
        as well as the current work also employ a batch-wise approach''. As a 
        matter of fact, the work in [14]  allows for continuous reprocessing 
        via introduction of ``reprocessing'' time constants. The work from  
        Aufiero (mentioned in the following paragraph) actually used the 
        methodology previously developed in [14]  for verification purposes.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Table 3. It is not clear what ``effective cycle times'' are. 
        Please clarify.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question The removal of fission products is made batch wise in the 
        described algorithms. However it is not clear how the fission products 
        with the longest ``effective cycle times'' are removed. Part of them at 
        every batch? Or all of them at the end of the  ``effective cycle 
        times''.  Please clarify. And please clarify the relation between 
        ``effective cycle times'', batches and the average time spent by a 
        fission product in the reactor.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question The oscillatory behavior shown in Fig. 7 on the time scale of 
        months/years is hard to explain. Is this because the fission product 
        with longer residence time are batch-wise removed at their ``effective 
        cycle time''? In case, why not to remove part of them at every depletion 
        step?  
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Can the proposed tool adjust reactivity?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The main physical principle underlying the reactor 
        temperature feedback is an expansion of material that is heated''. This 
        sentence would deserve some support data. Can you please calculate 
        separately the effect of temperature (Doppler in fuel and spectral 
        shift in graphite) and density?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question How uncertainties have been calculated in Table 5? Is this 
        just statistical uncertainty from Serpent calculations? Please clarify
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question For calculating the coefficients in table 5, are you only 
        changing densities, or also dimensions? Please clarify and provide a 
        justification.  
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The fuel temperature coefficient (FTC) is negative for both 
        initial and equilibrium fuel compositions due to thermal Doppler 
        broadening of the resonance capture cross sections in the thorium.'' 
        What is the effect of density?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``This thorium consumption rate is in good agreement with a 
        recent online reprocessing study by ORNL [29].'' Please notice that in a 
        reactor with only Th as feed, and near equilibrium, the Th consumption 
        rate is  exclusively determined by the reactor power and by the energy 
        released per fission.  
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Are you considering the effect of the gradual poisoning of 
        the graphite with fission products? If not, it would be worthwhile 
        briefly discussing its effect.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question In the manuscript it is not always clear when the authors 
        refer to numerical approximations of physical situations. For instance, 
        the authors write ``Figure 16 demonstrates that batch-wise removal of 
        strong absorbers every 3 days did not necessarily leads to fluctuation 
        in results but rare earth elements 480 removal every 50 days causes an 
        approximately 600 pcm jump in reactivity.'' These 600 pcm are an effect 
        of a numerical approximation, but the way things are presented can be 
        confusing to the reader. Please try to explicitly separate physical and 
        numerical effects. And try to related numerical effects to physical 
        effects. For instance, how does these numerical ``jumps'' affect the 
        results?  In this sense, why the batch-wise removal of strong absorbers 
        every 3 days  was not done? And why a fraction of rare earths  is not 
        removed every three days?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The current work results show that a true equilibrium 
        composition cannot exist but balance between strong absorber 
        accumulation and new fissile material production can be achieved to 
        keep the reactor critical.'' Not clear. Do you mean that the equilibrium 
        composition cannot be achieved in a lifetime of the reactor? Please 
        clarify
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \section*{Reviewer 3}

        \question This paper presents a SaltProc-Serpent2 coupled code system 
        to simulate the depletion and online reprocessing process by directly 
        changing the isotropic composition of fuel salt. The Molten Salt 
        Breeder Reactor (MSBR) was analyzed to demonstrate the simulation 
        capability of the developed code system. However, large number of 
        similar works have been done and published on this topic. In 
        particular, this work is similar with that done by Park et al. with the 
        title of ``Whole core analysis of molten salt breeder reactor with 
        online fuel reprocessing'' published on ``International Journal of Energy 
        Research''. The authors need to prove the uniqueness and innovation 
        within their work.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------

        \question  What are the main differences of this work with the previous 
        works, especially with the work published by Park at al. in ``Whole core 
        analysis of molten salt breeder reactor with online fuel reprocessing''?
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  How did the authors verify the coupled SaltProc and Serpent 
        code system?  \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 3, the title of ``Table 1'' should not only contain 
        the ``fast spectrum system''. The work published by Zhou and Yang et al. 
        with the title of ``Fuel cycle analysis of molten salt reactors based on 
        coupled neutronics and thermal-hydraulics calculations'' needs to be 
        included in Table 1 for completeness.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 5, the following sentence needs to be explained. ``We 
        employed this extended SERPENT 2 for a simplified unit-cell geometry of 
        thermal spectrum thorium-fueled MSBR and obtained results which 
        contradict existing MSBR depletion simulations.''
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 10, ``SERPENT generates the problem-dependent nuclear 
        data library'', how did SERPENT generate the problem-dependent nuclear 
        data library? What kind of nuclear data library did SERPENT generate?
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 14, ``depletioncalculations'' should be ``depletion 
        calculations''.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 21, it looks like the neutron spectrum is not 
        normalized in Figure 10. It is recommended to normalize the neutron 
        spectrum for comparison.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 22, ``Figure 13 reflects the normalized power 
        distribution of the MSBR quarter core, which is the same at both the 
        initial and equilibrium states'' contradicts the following statement of 
        ``The spectral shift during reactor operation results in different power 
        fractions at startup and equilibrium''.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 24, it is hard to agree with the statement that ``the 
        majority of 233Th is produced in zone II.''. How did the authors draw 
        this conclusion?
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 24 and 25, why did the normalized power density 
        distribution and the 232Th neutron capture reaction rate distribution 
        share the same figure for both initial and equilibrium fuel salt 
        compositions?
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
        \question  Too much background information was contained in the 
        abstract, which deteriorates the readability of the abstract.
        \begin{solution}
                <++>
        \end{solution}

        %--------------------------------------------------------------------
\end{questions}
%\bibliographystyle{unsrt}
%\bibliography{review-responses}
\end{document}

%
% End of file `elsarticle-template-num.tex'.

### 2018-12-26 revisions/review-responses.tex
Reviewer #1 comment implemented addressing Issue #32
Reviewer #1 1-4 comments implemented #32

@@
         %---------------------------------------------------------------------
-        \question <++> 
-        \begin{solution}
-                <++>
-        \end{solution}
-
-        %---------------------------------------------------------------------
-
-        \question Overall, a well written article in a topic area of interest 
-        to a number of audiences. Technically very good, well written in the 
-        description and analysis.  Well done authors!
-
-        A few minor comments/suggestions/clarifications as follows:
-        \begin{solution}
-                <++>
-        \end{solution}
-
-        %---------------------------------------------------------------------
 
@@
         \begin{solution}
-                <++>
+        Thank you for your kind review. Current manuscript was submitted before announcement that TransAtomic is ceasing operations. It is removed from the list of MSR startups.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        Thank you for the recommendation. In Table 1 ``thermal'' has been changed to ``thermal/fast''.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        That statement has been modified as requested.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        Thank you for the update. This sentence has been added:
+
+        The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}
         \end{solution}
@@
 \end{questions}
-%\bibliographystyle{unsrt}
-%\bibliography{review-responses}
+\bibliographystyle{unsrt}
+\bibliography{../2018-msbr-reproc}
 \end{document}

### 2018-12-26 introduction.tex
Reviewer #1 1-4 comments implemented #32

@@
 2014; Betzler \emph{et al.}, 2017 
-\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
+\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/fast\\
 \hline
@@
 have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
-batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
+batch-wise approach to simulate a continuous reprocessing and refill using a single 
+or multiple unit cell. ChemTriton models salt 
 treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
@@
 introduced online fuel reprocessing in the system of equations by adding effective 
-decay and transmutation terms for the different nuclides. In his work SERPENT was 
+decay and transmutation terms for the different nuclides.
+The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}.
+In his work SERPENT was
 used for solution of the matrix exponential derived from the system of the Bateman 

### 2018-12-26 revisions/review-responses.tex
Reviewer #1: Pa removal reasons and cycle time footnote added #32

@@
         \begin{solution}
-                <++>
+        The image has been replotted.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        Thanks for catching this. Following passage has been added:
+
+        Protactinium presents a challenge, since it has a large absorption cross 
+		section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
+		 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
+		and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
+		Accordingly, $^{233}$Pa is continuously 
+		removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
+		to decay to $^{233}$U without negative impact on neutronics.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        The ``cycle time'' definition has been added in a first appearance in text.
         \end{solution}

### 2018-12-26 introduction.tex
Reviewer #1: Pa removal reasons and cycle time footnote added #32

@@
 \hline
-SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 
+SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
 \cite{aufiero_extended_2013} & fast \\
@@
 which expands the capability of the continuous-energy Monte Carlo Burnup 
-calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
+calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation 
 liquid-fueled \gls{MSR} operation 
-\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
+\cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
 application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 

### 2018-12-26 methods.tex
Reviewer #1: Pa removal reasons and cycle time footnote added #32

@@
 Protactinium presents a challenge, since it has a large absorption cross 
-section in the thermal energy spectrum. Accordingly, $^{233}$Pa is continuously 
+section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
+ would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
+and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
+Accordingly, $^{233}$Pa is continuously 
 removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
-system must separate $^{233}$Pa from the molten-salt fuel over 3 
+to decay to $^{233}$U without negative impact on neutronics. The reactor 
+reprocessing system must separate $^{233}$Pa from the molten-salt fuel over 3 
 days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
@@
 efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
-full list of nuclides and the cycle times used for modeling salt treatment and 
+full list of nuclides and the ``cycle times''\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel 
+salt \cite{robertson_conceptual_1971}.} used for modeling salt treatment and 
 separations \cite{robertson_conceptual_1971}.
@@
 \subsubsection{The SaltProc modeling and simulation code}
-The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_2018} is designed to 
+The SaltProc tool \cite{rykhlevskii_arfc/saltproc:_2018} is designed to 
 expand SERPENT 2

### 2018-12-26 results.tex
Fix issue #29
Reviewer #1: Pa removal reasons and cycle time footnote added #32

@@
 Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
-cycle time\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
-        amount of time required to remove 100\% of a target nuclide from a fuel 
-salt.} (3 days for this work). The effective multiplication 
+cycle time (3 days for this work). The effective multiplication 
 factor fluctuates significantly as a result of the batch-wise nature of this 
@@
   \includegraphics[width=\textwidth]{power_distribution_eq.png} 
-  \caption{Normalized power density for both initial and equilibrium fuel salt 
+  \caption{Normalized power density for equilibrium fuel salt 
   composition.}
@@
   \caption{$^{232}$Th neutron capture reaction rate normalized by total flux 
-  for both initial and equilibrium fuel salt composition.}
+  for equilibrium fuel salt composition.}
   \label{fig:breeding_den}

### 2018-12-26 revisions/review-responses.tex
Reviewer #1 70% of comments implemented #32

@@
         \begin{solution}
-        Thank you for your kind review. Current manuscript was submitted before announcement that TransAtomic is ceasing operations. It is removed from the list of MSR startups.
+        		Thank you for your kind review. Current manuscript was submitted before 
+		        announcement that TransAtomic is ceasing operations. It is removed from 
+		        the list of MSR startups.
         \end{solution}
@@
         \begin{solution}
-        Thank you for the recommendation. In Table 1 ``thermal'' has been changed to ``thermal/fast''.
+		        Thank you for the recommendation. In Table 1 ``thermal'' has been changed 
+		        to ``thermal/fast''.
         \end{solution}
@@
 
-        The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}
+		        The latest SCALE release will also have the same functionality using 
+        		truly continuous removals \cite{betzler_implementation_2017}
         \end{solution}
@@
         \begin{solution}
-                <++>
+        		The reference to \cite{powers_new_2013} has been added.
         \end{solution}
@@
         \begin{solution}
-                <++>
+		        100 \% of those elements atoms removed every 3435 days. Full salt discard
+		         as it mentioned in Table 3 has not been implemented. More detailed 
+		         explanation of this has been added:
+
+		        Additionally, the presence of rubidium, strontium, cesium, and barium in
+		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
+		         removes all these elements every 3435 days (not a small mass fraction 
+		         every 3 days) which causes the multiplication factor to jump by 
+		        approximately 450 pcm, and limits using the batch approach for online 
+		        reprocessing simulations. In future versions of SaltProc this drawback 
+		        will be eliminated by removing elements with longer cycle times (seminoble 
+		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
+		        Only mass fraction (calculated separately for each reprocessing group) 
+		        will be removed every depletion step (e.g. 3 days) instead of removing 
+		        100\% of element atoms after cycle time. 
         \end{solution}
@@
         \begin{solution}
-                <++>
+		        Explanation of this phenomena has been added as follows:
+
+		         Small dips in neptunium and plutonium number density every 16 years are 
+		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
+		         ``Higher nuclides'', see Table~\ref{tab:reprocessing_list}) which decays
+        		  into $^{235}$Np, $^{239}$Pu, respectively. 
         \end{solution}
@@
         \begin{solution}
-                <++>
+        		Thank you for the excellent point. The corrected sentence reads thus:
+
+		        The neutron energy spectrum at equilibrium is harder than at startup due
+		         to plutonium and other strong absorbers accumulation in the core during 
+		         reactor operation.  
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thanks for catching this. Units $\frac{n}{cm^2 s}$ has been added.
         \end{solution}

### 2018-12-26 methods.tex
Reviewer #1 70% of comments implemented #32

@@
         Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
-        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
-                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
+        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
+        %Salt discard & Th, Li, Be, F & 3435 days \\ 
+        Protactinium & $^{233}$Pa & 3 days \\ Higher 
                 nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
@@
 captured. To compromise, the time interval for depletion calculations in this 
-model was selected as 3 days to correlate with the removal interval of 
+model was selected as 3 days\footnote{ Optimal depletion time step of 3 days for \gls{MSR} batch-wise depletion simulation was first described and concluded by Powers \emph{et al.} \cite{powers_new_2013}.} to correlate with the removal interval of
 $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
@@
 manage material streams while SERPENT 2 performs the neutron 
-transport and depletioncalculations. Saltproc is defined as a python class, where 
+transport and depletion calculations. Saltproc is defined as a python class, where 
 each material stream is defined as a isotopic atomic density

### 2018-12-26 results.tex
Reviewer #1 70% of comments implemented #32

@@
 Additionally, the presence of rubidium, strontium, cesium, and barium in the 
-core are disadvantageous to reactor physics. In fact, the removal of these elements 
-every 3435 days causes the multiplication factor to jump by approximately 450 
+core are disadvantageous to reactor physics. In fact, SaltProc fully removes all these elements every 3435 days (not a small mass fraction every 3 days) 
+which causes the multiplication factor to jump by approximately 450 
 pcm, and limits using the batch approach for online reprocessing simulations. 
+In future versions of SaltProc this drawback will be eliminated by removing 
+elements with longer cycle times (seminoble metals, volatile fluorides, Rb, Sr,
+ Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
+ separately for each reprocessing group) will be removed every depletion step 
+ (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
 Overall, the effective multiplication factor gradually decreases from 1.075 to 
@@
 atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
-isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
+isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Small dips 
+in neptunium and plutonium number density every 16 years are caused by removing
+$^{237}$Np, $^{242}$Pu (included in Processing group ``Higher nuclides'', see
+ Table~\ref{tab:reprocessing_list}) which decays into $^{235}$Np, $^{239}$Pu, 
+ respectively. Thus, 
 production of new fissile materials in the core, as well as $^{233}$U breeding, 
@@
 neutron energy spectrum at equilibrium is harder than at startup due to 
-$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
-the core during reactor operation.  
+plutonium and other strong absorbers accumulation in the core during reactor 
+operation.  
 \begin{figure}[ht!] % replace 't' with 'b'         to force it to 

### 2018-12-26 revisions/review-responses.tex
Reviewer #1 85% edits implemented #32

@@
         \begin{solution}
-                <++>
+                Yes, we meant $^{233}$U production. The typo has been fixed.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties has been added:
+
+                Uncertainty for each temperature coefficient was obtain by propagating 			  				statistical error for effective multiplication factor calculation (confidence
+                 interval $\pm$1.9 pcm) provided by SERPENT2 and also appears in Table 5.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Sentence has been extended as follows:
+
+                ... the total temperature coefficient of reactivity is relatively large and
+                 negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent
+                 reactor stability and control.
         \end{solution}

### 2018-12-26 results.tex
Reviewer #1 85% edits implemented #32

@@
 and equilibrium states. The distribution reflects the spatial distribution of 
-$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
+$^{233}$U production in the core. The thorium-233 produced after $^{232}$Th 
+captured neutron then $\beta$-decays to 
 $^{233}$Pa, which is the precursor for $^{233}$U production. Accordingly, this 
@@
 with the original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
-Uncertainty for each temperature coefficient also appears in 
+Uncertainty for each temperature coefficient was obtain by propagating statistical 
+ error for effective multiplication factor calculation (confidence interval for K$_{eff}$
+ is $\pm$1.9 pcm) provided by SERPENT2 and also appears in 
 Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
@@
   state.}
-\begin{tabularx}{\textwidth}{ m | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
+\begin{tabularx}{\textwidth}{ s | s | s | s } \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \qquad (initial)
         \cite{robertson_conceptual_1971} \\  \hline
@@
 summary, even after 20 years of operation the total temperature coefficient of 
-reactivity is relatively large and negative during reactor operation, despite 
-positive MTC, and affords excellent reactor stability and control.
+reactivity is relatively large and negative during reactor operation (comparing with conventional PWR which temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and affords excellent reactor stability and control.
 

### 2018-12-27 revisions/review-responses.tex
Reviewer #1 comments all implmented #32

@@
 
-                ... the total temperature coefficient of reactivity is relatively large and
+                ...the total temperature coefficient of reactivity is relatively large and
                  negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent
@@
         \begin{solution}
-                <++>
+                This has now been clarified in the text:
+
+                Table 7 summarizes the six factors for both initial and 
+				equilibrium fuel salt composition. These factors and their statistical 								uncertainties have been calculated using SERPENT2 code for initial fuel salt 
+				composition (see Table 2) and for equilibrium salt composition which was 
+				obtained with SaltProc. 
         \end{solution}

### 2018-12-28 revisions/review-responses.tex
Table 5 thermal coefficients recalculated.Resolve issue #31

@@
         \begin{solution}
-                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties has been added:
+                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties have been added:
 
-                Uncertainty for each temperature coefficient was obtain by propagating 			  				statistical error for effective multiplication factor calculation (confidence
-                 interval $\pm$1.9 pcm) provided by SERPENT2 and also appears in Table 5.
+                 Uncertainty for each temperature coefficient was obtain by 
+                 propagating statistical error of effective multiplication factor 
+                 calculation provided by SERPENT2 and also appears in Table 5. 
+                 Other sources of uncertainty, such as cross section libraries 
+				 uncertainty, error in salt and graphite density correlations, 
+				 are not treated here.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for the excellent recommendation. Effects of temperature
+                 and density have been calculated separately and added in Table 5.
+                 Moreover, during these simulations we have discovered mistake in 
+                 fuel salt and graphite density correlations and completely 
+                 recalculated temperature coefficients of reactivity with lower 
+                 statistical error. Now initial total temperature coefficient is 
+                 closer to the reference and statistical uncertainty was reduced 
+                 from 0.046 to 0.038 pcm/K.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Yes, uncertainties were determined from statistical error 
+                from SERPENT output. Following passage has been added to clarify
+                 this point:
+
+                 Uncertainty for each temperature coefficient was obtain by 
+                 propagating statistical error of effective multiplication factor 
+                 calculation provided by SERPENT2 and also appears in Table 5. 
+                 Other sources of uncertainty, such as cross section libraries 
+				 uncertainty, error in salt and graphite density correlations, 
+				 are not treated here.
         \end{solution}
@@
         \begin{solution}
-                <++>
+        		We have changed both densities and dimensions. This passage 
+        		has been modified to read:
+
+                A new geometry input for SERPENT2, which takes into account 
+                displacement of graphite surfaces, was created based on this information.
+                 For the displacements calculation it was assumed that the interface 
+                 between graphite reflector and vessel did not move, and the vessel 
+                 temperature did not change. This is the most reasonable assumption for
+				 the short-term reactivity effects because inlet salt is cooling graphite 
+				 reflector and inner surface of the vessel.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                This passage has been modified to illuminate the effect of density:
+
+				The fuel temperature coefficient (FTC) is negative for both initial and 
+				equilibrium fuel compositions due to thermal Doppler broadening of the 
+				resonance capture cross sections in the thorium. Small positive effect 
+				of fuel density on reactivity is increasing from +1.21 pcm/K for the 
+				reactor startup to +1.66 pcm/K for equilibrium fuel composition which 
+				has negative effect on FTC magnitude during the reactor operation. 
         \end{solution}

### 2018-12-28 results.tex
Reviewer #1 comments all implmented #32
Table 5 thermal coefficients recalculated.Resolve issue #31

--- 2018-12-26 results.tex
@@
 with the original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
-Uncertainty for each temperature coefficient also appears in 
-Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
+Uncertainty for each temperature coefficient was obtain by propagating statistical 
+ error of effective multiplication factor calculation 
+provided by SERPENT2 and also appears in 
+Table~\ref{tab:tcoef}. Other sources of uncertainty, such as cross section libraries 
+uncertainty, error in salt and graphite density correlations, are not treated here.
+ The main physical principle underlying the reactor 
 temperature feedback is an expansion of material that is heated. When the fuel 
@@
 \begin{tabularx}{\textwidth}{ m | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
-        \cite{robertson_conceptual_1971} \\  \hline
-Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
-Moderator        & $+1.61\pm0.044$ & $+0.97\pm0.046$ & $+2.35$  \\
-Total            & $-3.1\pm0.04$   & $-0.97\pm0.046$ & $-0.87$  \\ \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \qquad (initial)\cite{robertson_conceptual_1971} \\  \hline
+Doppler in fuel salt   			& $-4.73\pm0.038$ & $-4.69\pm0.038$ & $-4.37$  \\
+Fuel salt density      			& $+1.21\pm0.038$ & $+1.66\pm0.038$ & $+1.09$  \\
+Total fuel salt        			& $-3.42\pm0.038$ & $-2.91\pm0.038$ & $-3.22$  \\ \hline
+Graphite spectral shift    		& $+1.56\pm0.038$ & $+1.27\pm0.038$ &          \\
+Graphite density   				& $+0.14\pm0.038$ & $+0.23\pm0.038$ &          \\
+Total moderator (graphite)		& $+1.69\pm0.038$ & $+1.35\pm0.038$ & $+2.35$  \\ \hline
+Total core      				& $-1.64\pm0.038$ & $-1.58\pm0.038$ & $-0.87$  \\ \hline
 \end{tabularx}
@@
 coefficient of 1.3$\times10^{-6}$K$^{-1}$ \cite{robertson_conceptual_1971}. A new 
-geometry input was created based on this information.
+geometry input for SERPENT2, which takes into account displacement of graphite 
+surfaces, was created based on this information. For the displacements calculation 
+it was assumed that the interface between graphite reflector and vessel did not move,
+ and the vessel temperature did not change. This is the most reasonable assumption for
+ the short-term reactivity effects because inlet salt is cooling graphite reflector and 
+inner surface of the vessel.
 
@@
 equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
-capture cross sections in the thorium. This is in good agreement with earlier 
+capture cross sections in the thorium. Small positive effect of fuel density on 
+reactivity is increasing from +1.21 pcm/K for the reactor startup to +1.66 pcm/K for 
+equilibrium fuel composition which has negative effect on FTC magnitude during the 
+reactor operation. This is in good agreement with earlier 
 research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
@@
 summary, even after 20 years of operation the total temperature coefficient of 
-reactivity is relatively large and negative during reactor operation, despite 
-positive MTC, and affords excellent reactor stability and control.
+reactivity is relatively large and negative during reactor operation (comparing 
+with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F 
+$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and 
+affords excellent reactor stability and control.
 
@@
 Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
-equilibrium fuel salt composition. The non-leakage probability for both fast 
+equilibrium fuel salt composition. These factors and their statistical uncertainties
+ have been calculated using SERPENT2 code for initial fuel salt composition (see 
+Table~\ref{tab:msbr_tab}) and for equilibrium salt composition which was obtained 
+with SaltProc. The non-leakage probability for both fast 
 and thermal neutrons does not change during reactor operation because these 

### 2018-12-28 revisions/review-responses.tex
Table 5 thermal coefficients recalculated.Resolve issue #31

@@
         %---------------------------------------------------------------------
+        \question <++> 
+        \begin{solution}
+                <++>
+        \end{solution}
+
+        %---------------------------------------------------------------------
+
+        \question Overall, a well written article in a topic area of interest 
+        to a number of audiences. Technically very good, well written in the 
+        description and analysis.  Well done authors!
+
+        A few minor comments/suggestions/clarifications as follows:
+        \begin{solution}
+                <++>
+        \end{solution}
+
+        %---------------------------------------------------------------------
 
@@
         \begin{solution}
-        		Thank you for your kind review. Current manuscript was submitted before 
-		        announcement that TransAtomic is ceasing operations. It is removed from 
-		        the list of MSR startups.
+                <++>
         \end{solution}
@@
         \begin{solution}
-		        Thank you for the recommendation. In Table 1 ``thermal'' has been changed 
-		        to ``thermal/fast''.
+                <++>
         \end{solution}
@@
         \begin{solution}
-        		That statement has been modified as requested.
+                <++>
         \end{solution}
@@
         \begin{solution}
-		        Thank you for the update. This sentence has been added:
-
-		        The latest SCALE release will also have the same functionality using 
-        		truly continuous removals \cite{betzler_implementation_2017}
+                <++>
         \end{solution}
@@
         \begin{solution}
-        The image has been replotted.
+                <++>
         \end{solution}
@@
         \begin{solution}
-        		Thanks for catching this. Following passage has been added:
-
-		        Protactinium presents a challenge, since it has a large absorption cross 
-				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
-				 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
-				and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
-				Accordingly, $^{233}$Pa is continuously 
-				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-				to decay to $^{233}$U without negative impact on neutronics.
+                <++>
         \end{solution}
@@
         \begin{solution}
-		        The ``cycle time'' definition has been added in a first appearance in text.
+                <++>
         \end{solution}
@@
         \begin{solution}
-        		The reference to \cite{powers_new_2013} has been added.
+                <++>
         \end{solution}
@@
         \begin{solution}
-		        100 \% of those elements atoms removed every 3435 days. Full salt discard
-		         as it mentioned in Table 3 has not been implemented. More detailed 
-		         explanation of this has been added:
-
-		        Additionally, the presence of rubidium, strontium, cesium, and barium in
-		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
-		         removes all these elements every 3435 days (not a small mass fraction 
-		         every 3 days) which causes the multiplication factor to jump by 
-		        approximately 450 pcm, and limits using the batch approach for online 
-		        reprocessing simulations. In future versions of SaltProc this drawback 
-		        will be eliminated by removing elements with longer cycle times (seminoble 
-		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
-		        Only mass fraction (calculated separately for each reprocessing group) 
-		        will be removed every depletion step (e.g. 3 days) instead of removing 
-		        100\% of element atoms after cycle time. 
+                <++>
         \end{solution}
@@
         \begin{solution}
-		        Explanation of this phenomena has been added as follows:
-
-		         Small dips in neptunium and plutonium number density every 16 years are 
-		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
-		         ``Higher nuclides'', see Table~\ref{tab:reprocessing_list}) which decays
-        		  into $^{235}$Np, $^{239}$Pu, respectively. 
+                <++>
         \end{solution}
@@
         \begin{solution}
-        		Thank you for the excellent point. The corrected sentence reads thus:
-
-		        The neutron energy spectrum at equilibrium is harder than at startup due
-		         to plutonium and other strong absorbers accumulation in the core during 
-		         reactor operation.  
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Thanks for catching this. Units $\frac{n}{cm^2 s}$ has been added.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Yes, we meant $^{233}$U production. The typo has been fixed.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Sentence has been extended as follows:
-
-                ...the total temperature coefficient of reactivity is relatively large and
-                 negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent
-                 reactor stability and control.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                This has now been clarified in the text:
-
-                Table 7 summarizes the six factors for both initial and 
-				equilibrium fuel salt composition. These factors and their statistical 								uncertainties have been calculated using SERPENT2 code for initial fuel salt 
-				composition (see Table 2) and for equilibrium salt composition which was 
-				obtained with SaltProc. 
+                <++>
         \end{solution}
@@
 \end{questions}
-\bibliographystyle{unsrt}
-\bibliography{../2018-msbr-reproc}
+%\bibliographystyle{unsrt}
+%\bibliography{review-responses}
 \end{document}

### 2018-12-28 results.tex
Table 5 thermal coefficients recalculated.Resolve issue #31

@@
 Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of 
-cycle time (3 days for this work). The effective multiplication 
+cycle time\footnote{ The \gls{MSBR} program defined a ``cycle time" as the 
+        amount of time required to remove 100\% of a target nuclide from a fuel 
+salt.} (3 days for this work). The effective multiplication 
 factor fluctuates significantly as a result of the batch-wise nature of this 
@@
 Additionally, the presence of rubidium, strontium, cesium, and barium in the 
-core are disadvantageous to reactor physics. In fact, SaltProc fully removes all these elements every 3435 days (not a small mass fraction every 3 days) 
-which causes the multiplication factor to jump by approximately 450 
+core are disadvantageous to reactor physics. In fact, the removal of these elements 
+every 3435 days causes the multiplication factor to jump by approximately 450 
 pcm, and limits using the batch approach for online reprocessing simulations. 
-In future versions of SaltProc this drawback will be eliminated by removing 
-elements with longer cycle times (seminoble metals, volatile fluorides, Rb, Sr,
- Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
- separately for each reprocessing group) will be removed every depletion step 
- (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
 Overall, the effective multiplication factor gradually decreases from 1.075 to 
@@
 atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
-isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Small dips 
-in neptunium and plutonium number density every 16 years are caused by removing
-$^{237}$Np, $^{242}$Pu (included in Processing group ``Higher nuclides'', see
- Table~\ref{tab:reprocessing_list}) which decays into $^{235}$Np, $^{239}$Pu, 
- respectively. Thus, 
+isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
 production of new fissile materials in the core, as well as $^{233}$U breeding, 
@@
 neutron energy spectrum at equilibrium is harder than at startup due to 
-plutonium and other strong absorbers accumulation in the core during reactor 
-operation.  
+$^{238}$Pu, $^{239}$Pu, $^{240}$Pu, $^{241}$Pu, and $^{242}$Pu accumulation in 
+the core during reactor operation.  
 \begin{figure}[ht!] % replace 't' with 'b'         to force it to 
@@
 and equilibrium states. The distribution reflects the spatial distribution of 
-$^{233}$U production in the core. The thorium-233 produced after $^{232}$Th 
-captured neutron then $\beta$-decays to 
+$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
 $^{233}$Pa, which is the precursor for $^{233}$U production. Accordingly, this 
@@
 Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
-equilibrium fuel salt composition. These factors and their statistical uncertainties
- have been calculated using SERPENT2 code for initial fuel salt composition (see 
-Table~\ref{tab:msbr_tab}) and for equilibrium salt composition which was obtained 
-with SaltProc. The non-leakage probability for both fast 
+equilibrium fuel salt composition. The non-leakage probability for both fast 
 and thermal neutrons does not change during reactor operation because these 

### 2019-01-02 revisions/review-responses.tex
Reviewer 3 minor comments mostly resolved #35

@@
         \begin{solution}
-                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties have been added:
+                In the Table 5 was added information that reference column contains 
+                data for initial fuel salt composition. Details about uncertainties
+                 have been added:
 
@@
         \begin{solution}
-                <++>
+                The ``cycle time'' definition has been added in a first appearance in text.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                No, and we do not plan to add this capability.
         \end{solution}
@@
         \begin{solution}
-                Thank you for the excellent recommendation. Effects of temperature
-                 and density have been calculated separately and added in Table 5.
-                 Moreover, during these simulations we have discovered mistake in 
-                 fuel salt and graphite density correlations and completely 
-                 recalculated temperature coefficients of reactivity with lower 
-                 statistical error. Now initial total temperature coefficient is 
-                 closer to the reference and statistical uncertainty was reduced 
-                 from 0.046 to 0.038 pcm/K.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Yes, uncertainties were determined from statistical error 
-                from SERPENT output. Following passage has been added to clarify
-                 this point:
-
-                 Uncertainty for each temperature coefficient was obtain by 
-                 propagating statistical error of effective multiplication factor 
-                 calculation provided by SERPENT2 and also appears in Table 5. 
-                 Other sources of uncertainty, such as cross section libraries 
-				 uncertainty, error in salt and graphite density correlations, 
-				 are not treated here.
+                <++>
         \end{solution}
@@
         \begin{solution}
-        		We have changed both densities and dimensions. This passage 
-        		has been modified to read:
-
-                A new geometry input for SERPENT2, which takes into account 
-                displacement of graphite surfaces, was created based on this information.
-                 For the displacements calculation it was assumed that the interface 
-                 between graphite reflector and vessel did not move, and the vessel 
-                 temperature did not change. This is the most reasonable assumption for
-				 the short-term reactivity effects because inlet salt is cooling graphite 
-				 reflector and inner surface of the vessel.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                This passage has been modified to illuminate the effect of density:
-
-				The fuel temperature coefficient (FTC) is negative for both initial and 
-				equilibrium fuel compositions due to thermal Doppler broadening of the 
-				resonance capture cross sections in the thorium. Small positive effect 
-				of fuel density on reactivity is increasing from +1.21 pcm/K for the 
-				reactor startup to +1.66 pcm/K for equilibrium fuel composition which 
-				has negative effect on FTC magnitude during the reactor operation. 
+                <++>
         \end{solution}
@@
 
-        \question This paper presents a SaltProc-Serpent2 coupled code system 
-        to simulate the depletion and online reprocessing process by directly 
-        changing the isotropic composition of fuel salt. The Molten Salt 
-        Breeder Reactor (MSBR) was analyzed to demonstrate the simulation 
-        capability of the developed code system. However, large number of 
-        similar works have been done and published on this topic. In 
-        particular, this work is similar with that done by Park et al. with the 
-        title of ``Whole core analysis of molten salt breeder reactor with 
-        online fuel reprocessing'' published on ``International Journal of Energy 
-        Research''. The authors need to prove the uniqueness and innovation 
-        within their work.
-        \begin{solution}
-                <++>
-        \end{solution}
-
         %--------------------------------------------------------------------
@@
         \begin{solution}
-                <++>
+                Thank you for your question. The new paragraph has been added:
+
+                The works described in \cite{park_whole_2015} and 
+                \cite{jeong_equilibrium_2016} are most similar to the work 
+                presented in this paper. However, few major differences worse to 
+                be mentioned: (1) Park \emph{et al.} employed MCNP6 for depletion 
+				simulations while SERPENT2 was used in this work (SERPENT2 seems 
+				to be much faster in massively parallel simulations involving more 
+				than 1000 cores); (2) full-core reactor model herein is more 
+				detailed and has no major approximation comparing with Park \emph{et al.}
+				(detailed full-core models comparison might be found elsewhere
+				\cite{rykhlevskii_full-core_2017}); (3) Park \emph{et al.} and 
+				Jeong \emph{et al.} both considered volatile gases, noble metals 
+				removal and $^{233}$Pa separation while in the current work we are 
+				implemented detailed reprocessing scheme described in conceptual 
+				MSBR design \cite{robertson_conceptual_1971}; (4) $^{232}$Th 
+				neutron capture reaction rate has been investigated to prove 
+				advantages of two-region core design; (5) the effect of removing 
+				fission product removal from fuel salt has been studied. 
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for your excellent recommendations. The table has been 
+                enriched as requested.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for your kind review. The statement has been removed
+		        entirely and we emphasized that temperature of each material is 
+		        assumed to be constant over 60 years:
+
+		        The specific temperature was fixed for each material and did 
+		        not change during the reactor operation. 
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thanks for catching this, fixed.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thanks for catching this. The difference between power fraction
+                 is very small that could be seen from Table 4. It is impossible
+                  to see the difference in a contour plot that is why we left only 
+                 equilibrium composition on Figures 13 and 14. The paragraph has 
+                 been modified as follows:
+
+                 Table 4 shows the power fraction in each zone for initial and 
+                 equilibrium fuel compositions. Figure 13 reflects the normalized 
+                 power distribution of the MSBR quarter core for equilibrium 
+                 fuel salt composition. For both the initial and equilibrium 
+                 compositions, fission primarily occurs in the center of the core, 
+                 namely zone I. The spectral shift during reactor operation results 
+                 in slightly different power fractions at startup and equilibrium, 
+                 but most of the power is still generated in zone I at equilibrium 
+				 (table 4).
+
         \end{solution}
@@
         \begin{solution}
-                <++>
+                The statement has been removed entirely.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thanks for catching this, it is a typo. Figure 13 and 14 are plotted 
+                for equilibrium composition only.            	    
         \end{solution}

### 2019-01-02 introduction.tex
Reviewer 3 minor comments mostly resolved #35

--- 2018-09-10 introduction.tex
@@
 \begin{table}[ht!]
-\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
+\caption{Tools and methods for \glspl{MSR} fuel cycle analysis.}
 \begin{tabularx}{\textwidth}{ m | b | x } 
@@
 \hline
+DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
+\cite{zhou_fuel_2018} & fast \\
+\hline
 MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
@@
 2014; Betzler \emph{et al.}, 2017 
-\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
+\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/ fast\\
 \hline
@@
 
+The works described in \cite{park_whole_2015} and \cite{jeong_equilibrium_2016} 
+are most similar to the work presented in this paper. However, few major differences 
+worse to be mentioned: (1) Park \emph{et al.} employed MCNP6 for depletion 
+simulations while SERPENT2 was used in this work (SERPENT2 seems to be much faster in 
+massively parallel simulations involving more than 1000 cores); (2) full-core reactor 
+model herein is more detailed and has no major approximation comparing with Park 
+\emph{et al.} (detailed full-core models comparison might be found elsewhere
+\cite{rykhlevskii_full-core_2017}); (3) Park \emph{et al.} and Jeong \emph{et al.} 
+both considered volatile gases, noble metals removal and $^{233}$Pa separation while 
+in the current work we are implemented detailed reprocessing scheme described in 
+conceptual \gls{MSBR} design \cite{robertson_conceptual_1971}; (4) $^{232}$Th neutron 
+capture reaction rate has been investigated to prove advantages of two-region core 
+design; (5) the effect of removing fission product removal from fuel salt has been 
+studied.
+
 The complex \gls{MSBR} geometry is challenging to describe in software input, 

### 2019-01-02 results.tex
Reviewer 3 minor comments mostly resolved #35

@@
 initial and equilibrium fuel compositions. Figure~\ref{fig:pow_den} reflects the 
-normalized power distribution of the \gls{MSBR} quarter core, which is the same 
-at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 
+normalized power distribution of the \gls{MSBR} quarter core for equilibrium fuel
+ salt composition. For both the initial and equilibrium compositions, fission 
 primarily occurs in the center of the core, namely zone I. The spectral shift 
-during reactor operation results in different power fractions at startup and 
-equilibrium, but most of the power is still generated in zone I at equilibrium. 
+during reactor operation results in slightly different power fractions at startup and 
+equilibrium, but most of the power is still generated in zone I at equilibrium 
+(table~\ref{tab:powgen_fraction}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 distribution. Even after 20 years of operation, most of the power is still 
-generated in zone I and the majority of $^{233}$Th is 
-produced in zone II.
+generated in zone I.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
@@
 with the original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
-Uncertainty for each temperature coefficient was obtain by propagating statistical 
- error of effective multiplication factor calculation 
-provided by SERPENT2 and also appears in 
-Table~\ref{tab:tcoef}. Other sources of uncertainty, such as cross section libraries 
-uncertainty, error in salt and graphite density correlations, are not treated here.
- The main physical principle underlying the reactor 
+Uncertainty for each temperature coefficient also appears in 
+Table~\ref{tab:tcoef}. The main physical principle underlying the reactor 
 temperature feedback is an expansion of material that is heated. When the fuel 
@@
 \begin{tabularx}{\textwidth}{ m | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \qquad (initial)\cite{robertson_conceptual_1971} \\  \hline
-Doppler in fuel salt   			& $-4.73\pm0.038$ & $-4.69\pm0.038$ & $-4.37$  \\
-Fuel salt density      			& $+1.21\pm0.038$ & $+1.66\pm0.038$ & $+1.09$  \\
-Total fuel salt        			& $-3.42\pm0.038$ & $-2.91\pm0.038$ & $-3.22$  \\ \hline
-Graphite spectral shift    		& $+1.56\pm0.038$ & $+1.27\pm0.038$ &          \\
-Graphite density   				& $+0.14\pm0.038$ & $+0.23\pm0.038$ &          \\
-Total moderator (graphite)		& $+1.69\pm0.038$ & $+1.35\pm0.038$ & $+2.35$  \\ \hline
-Total core      				& $-1.64\pm0.038$ & $-1.58\pm0.038$ & $-0.87$  \\ \hline
+   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 
+        \cite{robertson_conceptual_1971} \\  \hline
+Fuel salt        & $-3.22\pm0.044$ & $-1.53\pm0.046$ & $-3.22$  \\
+Moderator        & $+1.61\pm0.044$ & $+0.97\pm0.046$ & $+2.35$  \\
+Total            & $-3.1\pm0.04$   & $-0.97\pm0.046$ & $-0.87$  \\ \hline
 \end{tabularx}
@@
 coefficient of 1.3$\times10^{-6}$K$^{-1}$ \cite{robertson_conceptual_1971}. A new 
-geometry input for SERPENT2, which takes into account displacement of graphite 
-surfaces, was created based on this information. For the displacements calculation 
-it was assumed that the interface between graphite reflector and vessel did not move,
- and the vessel temperature did not change. This is the most reasonable assumption for
- the short-term reactivity effects because inlet salt is cooling graphite reflector and 
-inner surface of the vessel.
+geometry input was created based on this information.
 
@@
 equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
-capture cross sections in the thorium. Small positive effect of fuel density on 
-reactivity is increasing from +1.21 pcm/K for the reactor startup to +1.66 pcm/K for 
-equilibrium fuel composition which has negative effect on FTC magnitude during the 
-reactor operation. This is in good agreement with earlier 
+capture cross sections in the thorium. This is in good agreement with earlier 
 research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
@@
 summary, even after 20 years of operation the total temperature coefficient of 
-reactivity is relatively large and negative during reactor operation (comparing 
-with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F 
-$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and 
-affords excellent reactor stability and control.
+reactivity is relatively large and negative during reactor operation, despite 
+positive MTC, and affords excellent reactor stability and control.
 

### 2019-01-02 revisions/review-responses.tex
Reviewer 2 minor comments mostly resolved #39

--- 2018-12-28 revisions/review-responses.tex
@@
         \begin{solution}
-                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties have been added:
-
-                 Uncertainty for each temperature coefficient was obtain by 
-                 propagating statistical error of effective multiplication factor 
-                 calculation provided by SERPENT2 and also appears in Table 5. 
-                 Other sources of uncertainty, such as cross section libraries 
-				 uncertainty, error in salt and graphite density correlations, 
-				 are not treated here.
+                <++>
         \end{solution}
@@
         %---------------------------------------------------------------------
-        \question The paper presents a python script (SaltProc) that can 
-        complement the Serpent 2 code capabilities in terms of fuel cycle 
-        analysis of MSRs. The paper is well written and the tool might be 
-        useful for the nuclear engineering community. However, before 
-        publishing the paper, I recommend some revisions.
-        \begin{solution}
-                <++>
-        \end{solution}
-
-        %---------------------------------------------------------------------
 
@@
 
-        \question In addition to this major point, I would suggest a few other 
-        revisions.
+        \question Considering the scope of the journal, mentioning the names of 
+        companies and start-up is not appropriate. I would suggest removing 
+        them.
         \begin{solution}
-                <++>
+                The names of companies have been removed.
         \end{solution}
@@
 
-        \question Abstract:
-        \begin{solution}
-                <++>
-        \end{solution}
-
-        %---------------------------------------------------------------------
-        - Considering the scope of the journal, mentioning the names of 
-        companies and start-up is not appropriate. I would suggest removing 
-        them.
-
-        \question Introduction:
-        \begin{solution}
-                <++>
-        \end{solution}
-
-        %---------------------------------------------------------------------
-        - The sentence ``Immediate advantages over traditional, solid-fueled, 
+        \question The sentence ``Immediate advantages over traditional, solid-fueled, 
         reactors include near-atmospheric pressure in the 15 primary loop, 
@@
         Pu-based SFRs. I would suggest reformulating.
+        \begin{solution}
+                Thank you for the exceptional recommendation. The sentence has been 
+                changed as follows:
+
+                ``Immediate advantages over traditional light water reactors 
+                include\dots''
+        \end{solution}
+
+        %---------------------------------------------------------------------
 
@@
         \begin{solution}
-                <++>
+                Thanks for your kind comment. The sentence has been removed.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for the information. [14] has been removed from the 
+                sentence, and following paragraph has been modified to read:
+
+                Accounting for continuous removal or addition presents a greater 
+                challenge since it requires adding a term to the Bateman equations. 
+                Fiorina \emph{et al.} simulated MSFR depletion with continuous
+                 fuel salt reprocessing via introducing ``reprocessing'' time 
+                constants into ERANOS transport code \cite{fiorina_investigation_2013}. 
+                Aufiero \emph{et al.} improved SERPENT2 using similar methodology by 
+                explicitly introducing continuous reprocessing in the system of Bateman 
+                equations by adding effective decay and transmutation terms for the 
+                different nuclides \cite{aufiero_extended_2013}. 
         \end{solution}
@@
         \begin{solution}
-                <++>
+                All of them at the end of the cycle time, and we agree that it
+                 was not best solution. To clarify this following paragraph has 
+                been added:
+
+				Current version of SaltProc only allows separate out 100\% of 
+				specific elements or group of elements (e.g. Processing Groups 
+				as described in Table 3 at the end
+				 of the specific cycle time. This approach works well for 
+				fast-removing elements (gases, noble metals, protactinium) which 
+				should be removed each depletion step. Unfortunately, for the 
+				elements with longer cycle time (i.e. rare earths should be removed 
+				every 50 days) this simplified approach leads to oscillatory 
+				behavior of all major parameters. In future releases of SaltProc
+				 this drawback will be eliminated by removing elements with longer 
+				cycle times using different method: only mass fraction (calculated 
+				separately for each reprocessing group) will be removed each 
+				depletion step (e.g. 3 days).	
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Yes, the oscillation happened because the fission products 
+        		with longer residence time are removed at the end of cycle time. We are 
+                definitely will take your advice and improve the code in future 
+                releases. Following text has been added to clarify this issue:
+
+                In fact, SaltProc fully removes all these elements every 3435 days 
+                (not a small mass fraction every 3 days) which causes the 
+                multiplication factor to jump by approximately 450 pcm, and limits 
+                using the batch approach for online reprocessing simulations. In 
+                future versions of SaltProc this drawback will be eliminated by 
+                removing elements with longer residence time (seminoble metals, 
+                volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
+                Only mass fraction (calculated separately for each reprocessing 
+                group) will be removed every depletion step (e.g. 3 days) instead 
+                of removing 100\% of element atoms after cycle time.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for the recommendation. Following sentence has been 
+                added:
+
+                It must be noted that for the reactor with only thorium feed, 
+                at near equilibrium state, the thorium consumption rate is 
+				determined by the reactor power, the energy released per fission, 
+				and neutron energy spectrum.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                This passage has been added:
+
+				$^{135}$Xe is a strong poison to the reactor, and some 
+				fraction of this gas is absorbed by graphite during \gls{MSBR} 
+				operation. ORNL calculations shown that for unsealed commercial 
+				graphite with helium permeability 10$^{-5}$ cm$^2$/s the 
+				calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
+				This parameter can be improved by using experimental graphites 
+				or by applying sealing technology. The effect of the gradual 
+				poisoning of the core graphite with xenon is not treated here.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                This statement has been removed completely.
         \end{solution}

### 2019-01-02 introduction.tex
Reviewer 2 minor comments mostly resolved #39

--- 2018-12-26 introduction.tex
@@
 circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
-Immediate advantages over traditional, solid-fueled, reactors include 
+Immediate advantages over traditional light water reactors include 
 near-atmospheric pressure in the primary loop, 
@@
 and good flow and heat transfer properties \cite{robertson_conceptual_1971}.  
-With regard to the nuclear fuel cycle, the thorium cycle produces a reduced quantity 
-of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
 Finally, the \gls{MSR} also could be employed as a converter reactor for 
@@
 \hline
-SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
+SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 
 \cite{aufiero_extended_2013} & fast \\
+\hline
+DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
+\cite{zhou_fuel_2018} & thermal/ fast \\
 \hline
@@
 2014; Betzler \emph{et al.}, 2017 
-\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/fast\\
+\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
 \hline
@@
 have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
-batch-wise approach to simulate a continuous reprocessing and refill using a single 
-or multiple unit cell. ChemTriton models salt 
+batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
 treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
@@
 reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
-references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
+references \cite{zhou_fuel_2018,sheu_depletion_2013,park_whole_2015, 
 jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
@@
 Accounting for continuous removal or addition presents a greater challenge since it 
-requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
-introduced online fuel reprocessing in the system of equations by adding effective 
-decay and transmutation terms for the different nuclides.
-The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}.
-In his work SERPENT was
+requires adding a term to the Bateman equations. Fiorina \emph{et al.} simulated 
+\gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
+``reprocessing'' time constants into ERANOS transport code \cite{fiorina_investigation_2013}. Aufiero \emph{et al.} improved SERPENT2 using similar methodology by explicitly introducing 
+continuous reprocessing in the system of Bateman equations by adding effective decay and transmutation terms for the different nuclides \cite{aufiero_extended_2013}.
+
+The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
 used for solution of the matrix exponential derived from the system of the Bateman 
@@
 which expands the capability of the continuous-energy Monte Carlo Burnup 
-calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation 
+calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
 liquid-fueled \gls{MSR} operation 
-\cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
+\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
 application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 

### 2019-01-02 methods.tex
Reviewer 3 minor comments mostly resolved #35
Reviewer 2 minor comments mostly resolved #39

--- 2018-09-11 methods.tex
@@
 surface of the graphite reflector blocks.
+
+$^{135}$Xe is a strong poison to the reactor, and some fraction of this gas 
+is absorbed by graphite during \gls{MSBR} operation. ORNL calculations shown 
+that for unsealed commercial graphite with helium permeability 10$^{-5}$ cm$^2$/s 
+the calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
+This parameter can be improved by using experimental graphites or by applying
+sealing technology. The effect of the gradual poisoning of the core graphite 
+with xenon is not treated here.
+% Consequently, minimizing
+% xenon absorption in a graphite is desirable. 
+%ORNL calculations shown 
+%that the graphite must have a gas permeability in the order of 10$^{-8}$ cm$^2$/s 
+%to keep the xenon poisoning about 0.5\%. The best commercially available graphites 
+%have this parameter in the range from 10$^{-3}$ to 10$^{-4}$ cm$^2$/s, hence, 
+%desirable parameters ca be achieved only by sealing the graphite
 
@@
 
+Current version of SaltProc only allows separate out 100\% of specific elements 
+or group of elements (e.g. Processing Groups as described in 
+Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
+This approach works well for fast-removing elements (gases, noble metals, 
+protactinium) which should be removed each depletion step. Unfortunately, 
+for the elements with longer cycle time (i.e. rare earths should be removed 
+every 50 days) this simplified approach leads to oscillatory behavior of all
+major parameters. In future releases of SaltProc this drawback will be eliminated 
+by removing elements with longer cycle times using different method: only mass 
+fraction (calculated separately for each reprocessing group) will be removed each
+ depletion step (e.g. 3 days).
+
 SaltProc, currently in active development on Github (https://github.com/ 

### 2019-01-02 results.tex
Reviewer 2 minor comments mostly resolved #39

--- 2019-01-02 results.tex
@@
 pcm, and limits using the batch approach for online reprocessing simulations. 
+In future versions of SaltProc this drawback will be eliminated by removing 
+elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
+ Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
+ separately for each reprocessing group) will be removed every depletion step 
+ (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
 Overall, the effective multiplication factor gradually decreases from 1.075 to 
@@
 initial and equilibrium fuel compositions. Figure~\ref{fig:pow_den} reflects the 
-normalized power distribution of the \gls{MSBR} quarter core for equilibrium fuel
- salt composition. For both the initial and equilibrium compositions, fission 
+normalized power distribution of the \gls{MSBR} quarter core, which is the same 
+at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 
 primarily occurs in the center of the core, namely zone I. The spectral shift 
-during reactor operation results in slightly different power fractions at startup and 
-equilibrium, but most of the power is still generated in zone I at equilibrium 
-(table~\ref{tab:powgen_fraction}. 
+during reactor operation results in different power fractions at startup and 
+equilibrium, but most of the power is still generated in zone I at equilibrium. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 distribution. Even after 20 years of operation, most of the power is still 
-generated in zone I.
+generated in zone I and the majority of $^{233}$Th is 
+produced in zone II.
 \begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
@@
 good agreement with a recent online reprocessing study by \gls{ORNL} 
-\cite{betzler_molten_2017}.
+\cite{betzler_molten_2017}. It must be noted that for the reactor with only 
+thorium feed, at near equilibrium state, the thorium consumption rate is 
+determined by the reactor power, the energy released per fission, and 
+neutron energy spectrum.
 

### 2019-01-02 abstract.tex
Reviewer #1 comment implemented addressing Issue #32
Reviewer 2 minor comments mostly resolved #39

@@
 with multiple new companies pursuing commercialization of \gls{MSR} 
-designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
+designs. To further 
 develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 

### 2019-01-02 introduction.tex
Reviewer 2 minor comments mostly resolved #39

--- 2019-01-02 introduction.tex
@@
 DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
-\cite{zhou_fuel_2018} & fast \\
+\cite{zhou_fuel_2018} & thermal/ fast \\
 \hline

### 2019-01-02 methods.tex
Reviewer 2 minor comments mostly resolved #39

--- 2018-12-26 methods.tex
@@
 \cite{oecd/nea_data_bank_jeff-3.1.2_2014}. 
-The specific temperature was fixed 
-for each material to correctly model the Doppler-broadening of resonance peaks 
-when SERPENT generates the problem-dependent nuclear data library. The isotopic 
+The specific temperature was fixed for each material and did not change during 
+the reactor operation. The isotopic 
 composition of each material at the initial state was described in detail in 

### 2019-01-02 results.tex
Reviewer 2 minor comments mostly resolved #39

--- 2019-01-02 results.tex
@@
 In future versions of SaltProc this drawback will be eliminated by removing 
-elements with longer cycle times (seminoble metals, volatile fluorides, Rb, Sr,
+elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
  Cs, Ba, Eu) using different approach. Only mass fraction (calculated 

### 2019-01-02 results.tex
Spectrum normalization units explained to resolve Reviewer 3 question 7 #35

@@
   \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
-  spectrum normalized by unit lethargy for initial and equilibrium fuel salt 
+  spectrum normalized by unit lethargy and area under the curve is normalized to 1 for initial and equilibrium fuel salt 
   composition.}
@@
   \caption{Neutron flux energy spectrum in different core regions normalized by 
-unit lethargy for the initial and equilibrium fuel salt composition.}
+unit lethargy and area under the curve is normalized to 1 for the initial and equilibrium fuel salt composition.}
   \label{fig:spectrum_zones}

### 2019-01-02 revisions/review-responses.tex
Spectrum normalization units explained to resolve Reviewer 3 question 7 #35
Verification explained to resolve Reviewer 3 question 2 #35

@@
         \question  How did the authors verify the coupled SaltProc and Serpent 
-        code system?  \begin{solution}
-                <++>
+        code system?  
+        \begin{solution}
+                We have compared few parameters (multiplication factor, Th refill 
+                rate, neutron energy spectrum) with Betzler \emph{et al.} 											\cite{betzler_molten_2017} and mentioned it in the Result section. 
+                We also compared neutron energy spectrum and temperature coefficients
+                 for equilibrium composition with Park \emph{et al.} \cite{park_whole_2015}.
+                In a future SaltProc release suite of unit tests will be added 
+                to make sure that results are consistent with our test cases.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for the comment. Neutron energy spectrum in Figure 
+                10 and 11 are normalized per unit lethargy and the area under 
+                the curve is normalized to 1.
         \end{solution}

### 2019-01-03 revisions/review-responses.tex
Units numerical density vs mas resolved. Issue #32

@@
 		        The latest SCALE release will also have the same functionality using 
-        		truly continuous removals \cite{betzler_implementation_2017}
+        		truly continuous removals \cite{betzler_implementation_2017}.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
+                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
+                be more understandable for the reader and will be added in a future releases.
         \end{solution}
@@
 				$^{135}$Xe is a strong poison to the reactor, and some 
-				fraction of this gas is absorbed by graphite during \gls{MSBR} 
+				fraction of this gas is absorbed by graphite during MSBR
 				operation. ORNL calculations shown that for unsealed commercial 

### 2019-01-03 revisions/review-responses.tex
Explanation why SERPENT2 online feature doesn't used added #34

@@
 
-\usepackage[acronym,toc]{glossaries}
-\include{acros}
+%\usepackage[acronym,toc]{glossaries}
+%\include{acros}
 
-\makeglossaries
+%\makeglossaries
 
@@
         \begin{solution}
-                <++>
+                It does. We tried use it before but these capabilities needs 
+                to be verified. Additional text to clarify this point has 
+                been add to solution for question 21.                
         \end{solution}
@@
 		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
-		         ``Higher nuclides'', see Table~\ref{tab:reprocessing_list}) which decays
+		         ``Higher nuclides'', see Table 3) which decays
         		  into $^{235}$Np, $^{239}$Pu, respectively. 
@@
         \begin{solution}
-                <++>
+                Thank you for your kind review. We tried to use these capabilities 
+                \cite{rykhlevskii_online_2017} but have had number of issues which 
+                are hard to resolve due to lack of documentation and publications 
+                involving this feature. Following paragraph has been added to 
+                clarify why these capabilities have not been used in current work:
+
+                We employed this extended SERPENT2 for a simplified unit-cell 
+                geometry of thermal spectrum thorium-fueled MSBR and have had 
+                following problems: (1) lack of documentation describing how 
+                to use this built-in SERPENT2 online reprocessing capabilities
+                \footnote{ Some challenges in no particular order: mass 
+                conservation is hard to achieve; not clear when use mflow card 
+                type 0, 1 or 2; difference between CRAM and TTA results; etc.} 
+				(Discussion forum for SERPENT users is only useful 
+				source of information at the moment); (2) reactivity control 
+				module described in Aufiero \emph{et al.} is not available 
+				in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
+				factor behavior for simplified unit-cell model obtained using 
+				SERPENT2 built-in capabilities \cite{rykhlevskii_online_2017} 
+				does not match with exist MCNP6/Python-script results for the 
+				similar model by Jeong and Park\footnote{ In our study 
+				k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of 
+				depletion simulation while in Jeong and Park work this parameter 
+				decreasing slowly from 1.065 to 1.05 for the 
+				similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few 
+				publication \cite{aufiero_extended_2013, ashraf_nuclear_2018} 
+				using these capabilities are available which is indicative of 
+				lack of reproducibility. Nevertheless, truly continuous 
+				online reprocessing capabilities of SERPENT2 is desirable feature 
+				for our future research. However, these capabilities should be 
+				carefully verified against ChemTriton/SCALE or proposed 
+				SaltProc/SERPENT2 package, and could be employed 
+				for removal of fission products with shorter residence time 
+				(e.g., Xe, Kr) which have a strong negative impact on core 
+				lifetime and breeding efficiency which we intent to do in 
+				the nearest future.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                This statement has been significantly extended (see Solution 21).
         \end{solution}

### 2019-01-03 conclusion.tex
Reviewer #1: Pa removal reasons and cycle time footnote added #32
Reviewer 2 minor comments mostly resolved #39
Explanation why SERPENT2 online feature doesn't used added #34

@@
 code to include online reprocessing in liquid-fueled \gls{MSR} operation 
-\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
+\cite{rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
 generic geometry modeling, multi-flow capabilities, time-dependent feed and 
@@
 Particularly, $^{233}$U number density equilibrates\footnote{fluctuates less 
-than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state 
-after 16 years of operation. However, a wide variety of nuclides, 
+than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state after 16 years of operation. However, a wide variety of nuclides, 
 including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
-absorbers (e.g. $^{234}$U), continue accumulating in the core. The current work results 
-show that a true equilibrium composition cannot exist but balance
-between strong absorber accumulation and new fissile material 
-production can be achieved to keep the reactor critical.
+absorbers (e.g. $^{234}$U), continue accumulating in the core. %The current work results 
+%show that a true equilibrium composition cannot exist but balance
+%between strong absorber accumulation and new fissile material 
+%production can be achieved to keep the reactor critical.
 
@@
 Only the batch-wise online reprocessing approach has been treated in this 
-work. However, the SERPENT 2 Monte Carlo code was recently extended for 
+work. However, the SERPENT 2 Monte Carlo code was extended for 
 continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 

### 2019-01-03 introduction.tex
Explanation why SERPENT2 online feature doesn't used added #34

@@
 \hline
-SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
-\cite{aufiero_extended_2013} & fast \\
+SERPENT2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
+\cite{aufiero_extended_2013}; Ashraf \emph{et al.}, 2018 \cite{ashraf_nuclear_2018} & fast \\
 \hline
@@
 \hline
-SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
+SERPENT2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
 thermal\\
@@
 
-Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
+Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT2 and 
 employed it to study the material isotopic evolution of the 
@@
 reprocessing on depletion calculations and features a reactivity control 
-algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
+algorithm. The extended version of SERPENT2 was assessed against a dedicated 
 version of the deterministic ERANOS-based EQL3D procedure 
-\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
-isotopic evolution. We employed this extended SERPENT 2 for a simplified 
-unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
-results which contradict existing \gls{MSBR} depletion simulations 
-\cite{jeong_equilibrium_2016}.
+\cite{ruggieri_eranos_2006, fiorina_investigation_2013} and adopted to analyze 
+the \gls{MSFR} fuel salt isotopic evolution.
+
+We employed this extended SERPENT2 for a simplified unit-cell geometry of 
+thermal spectrum thorium-fueled \gls{MSBR} and have had following problems: (1) 
+lack of documentation describing how to use this built-in SERPENT2 online 
+reprocessing capabilities\footnote{ Some challenges in no particular order: 
+mass conservation is hard to achieve; not clear when use mflow card type 0, 1 or 2; 
+difference between CRAM and TTA results; etc.} 
+(Discussion forum for SERPENT users is only useful 
+source of information at the moment); (2) reactivity control module described in Aufiero \emph{et al.} is 
+not available in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
+factor behavior for simplified unit-cell model obtained using SERPENT2 built-in 
+capabilities \cite{rykhlevskii_online_2017} does not match with exist MCNP6/Python-script
+ results for the similar model by Jeong and Park\footnote{ In our 
+study k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of depletion simulation 
+while in Jeong and Park work this parameter decreasing slowly from 1.065 to 1.05 for the 
+similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few publication \cite{aufiero_extended_2013, 
+ashraf_nuclear_2018} using these capabilities are available 
+which is indicative of lack of reproducibility. Nevertheless, truly continuous 
+online reprocessing capabilities of SERPENT2 is desirable feature for our 
+future research. However, these capabilities should be carefully verified against 
+ChemTriton/SCALE or proposed SaltProc/SERPENT2 package, and could be employed 
+for removal of fission products with shorter residence time (e.g., Xe, Kr) which 
+have a strong negative impact on core lifetime and breeding efficiency which 
+we intent to do in the nearest future.
 
@@
 which expands the capability of the continuous-energy Monte Carlo Burnup 
-calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation 
+calculation code, SERPENT2 \cite{leppanen_serpent_2015}, for simulation 
 liquid-fueled \gls{MSR} operation 
 \cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
-application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
+application of the coupled SaltProc-SERPENT2 system to the \gls{MSBR}, an 
 extension of the work presented in 

### 2019-01-03 introduction.tex
clarity about solid vs light water

@@
 sustainability, economics, safety and reliability, and proliferation resistance 
-and physical protection" \cite{doe_technology_2002}. To achieve the goals 
+and physical protection'' \cite{doe_technology_2002}. To achieve the goals 
 formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
@@
 circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
-Immediate advantages over traditional light water reactors include 
+Immediate advantages over traditional commercial reactors include 
 near-atmospheric pressure in the primary loop, 
-relatively high coolant temperature, outstanding neutron economy, improved 
-safety parameters, reduced fuel preprocessing, and the ability to continuously 
-remove fission products and add fissile and/or fertile elements 
+relatively high coolant temperature, outstanding neutron economy, and improved 
+safety parameters. Advantages over solid-fueled reactors in general include 
+reduced fuel preprocessing and the ability to continuously remove fission 
+products and add fissile and/or fertile elements 
 \cite{leblanc_molten_2010}.

### 2019-01-03 revisions/review-responses.tex
Batch vs average residual time resolved #39

@@
 				specific elements or group of elements (e.g. Processing Groups 
-				as described in Table 3 at the end
-				 of the specific cycle time. This approach works well for 
+				as described in Table 3) at the end
+				 of the specific cycle time which means the average time spent 
+				by a fission product in the core is equal cycle time. That is 
+				simplification because in reality fuel salt resides approximately 
+				1/2 of total time in the core and rest of the time in the primary 
+				loop pipes and the heat exchanger. This approach works well for 
 				fast-removing elements (gases, noble metals, protactinium) which 
@@
 				separately for each reprocessing group) will be removed each 
-				depletion step (e.g. 3 days).	
+				depletion step or batch (e.g. in the current work it was chosen 
+				3 days).	
         \end{solution}

### 2019-01-03 introduction.tex
rephrasing section about continous reprocessing.

@@
 have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
-batch-wise approach to simulate a continuous reprocessing and refill using a single 
-or multiple unit cell. ChemTriton models salt 
+batch-wise approach to simulate a continuous reprocessing and refill for either single 
+or multiple fluid designs. ChemTriton models salt 
 treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
@@
 \gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
-``reprocessing'' time constants into ERANOS transport code \cite{fiorina_investigation_2013}. Aufiero \emph{et al.} improved SERPENT2 using similar methodology by explicitly introducing 
-continuous reprocessing in the system of Bateman equations by adding effective decay and transmutation terms for the different nuclides \cite{aufiero_extended_2013}.
-
-The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
-used for solution of the matrix exponential derived from the system of the Bateman 
-equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
-continuous feeds and removals using MCNP transport code listed in references 
-\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
+``reprocessing'' time constants into the ERANOS transport code 
+\cite{fiorina_investigation_2013}. 
+The latest SCALE release will also have the same functionality using truly 
+continuous removals \cite{betzler_implementation_2017}. 
+A similar approach is adopted to model true continuous feeds and removals using the MCNP transport code listed in references \cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
 
@@
 
-Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT2 and 
-employed it to study the material isotopic evolution of the 
-\gls{MSFR}\cite{aufiero_extended_2013}. The 
-developed extension directly accounts for the effects of online fuel 
+Aufiero \emph{et al.} added an undocumented 
+feature to SERPENT2 
+using a similar methodology by explicitly introducing 
+continuous reprocessing in the system of Bateman equations and adding effective 
+decay and transmutation terms for each nuclide 
+\cite{aufiero_extended_2013}. This was employed to study the material isotopic evolution of the 
+\gls{MSFR}\cite{aufiero_extended_2013}. The developed extension directly accounts for the effects of online fuel 
 reprocessing on depletion calculations and features a reactivity control 
 algorithm. The extended version of SERPENT2 was assessed against a dedicated 
-version of the deterministic ERANOS-based EQL3D procedure 
+version of the deterministic ERANOS-based EQL3D procedure in
 \cite{ruggieri_eranos_2006, fiorina_investigation_2013} and adopted to analyze 
@@
 
-We employed this extended SERPENT2 for a simplified unit-cell geometry of 
-thermal spectrum thorium-fueled \gls{MSBR} and have had following problems: (1) 
-lack of documentation describing how to use this built-in SERPENT2 online 
-reprocessing capabilities\footnote{ Some challenges in no particular order: 
-mass conservation is hard to achieve; not clear when use mflow card type 0, 1 or 2; 
-difference between CRAM and TTA results; etc.} 
-(Discussion forum for SERPENT users is only useful 
-source of information at the moment); (2) reactivity control module described in Aufiero \emph{et al.} is 
-not available in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
+We employed this built-in SERPENT2 feature for a simplified unit-cell geometry of 
+the thermal spectrum thorium-fueled \gls{MSBR} and found it unusable\footnote{ 
+Some challenges in no particular order: mass conservation is hard to achieve; 
+three types of mflow cards (0, 1 or 2) are indistinguishable in purpose; an 
+unexplained difference between CRAM and TTA results; etc.}. Primarily,
+it is undocumented, and the discussion forum for SERPENT users is the only useful 
+source of information at the moment. Additionally, the reactivity control module described in Aufiero \emph{et al.} is 
+not available in the latest SERPENT 2.1.30 release. Third, the infinite multiplication 
 factor behavior for simplified unit-cell model obtained using SERPENT2 built-in 
@@
 while in Jeong and Park work this parameter decreasing slowly from 1.065 to 1.05 for the 
-similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few publication \cite{aufiero_extended_2013, 
-ashraf_nuclear_2018} using these capabilities are available 
-which is indicative of lack of reproducibility. Nevertheless, truly continuous 
-online reprocessing capabilities of SERPENT2 is desirable feature for our 
-future research. However, these capabilities should be carefully verified against 
-ChemTriton/SCALE or proposed SaltProc/SERPENT2 package, and could be employed 
-for removal of fission products with shorter residence time (e.g., Xe, Kr) which 
-have a strong negative impact on core lifetime and breeding efficiency which 
-we intent to do in the nearest future.
+similar time-frame.} \cite{jeong_equilibrium_2016}. Finally, only two publications \cite{aufiero_extended_2013, 
+ashraf_nuclear_2018} using these capabilities are available, reflecting the 
+reproducibility challenge inherent in this feature.
+
+If these challenges can be overcome through verification against
+ChemTriton/SCALE as well as this work (the SaltProc/SERPENT2 package), we hope to 
+employ this SERPENT2 feature 
+for removal of fission products with shorter residence time (e.g., Xe, Kr), 
+since these have a strong negative impact on core lifetime and breeding 
+efficiency.
 

### 2019-01-03 results.tex
Keff zoomed added in the paper

@@
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} shows the effective multiplication factors 
+Figures~\ref{fig:keff}, \ref{fig:keff_zoomed} show the effective multiplication factors 
 obtained using SaltProc and SERPENT 2. The effective multiplication factors were 
@@
 factor fluctuates significantly as a result of the batch-wise nature of this 
-online reprocessing strategy.
+online reprocessing strategy. Figure~\ref{fig:keff_zoomed} shows how different 
+reprocessing groups imposed on effective multiplication factor.
 
@@
   \label{fig:keff}
+\end{figure}
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=\textwidth]{keff_zoomed.png}
+  \caption{Effective multiplication factor for 150-EFPD time-frame.}
+  \label{fig:keff_zoomed}
 \end{figure}

### 2019-01-04 results.tex
Zoomed Th refill rate added

--- 2019-01-02 results.tex
@@
 \subsection{Effective multiplication factor}
-Figure~\ref{fig:keff} shows the effective multiplication factors 
-obtained using SaltProc and SERPENT 2. The effective multiplication factors were 
+Figures~\ref{fig:keff}, \ref{fig:keff_zoomed} show the effective multiplication factors 
+obtained using SaltProc and SERPENT2. The effective multiplication factors were 
 calculated after removing fission products listed in 
@@
   \label{fig:keff}
+\end{figure}
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=\textwidth]{keff_zoomed.png}
+  \caption{Zoomed effective multiplication factor for 150-EFPD time interval.}
+  \label{fig:keff_zoomed}
 \end{figure}
@@
 \end{figure}
+\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
+  \includegraphics[width=\textwidth]{Th_refill_rate_zoomed.png} \caption{Zoomed $^{232}$Th 
+  feed rate for 150-EFPD time interval.}
+  \label{fig:th_refill}
+\end{figure}
 

### 2019-01-04 methods.tex
grammar and clarity, mostly

--- 2018-12-26 methods.tex
@@
 surface of the graphite reflector blocks.
+
+$^{135}$Xe is a strong neutron poison, and some fraction of this gas 
+is absorbed by graphite during \gls{MSBR} operation. ORNL calculations show 
+that for unsealed commercial graphite with helium permeability 10$^{-5}$ 
+cm$^2$/s the calculated poison fraction is less than 2\% 
+\cite{robertson_conceptual_1971}.  This parameter can be improved by using 
+experimental graphites or by applying sealing technology. The effect of the 
+gradual poisoning of the core graphite with xenon is not treated here.
 
@@
 section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
- would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
-and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
+ would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel, 
+ would produce a smaller amount of $^{233}$Pa which decays into the fissile $^{233}$U.
 Accordingly, $^{233}$Pa is continuously 
 removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-to decay to $^{233}$U without negative impact on neutronics. The reactor 
+to decay to $^{233}$U without the corresponding negative neutronic impact. The reactor 
 reprocessing system must separate $^{233}$Pa from the molten-salt fuel over 3 
@@
 time interval is too long, the impact of short-lived fission products is not 
-captured. To compromise, the time interval for depletion calculations in this 
-model was selected as 3 days\footnote{ Optimal depletion time step of 3 days for \gls{MSR} batch-wise depletion simulation was first described and concluded by Powers \emph{et al.} \cite{powers_new_2013}.} to correlate with the removal interval of
+captured. To compromise, a 3 day time interval was selected for depletion 
+calculations\footnote{ Optimal depletion time step of 3 days for \gls{MSR} 
+batch-wise depletion simulation was first described and concluded by Powers 
+\emph{et al.} \cite{powers_new_2013}.} to correlate with the removal interval 
+of 
 $^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
@@
 \gls{MSR} and are sufficiently general to represent myriad reactor systems.
+
+The current version of SaltProc only allows 100\% separation efficiency for 
+either specific elements or groups of elements (e.g. Processing Groups as described in 
+Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
+This approach works well for fast-removing elements (gases, noble metals, 
+protactinium) which should be removed each depletion step. Unfortunately, 
+for the elements with longer cycle times (i.e. rare earths should be removed 
+every 50 days) this simplified approach leads to oscillatory behavior of all
+major parameters. In future releases of SaltProc, this drawback will be eliminated 
+by removing elements with longer cycle times using different method: only mass 
+fraction (calculated separately for each reprocessing group) will be removed each
+ depletion step (e.g. 3 days).
 

### 2019-01-04 results.tex
grammar and clarity, mostly

--- 2019-01-02 results.tex
@@
 in a single-fluid two-region \gls{MSBR} conceptual design the undermoderated 
-outer core zone II works as a virtual ``blanket", reduces neutron leakage and 
+outer core zone II works as a virtual ``blanket'', reduces neutron leakage and 
 improves breeding ratio due to neutron energy spectral shift, and (4) 
@@
 AMD 6276 Interlagos CPU per node, 16 floating-point Bulldozer core units per 
-node or 32 ``integer" cores per node, nominal clock speed is 2.45 GHz). The 
+node or 32 ``integer'' cores per node, nominal clock speed is 2.45 GHz). The 
 total computational time for calculating the equilibrium composition was 
@@
 Additionally, the presence of rubidium, strontium, cesium, and barium in the 
-core are disadvantageous to reactor physics. In fact, SaltProc fully removes all these elements every 3435 days (not a small mass fraction every 3 days) 
+core are disadvantageous to reactor physics. 
+Overall, the effective multiplication factor gradually decreases from 1.075 to 
+$\approx$1.02 at equilibrium after approximately 6 years of irradiation.
+
+In fact, SaltProc fully removes 
+all of these elements every 3435 days (not a small mass fraction every 3 days) 
 which causes the multiplication factor to jump by approximately 450 
@@
 elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
- Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
- separately for each reprocessing group) will be removed every depletion step 
- (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
-Overall, the effective multiplication factor gradually decreases from 1.075 to 
-$\approx$1.02 at equilibrium after approximately 6 years of irradiation.
+ Cs, Ba, Eu). In that approach, chemistry models will inform separation 
+ efficiencies for each reprocessing group and removal will optionally be spread more 
+ evenly accross the cycle time.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{spectrum.png} \caption{Neutron flux energy 
-  spectrum normalized by unit lethargy and area under the curve is normalized to 1 for initial and equilibrium fuel salt 
+  \includegraphics[width=\textwidth]{spectrum.png} \caption{The neutron flux energy 
+  spectrum is normalized by unit lethargy and the area under the curve is normalized to 1 for initial and equilibrium fuel salt 
   composition.}
@@
   \includegraphics[width=\textwidth]{spectrum_zones.png} 
-  \caption{Neutron flux energy spectrum in different core regions normalized by 
-unit lethargy and area under the curve is normalized to 1 for the initial and equilibrium fuel salt composition.}
+  \caption{The neutron flux energy spectrum in different core regions is normalized by 
+unit lethargy and the area under the curve is normalized to 1 for the initial and equilibrium fuel salt composition.}
   \label{fig:spectrum_zones}
@@
 equilibrium, but most of the power is still generated in zone I at equilibrium 
-(table~\ref{tab:powgen_fraction}. 
+(table~\ref{tab:powgen_fraction}). 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 and equilibrium states. The distribution reflects the spatial distribution of 
-$^{233}$U production in the core. The thorium-233 produced after $^{232}$Th 
-captured neutron then $\beta$-decays to 
-$^{233}$Pa, which is the precursor for $^{233}$U production. Accordingly, this 
+$^{233}$U production in the core. $^{232}$Th 
+neutron capture produces $^{233}Th$ which then $\beta$-decays to 
+$^{233}$Pa, the precursor for $^{233}$U production. Accordingly, this 
 characteristic represents the breeding distribution in the \gls{MSBR} core. 
@@
 with the original \gls{ORNL} report data \cite{robertson_conceptual_1971}. 
-Uncertainty for each temperature coefficient was obtain by propagating statistical 
- error of effective multiplication factor calculation 
-provided by SERPENT2 and also appears in 
-Table~\ref{tab:tcoef}. Other sources of uncertainty, such as cross section libraries 
-uncertainty, error in salt and graphite density correlations, are not treated here.
+By propagating the $k_{eff}$  statistical error provided by SERPENT2, 
+uncertainty for each temperature coefficient was obtained and appears in 
+Table~\ref{tab:tcoef}. Other sources of uncertainty are neglected, such as cross section 
+measurement error and approximations inherent in the equations of state 
+providing both the salt and graphite density dependence on temperature.
  The main physical principle underlying the reactor 
-temperature feedback is an expansion of material that is heated. When the fuel 
+temperature feedback is an expansion of heated material. When the fuel 
 salt temperature increases, the density of the salt decreases, but at the same 
@@
 geometry input for SERPENT2, which takes into account displacement of graphite 
-surfaces, was created based on this information. For the displacements calculation 
-it was assumed that the interface between graphite reflector and vessel did not move,
- and the vessel temperature did not change. This is the most reasonable assumption for
+surfaces, was created based on this information. For calculation of 
+displacement, it was assumed that the interface between the graphite reflector and vessel did not move,
+ and that the vessel temperature did not change. This is the most reasonable assumption for
  the short-term reactivity effects because inlet salt is cooling graphite reflector and 
@@
 equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
-capture cross sections in the thorium. Small positive effect of fuel density on 
-reactivity is increasing from +1.21 pcm/K for the reactor startup to +1.66 pcm/K for 
+capture cross sections in the thorium. A small positive effect of fuel density on 
+reactivity increases from $+1.21$ pcm/K at reactor startup to $+1.66$ pcm/K for 
 equilibrium fuel composition which has negative effect on FTC magnitude during the 
@@
 Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
-equilibrium fuel salt composition. These factors and their statistical uncertainties
- have been calculated using SERPENT2 code for initial fuel salt composition (see 
-Table~\ref{tab:msbr_tab}) and for equilibrium salt composition which was obtained 
-with SaltProc. The non-leakage probability for both fast 
-and thermal neutrons does not change during reactor operation because these 
-values are not largely affected by the neutron spectrum shift. In contrast, 
-neutron reproduction factor ($\eta$), resonance escape probability (p), and 
-fast fission factor ($\epsilon$) are considerably different between startup and 
+equilibrium fuel salt composition. Using SERPENT2 and SaltProc, tese factors and their statistical uncertainties
+ have been calculated for both initial and equilibrium fuel salt composition (see 
+Table~\ref{tab:msbr_tab}). The fast and thermal non-leakage probabilities 
+remain constant despite the evolving neutron spectrum during operation. In 
+contrast, the neutron reproduction factor ($\eta$), resonance escape 
+probability ($p$), and fast fission factor ($\epsilon$) are considerably different between startup and 
 equilibrium. As indicated in Figure~\ref{fig:spectrum}, the neutron spectrum is 
@@
 good agreement with a recent online reprocessing study by \gls{ORNL} 
-\cite{betzler_molten_2017}. It must be noted that for the reactor with only 
-thorium feed, at near equilibrium state, the thorium consumption rate is 
-determined by the reactor power, the energy released per fission, and 
-neutron energy spectrum.
+\cite{betzler_molten_2017}. At equilibrium, the thorium feed rate is determined 
+by the reactor power, the energy released per fission, and the neutron energy 
+spectrum.
 

### 2019-01-04 results.tex
Zoomed TH feed added #33

--- 2019-01-04 results.tex
@@
 fluctuates significantly as a result of the batch-wise nature of this online 
-reprocessing approach. For example, the large spikes of up to 36 kg/day in a 
-thorium consumption occurs every 3435 days. This is required due to batch-wise 
-removal of strong absorbers (Rb, Sr, Cs, Ba). The corresponding effective 
+reprocessing approach. Figure~\ref{fig:th_refill_zoomed} shows zoomed thorium feed 
+rate for short 150-EFPD interval. Note that the large spikes of up to 36 kg/day in a 
+thorium consumption occurs every 3435 days. This is required due to strong absorbers 
+(Rb, Sr, Cs, Ba) removal at the end of effective cycle (100\% of these elements 
+removing every 3435 days of operation). The corresponding effective 
 multiplication factor increase (Figure~\ref{fig:keff}) and breeding 
@@
   feed rate for 150-EFPD time interval.}
-  \label{fig:th_refill}
+  \label{fig:th_refill_zoomed}
 \end{figure}

### 2019-01-04 revisions/review-responses.tex
SERPENT2 reprocessing feature explanation conflict resolved
Few grammar issues fixed

--- 2019-01-03 revisions/review-responses.tex
@@
 
-%\usepackage[acronym,toc]{glossaries}
-%\include{acros}
+\usepackage[acronym,toc]{glossaries}
+\include{acros}
 
-%\makeglossaries
+\makeglossaries
 
@@
                  to be verified. Additional text to clarify this point has 	
-                been add to solution for question 21.                
+                been added to solution for question 21.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Zoomed portion for 150 EFPD interval has been added. We also 
+                added notes on a plot to explain swing in multiplication factor.
         \end{solution}
@@
         \begin{solution}
-                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
+                Thank you for the recommendation. Atom density was chosen for 
+                publication-to-publication comparison (e.g. Park \emph{et al.} and 
+                Betzler \emph{et al.}
                 \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
@@
 
-		        The neutron energy spectrum at equilibrium is harder than at startup due 
-                to plutonium and other strong absorbers accumulation in the core during 
-		        reactor operation.  
+		        The neutron energy spectrum at equilibrium is harder than at startup 
+		        due to plutonium and other strong absorbers accumulation in the core 
+		        during reactor operation.  
         \end{solution}
@@
         \begin{solution}
-                <++>
+                Zoomed portion for 150 EFPD interval and clarifying 
+                notes has been added.
         \end{solution}

### 2019-01-04 revisions/review-responses.tex
done with review responses edits

--- 2019-01-03 revisions/review-responses.tex
@@
 We would like to thank the reviewers for their detailed assessment of
-this paper. Your comments have resulted in changes which certainly improved the 
-paper.
+this paper. Your suggestions, clarifications, and comments have resulted in 
+changes which certainly improved the paper.
 
@@
         \section*{Reviewer 1}
+
+        \question Overall, a well written article in a topic area of interest 
+        to a number of audiences. Technically very good, well written in the 
+        description and analysis.  Well done authors!
+
+        A few minor comments/suggestions/clarifications as follows:
+        \begin{solution}
+                Thank you for these kind comments. Your suggestions have 
+                certainly improved the paper. 
+        \end{solution}
+
         %---------------------------------------------------------------------
@@
         \begin{solution}
-        		Thank you for your kind review. Current manuscript was submitted before 
+        		Thank you for your kind review. The current manuscript was submitted before 
 		        announcement that TransAtomic is ceasing operations. It is removed from 
-		        the list of MSR startups.
+                        the list of MSR startups (indeed, the whole list was 
+                        removed based on a comment by another reviewer).
         \end{solution}
@@
 
-		        The latest SCALE release will also have the same functionality using 
-        		truly continuous removals \cite{betzler_implementation_2017}.
+		        ``The latest SCALE release will also have the same functionality using 
+        		truly continuous removals \cite{betzler_implementation_2017}.''
         \end{solution}
@@
         \begin{solution}
-        		Thanks for catching this. Following passage has been added:
+        		Thanks for catching this. The following passage has been added:
 
-		        Protactinium presents a challenge, since it has a large absorption cross 
+		        ``Protactinium presents a challenge, since it has a large absorption cross 
 				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
@@
 				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-				to decay to $^{233}$U without negative impact on neutronics.
+				to decay to $^{233}$U without negative impact 
+                                on neutronics.''
         \end{solution}
@@
         \begin{solution}
-		        The ``cycle time'' definition has been added in a first appearance in text.
+                        The ``cycle time'' definition has been added at the first 
+                        appearance in text. 
         \end{solution}
@@
         \begin{solution}
-                It does. We tried use it before but these capabilities needs 
-                to be verified. Additional text to clarify this point has 
-                been add to solution for question 21.                
+                It does. Indeed, much of the inspiration for SaltProc was the 
+                lack of documentation, difficulty of use, and various 
+                inexplicable results we acquired when we tried use this 
+                built-in capability. This capability has not performed well and 
+                needs to be better documented and more robustly verified before 
+                we can use it. We fully intend to contribute to its improvement 
+                if it can be made to agree with expectations.  Additional text 
+                to clarify this point has been add to solution for question 
+                \ref{built-in}.                
         \end{solution}
@@
         \begin{solution}
-		        100 \% of those elements atoms removed every 3435 days. Full salt discard
+		        100 \% of those elements atoms are removed every 3435 
+                        days. Full salt discard
 		         as it mentioned in Table 3 has not been implemented. More detailed 
@@
 
-		        Additionally, the presence of rubidium, strontium, cesium, and barium in
-		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
-		         removes all these elements every 3435 days (not a small mass fraction 
-		         every 3 days) which causes the multiplication factor to jump by 
-		        approximately 450 pcm, and limits using the batch approach for online 
-		        reprocessing simulations. In future versions of SaltProc this drawback 
-		        will be eliminated by removing elements with longer cycle times (seminoble 
-		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
-		        Only mass fraction (calculated separately for each reprocessing group) 
-		        will be removed every depletion step (e.g. 3 days) instead of removing 
-		        100\% of element atoms after cycle time. 
+                        ``Additionally, the presence of rubidium, strontium, cesium, and barium in the
+                        core are disadvantageous to reactor physics.
+                        Overall, the effective multiplication factor gradually decreases from 1.075 to
+                        $\approx$1.02 at equilibrium after approximately 6 years of irradiation.
+
+                        In fact, SaltProc fully removes
+                        all of these elements every 3435 days (not a small mass fraction every 3 days)
+                        which causes the multiplication factor to jump by approximately 450
+                        pcm, and limits using the batch approach for online reprocessing simulations.
+                        In future versions of SaltProc this drawback will be eliminated by removing
+                        elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
+                         Cs, Ba, Eu). In that approach, chemistry models will inform separation
+                         efficiencies for each reprocessing group and removal will optionally be spread more
+                         evenly accross the cycle time.''
         \end{solution}
@@
         \begin{solution}
-		        Explanation of this phenomena has been added as follows:
+		        Explanation of this phenomenon has been added as follows:
 
-		         Small dips in neptunium and plutonium number density every 16 years are 
-		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
-		         ``Higher nuclides'', see Table 3) which decays
-        		  into $^{235}$Np, $^{239}$Pu, respectively. 
+                          ``Small dips in neptunium and plutonium number density 
+                          every 16 years are caused by removing $^{237}$Np and 
+                          $^{242}$Pu (included in Processing group ``Higher 
+                          nuclides'', see Table~\ref{tab:reprocessing_list}) 
+                          which decays into $^{235}$Np and $^{239}$Pu, 
+                          respectively.''
         \end{solution}
@@
 
-		        The neutron energy spectrum at equilibrium is harder than at startup due 
-                to plutonium and other strong absorbers accumulation in the core during 
-		        reactor operation.  
+                         ``The neutron energy spectrum at equilibrium is harder 
+                         than at startup due to plutonium and other strong 
+                         absorbers accumulation in the core during reactor 
+                         operation.''
         \end{solution}
@@
         \begin{solution}
-                Thanks for catching this. Units $\frac{n}{cm^2 s}$ has been added.
+                Thanks for catching this. The units $\frac{n}{cm^2 s}$ have been added.
         \end{solution}
@@
         \begin{solution}
-                Yes, we meant $^{233}$U production. The typo has been fixed.
+u                Yes, we meant $^{233}$U production. The typo has been fixed. 
+                Thanks so much for catching it!
         \end{solution}
@@
         \begin{solution}
-                In the Table 5 was added information that reference column contains 
-                data for initial fuel salt composition. Details about uncertainties
-                 have been added:
+                In Table 5, we added information in the reference column 
+                containing data for initial fuel salt composition. Details 
+                about uncertainties have been added:
 
-                Uncertainty for each temperature coefficient was obtain by 
-                propagating statistical error of effective multiplication factor 
-                calculation provided by SERPENT2 and also appears in Table 5. 
-                Other sources of uncertainty, such as cross section libraries 
-				uncertainty, error in salt and graphite density correlations, 
-				are not treated here.
+                ``Table 5 summarizes temperature effects on reactivity calculated 
+                in this work for both initial and equilibrium fuel 
+                compositions, compared with the original \gls{ORNL} report data 
+                \cite{robertson_conceptual_1971}.  By propagating the $k_{eff}$  
+                statistical error provided by SERPENT2, uncertainty for each 
+                temperature coefficient was obtained and appears in Table 5. 
+                Other sources of uncertainty are neglected, such as cross 
+                section measurement error and approximations inherent in the 
+                equations of state providing both the salt and graphite density 
+                dependence on temperature.''
+
         \end{solution}
@@
         \begin{solution}
-                Sentence has been extended as follows:
+                The sentence has been extended as follows:
 
-                ...the total temperature coefficient of reactivity is relatively large and
-                 negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent
-                 reactor stability and control.
+                ...the total temperature coefficient of reactivity is 
+                relatively large and negative during reactor operation 
+                (comparing with conventional PWR which 							
+                temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ 
+                -3.08 pcm/K 							
+                \cite{forget_integral_2018}), despite positive MTC, and affords 
+                excellent reactor stability and control.
+
+                The moderator
+temperature coefficient (MTC) is positive for the startup composition and decreases
+during reactor operation because of spectrum hardening with fuel depletion.
+Finally, the total temperature coefficient of reactivity is negative for both
+cases, but decreases during reactor operation due to spectral shift. In
+summary, even after 20 years of operation the total temperature coefficient of
+reactivity is relatively large and negative during reactor operation (comparing
+with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F
+$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and
+affords excellent reactor stability and control.
+
         \end{solution}
@@
 
-                Table 7 summarizes the six factors for both initial and 
-				equilibrium fuel salt composition. These factors and their statistical 								uncertainties have been calculated using SERPENT2 code for initial fuel salt 
-				composition (see Table 2) and for equilibrium salt composition which was 
-				obtained with SaltProc. 
+                ``Table~7 summarizes the six factors for both initial and 
+                equilibrium fuel salt composition. Using SERPENT2 and SaltProc, 
+                tese factors and their statistical uncertainties have been 
+                calculated for both initial and equilibrium fuel salt 
+                composition (see Table~2).''
         \end{solution}
@@
         %---------------------------------------------------------------------
+        \question The paper presents a python script (SaltProc) that can 
+        complement the Serpent 2 code capabilities in terms of fuel cycle 
+        analysis of MSRs. The paper is well written and the tool might be 
+        useful for the nuclear engineering community. However, before 
+        publishing the paper, I recommend some revisions.
+        \begin{solution}
+                Thanks very much for these comments. We appreciate your 
+                detailed review, which has certainly improved the paper.
+        \end{solution}
 
-        \question The most critical point of the work is that the built-in 
+        %---------------------------------------------------------------------
+
+        \question \label{built-in} The most critical point of the work is that the built-in 
         capabilities for online reprocessing of Serpent 2 have not been used. 
@@
         \begin{solution}
-                Thank you for your kind review. We tried to use these capabilities 
-                \cite{rykhlevskii_online_2017} but have had number of issues which 
-                are hard to resolve due to lack of documentation and publications 
-                involving this feature. Following paragraph has been added to 
-                clarify why these capabilities have not been used in current work:
+                Thank you for your helpful review. We tried to use these capabilities 
+                \cite{rykhlevskii_online_2017} but have had a number of issues which 
+                are hard to resolve due to lack of documentation and 
+                published verifications of this feature. The following 
+                paragraph has been added to clarify why these capabilities have 
+                not been used in current work:
 
-                We employed this extended SERPENT2 for a simplified unit-cell 
-                geometry of thermal spectrum thorium-fueled MSBR and have had 
-                following problems: (1) lack of documentation describing how 
-                to use this built-in SERPENT2 online reprocessing capabilities
-                \footnote{ Some challenges in no particular order: mass 
-                conservation is hard to achieve; not clear when use mflow card 
-                type 0, 1 or 2; difference between CRAM and TTA results; etc.} 
-				(Discussion forum for SERPENT users is only useful 
-				source of information at the moment); (2) reactivity control 
-				module described in Aufiero \emph{et al.} is not available 
-				in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
-				factor behavior for simplified unit-cell model obtained using 
-				SERPENT2 built-in capabilities \cite{rykhlevskii_online_2017} 
-				does not match with exist MCNP6/Python-script results for the 
-				similar model by Jeong and Park\footnote{ In our study 
-				k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of 
-				depletion simulation while in Jeong and Park work this parameter 
-				decreasing slowly from 1.065 to 1.05 for the 
-				similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few 
-				publication \cite{aufiero_extended_2013, ashraf_nuclear_2018} 
-				using these capabilities are available which is indicative of 
-				lack of reproducibility. Nevertheless, truly continuous 
-				online reprocessing capabilities of SERPENT2 is desirable feature 
-				for our future research. However, these capabilities should be 
-				carefully verified against ChemTriton/SCALE or proposed 
-				SaltProc/SERPENT2 package, and could be employed 
-				for removal of fission products with shorter residence time 
-				(e.g., Xe, Kr) which have a strong negative impact on core 
-				lifetime and breeding efficiency which we intent to do in 
-				the nearest future.
+                ``Aufiero \emph{et al.} added an undocumented feature to SERPENT2 
+                using a similar methodology by explicitly introducing 
+                continuous reprocessing in the system of Bateman equations and 
+                adding effective decay and transmutation terms for each nuclide 
+                \cite{aufiero_extended_2013}. This was employed to study the 
+                material isotopic evolution of the 
+                \gls{MSFR}\cite{aufiero_extended_2013}. The developed extension 
+                directly accounts for the effects of online fuel reprocessing 
+                on depletion calculations and features a reactivity control 
+                algorithm. The extended version of SERPENT2 was assessed 
+                against a dedicated version of the deterministic ERANOS-based 
+                EQL3D procedure in \cite{ruggieri_eranos_2006, 
+                fiorina_investigation_2013} and adopted to analyze the 
+                \gls{MSFR} fuel salt isotopic evolution.
+
+                We employed this built-in SERPENT2 feature for a simplified 
+                unit-cell geometry of the thermal spectrum thorium-fueled 
+                \gls{MSBR} and found it unusable\footnote{ Some challenges in 
+                no particular order: mass conservation is hard to achieve; 
+                three types of mflow cards (0, 1 or 2) are indistinguishable in 
+                purpose; an unexplained difference between CRAM and TTA 
+                results; etc.}. Primarily, it is undocumented, and the 
+                discussion forum for SERPENT users is the only useful source of 
+                information at the moment. Additionally, the reactivity control 
+                module described in Aufiero \emph{et al.} is not available in 
+                the latest SERPENT 2.1.30 release. Third, the infinite 
+                multiplication factor behavior for simplified unit-cell model 
+                obtained using SERPENT2 built-in capabilities 
+                \cite{rykhlevskii_online_2017} does not match with exist 
+                MCNP6/Python-script results for the similar model by Jeong and 
+                Park\footnote{ In our study k$_{\infty}$ drops from 1.05 to 
+                1.005 during a 1200 days of depletion simulation while in Jeong 
+                and Park work this parameter decreasing slowly from 1.065 to 
+                1.05 for the similar time-frame.} 
+                \cite{jeong_equilibrium_2016}. Finally, only two publications 
+                \cite{aufiero_extended_2013, ashraf_nuclear_2018} using these 
+                capabilities are available, reflecting the reproducibility 
+                challenge inherent in this feature.
+
+                If these challenges can be overcome through verification 
+                against ChemTriton/SCALE as well as this work (the 
+                SaltProc/SERPENT2 package), we hope to employ this SERPENT2 
+                feature for removal of fission products with shorter residence 
+                time (e.g., Xe, Kr), since these have a strong negative impact 
+                on core lifetime and breeding efficiency.''
+
         \end{solution}
@@
 
-        \question Considering the scope of the journal, mentioning the names of 
+        \question In addition to this major point, I would suggest a few other 
+        revisions. Considering the scope of the journal, mentioning the names of 
         companies and start-up is not appropriate. I would suggest removing 
@@
         \begin{solution}
-                Thank you for the exceptional recommendation. The sentence has been 
-                changed as follows:
+                Thank you for the exceptional recommendation. The sentence has 
+                been split into two, as follows:
 
-                ``Immediate advantages over traditional light water reactors 
-                include\dots''
+                Immediate advantages over traditional commercial reactors 
+                include near-atmospheric pressure in the primary loop, 
+                relatively high coolant temperature, outstanding neutron 
+                economy, and improved safety parameters. Advantages over 
+                solid-fueled reactors in general include reduced fuel 
+                preprocessing and the ability to continuously remove fission 
+                products and add fissile and/or fertile elements 
+                \cite{leblanc_molten_2010}.
+
         \end{solution}
@@
         \begin{solution}
-                Thanks for your kind comment. The sentence has been removed.
+                Thanks for your insightful comment. The sentence has been removed.
         \end{solution}
@@
         \begin{solution}
-                Thank you for the information. [14] has been removed from the 
+                Thank you for the information. That reference has been removed from the 
                 sentence, and following paragraph has been modified to read:
 
-                Accounting for continuous removal or addition presents a greater 
-                challenge since it requires adding a term to the Bateman equations. 
-                Fiorina \emph{et al.} simulated MSFR depletion with continuous
-                 fuel salt reprocessing via introducing ``reprocessing'' time 
-                constants into ERANOS transport code \cite{fiorina_investigation_2013}. 
-                Aufiero \emph{et al.} improved SERPENT2 using similar methodology by 
-                explicitly introducing continuous reprocessing in the system of Bateman 
-                equations by adding effective decay and transmutation terms for the 
-                different nuclides \cite{aufiero_extended_2013}. 
+                Accounting for continuous removal or addition presents a 
+                greater challenge since it requires adding a term to the 
+                Bateman equations. Fiorina \emph{et al.} simulated \gls{MSFR} 
+                depletion with continuous fuel salt reprocessing via 
+                introducing ``reprocessing'' time constants into the ERANOS 
+                transport code \cite{fiorina_investigation_2013}.  The latest 
+                SCALE release will also have the same functionality using truly 
+                continuous removals \cite{betzler_implementation_2017}.  A 
+                similar approach is adopted to model true continuous feeds and 
+                removals using the MCNP transport code listed in references 
+                \cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
+
         \end{solution}
@@
         \begin{solution}
-                The ``cycle time'' definition has been added in a first appearance in text.
+                The ``cycle time'' definition has been added to its first appearance in text.
         \end{solution}
@@
                 All of them at the end of the cycle time, and we agree that it
-                 was not best solution. To clarify this following paragraph has 
+                 was not best solution. Feature improvements in SaltProc are 
+                 underway to enable more realistic handling times in the 
+                 processing heuristics. To clarify this following paragraph has 
                 been added:
 
-				Current version of SaltProc only allows separate out 100\% of 
-				specific elements or group of elements (e.g. Processing Groups 
-				as described in Table 3 at the end
-				 of the specific cycle time. This approach works well for 
-				fast-removing elements (gases, noble metals, protactinium) which 
-				should be removed each depletion step. Unfortunately, for the 
-				elements with longer cycle time (i.e. rare earths should be removed 
+                The current version of SaltProc only allows 100\% separation 
+                efficiency for either specific elements or groups of elements 
+                (e.g. Processing Groups as described in 
+                Table~\ref{tab:reprocessing_list}) at the end of the specific 
+                cycle time.  This approach works well for fast-removing 
+                elements (gases, noble metals, protactinium) which should be 
+                removed each depletion step. Unfortunately, for the elements 
+                with longer cycle times (i.e. rare earths should be removed 
                 every 50 days) this simplified approach leads to oscillatory 
-				behavior of all major parameters. In future releases of SaltProc
-				 this drawback will be eliminated by removing elements with longer 
-				cycle times using different method: only mass fraction (calculated 
-				separately for each reprocessing group) will be removed each 
-				depletion step (e.g. 3 days).	
+                behavior of all major parameters. In future releases of 
+                SaltProc, this drawback will be eliminated by removing elements 
+                with longer cycle times using different method: only mass 
+                fraction (calculated separately for each reprocessing group) 
+                will be removed each depletion step (e.g. 3 days).
+
         \end{solution}
@@
                 Yes, the oscillation happened because the fission products 
-        		with longer residence time are removed at the end of cycle time. We are 
+                with longer residence time are removed at the end of cycle time. We 
                 definitely will take your advice and improve the code in future 
-                releases. Following text has been added to clarify this issue:
+                releases. The following text has been added to clarify this issue:
 
-                In fact, SaltProc fully removes all these elements every 3435 days 
-                (not a small mass fraction every 3 days) which causes the 
-                multiplication factor to jump by approximately 450 pcm, and limits 
-                using the batch approach for online reprocessing simulations. In 
-                future versions of SaltProc this drawback will be eliminated by 
-                removing elements with longer residence time (seminoble metals, 
-                volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
-                Only mass fraction (calculated separately for each reprocessing 
-                group) will be removed every depletion step (e.g. 3 days) instead 
-                of removing 100\% of element atoms after cycle time.
+                In fact, SaltProc fully removes all of these elements every 
+                3435 days (not a small mass fraction every 3 days) which causes 
+                the multiplication factor to jump by approximately 450 pcm, and 
+                limits using the batch approach for online reprocessing 
+                simulations.  In future versions of SaltProc this drawback will 
+                be eliminated by removing elements with longer residence times 
+                (seminoble metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu). In 
+                that approach, chemistry models will inform separation 
+                efficiencies for each reprocessing group and removal will 
+                optionally be spread more evenly accross the cycle time.
+
         \end{solution}
@@
         \begin{solution}
-                No, and we do not plan to add this capability.
+                No, and we may someday add this capability, but we expect this 
+                will be a challenge outside of the depletion code.
         \end{solution}
@@
 
-                 Uncertainty for each temperature coefficient was obtain by 
-                 propagating statistical error of effective multiplication factor 
-                 calculation provided by SERPENT2 and also appears in Table 5. 
-                 Other sources of uncertainty, such as cross section libraries 
-				 uncertainty, error in salt and graphite density correlations, 
-				 are not treated here.
+                 By propagating the $k_{eff}$  statistical error provided by 
+                 SERPENT2, uncertainty for each temperature coefficient was 
+                 obtained and appears in Table~\ref{tab:tcoef}. Other sources 
+                 of uncertainty are neglected, such as cross section 
+                 measurement error and approximations inherent in the equations 
+                 of state providing both the salt and graphite density 
+                 dependence on temperature.  
         \end{solution}
@@
 
-                A new geometry input for SERPENT2, which takes into account 
-                displacement of graphite surfaces, was created based on this information. 
-                For the displacements calculation it was assumed that the interface 
-                between graphite reflector and vessel did not move, and the vessel 
-                temperature did not change. This is the most reasonable assumption for 
-				the short-term reactivity effects because inlet salt is cooling graphite 
-				reflector and inner surface of the vessel.
+                        A new geometry input for SERPENT2, which takes into 
+                        account displacement of graphite surfaces, was created 
+                        based on this information. For calculation of 
+                        displacement, it was assumed that the interface between 
+                        the graphite reflector and vessel did not move, and 
+                        that the vessel temperature did not change. This is the 
+                        most reasonable assumption for the short-term 
+                        reactivity effects because inlet salt is cooling 
+                        graphite reflector and inner surface of the vessel.
+
         \end{solution}
@@
 
-				The fuel temperature coefficient (FTC) is negative for both initial and 
-				equilibrium fuel compositions due to thermal Doppler broadening of the 
-				resonance capture cross sections in the thorium. Small positive effect 
-				of fuel density on reactivity is increasing from +1.21 pcm/K for the 
-				reactor startup to +1.66 pcm/K for equilibrium fuel composition which 
-				has negative effect on FTC magnitude during the reactor operation. 
+                The fuel temperature coefficient (FTC) is negative for both 
+                initial and equilibrium fuel compositions due to thermal 
+                Doppler broadening of the resonance capture cross sections in 
+                the thorium. A small positive effect of fuel density on 
+                reactivity increases from $+1.21$ pcm/K at reactor startup to 
+                $+1.66$ pcm/K for equilibrium fuel composition which has 
+                a negative effect on FTC magnitude during the reactor operation. 
         \end{solution}
@@
         \begin{solution}
-                This statement has been removed completely.
+                This statement, being unclear and misleading, has been removed 
+                completely. The intention was to communicate that for a relaxed 
+                definition of equillibrium, it can be acheived.
         \end{solution}
@@
         \section*{Reviewer 3}
+
+        \question This paper presents a SaltProc-Serpent2 coupled code system
+        to simulate the depletion and online reprocessing process by directly
+        changing the isotropic composition of fuel salt. The Molten Salt
+        Breeder Reactor (MSBR) was analyzed to demonstrate the simulation
+        capability of the developed code system. However, large number of
+        similar works have been done and published on this topic. In
+        particular, this work is similar with that done by Park et al. with the
+        title of ``Whole core analysis of molten salt breeder reactor with
+        online fuel reprocessing'' published on ``International Journal of Energy
+        Research''. The authors need to prove the uniqueness and innovation
+        within their work.
+        \begin{solution}
+                We appreciate this comment and have made clarifying 
+                improvements to indicate the impact of this work throughout the 
+                paper. More detail is described regarding these changes in the 
+                specific comment responses below.
+        \end{solution}
 
@@
                 \cite{jeong_equilibrium_2016} are most similar to the work 
-                presented in this paper. However, few major differences worse to 
-                be mentioned: (1) Park \emph{et al.} employed MCNP6 for depletion 
-				simulations while SERPENT2 was used in this work (SERPENT2 seems 
-				to be much faster in massively parallel simulations involving more 
-				than 1000 cores); (2) full-core reactor model herein is more 
-				detailed and has no major approximation comparing with Park \emph{et al.}
-				(detailed full-core models comparison might be found elsewhere
-				\cite{rykhlevskii_full-core_2017}); (3) Park \emph{et al.} and 
-				Jeong \emph{et al.} both considered volatile gases, noble metals 
-				removal and $^{233}$Pa separation while in the current work we are 
-				implemented detailed reprocessing scheme described in conceptual 
-				MSBR design \cite{robertson_conceptual_1971}; (4) $^{232}$Th 
-				neutron capture reaction rate has been investigated to prove 
-				advantages of two-region core design; (5) the effect of removing 
-				fission product removal from fuel salt has been studied. 
+                presented in this paper. However, a few major differences 
+                follow: (1) Park \emph{et al.} employed MCNP6 for depletion 
+                simulations while this work used SERPENT2; (2) the full-core 
+                reactor geometry herein is more detailed 
+                \cite{rykhlevskii_full-core_2017}; (3) Park \emph{et al.} and 
+                Jeong \emph{et al.} both only considered volatile gas removal, 
+                noble metal removal, and $^{233}$Pa separation while the 
+                current work implemented the more detailed reprocessing scheme 
+                specified in the conceptual \gls{MSBR} design 
+                \cite{robertson_conceptual_1971}; (4) the $^{232}$Th neutron 
+                capture reaction rate has been investigated to prove advantages 
+                of two-region core design; (5) the current work explicitly 
+                examines the independent impacts of removing specific fission 
+                product groups.
         \end{solution}
@@
                 We have compared few parameters (multiplication factor, Th refill 
-                rate, neutron energy spectrum) with Betzler \emph{et al.} 											\cite{betzler_molten_2017} and mentioned it in the Result section. 
+                rate, neutron energy spectrum) with Betzler \emph{et al.} 										
+                \cite{betzler_molten_2017} and mentioned it in the Result section. 
                 We also compared neutron energy spectrum and temperature coefficients
@@
                 10 and 11 are normalized per unit lethargy and the area under 
-                the curve is normalized to 1.
+                the curve is normalized to 1. The caption has been edited to 
+                make this more clear.
         \end{solution}
@@
 
-                 Table 4 shows the power fraction in each zone for initial and 
-                 equilibrium fuel compositions. Figure 13 reflects the normalized 
-                 power distribution of the MSBR quarter core for equilibrium 
-                 fuel salt composition. For both the initial and equilibrium 
-                 compositions, fission primarily occurs in the center of the core, 
-                 namely zone I. The spectral shift during reactor operation results 
-                 in slightly different power fractions at startup and equilibrium, 
-                 but most of the power is still generated in zone I at equilibrium 
-				 (table 4).
+                 Table~4 shows the power fraction in each zone for initial and 
+                 equilibrium fuel compositions. Figure~13 reflects the 
+                 normalized power distribution of the \gls{MSBR} quarter core 
+                 for equilibrium fuel salt composition. For both the initial 
+                 and equilibrium compositions, fission primarily occurs in the 
+                 center of the core, namely zone I. The spectral shift during 
+                 reactor operation results in slightly different power 
+                 fractions at startup and equilibrium, but most of the power is 
+                 still generated in zone I at equilibrium (table~4).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-01-04 results.tex
done with review responses edits

--- 2019-01-04 results.tex
@@
 in neptunium and plutonium number density every 16 years are caused by removing
-$^{237}$Np, $^{242}$Pu (included in Processing group ``Higher nuclides'', see
- Table~\ref{tab:reprocessing_list}) which decays into $^{235}$Np, $^{239}$Pu, 
+$^{237}$Np and $^{242}$Pu (included in Processing group ``Higher nuclides'', see
+ Table~\ref{tab:reprocessing_list}) which decay into $^{235}$Np and $^{239}$Pu, 
  respectively. Thus, 
@@
 reactivity increases from $+1.21$ pcm/K at reactor startup to $+1.66$ pcm/K for 
-equilibrium fuel composition which has negative effect on FTC magnitude during the 
+equilibrium fuel composition which has a negative effect on FTC magnitude during the 
 reactor operation. This is in good agreement with earlier 

### 2019-01-04 revisions/review-responses.tex

--- 2019-01-04 revisions/review-responses.tex
@@
         \begin{solution}
-                It does. We tried use it before but these capabilities needs
-                 to be verified. Additional text to clarify this point has 	
-                been added to solution for question 21.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Thank you for the recommendation. Atom density was chosen for 
-                publication-to-publication comparison (e.g. Park \emph{et al.} and 
-                Betzler \emph{et al.}
+                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
                 \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
@@
 		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
-		         ``Higher nuclides'', see Table 3) which decays
+		         ``Higher nuclides'', see Table~\ref{tab:reprocessing_list}) which decays
         		  into $^{235}$Np, $^{239}$Pu, respectively. 
@@
 
-		        The neutron energy spectrum at equilibrium is harder than at startup 
-		        due to plutonium and other strong absorbers accumulation in the core 
-		        during reactor operation.  
+		        The neutron energy spectrum at equilibrium is harder than at startup due 
+                to plutonium and other strong absorbers accumulation in the core during 
+		        reactor operation.  
         \end{solution}
@@
         \begin{solution}
-                Zoomed portion for 150 EFPD interval and clarifying 
-                notes has been added.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                Thank you for your kind review. We tried to use these capabilities 
-                \cite{rykhlevskii_online_2017} but have had number of issues which 
-                are hard to resolve due to lack of documentation and publications 
-                involving this feature. Following paragraph has been added to 
-                clarify why these capabilities have not been used in current work:
-
-                We employed this extended SERPENT2 for a simplified unit-cell 
-                geometry of thermal spectrum thorium-fueled MSBR and have had 
-                following problems: (1) lack of documentation describing how 
-                to use this built-in SERPENT2 online reprocessing capabilities
-                \footnote{ Some challenges in no particular order: mass 
-                conservation is hard to achieve; not clear when use mflow card 
-                type 0, 1 or 2; difference between CRAM and TTA results; etc.} 
-				(Discussion forum for SERPENT users is only useful 
-				source of information at the moment); (2) reactivity control 
-				module described in Aufiero \emph{et al.} is not available 
-				in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
-				factor behavior for simplified unit-cell model obtained using 
-				SERPENT2 built-in capabilities \cite{rykhlevskii_online_2017} 
-				does not match with exist MCNP6/Python-script results for the 
-				similar model by Jeong and Park\footnote{ In our study 
-				k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of 
-				depletion simulation while in Jeong and Park work this parameter 
-				decreasing slowly from 1.065 to 1.05 for the 
-				similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few 
-				publication \cite{aufiero_extended_2013, ashraf_nuclear_2018} 
-				using these capabilities are available which is indicative of 
-				lack of reproducibility. Nevertheless, truly continuous 
-				online reprocessing capabilities of SERPENT2 is desirable feature 
-				for our future research. However, these capabilities should be 
-				carefully verified against ChemTriton/SCALE or proposed 
-				SaltProc/SERPENT2 package, and could be employed 
-				for removal of fission products with shorter residence time 
-				(e.g., Xe, Kr) which have a strong negative impact on core 
-				lifetime and breeding efficiency which we intent to do in 
-				the nearest future.
+                <++>
         \end{solution}
@@
         \begin{solution}
-                This statement has been significantly extended (see Solution 21).
+                <++>
         \end{solution}

### 2019-01-04 methods.tex

--- 2019-01-02 methods.tex
@@
 or group of elements (e.g. Processing Groups as described in 
-Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
+Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. That is 
+simplification because in reality fuel salt resides approximately 1/2 of total time 
+in the core and rest of the time in the primary loop pipes and the heat exchanger.  
 This approach works well for fast-removing elements (gases, noble metals, 
@@
 fraction (calculated separately for each reprocessing group) will be removed each
- depletion step (e.g. 3 days).
+ depletion step or batch (e.g. in the current work it was chosen 3 days).
 

### 2019-01-04 methods.tex

--- 2019-01-04 methods.tex
@@
 Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
+This simplification neglects the reality that the salt spends appreciable time 
+out of the core, in the primary loop pipes and the heat exchanger.
+
 This approach works well for fast-removing elements (gases, noble metals, 

### 2019-01-04 revisions/review-responses.tex
fixes conflicts

--- 2019-01-04 revisions/review-responses.tex
@@
 
-                ...the total temperature coefficient of reactivity is 
-                relatively large and negative during reactor operation 
-                (comparing with conventional PWR which 							
-                temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ 
-                -3.08 pcm/K 							
+                The moderator temperature coefficient (MTC) is positive for the 
+                startup composition and decreases during reactor operation 
+                because of spectrum hardening with fuel depletion.  Finally, 
+                the total temperature coefficient of reactivity is negative for 
+                both cases, but decreases during reactor operation due to 
+                spectral shift. In summary, even after 20 years of operation 
+                the total temperature coefficient of reactivity is relatively 
+                large and negative during reactor operation (comparing with 
+                conventional PWR which has temperature coefficient about -1.71 
+                pcm/$^\circ$F $\approx$ -3.08 pcm/K 
                 \cite{forget_integral_2018}), despite positive MTC, and affords 
                 excellent reactor stability and control.
-
-                The moderator
-temperature coefficient (MTC) is positive for the startup composition and decreases
-during reactor operation because of spectrum hardening with fuel depletion.
-Finally, the total temperature coefficient of reactivity is negative for both
-cases, but decreases during reactor operation due to spectral shift. In
-summary, even after 20 years of operation the total temperature coefficient of
-reactivity is relatively large and negative during reactor operation (comparing
-with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F
-$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and
-affords excellent reactor stability and control.
 
@@
         \begin{solution}
-                This statement has been significantly extended (see Solution 21).
+                This statement has been significantly extended (see solution 
+                \ref{built-in}).
         \end{solution}

### 2019-01-04 revisions/review-responses.tex

@@
                          than at startup due to plutonium and other strong 
-                         absorbers accumulation in the core during reactor 
+                         absorbers accumulating in the core during reactor 
                          operation.''
@@
         \begin{solution}
-u                Yes, we meant $^{233}$U production. The typo has been fixed. 
+                Yes, we meant $^{233}$U production. The typo has been fixed. 
                 Thanks so much for catching it!

### 2019-01-04 abstract.tex

@@
 
-Today, climate change drives humanity's search for new ways to generate 
-carbon-free, reliable base-load power. Thus,
+In the search for new ways to generate carbon-free, reliable base-load power, 
 interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
@@
 introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
-SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
+SERPENT2 to simulate \gls{MSR} online reprocessing by modeling the changing 
 isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities

### 2019-01-04 introduction.tex

@@
 The works described in \cite{park_whole_2015} and \cite{jeong_equilibrium_2016} 
-are most similar to the work presented in this paper. However, few major differences 
-worse to be mentioned: (1) Park \emph{et al.} employed MCNP6 for depletion 
-simulations while SERPENT2 was used in this work (SERPENT2 seems to be much faster in 
-massively parallel simulations involving more than 1000 cores); (2) full-core reactor 
-model herein is more detailed and has no major approximation comparing with Park 
-\emph{et al.} (detailed full-core models comparison might be found elsewhere
-\cite{rykhlevskii_full-core_2017}); (3) Park \emph{et al.} and Jeong \emph{et al.} 
-both considered volatile gases, noble metals removal and $^{233}$Pa separation while 
-in the current work we are implemented detailed reprocessing scheme described in 
-conceptual \gls{MSBR} design \cite{robertson_conceptual_1971}; (4) $^{232}$Th neutron 
+are most similar to the work presented in this paper. However, a few major 
+differences follow: (1) Park \emph{et al.} employed MCNP6 for depletion 
+simulations while this work used SERPENT2; (2) the full-core reactor 
+geometry herein is more detailed \cite{rykhlevskii_full-core_2017}; (3) Park \emph{et al.} and Jeong \emph{et al.} 
+both only considered volatile gas removal, noble metal removal, and $^{233}$Pa separation while 
+the current work implemented the more detailed reprocessing scheme specified in 
+the conceptual \gls{MSBR} design \cite{robertson_conceptual_1971}; (4) the $^{232}$Th neutron 
 capture reaction rate has been investigated to prove advantages of two-region core 
-design; (5) the effect of removing fission product removal from fuel salt has been 
-studied.
+design; (5) the current work explicitly examines the independent impacts of removing specific fission product groups.
 

### 2019-01-04 results.tex

@@
 neutron energy spectrum at equilibrium is harder than at startup due to 
-plutonium and other strong absorbers accumulation in the core during reactor 
+plutonium and other strong absorbers accumulating in the core during reactor 
 operation.  
@@
   state.}
-\begin{tabularx}{\textwidth}{ m | s | s | x } \hline
-   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \qquad (initial)\cite{robertson_conceptual_1971} \\  \hline
+\begin{tabularx}{\textwidth}{ X | r | r | r } \hline
+Reactivity coefficient               & Initial         & Equilibrium     & Reference                                 \\ \hline
+                                        & [pcm/k]         &  [pcm/k]        & (initial)\cite{robertson_conceptual_1971} \\  \hline
 Doppler in fuel salt                    & $-4.73\pm0.038$ & $-4.69\pm0.038$ & $-4.37$  \\

### 2019-01-04 revisions/review-responses.tex

--- 2019-01-04 revisions/review-responses.tex
@@
         \begin{solution}
-        		Thanks for catching this. The following passage has been added:
-
         		``Protactinium presents a challenge, since it has a large absorption cross 
 				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
-				 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
-				and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
-				Accordingly, $^{233}$Pa is continuously 
-				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
-				to decay to $^{233}$U without negative impact 
-                                on neutronics.''
+				 would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel, 
+				 would produce a smaller amount of $^{233}$Pa which decays into the fissile $^{233}$U.
+				Accordingly, $^{233}$Pa is continuously removed from the fuel salt into 
+				a protactinium decay tank to allow $^{233}$Pa to decay to $^{233}$U 
+				without the corresponding negative neutronic impact.''
         \end{solution}
@@
                          efficiencies for each reprocessing group and removal will optionally be spread more
-                         evenly accross the cycle time.''
+                         evenly across the cycle time.''
         \end{solution}
@@
                 equilibrium fuel salt composition. Using SERPENT2 and SaltProc, 
-                tese factors and their statistical uncertainties have been 
+                these factors and their statistical uncertainties have been 
                 calculated for both initial and equilibrium fuel salt 
@@
         \begin{solution}
-                <++>
+                Zoomed portion for 150 EFPD interval has been added. 
         \end{solution}
@@
 				Table~\ref{tab:reprocessing_list}) at the end of the specific 
-                cycle time.  This approach works well for fast-removing 
-                elements (gases, noble metals, protactinium) which should be 
-                removed each depletion step. Unfortunately, for the elements 
-                with longer cycle times (i.e. rare earths should be removed 
-                every 50 days) this simplified approach leads to oscillatory 
-                behavior of all major parameters. In future releases of 
-                SaltProc, this drawback will be eliminated by removing elements 
-                with longer cycle times using different method: only mass 
-                fraction (calculated separately for each reprocessing group) 
-                will be removed each depletion step (e.g. 3 days).
+				cycle time. This simplification neglects the reality that 
+				the salt spends appreciable time out of the core, in the 
+				primary loop pipes and the heat exchanger.
 
+				This approach works well for fast-removing elements (gases, 
+				noble metals, protactinium) which should be removed each 
+				depletion step. Unfortunately, for the elements with longer 
+				cycle times (i.e. rare earths should be removed every 50 days) 
+				this simplified approach leads to oscillatory behavior of all
+				major parameters. In future releases of SaltProc, this drawback 
+				will be eliminated by removing elements with longer cycle times 
+				using different method: only mass fraction (calculated separately 
+				for each reprocessing group) will be removed each depletion step 
+				or batch (e.g. 3 days in the current work).
         \end{solution}

### 2019-01-04 conclusion.tex

@@
 This work introduces the open source \gls{MSR} simulation package SaltProc. 
-SaltProc expands the capability of SERPENT 2, the continuous-energy Monte Carlo 
+SaltProc expands the capability of SERPENT2, the continuous-energy Monte Carlo 
 code to include online reprocessing in liquid-fueled \gls{MSR} operation 
@@
 To achieve these goals, a full-core high-fidelity benchmark model of the \gls{MSBR} 
-was implemented in SERPENT 2. The full-core model was used instead of the 
+was implemented in SERPENT2. The full-core model was used instead of the 
 the simplified single-cell model \cite{betzler_molten_2017, 
@@
 including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
-absorbers (e.g. $^{234}$U), continue accumulating in the core. %The current work results 
-%show that a true equilibrium composition cannot exist but balance
-%between strong absorber accumulation and new fissile material 
-%production can be achieved to keep the reactor critical.
+absorbers (e.g. $^{234}$U), continue accumulating in the core.
 
@@
 We compared the safety parameters for the initial fuel loading and 
-equilibrium compositions using the SERPENT 2 Monte Carlo code. 
+equilibrium compositions using the SERPENT2 Monte Carlo code. 
 The total temperature coefficient 
@@
 Only the batch-wise online reprocessing approach has been treated in this 
-work. However, the SERPENT 2 Monte Carlo code was extended for 
+work. However, the SERPENT2 Monte Carlo code was extended for 
 continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
@@
 fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
-core lifetime and breeding efficiency. Finally, using the built-in SERPENT 2 
+core lifetime and breeding efficiency. Finally, using the built-in SERPENT2 
 Monte Carlo code online reprocessing \& refueling material burnup routine would 

### 2019-01-04 results.tex
gets rid of centering causing issues with noalign
explicit tabularnewlines

--- 2019-01-04 results.tex
@@
 Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
-equilibrium fuel salt composition. Using SERPENT2 and SaltProc, tese factors and their statistical uncertainties
+equilibrium fuel salt composition. Using SERPENT2 and SaltProc, these factors and their statistical uncertainties
  have been calculated for both initial and equilibrium fuel salt composition (see 

### 2019-01-04 revisions/review-responses.tex

@@
         \begin{solution}
-                Zoomed portion for 150 EFPD interval has been added. 
+                Zoomed portion for 150 EFPD interval has been added along with 
+        clarifying details.
         \end{solution}

### 2019-01-04 results.tex

--- 2019-01-04 results.tex
@@
 \begin{table}[ht!]
-  \centering
   \caption{Power generation fraction in each zone for initial and equilibrium 
@@
 \begin{table}[ht!]
-  \centering
   \caption{Temperature coefficients of reactivity for initial and equilibrium 
@@
 \begin{tabularx}{\textwidth}{ X | r | r | r } \hline
-Reactivity coefficient               & Initial         & Equilibrium     & Reference                                 \\ \hline
-                                        & [pcm/k]         &  [pcm/k]        & (initial)\cite{robertson_conceptual_1971} \\  \hline
-Doppler in fuel salt                    & $-4.73\pm0.038$ & $-4.69\pm0.038$ & $-4.37$  \\
-Fuel salt density                       & $+1.21\pm0.038$ & $+1.66\pm0.038$ & $+1.09$  \\
-Total fuel salt                         & $-3.42\pm0.038$ & $-2.91\pm0.038$ & $-3.22$  \\ \hline
-Graphite spectral shift                 & $+1.56\pm0.038$ & $+1.27\pm0.038$ &          \\
-Graphite density                        & $+0.14\pm0.038$ & $+0.23\pm0.038$ &          \\
-Total moderator (graphite)              & $+1.69\pm0.038$ & $+1.35\pm0.038$ & $+2.35$  \\ \hline
-Total core                              & $-1.64\pm0.038$ & $-1.58\pm0.038$ & $-0.87$  \\ \hline
+Reactivity coefficient               & Initial         & Equilibrium     & Reference                                 \\ 
+                                        & [pcm/k]         &  [pcm/k]        & (initial)\cite{robertson_conceptual_1971} \tabularnewline  \hline
+Doppler in fuel salt                    & $-4.73\pm0.038$ & $-4.69\pm0.038$ & $-4.37$  \tabularnewline
+Fuel salt density                       & $+1.21\pm0.038$ & $+1.66\pm0.038$ & $+1.09$  \tabularnewline
+Total fuel salt                         & $-3.42\pm0.038$ & $-2.91\pm0.038$ & $-3.22$  \tabularnewline \hline
+Graphite spectral shift                 & $+1.56\pm0.038$ & $+1.27\pm0.038$ &          \tabularnewline
+Graphite density                        & $+0.14\pm0.038$ & $+0.23\pm0.038$ &          \tabularnewline
+Total moderator (graphite)              & $+1.69\pm0.038$ & $+1.35\pm0.038$ & $+2.35$  \tabularnewline \hline
+Total core                              & $-1.64\pm0.038$ & $-1.58\pm0.038$ & $-0.87$  \tabularnewline \hline
 \end{tabularx}
@@
 \begin{table}[ht!]
-  \centering
   \caption{Control system rod worth for initial and equilibrium fuel 
@@
 \begin{table}[hb!]
-  \centering
   \caption{Six factors for the full-core \gls{MSBR} model for initial and 

### 2019-01-04 revisions/review-responses.tex
typo

@@
                           $^{242}$Pu (included in Processing group ``Higher 
-                          nuclides'', see Table~\ref{tab:reprocessing_list}) 
+                          nuclides'', see Table~3
                           which decays into $^{235}$Np and $^{239}$Pu, 

### 2019-01-04 revisions/review-responses.tex
comments on abstract and oscillations

@@
 
-        \question The oscillatory behavior shown in Fig. 7 on the time scale of 
+        \question \label{osc} The oscillatory behavior shown in Fig. 7 on the time scale of 
         months/years is hard to explain. Is this because the fission product 
@@
         \begin{solution}
-                <++>
+                This sentence was quite unclear and we have rewritten it to 
+                address your concerns. Effectively these simulations exactly 
+                simulated the batch-wise refuelling detailed in the Robertson 
+                design document, while a more realistic approach would give 
+                smooth behavior. A description of the changes to the text 
+                appears in solution \ref{osc}.
         \end{solution}
@@
         \begin{solution}
-                <++>
+                The abstract has been shortened.
         \end{solution}

### 2019-01-05 abstract.tex
energy -> energy technologies

@@
 In the search for new ways to generate carbon-free, reliable base-load power, 
-interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
+interest in advanced nuclear energy technologies and particularly \glspl{MSR} has resurged, 
 with multiple new companies pursuing commercialization of \gls{MSR} 

### 2019-01-05 methods.tex
explicit tabularnewlines
weird sentence about pa233 fixed

@@
 \begin{table}[h!]
-        %\centering
         \caption{Summary of principal data for \gls{MSBR} 
@@
 section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
- would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel, 
- would produce a smaller amount of $^{233}$Pa which decays into the fissile $^{233}$U.
+would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel. 
 Accordingly, $^{233}$Pa is continuously 
@@
 \begin{table}[ht!]
-        \centering
         \caption{The effective cycle times for protactinium and fission 
@@
 fraction (calculated separately for each reprocessing group) will be removed each
- depletion step or batch (e.g. in the current work it was chosen 3 days).
+ depletion step or batch (e.g. 3 days in the current work).
 
